### 2022-02-17 draft.tex
First commit with CC draft and references included

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\usepackage{changepage}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\usepackage{apacite}

\begin{document}

\section{Introduction}
Forecasting has become increasingly important for private and public decision 
making. Because predictions cannot generally be free of uncertainty many 
thinkers prefer probabilistic forecasts over deterministic and probabilistic 
forecasts have become the norm in many fields including meteorology, economics,
finance and epidimiology.

Ensemble forecasting is the combination of several forecast models into one 
model which often yields better predicting power than the individual models
\cite{cramer2021evaluation} and has a solid station in dynamical weather 
prediction \cite{lewis2005roots}. In weather forecasting, individual members of 
an ensemble are generated from perturbations of initial conditions, see Baran 
section 2. Data \cite{baran2018combining} \cite{leutbecher2008ensemble}.
\cite{yamana2016superensemble}

A probabilistic forecasts may be represented in a variety of ways, a common way
being the form of a continuous or discrete probability distribution. Indeed much 
of the literature pertaining to scoring forecast models, combining models 
into ensemble forecasts and calibration pertain to methods for continuous
and/or discrete probability functions see for example 
\cite{gneiting2007probabilistic},
\cite{gneiting2013combining} \cite{baran2018combining}. Though such methods have
also been treated for samples, such as MCMC draws of a posterior predictive
distribution see for example \cite{krueger2016probabilistic}
and for quantile or interval type and expectile type forecasts 
\cite{taylor2021evaluating} \cite{bracher2021evaluating}.

Since 2013 the United States Center for Disease Control (CDC) has hosted an
annual competition for predicting the timing, peak and intensity of the year's 
flu season. In this competition, the CDC provides academic researchers with data
, relevant forecasting targets and other guidlines and the various teams produce
forecasts later evaluated against actual flu acticity. Details on the 
competition may be found on the CDC FluSight \cite{cdcflusight}.

The ReichLab of the University of Massachusettes Amherst and a 
CDC-funded Influenza Forecasting Centers of Excellence has been heavily 
involved in the CDC influenza competition and disease outbreak research.
In their work they have provided insight into the usefulness of collaboration 
and ensemble modeling in disease outbreaks, see for example 
\cite{reich2019collaborative}, \cite{reich2019accuracy} and 
\cite{mcandrew2019adaptively}.

In March 2020, at the onset of the COVID-19 pandemic, the Reich Lab in
association with others founded the COVID-19 Forecast Hub. Every week relevant
pandemic data is provided to several teams who build probabilistic models for
forecasting cases, hospitalizations and deaths due to COVID-19 for various 
regions of different levels with predictions of days, weeks and months ahead.
These forecasts are combined into a single ensemble forecast. The model data,
forecasts and the ensemble are passed along to the CDC which uses in official
communication \cite{Cramer2021-hub-dataset}.

Though similar to the forecasting in the influenza competition, the format of 
the COVID-19 Forecast Hub has some key distinctions. For one, the Forecast Hub
has as a key component the construction of a multi-model ensemble forecast 
whereas that has not as yet been the case in the influenza competition. Another 
key difference is the format which the individual forecasts are submitted. In 
the influenza forecast, a set of discretized bins on a numeric scale were set
for each target and participating researchers were asked to submit their 
probabilistic predictions as a list of probabilities in for each bin essentially
making each prediction a bounded pmf \cite{mcgowan2019collaborative}.
Due to the initial lack of understanding of COVID-19 and the time pressure of
creating forecasts, the forecasts were requested as the predictive mean and 
predictive intervals for various nominal levels depending on the target to be
predicted \cite{bracher2021evaluating}.

Though the representation of a set of intervals can bring added flexibility, 
there is also some loss in what can be said about a forecast. This will be 
discussed further herein. In this paper we propose as an alternative to 
requesting probabilistic forecasts in binned, quantiled, sampled or common 
distribution format requesting forecasts in a format conducive to discrete 
mixture distribution. Discussed will be advantages and disadvantages of
a forecast of this form.

In the next section, popular probabilistic forecast representation types
will be reviewed included standard pieces of definitions. These include 
continuous/discrete probability functions, discretized bin distributions,
samples from a distribution and quantile or interval distributions. In the 
following section common methods for scoring forecasts, constructing multi-model
ensembles will be reviewed and compared for the different representation types. 
In the same section, other practical considerations for a forecast hub will be
discussed.

\section{Probability Distributions}

A probabilistic forecast model may be represented in a number of ways. A 
forecast should always come with a point estimate for a prediction and a 
characterization of the uncertainty associated with the point prediction.
Common representations which we review include parametric distributions,
discretized bin probabilities, samples and quantile or interval values.
In what follows, let $D$ be a distribution.

\subsection{Parametric distributions}
In a parametric distribution representation we let $D := D(\theta)$ 
where $\theta$ is vector of known or unkown parameters contained in a parameter 
space. We consider a parametric distribution any probability distribution with a 
fixed parameter set and a known probability density function (pdf) or 
probability mass function (pmf) for continuous and discrete distributions
repsectively. The pdf or pmf is represented as $p(y|\theta)$ where $\theta$ is 
a parameter, usually unknown but estimated using given data.

The value of $p(\cdot|\theta)$ evaluated at $y$ is defined as 
$p(y|\theta) = P(D = y)$ or the probability that the random variable $D$ takes
on $y$. In the continuous case $P(D = y) = 0$ for all $y$, but the probability 
that $D$ falls within an interval $(a,b)$ is calculated as

$$P(a < y < b) = \int_a^b p(y|\theta) dy$$

(??Note: I'm trying to decide how detailed I should be here. Have I already said
more than is necessary? Should I define the CDF and inverse CDF functions?)

In forecast modeling with a parametric distribution, data is used to obtain a 
likelihood function $L(\theta|y)$ and the unknown parameter $\theta$ is 
estimated as $\hat{\theta}$. (more/less detail ??) The mean or the median is
then used as a point estimate of the forecast and estimated probabilities for 
all other possible values may be calculated. For the most commonly used families
of distributions (Normal, Gamma, Poisson etc.) calculating point estimates and 
probabilities is easy due to the availability of software.

A drawback of representing a forecast in a parametric distribution is the lack 
of flexibility in the model selection. Easy computation and evaluation of these 
models is limited to what is available in software, so certain distributional
shapes may unattainable. The distribution may assign probability to values
outside the range of the forecast. There are remedies for this such as 
truncation, but these increase the complexity in evaluation and scoring.
Requiring a parametric forecast also bars the use of some statistical methods
which might be used including certain Bayesian methods.

\subsection{Forecast as samples}
A random sample $(X_1,...,X_n)$ where $X_i \sim D$ may be used to 
estimate values such as the mean or quantiles of the distribution $D$.

According to the Strong Law of Large numbers, the sample mean will converge to
the expected value of distribution as $n$ approaches $\infty$ as long as the 
expected value of that distribution exists. Likewise by the same law the 
empirical distribution function will converge to the true cumulative 
distribution function as $n$ approches $\infty$. Thus, if a sufficiently large 
sample is generated from a distribution, the sample will closely approximate the 
true distribution.

For common distribution families it is easy to generate large samples using 
existing functions in R and other programming platforms. For some distributions 
for which the mathematical formula is unkown or is not in closed form, more 
sophisticated methods may be required to generate samples. Bayesian analyses may 
require a Gibbs or Metropolis-Hastings algorithm, among others, to generate a 
sample. Such samples are useful in that the true distribution may be closely 
approximated without knowing the true mathematical form.

In the last few decades, increased computing power and improvements in MCMC
sampling have greatly contributed to growth in the use of
predictive distributions \cite{gneiting2007strictly}.

\subsection{Discretized probability bins}
A discretized bin probability distribution may be constructed over a set 
$A = [a, b]$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
where $B_i = [b_{i-1}, b_i)$ and $\cup_{i=1}^{K} B_i = A$. Based on the problem
to be forecasted, a forecast hub will determine the possible values for $A$ and 
select the number of bins and the sizes for each. It may the case
that a forecast hub will set the width of all bins to be equal so that 
$\Delta = b_i - b_{i-1}$ is the width for all $i$ see for example
\cite{mcgowan2019collaborative}. 
For this paper, we will consider the case where all bins share a common width.
To complete the construction, a probability $p_i$ is assigned to each $b_i$ 
where $\sum_{i=1}^{K}p_i = 1$. These probabilities are determined by the 
forecasters. 
This discrete representation with a given bin and assigned probability is in
essence a probability mass function, so a given forecast may be evaluated and 
scored the same as a discrete parametric distribution.

If the value to be forecasted takes on discrete values, a common discrete 
distribution, such as a binary or Poisson distribution, may sometimes be used to 
assign probabilities to each of the bins. When the values to be forecasted are
continuous, a forecaster may need to employ some method of discretization to a 
forecast distribution. There are a number of possible ways to do this including
those outlined by Chakraborty and Subrata \cite{chakraborty2015generating}.
In a retroactive analysis of forecast predictions from the CDC influenza 
competition, we attempt to evaluate whether some or any teams made their 
predictions by discretizing from a common continuous distribution function.

The CDC has used a discretized distribution representation as the representation
for their annual influenza forecasting competition and other disease outbreaks.
In that context it has become the standard representation 
\cite{brooks2020comparing}.

Most statistical models such as parametric models 
or distributions made from samples may be readily translated into a discretized 
distribution -see \cite{chakraborty2015generating} for a summary of several-
giving forecasters flexibility in how they build their 
models and assign probabilities. 
There is however some sacrifice in what can be 
forecasted as the possible range of the distribution may be limited to what the
forecast hub requires. This limitation is in part what prompted the COVID-19
Forecast Hub to use quantile forecasts rather than binned distributions.
\cite{bracher2021evaluating}.
In a simulation study outlined later, we will
consider a construction from Kemp \cite{kemp2004classes} to discretize known
continuous distributions.

\subsection{Quantile representation}
Uncertainty in a forecast prediction may also be characterized by  including
multiple quantiles along with corresponding values. Often the median value will
be reported as a point forecast with a number of quantiles included which form 
confidence intervals of various levels.
A quantile forecast is constructed as follows.
For $N$ given quantiles $\alpha_1,..., \alpha_N$, $q_1,..., q_N$ are the values
such that

\begin{equation}
  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ..., 
  P(Y \leq q_N) = \alpha_N
\end{equation}

When the quantiles are reported as a median and confidence intervals we have

\begin{equation}
  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ..., P(Y \leq q_k) = .5, 
  ..., 
  P(Y \leq q_{N-1}) = 1 - \alpha_{N-1}, P(Y \leq q_N) = 1 - \alpha_N
\end{equation}

The COVID-19 Forecast Hub requires that participating teams report their
forecasts as quantile values corresponding to 23 or 7 quantiles -depending on 
the target or time being forecasted. The quantile representation was selected
over the discretized bins used in the influenza competition because the range 
of observation outcomes of interest was much larger and an appropriate binning
scheme would have been difficult to define \cite{bracher2021evaluating}.

The quantile or interval format is somewhat unique among forecast 
representations discussed in this paper. What is possible for scoring forecasts
or building ensemble models in other representations is often not possible with
quantile forecasts. Yet it has its advantages.

Quantile representation allows for forecasters to submit fairly detailed
forecasts without restricting the range of possible values -a major reason for 
selecting a quantile representation over discretized bins 
\cite{bracher2021evaluating}.

Since quantiles are easily calculated from any regular distribution type
-e.g. inverse CDF for parametric functions and inverse ECDF from data or 
samples- we consider quantile forecasts to have high flexbility in terms of 
shape and range.

As in the
discretized representation, the resolution of a distribution based on quantiles
will depend on the number of quantiles to be forecasted. There is however a 
significant loss of information in reporting the extreme outcomes in a quantile
model. Since reported intervals can only be so wide, it is possible that tail 
information is lost. The COVID-19 Forecast Hub for example requires forecast 
values up to the $99^{th}$ and down to the $1^{st}$ percentile. For values any
more extreme, exactly assigning probabilities is impossible.

\subsection{Discrete mixture of parametric distributions}
In a parametric setting, forecasters may be permitted to submit a forecast as a
discrete mixture. Such a distribution may be constructed in the same way as the
ensemble described under Parametric distributions where for $T$ models with pdf
$p_t(y|\theta)$ $p^{M} = \sum_{t=1}^T z_tp_t(y|\theta)$ where 
$z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$

Like the standard parametric model, a discrete mixture is easily evaluated with
exisiting software (like distr R package) (cite??) and scoring may be done by 
most or all of the same methods. The resolution of a discrete mixture is high 
and the support need not be limited by submission requirements.

A mixture distribution may be much more flexible than a simple parametric in 
terms of distributional shape. But as it is essentially parametric, forecasters
mays still be limited in how they construct their models. But it may be possible
to fit a mixture distribution to probability models with the other 
representations discussed. Further discussion on methods for fitting mixture 
distributions to different types of model representations is included in this 
paper.

An ensemble model may be built by constructing a mixture of mixtures. Where for 
$J$ forecasts $p^{E}(y|\theta) = \sum_{j=1}^{J} w_j p^{M}_j(y|\theta)$ where 
$w_j > 0$ and $\sum_{j=1}^J w_j = 1$. (is it necessary to describe this
construction).

Depending on the number of components a forecaster includes in a mixture 
forecast, the amount of storage per forecast might be as little as for a 
parametric forecast and as much as a forecast hub will allow.

\section{Forecast specifics on scoring, ensembling, etc.}

\subsection{Scoring}

Scoring rules are used to assign a numeric score to a probability forecast. The
score is a measure on the accuracy of the forecast and where multiple forecasts
exist may provide a rank for each relative to the others. If a scoring rule is 
proper, then the highest possible reward is obtained by reporting the true 
distribution. The rule is strictly proper if that value is unique.(define??) 
Under proper
scoring rules, a forecaster has no incentive to be dishonest in their 
submission \cite{gneiting2007strictly}. This makes proper scoring rules ideal
for grading forecasts.

Commonly used proper scoring rules include the Logarithmic score (LogS), 
continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
\cite{alves2013ncep} and the interval/Brier 
score \cite{gneiting2007strictly} among 
others. See also \cite{gneiting2014probabilistic}
section 3 for on proper scoring functions. Unless otherwise noted, the following
definitions/reviews can be found in the review by Krueger.

For a forecast with pdf/pmf $p_m(y)$, the Logarithmic score evaluates the 
probability of the observed value $y^*$. It is defined as

\begin{equation}
  LS(p_m,y*) = -log\;p_m(y^*)
\end{equation}

This scoring method is appropriate for scoring density forecasts as well as 
descretized bins. The smaller the score, the better the forecast.
Because the probability evaluation is only at the observed 
point \cite{reich2019accuracy} used a modified Logarithmic score 
known as the multibin logarithmic score (MBlogS) for scoring
forecasts. This allowed for a range of values to be considered "correct" or 
accurate. MGlogS is defined as

\begin{equation}
  MBlogS(F_m, y^*) = log(\sum_{i=-d}^{d} p_m(y^* + i))
\end{equation}

\begin{equation}
  \int_{y*-\epsilon}^{y^*+\epsilon} -log\;p_m(y^*) (??)
\end{equation}

The MBlogS has the advantage of offering a more accesible interpretation but the
drawback of being improper \cite{bracher2021evaluating}.

Another commonly used score, the interval score, may also be used on density 
forecasts including discretized bin forecasts. With the right smoothing of
a distribution of drawn samples, 
such as Gaussian approximation or Kernel density estimation, these methods may 
be used for scoring, see for example \cite{krueger2016probabilistic}.
These scoring methods will not work for raw samples however.

The Continuous ranked probability score (CRPS) is a function of a CDF $F$, 
including an Empirical CDF, $\hat{F}(x) = n^{-1} \sum_{i=1}^n 1\{x \geq X_i\}$
and so 
can be used a bit more extensively. For the CDF $F_m$, the CRPS is defined as

\begin{equation}
  CRPS(F_m, y^*) = \int_{-\infty}^{\infty} (F_m(y) - 1_{\{y*\leq y\}})^2 dy
\end{equation}

For a forecast of drawn samples, the ECDF may be computed and the CRPS used to 
score the prediction. The CRPS has some nice properties, but can sometimes be
difficult to compute. For example, when the forecast is a mixture of a 
Truncated Normal distribution (TN) and a Truncated Lognormal (TL) the CRPS is 
not available in closed form \cite{baran2018combining}.

The Interval score (IS), a consistent and elicitable proper score 
(see \cite{gneiting2014probabilistic} for definitions) is defined as

\begin{equation}
  IS_{\alpha}(l,r; y^*) = (r-l) + \frac{2}{\alpha}(l-y^*)1\{y^*<l\} 
  + \frac{2}{\alpha}(y-r)1\{y>r\}
\end{equation}

where $l$ and $r$ are the $\alpha/2$ and $(1-\alpha/2)$ quantiles that bound
the central $(1-\alpha)$ prediction interval. This is a sum -weighted by 
$\alpha$- of the width of the
interval and the distance between $y^*$ and the interval (if $y^*$ is not 
captured in the interval). The IS requires only a single central 
$(1-\alpha) \times 100$ prediction interval.

When an interval forecast is made up of more than one interval with different
$\alpha$ levels, a weighted interval score (WIS) may be evaluated. Bracher et.
al use the WIS to evaluate COVID-19 inverval forecasts 
\cite{bracher2021evaluating}. There are multiple versions of the WIS -some of 
which are described by Bracher et. al- but that used in the COVID-19 Forecast
Hub is defined as follows.

\begin{equation}
  WIS_{0,K}(F_m,y^*) = \frac{1}{K + 1/2} \times (w_0, \times |y^*-med|+
  \sum_{k=1}^K \{ w_k \times IS_{\alpha_k}(F_m,y) \} )
\end{equation}

where $F_m$ is the interval forecast, $K$ is the number of prediction intervals
each with level $\alpha_k$ and $med$ is the predictive median. $\alpha_0 = 1$ is 
is the $\alpha$ value corresponding to the predictive median which may also be
considered a level 0 prediction interval. $w_k = \alpha_k/2$ is the weight on
intervals which was used. With that choice of weights, it may be shown that the
WIS approximates CRPS see S1 Text  \cite{bracher2021evaluating} or

\begin{equation}
  WIS_{0,K}(F_m,y^*) \approx CRPS(F_m,y^*)
\end{equation}

Bogner, Liechti and Zappa compared scoring forecasts of quantiles with the 
Quantile Score similar to the interval score and scoring distribution functions
fit to those quantiles using CRPS \cite{bogner2017combining}. The CRPS 
corresponds to the integral of the QS over all possible thresholds rather than
just specific quantiles, it more effectively reveals deficiencies in parts of 
the distribution and especially in the tails past the end points of quantiles
used in QS or IS.

\subsection{Flexibility, resolution and information (such as tail info)}
The amount of info

\subsection{Ensemble}
A multi-model ensemble is a statistical model made by combining information from
2 or more individual statistical models. Private and public decisions are 
regularly made after combining information from multiple sources. For any given
situation, information from one source may shed light on a subject which other
sources fail to capture. Likewise one statistical model may provide perspective
that another model does not, so that when they are combined in an ensemble the 
resulting model is superior.

As probabilistic forecasting becomes more commonplace, so too does ensemble 
modeling. Multi-model ensembles have been used extensively in weather and
climate modeling see \cite{baran2018combining}, 
and they have been used increasingly in modeling infectious disease outbreaks
see for example \cite{yamana2016superensemble}. 
Multi-model ensembles allow for an incorporation of multiple signals -
often from differing data sources- and for individual model biases being canceled
out or reduced by biases in others \cite{reich2019accuracy}. (See specific citations in this paper 12-15??)
In several disease outbreak studies, multi-model ensemble forecasts have been 
shown to outperform individual model forecasts \cite{cramer2021evaluation} (see
10, 14-25 in this paper).

Construction of an ensemble may be done by combining individual forecast 
distributions using weighted averages. This has been called stacking 
\cite{wolpert1992stacked} or weighted density ensembles 
\cite{ray2018prediction}.

Considered the state-of-the-art techniques for combining component distributions
into a multi-model ensemble are nonhomogeneous regression (NR), also known as
ensemble model output statistics (EMOS), and ensemble Bayesian model averaging
(BMA), both of which will be defined as in \cite{gneiting2014probabilistic}.

In the context of an ensemble made from component models submitted from various
sources, contructed with different methods and with potentially different data,
BMA is the better option. In BMA, the final model does not have to be specified
beforehand and the resulting forecast will be a discrete mixture distribution
of all component forecasts. The general form for the ensemble distribution $p^E$
is

\begin{equation}
  p^E(y) = \sum_{j=1}^J w_jp_j(y)
\end{equation}
where $p_j$ is the $j^{th}$ component forecast distribution and 
$0 \leq w_j \leq 1$ is a weight assigned to each component where $\sum w_j = 1$.
Methods for estimating weights include Maximum Likelihood estimation
\cite{raftery2005using}, MCMC 
sampling see \cite{vrugt2008ensemble} (also in this paper it talks about how 
EM can get difficult as parameters i.e. number of distributions increase, and 
shows MCMC may be better with that high dimensionality and gives full posterior
of weights)
and minimizing CRPS as in 
\cite{baran2018combining}.

Reich et. al used BMA to combine multiple forecasts from the flu 
competition. There built and compared ensemble models with different weighting
schemes including equally weighted components $w_j = 1/J$ and estimating weights
according to the model specification. To estimate weights they used the 
Expectation Maximization (EM) algorithm \cite{reich2019accuracy}. See the
supplementary material for details. Other options for estimating the weights 
include Monte Carlo Markov Chain sampling ??\cite{vrugt2008ensemble} or a 
minimization of the ensemble CRPS score \cite{baran2018combining}.

The BMA ensemble construction works for discrete and continuous parametric 
distributions as well as discretized bin distributions, but is not useful when 
the forecasts are of the interval type.

Quantile averaging or Vincentization is defined as

\begin{equation}
  F_v^{-1}(\alpha) = \sum_{m=i}^M w_m F_m^{-1} (\alpha)
\end{equation}

where $F_m^{-1} (\alpha) = \inf \{y:F_m(y) \geq \alpha\}$ for 
$0 < \alpha \leq 1$. Some notable characteristics are that it is more likely
to be unimodal than linear averaging of densities like BMA 
\cite{busetti2017quantile} (this paper is a big comparison of QMA and 
linear or log averaging. Under some circumstances, such as when member
distributions are exponential, Weibull or logisitic the aggregated distribution
is the same \cite{ratcliff1979group}. It apparently produces smoother
distributions than BMA, at least in \cite{schepen2015model}.

These dudes seem to think averaging quantiles is better than simple averaging 
probabilities. More sharp (less variation), perform better in scoring etc.
\cite{lichtendahl2013better}.

\subsection{Storage}
For a forecast hub collecting many predictions, computer storage is something
that needs to be addressed. For a project involving many researchers, the 
number of forecast predictions can add up. For example, the repository for the
COVID-19 Forecast Hub predictions contained 85.4 million predictions as of 
February 5, 2022! (cite zoltr??)
When determining the goals of a forecast project, there should be consideration 
of the storage required for different representations.

The data requirement for a parametric distribution small and will usually be the 
least when compared with other representations. As long as the forecast is 
allowed to have an unbounded range, only 3 or 4 pieces of information will be
required including specification of the distribution family and model 
parameters. See the table below for an example of a normal distribution with 
mean 0 and variance 1.

\begin{table}[h!]
\centering
 \begin{tabular}{||c c c c||} 
 \hline
 Family & param1 & param2 & param3 \\ [0.5ex] 
 \hline\hline
 normal & 0 & 1 & NA \\ 
 \hline
 \end{tabular}
\end{table}

With those three pieces of information, the whole distribution is completely
defined and software is readily available for calculating moments, percentiles,
probabilities and generating random samples. The third box under param3 is there
in case a particular distribution family has three parameters -a location-scale
T distribution for example.

If the distribution is made up of samples from a distribution, like posterior
predictive distribution, much more space will be required to contain all the 
information. A sample using MCMC sampling may have thousands or even tens of 
thousands of draws. It's easy to see why this could be a problem if millions of
predictive distributions are collected and saved.

The exact amount of information required for a discretized bin forecast will 
vary depending on permitted range of the forecast and the desired resolution. 
In the CDC flu contest, a forecast could have 131 bins between 0\% and 13\% 
-bins having increments of 0.1- with 
corresponding probabilities in each. That makes 262 pieces of information per
prediction. A much larger number than what is required for a fully defined
parametric distribution. The following table shows what a discretized standard
normal distribution looks like in 131 discretized bins. Note that for the sum of 
the probabilities to equal one, it was essential to normalize the probabilites
within the range $[-6.5,6.5]$ since the full range of a normal distribution is
$(-\infty, \infty)$.

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|} 
 \hline
    bin & prob \\ \hline
    -6.5 & 3.75e-11 \\
    -6.4 & 7.11e-11 \\
    -6.3 & 1.33e-10 \\
    ...  & ... \\
    6.3 & 7.11e-11 \\
    6.4 & 3.75e-11 \\
    6.5 & 1.96e-11 \\
 \hline
 \end{tabular}
\end{table}

Like in the last two representations, data storage for interval forecasts will
depend on the desired clarity of resolution. For the COVID-19 forecasts 
submitted to the forecast hub, twenty-three quantile values are requested for 
the quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This included a 
median along with eleven confidence intervals \cite{bracher2021evaluating}. This
requires forecasters to submit forty-six values in each short-term forecast 
(some of the longer term forecasts only include seven quantiles). In terms of 
storage, this is an improvement over requirements for the flu contest.

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|} 
 \hline
    quantile & value \\ \hline
    0.01 & -2.326 \\
    0.025 & -1.96 \\
    0.05 & -1.645 \\
    0.01 & -1.282 \\
    ...  & ... \\
    0.9 & 1.282 \\
    0.95 & 1.645 \\
    0.975 & 1.96 \\
    0.99 & 2.326 \\
 \hline
 \end{tabular}
\end{table}

\begin{flushleft}
    \begin{adjustwidth}{-3cm}{-1cm}
    \begin{tabular}{ | p{2.4cm} | p{2cm} | p{4cm} | p{3cm} | l |}
    \hline
    Representation & Scoring & Flexibility/Information & Ensemble &
    Storage Requirement
    \\ \hline

    Parametric & All methods & Limited to common distribution families 
    &  & Low 3-6 values \\ \hline

    Discretized bins & All methods, more computation required for some (CRPS) &
    Any shape allowed, but limited to bin description and range & &
    High
    \\ \hline

    Samples & Limited to CRPS and IS unless smoothing is performed & High & & 
    Very high, thousands of values
    \\ \hline

    Quantiles & IS, WIS & High & & Medium 
    \\ \hline

    Discrete Mixture & All methods, but may be limited by computation & 
    High with proper approximation &
    & Low-Medium
    \\ \hline

	 \end{tabular}
	 \end{adjustwidth}
\end{flushleft}

% bin & -6.5 & -6.4 & -6.3 $ ... & 6.3 & 6.4 & 6.5 \\  
%  prob & 3.75e-11 & 1 7.11e-11 & 1.33e-10 & ... & 7.11e-11 & 3.75e-11 & 1.96e-11\\

\newpage

\section{Retrospective Analysis}

\subsection{CDC Influenza like Illness}
The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
850,000 probabilistic ILI predictions for all combinations of of eleven regions 
in the United States and seven targets from twenty-seven different models. These
include predictions during Influenza season between October 2010 and December
2018. All predictions are in the form of discretized probability bins.

We wanted to determine whether or not some or any of these binned forecasts may
have come from known continuous distribution families such as Uniform, Normal, 
Lognormal or Gamma families. The process we followed for making such a claim was
to "fit" a distribution to the probabilities provided in the forecast by
minimizing

\begin{equation}
  \sum_{i=1}^K (p_i - [F(b_i; \theta) - F(b_{i-1}; \theta)])^2
\end{equation}

Here $F(\cdot; \hat{\theta})$ is a CDF, $p_i$ is the reported probability for 
the $i^{th}$ bin $B_i := [b_{i-1}, b_i)$ and $K$ is the number of bins.
The fitted parameter vector $\hat{\theta}$ is the solution to

\begin{equation}
\arg\min_{\theta}\sum_{i=1}^K (p_i - 
[F(b_i; \theta) - F(b_{i-1}; \theta)])^2
\end{equation}

If well known continuous distribution was fit to the submitted binned prediction
and the mean sum of squared differences fell below a specified cutoff value, we
considered that the binned predictions were plausibly discretized from the 
continuous distribution.

To determine what values to use as cutoffs we conducted a study where 
binned distributions were discretized from known continuous distributions, 
parameters were fit to the binned distrubtions and the mean sum of squared 
differences was calculated.

For each of Uniform, Truncated Normal (TN), Truncated Lognormal (TL) and 
Truncated Gamma (TG) distributions the following was
done 1,000 times. A set of 131 bins with interval lengths of 
0.1 between 0 and 13.1 was constructed. 
A value $\mu$ was selected from a $Uniform(a,b)$ distribution and $\sigma$ from 
a $Uniform(.05,1.6)$ distribution. $\mu$ and $\sigma$ were taken as respectively 
the center and scale parameters of a TN distribution. 
For Uniform, TL and TG family
distributions, model parameters were solved for so that $\mu$ and $\sigma$ 
were roughly the mean and standard deviation. The minimization was done using 
the `optim` function in the R `stats` package.
Had we accounted for the changes
in moment values from the truncation, the means and standard deviations could 
have been exactly $\mu$ and $\sigma$. But we considered the differences small 
enough that it didn't matter for our purpose.

With a known distribution, probabilities $p_i =F(b_i; \theta) - F(b_{i-1})$ were
calculated for each bin. A Uniform or truncated distribution from the same
family was fit to the bins by minimizing (equation number) with the resulting
distribution function $F(\cdot; \hat{theta})$. From the fitted distribution
$\hat{p_i} = F(b_i; \hat{\theta}) - F(b_{i-1}; \hat{\theta})$ was computed for 
each of the 131 bins. Finally the mean sum of squared probability differences
$\frac{1}{K}\sum_{i=1}^K (\hat{p_i} - p_i)^2$ was calculated. Table (table number)
below shows MSD value for which 95\% of all 1,000 MSDs fell below. Other than in
the case of the Uniform distribution family, those values were selected as the 
cutoff values for declaring whether or not a binned distribution was discretized
from a common continuous distribution.

\begin{table}[h!]
  \centering
  \begin{tabular}{l*{6}{c}r}
  Distribution          & Mean Square Difference 95\%  \\
  \hline
  Uniform               & 8.809460e-05   \\
  Truncated Normal      & 1.126683e-07  \\
  Truncated Lognormal   & 3.877829e-06  \\
  Truncated Gamma       & 1.500152e-06  \\
  \end{tabular}
\end{table}

Of the 869,638 predictions from the CDC Retrospective Forecast project, we fit
each of Uniform, TN, TL and TG distributions to 11,715 of the individual 
predictions. The MSD between the prediction probabilities and the fit
discretized probabilities was calcuated. For each prediction, the fitted 
distribution with the lowest MSD was considered the best fit and if the MSD fell
below the corresponding cutoff value listed in (table number) we consider that 
the prediction approximately follows the fit distribution. The results for the
11,715 fit distributions are seen below.

\begin{table}[h!]
  \centering
  \begin{tabular}{l*{6}{c}r}
  Distribution Family   & Total    & Total Below MSD Cutoff \\
  \hline
  Uniform               & 896      & 669    \\
  Truncated Normal      & 3,804    & 198    \\
  Truncated Lognormal   & 4,501    & 1,340  \\
  Truncated Gamma       & 2,514    & 295    \\
  \end{tabular}
\end{table}

\subsection{COVID-19 Forecast Hub}

As of January 24, 2022 there were nearly 85,000,000 prediction distributions 
from 114 different models submitted to the COVID-19 Forecast Hub (cite??). These 
distributions covered all combinations of 3,202 municipalities (mostly counties) 
in the United States with 441 targets. The first of these forecasts was 
submitted in March of 2020 shortly after the initial outbreak of the virus in 
the US and forecasts had been received weekly since. The forecast representation
for these predictions is the quantile representation where a point estimated is
submitted along with a number of confidence intervals -three or eleven for most
targets. So the predictions typically include seven or twenty-three quantiles.

To assess whether or not a quantile based forecast was formulated from a well
known continuous distribution, we minimized the MSE between the cumulative
density function and the given quantiles. The estimated parameters are the 
solution to $argmin_{\theta} \sum_{i=1}^m (q_i - F(y; \theta))$ where $q_i$ is
the $i^{th}$ given quantile value and $F(y; \theta)$ is the CDF with parameter
$\theta$. This least squares estimating is a more common way to fit a model but
other methods have been presented including Bayesian Quantile Matching
\cite{nirwan2020bayesian}, step interpolation with exponential tails 
\cite{quinonero2005evaluating}
and the Method of Simulated Quantiles 
\cite{dominicy2013method}.

For each prediction used, we fit the quantiles to a Uniform, Normal, Lognormal,
Gamma and Location-scale T CDF. We included the T distribution in case of any
symmetric forecasts with tails heavier than in a Normal distribution.

If the MSE between a given forecast and a fit CDF fell below a certain cutoff,
we considered the quantiles as approximately coming from the fit CDF. To
determine the cutoff values, for each of the five distribution families the same
procedure was followed 1,000 times.

A decision was made on creating a quantile distribution with 7 quantiles or 23
quantiles with probabilities 1/3 and 2/3 respectively. This was done because 
in the COVID-19 Forecast Hub certain targets require 7 quantiles and others 
require 23. After that decision was made, a random value $\mu$ was drawn from
a $Uniform(2,000,\; 25,000)$ distribution and another value $\sigma$ was drawn
from a $Uniform(3, 200)$ distribution. These values were taken as the mean and
standard deviation and for each of the distribution families considered, the
proper transformations computed to find model parameters corresponding to the 
distribution. Quantile values were calculated for each quantile. When using an 
LST distribution, a value for degrees of freedom was drawn from a 
$Uniform(2,35)$ distribution. A CDF
was fit by minimizing $\sum_{i=1}^m (q_i - F(y; \theta))$ over the parameter
vector $\theta$ and the MSD value $\sum_{i=1}^m (q_i - F(y; \hat{\theta}))$ was 
calculated. The MSD value for which 95\% of the 1,000 simulated distributions
fell below was considered the cutoff and is seen in the table below.

\begin{table}[h!]
  \centering
  \begin{tabular}{l*{6}{c}r}
  Distribution          & Mean Square Difference 95\%  \\
  \hline
  Uniform               & 7.220667e-07   \\
  Normal                & 3.097645e-05  \\
  Lognormal             & 1.166775e-07  \\
  Gamma                 & 2.953370e-05  \\
  Location-scale T      & 0.4894471 \\
  \end{tabular}
\end{table}

With these cutoff values selected, models were then fit to quantile forecasts
from the COVID-19 Forecasts on zoltardata.com. This was a computationally more
difficult problem than fitting distributions to the binned forecasts of the 
influenza project, so the number of predictions fit is much smaller. The 
predictions fit were selected from each of the 115 models with model weeks, 
targets and units selected randomly. In total 2,504 predictions were fit to each
of the five distributions, the MSE was calculated for each and the fit with the
lowest MSE was selected as the closest fit. If the MSE fell below the cutoff
specified above, we considered that the quantile prediction was approximately
from the same distribution as the fit distribution. The results are below.

\begin{table}[h!]
  \centering
  \begin{tabular}{l*{6}{c}r}
  Distribution Family   & Total    & Total Below MSD Cutoff \\
  \hline
  Uniform               & 239      & 0        \\
  Normal                & 609      & 74       \\
  Lognormal             & 694      & 0        \\
  Gamma                 & 597      & 0        \\
  Location-scale T      & 365      & 25       \\
  \end{tabular}
\end{table}

\newpage

\section*{everything below here is just notes for now}

Even as computing power and memory storage continue to improve, 
A single probabilistic forecast can range from only a few pieces of data, such 
as a well known distribution family and two given parameters, to thousands or
tens of thousands of MCMC draws from a posterior distribution. When a repository
of forecasts contains many millions of individual prediction distributions, such
as the COVID-19 Forecast Hub \cite{Cramer2021-hub-dataset}, large file type forecasts can become a 
problem. (Say something about MechBayes posterior samples vs. quantile version
of the forecast).
Something about ensemble storage...

Bogner, Liechti and Zappa compared scoring forecasts of quantiles with the 
Quantile Score similar to the interval score and scoring distribution functions
fit to those quantiles using CRPS \cite{bogner2017combining}. 
The CRPS proves more effective than QS in 
revealing model issues especially in the tails.

Depending on the forecast representation, certain scoring rules may not work to 
assess a forecast. For example, for a quantile or interval representation, LogS
and CPRS may not be used. The weighted interval score was used by Bracher et. al
to evaluate forecasts collected by the COVID-19 Forecast Hub. 
\cite{bracher2021evaluating}

As the number of quantiles required increases, so does the per forecast storage 
requirment. In the COVID-19 Forecast Hub, $23\times 2 = 46$ pieces of 
information are required for certain targets. And because quantiles are easily 
obtained from most methods of probabilistic modeling, teams have much 
flexibility in the type of modeling they perform.

Ensemble modeling under quantiles is done by averaging each quantile over all 
forecast models. Weighting the models based on past performance may be done, but
may not always prove worth the effort. (cite??) A shortcoming of quantile
averaging is the limit that ensemble distributions shapes may take. It has been
shown that quantile averaging may only produce quantiles for distributions which
are unimodal. (cite??) Another shortcoming is that not all proper scoring
methods are appropriate in scoring quantile forecasts. The log-score may not be 
used for example. There are, however, alternatives for scoring such as the
weighted interval score. (cite??)

\subsection*{Above quantiles below bins}

Thus point estimates and
probabilities are easily calculated and proper scoring of each forecast may be 
done with the usual methods.

To build an ensemble forecast from several individual forecasts, each bin may be
averaged over all forecasts. This may be done with or without weighting of the 
various models and the weights if selected may be assigned using the same 
methods that may be used for parametric distribution forecasts.

The discretized representation can provide distributions with reasonably high
resolution but with some cost. As the width of the bins decreases, the 
resolution increases but the storage increases. The number of bins may range 
from a few dozen to hundreds requiring just as many rows in a data table and at 
least two columns. The CDC for example reuqired participants to submit 
probabilities for 51 bins per forecast in the influenza forecasting competition. 
Each team then, had to submit $51\times2 = 102$ pieces of information.

\subsection*{Above bins, below pdfs}

Where a forecast hub requests a parametric distribution as a forecast, a 
submission of three or four cells of data per forecast may suffice making this
representation very efficient for storage. (See table ??)
That little information is enough to provide a high resolution forecast over
all possible values of the forecast. Evaluation of parametric forecasts may be 
done using most proper scoring methods such as the log-scoring method
\cite{gneiting2007strictly}
or modifications of the log-scoring method such as that used by the CDC in 
influenza forecasting \cite{reich2019collaborative}.

In building an ensemble forecast, a discrete mixture distribution may be used.  
To construct a mixture distribution suppose there are $J$ forecasts represented
by parametric distributions with probability density functions $p_j(y|\theta)$ 
for $j = 1,..,J$. A mixture distribution of the $J$ forecasts is

$$p^{E}(y|\theta) = \sum_{j=1}^{J} w_j p_j(y|\theta)$$
where $w_j > 0$ and $\sum_{j=1}^{J} = 1$ are weights assigned to each to each 
component. Equal weights may be assigned to each forecast so $w_j = 1/J$ for all
$j$ or they may be determined by the accuracy and precision of the individual
forecast. Bayesian model averaging \cite{raftery2005using}
is one reasonable way to select weights, though there are

A drawback of representing a forecast in a parametric distribution is the lack 
of flexibility in the model selection. Easy computation and evaluation of these 
models is limited to what is available in software, so certain distributional
shapes may unattainable. The distribution may assign probability to values
outside the range of the forecast. There are remedies for this such as 
truncation, but these increase the complexity in evaluation and scoring.
Requiring a parametric forecast also bars the use of some statistical methods
which might be used including certain Bayesian methods.

\begin{table}[h!]
\centering
 \begin{tabular}{||c c c c||} 
 \hline
 Family & param1 & param2 & param3 \\ [0.5ex] 
 \hline\hline
 normal & $\hat{\mu}$ & $\hat{\sigma}$ & NA \\ 
 lst & $\hat{\mu}$ & $\hat{\sigma}$ & $\hat{\nu}$ \\ [1ex] 
 \hline
 \end{tabular}
\end{table}

\subsection*{Information}

\newpage    
\bibliographystyle{apacite}
\bibliography{references}
\end{document}

### 2022-02-19 draft2.tex
Introduction of cc reworked and a few images added

--- 2022-02-17 draft.tex
@@
 \section{Introduction}
-Forecasting has become increasingly important for private and public decision 
-making. Because predictions cannot generally be free of uncertainty many 
-thinkers prefer probabilistic forecasts over deterministic and probabilistic 
-forecasts have become the norm in many fields including meteorology, economics,
-finance and epidimiology.
+Predicting the outcomes of prospective events is the object of much scientific
+inquiry and the basis for many decisions both public and private. Because 
+predictions of the future can almost never be precise, it is usually desirable
+that a level of uncertainty be attached to any prediction. In recent years, it
+has become increasingly desirable that forecasts be probabilistic in order to 
+account for uncertainty in predicted quantities or events 
+\cite{gneiting2014probabilistic}. Specific problems for 
+which probabilistic forecasts is used include weather forecasting
+\cite{baran2018combining}, economics \cite{groen2013real} and disease outbreaks
+\cite{yamana2016superensemble}.
 
-Ensemble forecasting is the combination of several forecast models into one 
-model which often yields better predicting power than the individual models
-\cite{cramer2021evaluation} and has a solid station in dynamical weather 
-prediction \cite{lewis2005roots}. In weather forecasting, individual members of 
-an ensemble are generated from perturbations of initial conditions, see Baran 
-section 2. Data \cite{baran2018combining} \cite{leutbecher2008ensemble}.
-\cite{yamana2016superensemble}
+A probabilistic forecast is a probability distribution that may be represented
+in a few different formats. A common representation is either a continuous or
+discrete parametric distribution function (a pdf or pmf). Much of the literature 
+on calibration, sharpness and scoring of a forecast pertains to parametric 
+distribution forecasts (see for example 
+\cite{gneiting2007probabilistic},
+\cite{gneiting2013combining} \cite{baran2018combining}).
+Other common representations include samples \cite{krueger2016probabilistic}, 
+discretized bins 
+and quantile or interval type forecasts \cite{taylor2021evaluating} 
+\cite{bracher2021evaluating}. Each representation may be more or less 
+appropriate than the others for a given problem but knowing how to interpret, 
+score and contruct ensemble forecasts for a selected representation is a must 
+when multiple forecasts of the same event are involved.
 
-A probabilistic forecasts may be represented in a variety of ways, a common way
-being the form of a continuous or discrete probability distribution. Indeed much 
-of the literature pertaining to scoring forecast models, combining models 
-into ensemble forecasts and calibration pertain to methods for continuous
-and/or discrete probability functions see for example 
-\cite{gneiting2007probabilistic},
-\cite{gneiting2013combining} \cite{baran2018combining}. Though such methods have
-also been treated for samples, such as MCMC draws of a posterior predictive
-distribution see for example \cite{krueger2016probabilistic}
-and for quantile or interval type and expectile type forecasts 
-\cite{taylor2021evaluating} \cite{bracher2021evaluating}.
+Two projects on forecasting disease outbreaks for which many separate forecasts 
+are used include the United States Center for Disease Control (CDC) hosted
+annual competition for forecasting influenza \cite{cdcflusight}
+and the COVID-19 Forecast Hub which has 
+continuously operated since the start of the COVID-19 pandemic in the US in 
+early 2020 \cite{Cramer2021-hub-dataset}.
 
-Since 2013 the United States Center for Disease Control (CDC) has hosted an
-annual competition for predicting the timing, peak and intensity of the year's 
-flu season. In this competition, the CDC provides academic researchers with data
-, relevant forecasting targets and other guidlines and the various teams produce
-forecasts later evaluated against actual flu acticity. Details on the 
-competition may be found on the CDC FluSight \cite{cdcflusight}.
+\subsection{CDC Influenza Like Illness}
 
-The ReichLab of the University of Massachusettes Amherst and a 
-CDC-funded Influenza Forecasting Centers of Excellence has been heavily 
-involved in the CDC influenza competition and disease outbreak research.
-In their work they have provided insight into the usefulness of collaboration 
-and ensemble modeling in disease outbreaks, see for example 
-\cite{reich2019collaborative}, \cite{reich2019accuracy} and 
-\cite{mcandrew2019adaptively}.
+Since the 2013-14 flu season, the CDC has hosted an annual competition for 
+predicting the timing, peak and intensity of the year's flu season. Forecasts
+for the different targets also include predictions for one, two, three and 
+four weeks ahead of the prediction time. National flu data is weekly provided 
+to outside academic teams who use that data to construct forecasts however they
+will, but the forecast predictions are always submitted in a discretized bin
+format. Here the binning scheme was on a bounded numeric scale and the 
+prediction of a specific target was a set of probabilities assigned to each bin
+\cite{mcgowan2019collaborative}.
+These forecasts are then evaluated against actual flu activity, and at 
+the end of the season a winning team is declared \cite{cdcflusight}.
 
+This competition has provided the CDC, competing teams and other interested
+parties a chance to collaborate and improve forecasting each season. One 
+proposed way to enhance prediction has been to aggregate the various by team
+forecasts into a multi-model ensemble forecast \cite{mcgowan2019collaborative}
+\cite{mcandrew2019adaptively} \cite{reich2019accuracy}.
+
+A multi-model ensemble forecast is combination of several component forecast 
+models into one model which often yields better predicting power than the 
+individual models \cite{cramer2021evaluation} (and did lead to better average 
+results with flu competition forecasts in \cite{reich2019accuracy}.) 
+In the COVID-19 Forecast Hub, construction of ensemble forecasts is a main
+priority.
+
+% Ensemble building has a history in dynamical weather 
+% prediction \cite{lewis2005roots}. In weather forecasting, individual members of 
+% an ensemble are generated from perturbations of initial conditions, see Baran 
+% section 2. Data \cite{baran2018combining} \cite{leutbecher2008ensemble}.
+% \cite{yamana2016superensemble}
+
+\subsection{COVID-19 Forecast Hub}
 In March 2020, at the onset of the COVID-19 pandemic, the Reich Lab in
-association with others founded the COVID-19 Forecast Hub. Every week relevant
-pandemic data is provided to several teams who build probabilistic models for
-forecasting cases, hospitalizations and deaths due to COVID-19 for various 
-regions of different levels with predictions of days, weeks and months ahead.
+association with others founded the COVID-19 Forecast Hub. Borrowing on work and 
+ideas from the CDC annual competition, the Forecast Hub is a central site in 
+which dozens of academic teams collaborate to forecast the ongoing COVID-19 
+pandemic.
+Every week relevant
+pandemic data is provided to these teams who build probabilistic models for 
+their use in
+forecasting cases, hospitalizations and deaths due to COVID-19. Forecasts are 
+made on the US county,
+state and national level with predictions for days, weeks and months ahead.
 These forecasts are combined into a single ensemble forecast. The model data,
-forecasts and the ensemble are passed along to the CDC which uses in official
+forecasts and the ensemble are passed along to the CDC for its use in official
 communication \cite{Cramer2021-hub-dataset}.
@@
 Though similar to the forecasting in the influenza competition, the format of 
-the COVID-19 Forecast Hub has some key distinctions. For one, the Forecast Hub
-has as a key component the construction of a multi-model ensemble forecast 
-whereas that has not as yet been the case in the influenza competition. Another 
-key difference is the format which the individual forecasts are submitted. In 
-the influenza forecast, a set of discretized bins on a numeric scale were set
-for each target and participating researchers were asked to submit their 
-probabilistic predictions as a list of probabilities in for each bin essentially
-making each prediction a bounded pmf \cite{mcgowan2019collaborative}.
-Due to the initial lack of understanding of COVID-19 and the time pressure of
-creating forecasts, the forecasts were requested as the predictive mean and 
+the COVID-19 Forecast Hub has some key distinctions. For one this project has
+been operating continuously since it first began, so forecasts have been made
+for over one-hundred straight weeks. 
+As well due to the initial lack of understanding of COVID-19 and the time 
+pressure of
+creating forecasts, rather than requesting forecasts as binned probabilities
+the forecasts were requested as the predictive mean and 
 predictive intervals for various nominal levels depending on the target to be
-predicted \cite{bracher2021evaluating}.
+predicted \cite{bracher2021evaluating}. Collecting forecasts in this quantile
+or interval type brings with it differences in how to score, construct ensemble
+models and store the forecasts along with other considerations.
 
-Though the representation of a set of intervals can bring added flexibility, 
-there is also some loss in what can be said about a forecast. This will be 
-discussed further herein. In this paper we propose as an alternative to 
-requesting probabilistic forecasts in binned, quantiled, sampled or common 
-distribution format requesting forecasts in a format conducive to discrete 
-mixture distribution. Discussed will be advantages and disadvantages of
-a forecast of this form.
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.12]{8_30_21_cvd_deaths.jpeg}}
+\caption{Figure this out later}
+\label{fig}
+\end{figure}
 
-In the next section, popular probabilistic forecast representation types
-will be reviewed included standard pieces of definitions. These include 
-continuous/discrete probability functions, discretized bin distributions,
-samples from a distribution and quantile or interval distributions. In the 
-following section common methods for scoring forecasts, constructing multi-model
-ensembles will be reviewed and compared for the different representation types. 
-In the same section, other practical considerations for a forecast hub will be
-discussed.
+\subsection{...}
+In the context of collaborative forecasting like that of the CDC flu competition
+or the COVID-19 Forecast Hub, discretized bins and quantile forecasts have 
+proven useful and effective. Yet both types come with their drawbacks. Data 
+storage for instance might be a concern if many bins are allowed for a 
+prediction. And scoring methods are limited if forecasts are made of quantiles.
+
+In this paper, we propose the use of discrete mixture distributions as a means 
+of forecasting for projects similar to the CDC flu competition or the COVID-19
+Forecast Hub. In section 2, popular probabilistic forecast representation 
+types will be defined and reviewed. Methods of scoring, storing, building 
+ensembles and other aspects will be reviewed and compared for each 
+representation type.
+Section 3 is a retrospective study of the CDC flu competition and COVID-19 
+forecast predictions and an attempt to assess whether any predictions 
+approximately come from well known continuous distributions.
 
@@
 parametric forecast and as much as a forecast hub will allow.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.4]{dens_comp.png}}
+\caption{Figure this out later}
+\label{fig}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.4]{cum_comp.png}}
+\caption{Figure this out later}
+\label{fig}
+\end{figure}
 
@@
  \hline\hline
- normal & 0 & 1 & NA \\ 
+ lnorm & 1 & 0.4 & NA \\ 
  \hline
@@
     bin & prob \\ \hline
-    -6.5 & 3.75e-11 \\
-    -6.4 & 7.11e-11 \\
-    -6.3 & 1.33e-10 \\
     ... & ... \\
-    6.3 & 7.11e-11 \\
-    6.4 & 3.75e-11 \\
-    6.5 & 1.96e-11 \\
+    {[1.4,\;1.6)} & 0.04414 \\
+    {[1.6,\;1.8)} & 0.05896 \\
+    {[1.8,\;2.0)} & 0.07032 \\
+    {[2.0,\;2.2)} & 0.07172 \\
+    {[2.2,\;2.4)} & 0.07955 \\
+    ... & ... \\
  \hline
@@
     quantile & value \\ \hline
-    0.01 & -2.326 \\
-    0.025 & -1.96 \\
-    0.05 & -1.645 \\
-    0.01 & -1.282 \\
+    0.01 & 1.07137 \\
+    0.025 & 1.2404 \\
+    0.05 & 1.40689 \\
+    0.01 & 1.62675 \\
     ...  & ... \\
-    0.9 & 1.282 \\
-    0.95 & 1.645 \\
-    0.975 & 1.96 \\
-    0.99 & 2.326 \\
+    0.9 & 4.50667 \\
+    0.95 & 5.18328 \\
+    0.975 & 5.82391 \\
+    0.99 & 6.58783 \\
  \hline

### 2022-02-19 make pictures.R

@@ -1,0 +1,140 @@
+
+source('~/Documents/GitTest/mixture_distributions_for_forecasting/simulate_functions.R')
+
+
+set.seed(168)
+# lnorm_params <- getLnormParams(par=c(3,1))
+lnorm_params <- c(1,.4)
+
+x <- seq(0,8,length.out = 1001)
+# y <- dlnorm(x,lnorm_params[1],lnorm_params[2])
+
+y <- EnvStats::dlnormTrunc(x,meanlog = lnorm_params[1],
+                           sdlog = lnorm_params[2],min = x[1],
+                           max=x[length(x)])
+
+yp <- EnvStats::plnormTrunc(x,meanlog = lnorm_params[1],
+                                 sdlog = lnorm_params[2],min = x[1],
+                                 max=x[length(x)])
+
+par(mfrow=c(2,2))
+plot(y~x,col='blue',type='l',main='(a)',
+     ylab = 'p(x)')
+
+wid <- .2
+lnbins <- seq(0,8,by=wid)
+disc_lnorm <- discretizeDist(bins=lnbins,par=lnorm_params,
+                             family='trlnorm',nu=NA)
+
+lnorm_samp <- EnvStats::rlnormTrunc(1000,meanlog = lnorm_params[1],
+                                    sdlog = lnorm_params[2],min = x[1],
+                                    max=x[length(x)])
+hist(lnorm_samp,main='(b)',xlab='x',border='purple',axes=TRUE)
+box()
+
+secdf <- ecdf(lnorm_samp)
+
+
+outl <- disc_lnorm$bins
+plot((disc_lnorm$probs*5)~disc_lnorm$bins,type='s',col='red',xlab='x',lwd=1.5,
+     ylab='Prob',main='(c)')
+lines((disc_lnorm$probs*5)~outl,type='h',col='black')
+lines((disc_lnorm$probs*5)~outl,type='h',col='red')
+
+
+
+quant_23 <- c(0.010, 0.025, 0.050, 0.100, 0.150, 0.200, 0.250, 0.300, 0.350, 
+              0.400, 0.450, 0.500, 0.550, 0.600, 0.650, 0.700,
+              0.750, 0.800, 0.850, 0.900, 0.950, 0.975, 0.990)
+
+quant_7 <- c(0.025, 0.100, 0.250, 0.500, 0.750, 0.900, 0.975)
+quants <- quant_23
+
[…]

### 2022-02-22 draft2.tex
revisions to representations section

@@
 \usepackage{changepage}
+\usepackage{amsfonts}
 \makeatletter
@@
 
-A probabilistic forecast is a probability distribution that may be represented
-in a few different formats. A common representation is either a continuous or
+A probabilistic forecast is a forecast to which probabilities are assigned to 
+various possible outcomes. There are a number of ways the probabilities or 
+uncertainty may be represented. A common representation is either a continuous 
+or
 discrete parametric distribution function (a pdf or pmf). Much of the literature 
@@
 
-\section{Probability Distributions}
-
-A probabilistic forecast model may be represented in a number of ways. A 
-forecast should always come with a point estimate for a prediction and a 
-characterization of the uncertainty associated with the point prediction.
-Common representations which we review include parametric distributions,
-discretized bin probabilities, samples and quantile or interval values.
-In what follows, let $D$ be a distribution.
-
-\subsection{Parametric distributions}
-In a parametric distribution representation we let $D := D(\theta)$ 
-where $\theta$ is vector of known or unkown parameters contained in a parameter 
-space. We consider a parametric distribution any probability distribution with a 
-fixed parameter set and a known probability density function (pdf) or 
-probability mass function (pmf) for continuous and discrete distributions
-repsectively. The pdf or pmf is represented as $p(y|\theta)$ where $\theta$ is 
-a parameter, usually unknown but estimated using given data.
-
-The value of $p(\cdot|\theta)$ evaluated at $y$ is defined as 
-$p(y|\theta) = P(D = y)$ or the probability that the random variable $D$ takes
-on $y$. In the continuous case $P(D = y) = 0$ for all $y$, but the probability 
-that $D$ falls within an interval $(a,b)$ is calculated as
-
-$$P(a < y < b) = \int_a^b p(y|\theta) dy$$
-
-(??Note: I'm trying to decide how detailed I should be here. Have I already said
-more than is necessary? Should I define the CDF and inverse CDF functions?)
-
-In forecast modeling with a parametric distribution, data is used to obtain a 
-likelihood function $L(\theta|y)$ and the unknown parameter $\theta$ is 
-estimated as $\hat{\theta}$. (more/less detail ??) The mean or the median is
-then used as a point estimate of the forecast and estimated probabilities for 
-all other possible values may be calculated. For the most commonly used families
-of distributions (Normal, Gamma, Poisson etc.) calculating point estimates and 
-probabilities is easy due to the availability of software.
+\section{Probabilistic Forecast Representations}
+
+Before introducing discrete mixture distributions as a candidate for a
+probabilistic forecast, we review representations already commonplace in 
+forecasting. In a collaborative setting, certain aspects of each representation
+should be considered. With each representation presented, 
+commmon application of 
+scoring, data storage and ensemble construction will be considered for each type
+as well as other notable properties.
+
+\subsection{Considerations...}
+\subsubsection{Scoring}
+Scoring rules are used to evaluate numerically a probability forecast. The
+score is a measure on the accuracy of the forecast and where multiple forecasts
+exist may provide a rank for each relative to the others. If a scoring rule is 
+proper, then the highest possible reward is obtained by reporting the true 
+distribution. The rule is strictly proper if that value is unique. 
+Under proper
+scoring rules, a forecaster has no incentive to be dishonest in their 
+submission \cite{gneiting2007strictly}. This makes proper scoring rules ideal
+for grading forecasts. We will limit our review of scoring methods to rules
+which are proper.
+
+\subsubsection{Storage}
+For a forecast hub collecting many predictions, computer storage is something
+that needs to be addressed. For a project involving many researchers, the 
+number of forecast predictions can add up. For example, the repository for the
+COVID-19 Forecast Hub predictions contained 85.4 million predictions as of 
+February 5, 2022! (cite zoltar??)
+When determining the goals of a forecast project, there should be consideration 
+of the storage required for different representations.
+
+\subsubsection{Ensemble Modeling}
+A multi-model ensemble is a statistical model made by combining information from
+2 or more individual statistical models. Private and public decisions are 
+regularly made after combining information from multiple sources. For any given
+situation, information from one source may shed light on a subject which other
+sources fail to capture. Likewise one statistical model may provide perspective
+that another model does not, so that when they are combined in an ensemble the 
+resulting model is superior.
+
+As probabilistic forecasting becomes more commonplace, so too does ensemble 
+modeling. Multi-model ensembles have been used extensively in weather and
+climate modeling see \cite{baran2018combining}, 
+and they have been used increasingly in modeling infectious disease outbreaks
+see for example \cite{yamana2016superensemble}. 
+Multi-model ensembles allow for an incorporation of multiple signals -
+often from differing data sources- and for individual model biases being canceled
+out or reduced by biases in others (\cite{reich2019accuracy} see references
+therein). 
+In several disease outbreak studies, multi-model ensemble forecasts have been 
+shown to outperform individual model forecasts (\cite{cramer2021evaluation} see
+references therein).
+
+Construction of an ensemble may be done by combining individual forecast 
+distributions using weighted averages. This has been called stacking 
+\cite{wolpert1992stacked} or weighted density ensembles 
+\cite{ray2018prediction}.
+
+\subsection{Representations}
+\subsubsection{Parametric distributions}
+A parametric distribution is a discrete or continuous probability distribution 
+described by a known function $p(x) := p(x|\theta)$ -pmf in the discrete case or 
+pdf in the continuous case. $\theta$ is a vector of known or unkown parameters 
+contained in a parameter space.
+
+The value of $p(\cdot)$ evaluated at $x$ is defined as 
+$p(x) = P(X = x)$ or the probability that the random variable $X$ takes
+on $x$ in the space of the random variable. In the continuous case 
+$P(D = x) = 0$ for all $x$, but the probability 
+that $X$ falls within an interval $(a,b)$ is calculated as
+
+\begin{equation}
+  P(a < X < b) = \int_a^b p(x) dx
+\end{equation}
+
+Other functions classified by a parameteric distribution include the cumulative
+distribution function (CDF) and the inverse CDF or quantile function. The CDF 
+in the continuous case is defined as
+
+\begin{equation}
+  F_X(x) = P(X \leq b) = \int_{-\infty}^x p(t) dt
+\end{equation}
+or in the discrete case
+
+\begin{equation}
+  F_X(x) = P(X \leq b) = \sum_{k=1}^n p(x_k) dt
+\end{equation}
+where $x_n$ is the largest value of X less than or equal to $x$.
+The quantile function is defined as
+\begin{equation}
+  Q(p) = \inf \{ y \in \mathbb{R} : p \leq F_X(x) \}
+\end{equation}
+returning a quantile value where $p$ is a given probability $0\leq p \leq 1$.
+
+For a forecast represented as a parametric function with pmf/pdf $p_m(x)$, 
+the accuracy of the forecast may be measured as how likely realized value $x^*$
+is to occur. Commonly used proper scoring rules for parametric distributions
+include the Logarithmic score (LogS), 
+continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
+\cite{alves2013ncep} and the interval/Brier 
+score \cite{gneiting2007strictly} among 
+others. See also \cite{gneiting2014probabilistic}
+section 3 for on proper scoring functions. Unless otherwise noted, the following
+definitions/reviews can be found in the review by Krueger.
+
+For a forecast with pdf/pmf $p_m(x)$, the Logarithmic score evaluates the 
+probability of the observed value $x^*$. It is defined as
+
+\begin{equation}
+  LS(p_m,x*) = -log\;p_m(x^*)
+\end{equation}
 
@@
 
-Scoring rules are used to assign a numeric score to a probability forecast. The
-score is a measure on the accuracy of the forecast and where multiple forecasts
-exist may provide a rank for each relative to the others. If a scoring rule is 
-proper, then the highest possible reward is obtained by reporting the true 
-distribution. The rule is strictly proper if that value is unique.(define??) 
-Under proper
-scoring rules, a forecaster has no incentive to be dishonest in their 
-submission \cite{gneiting2007strictly}. This makes proper scoring rules ideal
-for grading forecasts.
-
-Commonly used proper scoring rules include the Logarithmic score (LogS), 
-continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
-\cite{alves2013ncep} and the interval/Brier 
-score \cite{gneiting2007strictly} among 
-others. See also \cite{gneiting2014probabilistic}
-section 3 for on proper scoring functions. Unless otherwise noted, the following
-definitions/reviews can be found in the review by Krueger.
-
-For a forecast with pdf/pmf $p_m(y)$, the Logarithmic score evaluates the 
-probability of the observed value $y^*$. It is defined as
-
-\begin{equation}
-  LS(p_m,y*) = -log\;p_m(y^*)
-\end{equation}
-
-This scoring method is appropriate for scoring density forecasts as well as 
-descretized bins. The smaller the score, the better the forecast.
 Because the probability evaluation is only at the observed 
@@
 \subsection{Ensemble}
-A multi-model ensemble is a statistical model made by combining information from
-2 or more individual statistical models. Private and public decisions are 
-regularly made after combining information from multiple sources. For any given
-situation, information from one source may shed light on a subject which other
-sources fail to capture. Likewise one statistical model may provide perspective
-that another model does not, so that when they are combined in an ensemble the 
-resulting model is superior.
-
-As probabilistic forecasting becomes more commonplace, so too does ensemble 
-modeling. Multi-model ensembles have been used extensively in weather and
-climate modeling see \cite{baran2018combining}, 
-and they have been used increasingly in modeling infectious disease outbreaks
-see for example \cite{yamana2016superensemble}. 
-Multi-model ensembles allow for an incorporation of multiple signals -
-often from differing data sources- and for individual model biases being canceled
-out or reduced by biases in others \cite{reich2019accuracy}. (See specific citations in this paper 12-15??)
-In several disease outbreak studies, multi-model ensemble forecasts have been 
-shown to outperform individual model forecasts \cite{cramer2021evaluation} (see
-10, 14-25 in this paper).
-
-Construction of an ensemble may be done by combining individual forecast 
-distributions using weighted averages. This has been called stacking 
-\cite{wolpert1992stacked} or weighted density ensembles 
-\cite{ray2018prediction}.
 
@@
 \subsection{Storage}
-For a forecast hub collecting many predictions, computer storage is something
-that needs to be addressed. For a project involving many researchers, the 
-number of forecast predictions can add up. For example, the repository for the
-COVID-19 Forecast Hub predictions contained 85.4 million predictions as of 
-February 5, 2022! (cite zoltr??)
-When determining the goals of a forecast project, there should be consideration 
-of the storage required for different representations.
 

### 2022-02-22 draft2.tex
sample distributions reworked

@@
 
+% \subsubsubsection{Scoring}
 For a forecast represented as a parametric function with pmf/pdf $p_m(x)$, 
@@
 \end{equation}
+The goal is to minimize the LogS, so that a forecast $p{'}_m(x^*)$ is deemed 
+superior to $p_m$ if
+$LS(p{'}_m, x^*) < LS(p_m, x^*)$.
+The LogS is strictly limited to scoring forecasts with density functions and
+evaluating those densities only at the point $x^*$.
+
+The CRPS is a function of a CDF $F$
+and so 
+can be used a bit more extensively than the LogS which is limited to 
+distributions which carry a density. For the CDF $F_m$, the CRPS is defined as
+
+\begin{equation}
+\label{eq:crps}
+  CRPS(F_m, x^*) = \int_{-\infty}^{\infty} (F_m(x)- 1_{\{x*\leq x\}})^2 dy
+\end{equation}
+Here too a smaller score indicates a better forecast.
+
+Besides evaluating forecasts, the CRPS is also used in optimizing weights used
+to build ensembles. Considered the state-of-the-art techniques for combining 
+component distributions
+into a multi-model ensemble are nonhomogeneous regression (NR), also known as
+ensemble model output statistics (EMOS), and ensemble Bayesian model averaging
+(BMA), both of which will be defined as in \cite{gneiting2014probabilistic}.
+
+In the context of an ensemble made from component models submitted from various
+sources, contructed with different methods and with potentially different data,
+BMA is the better option. In BMA, the final model does not have to be specified
+beforehand and the resulting forecast will be a discrete mixture distribution
+of all component forecasts. The general form for the ensemble distribution $p^E$
+is
+
+\begin{equation}
+  p^E(x) = \sum_{jm=1}^M w_mp_m(x)
+\end{equation}
+where $p_m$ is the $j^{th}$ component forecast distribution and 
+$0 \leq w_m \leq 1$ is a weight assigned to each component where $\sum w_m = 1$.
+Methods for estimating weights include Maximum Likelihood estimation
+\cite{raftery2005using}, MCMC 
+sampling see \cite{vrugt2008ensemble} (also in this paper it talks about how 
+EM can get difficult as parameters i.e. number of distributions increase, and 
+shows MCMC may be better with that high dimensionality and gives full posterior
+of weights)
+and minimizing the CRPS as in 
+\cite{baran2018combining}.
+
+For selecting distribution weights, the CRPS has some nice properties, but can 
+sometimes be
+difficult to compute. For example, when the forecast is a mixture of a 
+Truncated Normal distribution (TN) and a Truncated Lognormal (TL) the CRPS is 
+not available in closed form \cite{baran2018combining}.
+
+Generally computation and evaluation of parametric distributions is not hard. 
+For most commonly used parametric distributions -Normal, Lognorm, Poisson,
+Gamma, etc.- there is software readily available to compute density, 
+distribution and quantile values. Likewise, requirements for storage are low 
+compared to other uncertainty representations we will discuss. The most common
+parametric distributions can be fully defined with three or pieces of data.
+The distribution family and two or three parameters. Below shows a table with
+enough information to completely define a $Lognormal(1,0.4)$ distribution.
+
+\begin{table}[h!]
+\centering
+ \begin{tabular}{|c c c|} 
+ \hline
+ Family & param1 & param2 \\ [0.5ex] 
+ \hline
+ lnorm & 1 & 0.4 \\ 
+ \hline
+ \end{tabular}
+\end{table}
+
+A completely defined continuous parametric distribution can be evaluated at an
+infinite number of values. We will call this an infinite resolution.
 
@@
 Requiring a parametric forecast also bars the use of some statistical methods
-which might be used including certain Bayesian methods.
-
-\subsection{Forecast as samples}
-A random sample $(X_1,...,X_n)$ where $X_i \sim D$ may be used to 
-estimate values such as the mean or quantiles of the distribution $D$.
+which might be used to create a forecast model including some Bayesian methods
+where a posterior distribution cannot be computed in closed form.
+
+\subsubsection{Sample Distributions}
+Some forecast model builders may want more flexibility than a parametric 
+distribution can provide. Some methods such as sampling from a posterior 
+distribution or resampling methods like Bootstrap will produce forecasts of
+sample distributions.
+
+A sample distribution is built of a sample of random variables 
+$(X_1,...,X_n)$ where $X_i \sim D$ and $D$ is a distribution. From this, sample
+statistics such as mean, median, variance and quantiles may be calculated. 
+An empirical cumulative distribution function (ECDF) may also be calculated as
+
+\begin{equation}
+\label{eq:ecdf}
+  F_n(x) = \frac{1}{n} \sum_{i=1}^n \mathbb{I}(X_i \leq x)
+\end{equation}
 
 According to the Strong Law of Large numbers, the sample mean will converge to
-the expected value of distribution as $n$ approaches $\infty$ as long as the 
+the expected value of distribution as $n \rightarrow \infty$ as long as the 
 expected value of that distribution exists. Likewise by the same law the 
-empirical distribution function will converge to the true cumulative 
-distribution function as $n$ approches $\infty$. Thus, if a sufficiently large 
+ECDF will converge to the true CDF 
+distribution function as $n \rightarrow \infty$. Thus, if a sufficiently large 
 sample is generated from a distribution, the sample will closely approximate the 
@@
 sampling have greatly contributed to growth in the use of
-predictive distributions \cite{gneiting2007strictly}.
+predictive distributions \cite{gneiting2007strictly}. (See examples listed in
+\cite{krueger2016probabilistic}).
+
+To properly score a forecast represented by a sample distribution, both the CRPS
+and LogS may be used. The CRPS has the advantage here of scoring the sample 
+distribution directly since the CDF in  (\ref{eq:crps}) may be replaced by 
+(\ref{eq:ecdf}). To use the LogS to score a forecast, a density function for the 
+sample must be approximated. Common approximations include a kernel density (KD)
+or Gaussian approximation (GA).
+
+KD is defined in Kruger as
+
+\begin{equation}
+\label{eq:kd}
+  \hat{p}_n(x) = \frac{1}{n h_n} \sum_{i=1}^n K \left( \frac{x-X_i}{h_n} \right) 
+\end{equation}
+where $K$ is a kernel function, and $h_n$ is a bandwidth
+
+Kruger et. al compare scoring of MCMC drawn forecast distributions using CRPS 
+and LogS over samples directly using ECDF or over density approximations using
+KD or GA.
 
@@
 For a forecast of drawn samples, the ECDF may be computed and the CRPS used to 
-score the prediction. The CRPS has some nice properties, but can sometimes be
-difficult to compute. For example, when the forecast is a mixture of a 
-Truncated Normal distribution (TN) and a Truncated Lognormal (TL) the CRPS is 
-not available in closed form \cite{baran2018combining}.
+score the prediction.
 
@@
 \subsection{Ensemble}
-
-Considered the state-of-the-art techniques for combining component distributions
-into a multi-model ensemble are nonhomogeneous regression (NR), also known as
-ensemble model output statistics (EMOS), and ensemble Bayesian model averaging
-(BMA), both of which will be defined as in \cite{gneiting2014probabilistic}.
-
-In the context of an ensemble made from component models submitted from various
-sources, contructed with different methods and with potentially different data,
-BMA is the better option. In BMA, the final model does not have to be specified
-beforehand and the resulting forecast will be a discrete mixture distribution
-of all component forecasts. The general form for the ensemble distribution $p^E$
-is
-
-\begin{equation}
-  p^E(y) = \sum_{j=1}^J w_jp_j(y)
-\end{equation}
-where $p_j$ is the $j^{th}$ component forecast distribution and 
-$0 \leq w_j \leq 1$ is a weight assigned to each component where $\sum w_j = 1$.
-Methods for estimating weights include Maximum Likelihood estimation
-\cite{raftery2005using}, MCMC 
-sampling see \cite{vrugt2008ensemble} (also in this paper it talks about how 
-EM can get difficult as parameters i.e. number of distributions increase, and 
-shows MCMC may be better with that high dimensionality and gives full posterior
-of weights)
-and minimizing CRPS as in 
-\cite{baran2018combining}.
 
@@
 mean 0 and variance 1.
-
-\begin{table}[h!]
-\centering
- \begin{tabular}{||c c c c||} 
- \hline
- Family & param1 & param2 & param3 \\ [0.5ex] 
- \hline\hline
- lnorm & 1 & 0.4 & NA \\ 
- \hline
- \end{tabular}
-\end{table}
 

### 2022-02-24 draft2.tex
draft of sections 1 and 2 including images

@@
 \begin{equation}
+\label{eq:dcdf}
   F_X(x) = P(X \leq b) = \sum_{k=1}^n p(x_k) dt
@@
 \begin{equation}
+\label{eq:bma}
   p^E(x) = \sum_{jm=1}^M w_mp_m(x)
@@
 
+So the options that a researcher has for constructing a forecast are more than
+if they are asked to submit a parametric distribution and the characterisitcs 
+and potential shapes of distributions is much larger.
 In the last few decades, increased computing power and improvements in MCMC
@@
 \end{equation}
-where $K$ is a kernel function, and $h_n$ is a bandwidth
+where $K$ is a kernel function, and $h_n$ is a suitable bandwidth. GA is defined
+as
+
+\begin{equation}
+\label{eq:ga}
+  \hat{F}_n(x) = \Phi  \left( \frac{x-\hat{\mu}_n}{\hat{\sigma}_n} \right)
+\end{equation}
+where $\Phi$ is the standard normal CDF and $\hat{\mu}_n$ and $\hat{\sigma}_n$
+are the empirical mean and standard deviation of the sample $(X_i)$. (See
+\cite{krueger2016probabilistic} for definitions of \ref{eq:kd} and \ref{eq:ga}).
 
@@
 
-\subsection{Discretized probability bins}
+To build an ensemble model from sample distribution forecasts, the BMA 
+construction from (\ref{eq:bma}) would work only replacing $p_m$ with 
+$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$. Here as well the optimal weights 
+$w_m$ may be estimated by maximizing the likelihood or minimizing CRPS. Then 
+the ensemble distribution would take the form of a continuous or discrete
+probability mixture distribution. If the desire is that the ensemble still be
+a sample distribution, after selecting weights, a sample may be selected by 
+randomly selecting a sample from $(X_n)_m$ with probability $w_m$.
+
+A potentially big issue with using sample distributions is the amount of storage
+it would require. For example when making MCMC draws from a posterior 
+distribution, the final sample distribution can have a sample size of thousands
+or tens of thousands. Maybe not all distributions would require such a large 
+sample size, but sizes of at least dozens or hundreds would be required for each
+forecast prediction. For any project the size of the CDC flu competition or the
+COVID-19 Forecast Hub, the storage required would be large and potentially 
+expensive.
+
+\subsection{Discretized bin distributions}
+An alternative to parametric distributions and sample distributions which allows
+for high flexibility in distribution shape but is more manageable in terms of 
+storage is a discretized bin distribution.
+
 A discretized bin probability distribution may be constructed over a set 
@@
 to be forecasted, a forecast hub will determine the possible values for $A$ and 
-select the number of bins and the sizes for each. It may the case
+select the number of bins and the sizes for each. It may be the case
 that a forecast hub will set the width of all bins to be equal so that 
@@
 \cite{mcgowan2019collaborative}.
-For this paper, we will consider the case where all bins share a common width.
 To complete the construction, a probability $p_i$ is assigned to each $b_i$ 
@@
 This discrete representation with a given bin and assigned probability is in
-essence a probability mass function, so a given forecast may be evaluated and 
-scored the same as a discrete parametric distribution.
+essence a probability mass function in that the calculation of moments and the 
+the cumulative distribution are done the same as for a discrete parametric 
+distribution. For a random variable X from a binned distribution to calculate
+the $j^{th}$ moment we may use
+
+\begin{equation}
+\label{eq:bev}
+  EX^j = \sum_{i=1}^n \beta_i^j p_i
+\end{equation}
+where $\beta_i$ is a value related to the bin $B_i$ such as $\beta_i = b_i$,
+$\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$. The 
+cumulative distribution may be
+
+\begin{equation}
+\label{eq:bcdf}
+  P(X \leq b) = \sum_{i=1}^n p_i
+\end{equation}
+where $p_n$ is the probability for the bin $B_n$ where $b \in B_n$.
 
@@
 assign probabilities to each of the bins. When the values to be forecasted are
-continuous, a forecaster may need to employ some method of discretization to a 
+continuous, a forecaster may need to employ a method of discretization to a 
 forecast distribution. There are a number of possible ways to do this including
 those outlined by Chakraborty and Subrata \cite{chakraborty2015generating}.
-In a retroactive analysis of forecast predictions from the CDC influenza 
-competition, we attempt to evaluate whether some or any teams made their 
-predictions by discretizing from a common continuous distribution function.
 
@@
 In that context it has become the standard representation 
-\cite{brooks2020comparing}.
-
-Most statistical models such as parametric models 
-or distributions made from samples may be readily translated into a discretized 
-distribution -see \cite{chakraborty2015generating} for a summary of several-
-giving forecasters flexibility in how they build their 
-models and assign probabilities. 
-There is however some sacrifice in what can be 
-forecasted as the possible range of the distribution may be limited to what the
-forecast hub requires. This limitation is in part what prompted the COVID-19
-Forecast Hub to use quantile forecasts rather than binned distributions.
-\cite{bracher2021evaluating}.
-In a simulation study outlined later, we will
-consider a construction from Kemp \cite{kemp2004classes} to discretize known
-continuous distributions.
-
-\subsection{Quantile representation}
-Uncertainty in a forecast prediction may also be characterized by  including
-multiple quantiles along with corresponding values. Often the median value will
-be reported as a point forecast with a number of quantiles included which form 
-confidence intervals of various levels.
-A quantile forecast is constructed as follows.
-For $N$ given quantiles $\alpha_1,..., \alpha_N$, $q_1,..., q_N$ are the values
-such that
-
-\begin{equation}
-  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ..., 
-  P(Y \leq q_N) = \alpha_N
-\end{equation}
-
-When the quantiles are reported as a median and confidence intervals we have
-
-\begin{equation}
-  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ..., P(Y \leq q_k) = .5, 
-  ..., 
-  P(Y \leq q_{N-1}) = 1 - \alpha_{N-1}, P(Y \leq q_N) = 1 - \alpha_N
-\end{equation}
-
-The COVID-19 Forecast Hub requires that participating teams report their
-forecasts as quantile values corresponding to 23 or 7 quantiles -depending on 
-the target or time being forecasted. The quantile representation was selected
-over the discretized bins used in the influenza competition because the range 
-of observation outcomes of interest was much larger and an appropriate binning
-scheme would have been difficult to define \cite{bracher2021evaluating}.
-
-The quantile or interval format is somewhat unique among forecast 
-representations discussed in this paper. What is possible for scoring forecasts
-or building ensemble models in other representations is often not possible with
-quantile forecasts. Yet it has its advantages.
-
-Quantile representation allows for forecasters to submit fairly detailed
-forecasts without restricting the range of possible values -a major reason for 
-selecting a quantile representation over discretized bins 
-\cite{bracher2021evaluating}.
-
-Since quantiles are easily calculated from any regular distribution type
--e.g. inverse CDF for parametric functions and inverse ECDF from data or 
-samples- we consider quantile forecasts to have high flexbility in terms of 
-shape and range.
-
-As in the
-discretized representation, the resolution of a distribution based on quantiles
-will depend on the number of quantiles to be forecasted. There is however a 
-significant loss of information in reporting the extreme outcomes in a quantile
-model. Since reported intervals can only be so wide, it is possible that tail 
-information is lost. The COVID-19 Forecast Hub for example requires forecast 
-values up to the $99^{th}$ and down to the $1^{st}$ percentile. For values any
-more extreme, exactly assigning probabilities is impossible.
-
-\subsection{Discrete mixture of parametric distributions}
-In a parametric setting, forecasters may be permitted to submit a forecast as a
-discrete mixture. Such a distribution may be constructed in the same way as the
-ensemble described under Parametric distributions where for $T$ models with pdf
-$p_t(y|\theta)$ $p^{M} = \sum_{t=1}^T z_tp_t(y|\theta)$ where 
-$z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$
-
-Like the standard parametric model, a discrete mixture is easily evaluated with
-exisiting software (like distr R package) (cite??) and scoring may be done by 
-most or all of the same methods. The resolution of a discrete mixture is high 
-and the support need not be limited by submission requirements.
-
-A mixture distribution may be much more flexible than a simple parametric in 
-terms of distributional shape. But as it is essentially parametric, forecasters
-mays still be limited in how they construct their models. But it may be possible
-to fit a mixture distribution to probability models with the other 
-representations discussed. Further discussion on methods for fitting mixture 
-distributions to different types of model representations is included in this 
-paper.
-
-An ensemble model may be built by constructing a mixture of mixtures. Where for 
-$J$ forecasts $p^{E}(y|\theta) = \sum_{j=1}^{J} w_j p^{M}_j(y|\theta)$ where 
-$w_j > 0$ and $\sum_{j=1}^J w_j = 1$. (is it necessary to describe this
-construction).
-
-Depending on the number of components a forecaster includes in a mixture 
-forecast, the amount of storage per forecast might be as little as for a 
-parametric forecast and as much as a forecast hub will allow.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[scale=.4]{dens_comp.png}}
-\caption{Figure this out later}
-\label{fig}
-\end{figure}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[scale=.4]{cum_comp.png}}
-\caption{Figure this out later}
-\label{fig}
-\end{figure}
-
-\section{Forecast specifics on scoring, ensembling, etc.}
-
-\subsection{Scoring}
-
-Because the probability evaluation is only at the observed 
-point \cite{reich2019accuracy} used a modified Logarithmic score 
-known as the multibin logarithmic score (MBlogS) for scoring
-forecasts. This allowed for a range of values to be considered "correct" or 
-accurate. MGlogS is defined as
-
-\begin{equation}
-  MBlogS(F_m, y^*) = log(\sum_{i=-d}^{d} p_m(y^* + i))
-\end{equation}
-
-\begin{equation}
-  \int_{y*-\epsilon}^{y^*+\epsilon} -log\;p_m(y^*) (??)
-\end{equation}
-
-The MBlogS has the advantage of offering a more accesible interpretation but the
-drawback of being improper \cite{bracher2021evaluating}.
-
-Another commonly used score, the interval score, may also be used on density 
-forecasts including discretized bin forecasts. With the right smoothing of
-a distribution of drawn samples, 
-such as Gaussian approximation or Kernel density estimation, these methods may 
-be used for scoring, see for example \cite{krueger2016probabilistic}.
-These scoring methods will not work for raw samples however.
-
-The Continuous ranked probability score (CRPS) is a function of a CDF $F$, 
-including an Empirical CDF, $\hat{F}(x) = n^{-1} \sum_{i=1}^n 1\{x \geq X_i\}$
-and so 
-can be used a bit more extensively. For the CDF $F_m$, the CRPS is defined as
-
-\begin{equation}
-  CRPS(F_m, y^*) = \int_{-\infty}^{\infty} (F_m(y) - 1_{\{y*\leq y\}})^2 dy
-\end{equation}
-
-For a forecast of drawn samples, the ECDF may be computed and the CRPS used to 
-score the prediction.
-
-The Interval score (IS), a consistent and elicitable proper score 
-(see \cite{gneiting2014probabilistic} for definitions) is defined as
-
-\begin{equation}
-  IS_{\alpha}(l,r; y^*) = (r-l) + \frac{2}{\alpha}(l-y^*)1\{y^*<l\} 
-  + \frac{2}{\alpha}(y-r)1\{y>r\}
-\end{equation}
-
-where $l$ and $r$ are the $\alpha/2$ and $(1-\alpha/2)$ quantiles that bound
-the central $(1-\alpha)$ prediction interval. This is a sum -weighted by 
-$\alpha$- of the width of the
-interval and the distance between $y^*$ and the interval (if $y^*$ is not 
-captured in the interval). The IS requires only a single central 
-$(1-\alpha) \times 100$ prediction interval.
-
-When an interval forecast is made up of more than one interval with different
-$\alpha$ levels, a weighted interval score (WIS) may be evaluated. Bracher et.
-al use the WIS to evaluate COVID-19 inverval forecasts 
-\cite{bracher2021evaluating}. There are multiple versions of the WIS -some of 
-which are described by Bracher et. al- but that used in the COVID-19 Forecast
-Hub is defined as follows.
-
-\begin{equation}
-  WIS_{0,K}(F_m,y^*) = \frac{1}{K + 1/2} \times (w_0, \times |y^*-med|+
-  \sum_{k=1}^K \{ w_k \times IS_{\alpha_k}(F_m,y) \} )
-\end{equation}
-
-where $F_m$ is the interval forecast, $K$ is the number of prediction intervals
-each with level $\alpha_k$ and $med$ is the predictive median. $\alpha_0 = 1$ is 
-is the $\alpha$ value corresponding to the predictive median which may also be
-considered a level 0 prediction interval. $w_k = \alpha_k/2$ is the weight on
-intervals which was used. With that choice of weights, it may be shown that the
-WIS approximates CRPS see S1 Text  \cite{bracher2021evaluating} or
-
-\begin{equation}
-  WIS_{0,K}(F_m,y^*) \approx CRPS(F_m,y^*)
-\end{equation}
-
-Bogner, Liechti and Zappa compared scoring forecasts of quantiles with the 
-Quantile Score similar to the interval score and scoring distribution functions
-fit to those quantiles using CRPS \cite{bogner2017combining}. The CRPS 
-corresponds to the integral of the QS over all possible thresholds rather than
-just specific quantiles, it more effectively reveals deficiencies in parts of 
-the distribution and especially in the tails past the end points of quantiles
-used in QS or IS.
-
-\subsection{Flexibility, resolution and information (such as tail info)}
-The amount of info
-
-\subsection{Ensemble}
-
-Reich et. al used BMA to combine multiple forecasts from the flu 
+\cite{brooks2020comparing}. A decent amount of work has been done in evaluating 
+and constructing ensemble models on influenza forecasts represented by 
+discretized bins \cite{mcgowan2019collaborative}, \cite{mcandrew2019adaptively}
+\cite{reich2019collaborative}.
+
+Because discretized bins can be seen as a pmf, methods for proper scoring 
+already 
+discussed -LogS and CRPS- are useable and BMA is valid method for ensemble 
+construction. Reich et. al used BMA to combine multiple forecasts from the flu 
 competition. There built and compared ensemble models with different weighting
@@
 Expectation Maximization (EM) algorithm \cite{reich2019accuracy}. See the
-supplementary material for details. Other options for estimating the weights 
-include Monte Carlo Markov Chain sampling ??\cite{vrugt2008ensemble} or a 
-minimization of the ensemble CRPS score \cite{baran2018combining}.
-
-The BMA ensemble construction works for discrete and continuous parametric 
-distributions as well as discretized bin distributions, but is not useful when 
-the forecasts are of the interval type.
-
-Quantile averaging or Vincentization is defined as
-
-\begin{equation}
-  F_v^{-1}(\alpha) = \sum_{m=i}^M w_m F_m^{-1} (\alpha)
-\end{equation}
-
-where $F_m^{-1} (\alpha) = \inf \{y:F_m(y) \geq \alpha\}$ for 
-$0 < \alpha \leq 1$. Some notable characteristics are that it is more likely
-to be unimodal than linear averaging of densities like BMA 
-\cite{busetti2017quantile} (this paper is a big comparison of QMA and 
-linear or log averaging. Under some circumstances, such as when member
-distributions are exponential, Weibull or logisitic the aggregated distribution
-is the same \cite{ratcliff1979group}. It apparently produces smoother
-distributions than BMA, at least in \cite{schepen2015model}.
-
-These dudes seem to think averaging quantiles is better than simple averaging 
-probabilities. More sharp (less variation), perform better in scoring etc.
-\cite{lichtendahl2013better}.
-
-\subsection{Storage}
-
-The data requirement for a parametric distribution small and will usually be the 
-least when compared with other representations. As long as the forecast is 
-allowed to have an unbounded range, only 3 or 4 pieces of information will be
-required including specification of the distribution family and model 
-parameters. See the table below for an example of a normal distribution with 
-mean 0 and variance 1.
-
-With those three pieces of information, the whole distribution is completely
-defined and software is readily available for calculating moments, percentiles,
-probabilities and generating random samples. The third box under param3 is there
-in case a particular distribution family has three parameters -a location-scale
-T distribution for example.
-
-If the distribution is made up of samples from a distribution, like posterior
-predictive distribution, much more space will be required to contain all the 
-information. A sample using MCMC sampling may have thousands or even tens of 
-thousands of draws. It's easy to see why this could be a problem if millions of
-predictive distributions are collected and saved.
+supplementary material for details.
 
@@
 corresponding probabilities in each. That makes 262 pieces of information per
-prediction. A much larger number than what is required for a fully defined
-parametric distribution. The following table shows what a discretized standard
-normal distribution looks like in 131 discretized bins. Note that for the sum of 
-the probabilities to equal one, it was essential to normalize the probabilites
-within the range $[-6.5,6.5]$ since the full range of a normal distribution is
-$(-\infty, \infty)$.
+prediction. For any binning scheme of more than two bins, the information 
+requirement for discretized bins will be higher than for parametric distrbutions.
+Table \ref{tab:dbins} illustrates what a discretized 
+Lognormal$(1,0.4)$ distribution truncated over $[0,8]$
+looks like in 41 equally spaced discretized bins. The discretization was done
+such that
+
+\begin{equation}
+\label{eq:disc}
+  p_i = \int_{b_{i-1}}^{b_i} p^{TL}(x) dx
+\end{equation}
+where $p^{TL}$ is the pdf of a truncated Lognormal$(1,0.4)$. This is similar
+to Methodology-IV from Chakraborty \cite{chakraborty2015generating}
+ \cite{kemp2004classes}.
 
@@
 \centering
+\label{tab:dbins}
  \begin{tabular}{|c|c|} 
@@
 \end{table}
-
-Like in the last two representations, data storage for interval forecasts will
+Submitted as a forecast prediction, the distribution in table \ref{tab:dbins} 
+includes 82 pieces of data. For parts 
+of the CDC influenza competition some forecasts included upt to 262. This is 
+much more manageable than possible thousands of samples from a samle 
+distribution but is 
+still much larger than the 3 or 5 data pieces required to report a lognormal
+or truncated lognormal distribution.
+
+Depending on what is known about the problem to be solved, creating the right 
+binning scheme might be a challenge. Because there must be a finite number of
+bins, forecast distributions must have a finite support. Where the range of 
+possible outcomes to a problem is little known, the right binning scheme may be
+hard to produce.
+
+\subsection{Quantile representation}
+When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
+the time pressure of generating forecasts and the consideration of the large
+range for possible outcomes contributed to the COVID-19 Forecast Hub decision
+to forego trying to create the right binning scheme and use sets of prediction
+intervals to represent uncertainty in predictions \cite{bracher2021evaluating}.
+
+The Forecast Hub requires predictions to be submitted as 11 or 3 nominal 
+intervals -depending on the specific target- and a median.
+Using this interval or quantile representation lead to a number of changes in 
+the evaluation and aggregation of forecasts.
+
+A quantile forecast is constructed as follows.
+For $N$ given quantiles $\alpha_1,..., \alpha_N$, $q_1,..., q_N$ are the values
+such that
+
+\begin{equation}
+  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ..., 
+  P(Y \leq q_N) = \alpha_N
+\end{equation}
+When the quantiles are reported as prediction intervals we have more 
+specifically
+
+\begin{equation}
+  P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ...,
+  P(Y \leq q_{N-1}) = 1 - \alpha_{N-1}, P(Y \leq q_N) = 1 - \alpha_N
+\end{equation}
+
+The quantile or interval format is somewhat unique among forecast 
+representations discussed in this paper. What is possible for scoring forecasts
+or building ensemble models in other representations is often not possible with
+quantile forecasts. The shape of a distribution is also not known and in fact,
+nothing is known about the tails of the uncertainty or ouside of the most 
+extreme reported quantile values. In the Forecast Hub predictions, nothing 
+is said about the range below the $1^{st}$ quantile or above the $99^{ths}$.
+Yet the quantile representation has its advantages.
+
+Quantile representation allows for forecasters to submit fairly detailed
+forecasts without restricting the range of possible values.
+Since quantiles are easily calculated from any regular distribution type
+-e.g. quantile function for parametric functions or calculating sample 
+quantiles- we consider quantile forecasts to have high flexbility in terms of 
+what methods forecasters may employ in modeling.
+
+To score predictions from a prediction interval, 
+neither the LogS nor the CRPS may be used, 
+but another proper scoring rule the interval score (IS) may be.
+For an observed outcome $x^*$ and a prediction interval $(l,r)$ 
+where $l$ and $r$ are the $\alpha/2$ and $(1-\alpha/2)$ quantiles that bound
+the central $(1-\alpha)$ prediction interval the IS is defined as
+
+\begin{equation}
+\label{eq:is}
+  IS_{\alpha}(l,r; x^*) = (r-l) + \frac{2}{\alpha}(l-x^*)1\{x^*<l\} 
+  + \frac{2}{\alpha}(y-r)1\{x^* > r\}
+\end{equation}
+This is a sum -weighted by 
+$\alpha$- of the width of the
+interval and the distance between $x^*$ and the interval (if $x^*$ is not 
+captured in the interval) \cite{gneiting2014probabilistic}. 
+The IS requires only a single central 
+$(1-\alpha) \times 100$ prediction interval.
+
+When an interval forecast is made up of more than one interval with different
+$\alpha$ levels, a weighted interval score (WIS) may be evaluated. Bracher et.
+al use the WIS to evaluate COVID-19 inverval forecasts 
+\cite{bracher2021evaluating}.
+There are multiple versions of the WIS -some of 
+which are described by Bracher et. al- but that used in the COVID-19 Forecast
+Hub is defined as follows
+
+\begin{equation}
+  WIS_{0,K}(F_m,y^*) = \frac{1}{K + 1/2} \times (w_0, \times |y^*-med|+
+  \sum_{k=1}^K \{ w_k \times IS_{\alpha_k}(F_m,y) \} )
+\end{equation}
+$w_k = \alpha_k/2$ is the weight on
+intervals which was used. With that choice of weights, it may be shown that the
+WIS approximates CRPS see S1 Text  \cite{bracher2021evaluating}
+
+Bogner, Liechti and Zappa compared scoring forecasts of quantiles with the 
+Quantile Score similar to the interval score and scoring distribution functions
+fit to those quantiles using CRPS \cite{bogner2017combining}. The CRPS 
+corresponds to the integral of the QS over all possible thresholds rather than
+just specific quantiles, it more effectively reveals deficiencies in parts of 
+the distribution and especially in the tails past the end points of quantiles
+used in QS or IS.
+
+Like the CRPS, not only does the WIS provide an easily interpretable proper 
+score for interval forecasts, but it may also be useful when building an 
+ensemble forecast.
+
+The ensemble forecast constructed by the COVID-19 Forecast Hub was made as an
+equally-weighted average of forecasts from the component models. More 
+specifically, each quantile value of the ensemble was the average of values from
+all models corresponding to the same quantile \cite{ray2020ensemble}. For $M$ 
+models each with $K$ quantiles, the $k^{th}$ ensemble quantile $q_k$ is 
+calculated as
+
+\begin{equation}
+\label{eq:qa}
+  q_k = \sum_{m=1}^M \nu_m q_k^m 
+\end{equation}
+where $\nu_m$ is the weight assigned to each forecast and $\sum \nu_m = 1$. In
+the Forecast Hub model, $\nu_m = \nu = 1/M$. Where the overall mean or a
+weighted mean may be used, the median may also be used.
+Brooks et. al compare performance of the COVID-19 ensemble
+between equally-weighted means, weighted means and median value constructions.
+\cite{brooks2020comparing} (is is appropriate to cite this blog??)
+In their report, they show that weighted means and median constructions tend
+to outperform equally-weighted mean construction. To come up with optimal 
+weights, they select values $\nu_m$ from \ref{eq:qa} which minimize the WIS of 
+the ensemble forecast.
+
+Averaging quantiles in this way the same as quantile averaging or Vincentization
+only with an incomplete quantile function. It thus carries with it many of the
+same characteristics.
+Quantile averaging or Vincentization for a complete distribution is defined as
+
+\begin{equation}
+\label{eq:vinc}
+  F_v^{-1}(\alpha) = \sum_{m=i}^M w_m F_m^{-1} (\alpha)
+\end{equation}
+where $F_m^{-1} (\alpha) = \inf \{y:F_m(y) \geq \alpha\}$ for 
+$0 < \alpha \leq 1$. Some notable characteristics are that it is more likely
+to be unimodal than linear averaging of densities like BMA 
+\cite{busetti2017quantile} (this paper is a comparison of QMA and 
+linear or log averaging. Under some circumstances, such as when member
+distributions are exponential, Weibull or logisitic the aggregated distribution
+is the same \cite{ratcliff1979group}. It produces smoother
+distributions than BMA according to Schepen and Wang \cite{schepen2015model}.
+Lichtendahl et. al conclude that quantile averaging produces sharper forecasts
+and tends to perform better in scoring than probability averaging
+\cite{lichtendahl2013better}.
+
+As in sample distributions and binned distributions, 
+data storage for interval forecasts will
 depend on the desired clarity of resolution. For the COVID-19 forecasts 
@@
 (some of the longer term forecasts only include seven quantiles). In terms of 
-storage, this is an improvement over requirements for the flu contest.
+storage, this is an improvement over requirements for the flu contest. Table
+\ref{tab:qstor} shows what a submission of 23 quantiles from a 
+Lognormal $(1,0.4)$ looks like.
+
+% \begin{table}[h!]
+% \centering
+%  \begin{tabular}{|c|c|} 
+%  \hline
+%     quantile & value \\ \hline
+%     0.01 & 1.07137 \\
+%     0.025 & 1.2404 \\
+%     0.05 & 1.40689 \\
+%     0.01 & 1.62675 \\
+%     ...  & ... \\
+%     0.9 & 4.50667 \\
+%     0.95 & 5.18328 \\
+%     0.975 & 5.82391 \\
+%     0.99 & 6.58783 \\
+%  \hline
+%  \end{tabular}
+% \end{table}
 
@@
 \centering
- \begin{tabular}{|c|c|} 
- \hline
-    quantile & value \\ \hline
-    0.01 & 1.07137 \\
-    0.025 & 1.2404 \\
-    0.05 & 1.40689 \\
-    0.01 & 1.62675 \\
-    ...  & ... \\
-    0.9 & 4.50667 \\
-    0.95 & 5.18328 \\
-    0.975 & 5.82391 \\
-    0.99 & 6.58783 \\
+\label{tab:qstor}
+ \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
+ % \begin{tabular}{|c|c|}
+ \hline
+    quantile & 0.01 & 0.025 & 0.05  & ...  & 0.95 & 0.975 & 0.99 \\ \hline
+    value & 1.07137 & 1.2404 & 1.40689 & ... & 5.18328 &
+    5.82391 & 6.58783 \\
+    % quantile & value \\ \hline
+    % 0.01 & 1.07137 \\
+    % 0.025 & 1.2404 \\
+    % 0.05 & 1.40689 \\
+    % 0.01 & 1.62675 \\
+    % ...  & ... \\
+    % 0.9 & 4.50667 \\
+    % 0.95 & 5.18328 \\
+    % 0.975 & 5.82391 \\
+    % 0.99 & 6.58783 \\
  \hline
@@
 \end{table}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.4]{dens_comp.png}}
+\caption{Figure this out later}
+\label{fig}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.4]{cum_comp.png}}
+\caption{Figure this out later}
+\label{fig}
+\end{figure}
+
+\subsection{Discrete mixture of parametric distributions}
+In a parametric setting, forecasters may be permitted to submit a forecast as a
+discrete mixture. Such a distribution may be constructed in the same way as the
+ensemble described under Parametric distributions (\ref{eq:bma}) 
+where for $T$ distributions
+with pdfs $p_t(x)$ and $z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$
+
+\begin{equation}
+\label{eq:dmd}
+  p^{M} = \sum_{t=1}^T z_tp_t(x)
+\end{equation}
+
+Like the standard parametric model, a discrete mixture is easily evaluated with
+exisiting software (like distr R package \cite{camphausen2007distr}). And 
+scoring may be done by 
+using the LogS, CRPS and IS. The resolution of a discrete mixture is high 
+and the support need not be limited by submission requirements.
+
+A mixture distribution may be much more flexible than a simple parametric in 
+terms of distributional shape. But as it is essentially parametric, forecasters
+mays still be limited in how they construct their models. But it may be possible
+to fit a mixture distribution to probability models with the other 
+representations discussed. Further discussion on methods for fitting mixture 
+distributions to different types of model representations is included in this 
+paper.
+
+An ensemble model may be built by using (\ref{eq:bma}) only replacing $p_m$
+with $p^M$. Solving for weights may also be done similarly, though with the 
+added complexity of component models being mixture distributions, the 
+computation is likely to get more expensive. An example where this may be
+especially true is when minimizing of CRPS, but the exact mixture doesn't 
+result in CRPS in closed form \cite{baran2018combining}.
+
+Depending on the number of components a forecaster includes in a mixture 
+forecast, the amount of storage per forecast might be as little as for a 
+parametric forecast and as much as a forecast hub will allow. For modelers whose
+models produce distributions with irregular shapes, it may be that those
+distributions can be closely approximated by the right mixture distribution.
 

### 2022-02-24 draft2.tex
rough draft of sections 1, 2 and 3

@@
     \begin{adjustwidth}{-3cm}{-1cm}
-    \begin{tabular}{ | p{2.4cm} | p{2cm} | p{4cm} | p{3cm} | l |}
+    \begin{tabular}{ | p{2.4cm} | p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
     \hline
@@
 
-    Parametric & All methods & Limited to common distribution families 
-    &  & Low 3-6 values \\ \hline
-
-    Discretized bins & All methods, more computation required for some (CRPS) &
-    Any shape allowed, but limited to bin description and range & &
-    High
+    Parametric & LogS, CRPS, IS & Limited to common distribution families. 
+    Infinite resoution
+    & BMA & Low 3-6 values/prediction \\ \hline
+
+    Samples & CRPS and IS. LogS after smoothing & Any shape. Resolution may be
+    high but depends on sample size & BMA after smoothing. Resampling otherwise& 
+    Hundreds or thousands of values/prediction
     \\ \hline
 
-    Samples & Limited to CRPS and IS unless smoothing is performed & High & & 
-    Very high, thousands of values
+    Discretized bins & LogS, CRPS, IS &
+    Any shape allowed, but limited by binning scheme & BMA &
+    Depends on binning scheme but dozens to hundreds of values
     \\ \hline
 
-    Quantiles & IS, WIS & High & & Medium 
+    Quantiles & IS, WIS & Shape unknown but may still have much info with 
+    enough quantiles. No tail information & Quantile averaging & Depends on 
+    quantiles requested but dozens of values
     \\ \hline
 
-    Discrete Mixture & All methods, but may be limited by computation & 
-    High with proper approximation &
-    & Low-Medium
+    Discrete Mixture & LogS, CRPS, IS. May be more limited by computation & Can
+    take on many shapes/approximate most & BMA 
+    & 3 to limit values permitted
     \\ \hline

### 2022-02-28 code/ensemble_toy.R
Created new code foleder

@@ -1,0 +1,127 @@
+library(scoringutils)
+
+md1 <- distr::UnivarMixingDistribution(distr::Norm(1.5,1), 
+                                       distr::Norm(2,2),
+                                       mixCoeff = c(.3,.7))
+
+md2 <- distr::UnivarMixingDistribution(distr::Lnorm(2,1),
+                                       distr::Norm(2.1,1),
+                                       mixCoeff = c(.4,.6))
+
+md2 <- distr::Truncate(md2,lower=0,upper=4)
+
+pmd1 <- function(x) {p(md1)(x)}
+pmd2 <- function(x) {p(md2)(x)}
+
+
+crps_integrand <- function(x,dist,y) {(dist(x) - as.numeric(y <= x))^2}
+CRPS <- function(y,dist) {
+  int <- integrate(crps_integrand,-Inf,Inf,y,dist=dist)
+  return(int$value)
+}
+
+CRPS(pmd1,y=4)
+CRPS(pmd2,y=4)
+ens(lw1,x=4)
+CRPS(pmd1+.6*pmd2,y=2.2)
+
+ens <- function(lw1,x) {
+  w1 <- boot::inv.logit(lw1)
+  w2 <- 1-w1
+  p <- function(y) {w1*pmd1(y) + w2*pmd2(y)}
+  s <- CRPS(x,p)
+  return(s)
+}
+
+j <- integrate(dnorm,-Inf,Inf)
+test <- optim(fn=ens,par=c(12),x=4)
+optimize(f=CRPS,interval=c(-3,3),dist=pmd1)
+
+weight_ensemble <- function(w1,w2,x) {
+  ens <- w1*pmd1(x) + w2*pmd2(x)
+  return(ens)
+}
+
+optim()
+
+crps(y=2.2,family='normal',mean=0,sd=1)
+
+install.packages('scoringRules')
+
+crps(y=2.1,family='mixnorm',m=c(1,2),s=c(1,1),w=c(.5,.5))
+
+
+
+
+
+
+
+
+
+
+
+
+bruh(fn=ens,par=0,x=.5,lower=-30,upper=30,method='Brent')
+
+
+bruh <- function (par, fn, gr = NULL, ..., method = c("Nelder-Mead", 
+                                              "BFGS", "CG", "L-BFGS-B", "SANN", "Brent"), lower = -Inf, 
+          upper = Inf, control = list(), hessian = FALSE) 
+{
+  fn1 <- function(par) fn(par, ...)
+  gr1 <- if (!is.null(gr)) 
[…]

### 2022-02-28 code/makemixdist.R

@@ -1,0 +1,35 @@
+MakeDist <- function(distsdf){
+  
+  distdf <- distsdf[distsdf[,1] != 'Lst',]
+  tdist <- distsdf[distsdf[,1] == 'Lst',]
+  
+  fun_dist <- 
+    apply(distdf, FUN=function(x) {
+      paste('distr::',x[1], '(', 
+            ifelse(!is.na(x[2]) & (!is.na(x[3]) | !is.na(x[4])),
+                   paste(x[2],',',sep=''),
+                   ifelse(!is.na(x[2]) & is.na(x[3]) & is.na(x[4]),
+                          x[2], '')), 
+            ifelse(!is.na(x[3]) & !is.na(x[4]),
+                   paste(x[3],',',sep=''),
+                   ifelse(!is.na(x[3]) & is.na(x[4]), x[3],'')), 
+            ifelse(!is.na(x[4]),x[4],''), ')',sep='')
+    }, MARGIN = 1
+    )
+  
+  fun_tdist <- apply(tdist, FUN=function(x) {
+    paste0('distr::Td(',x[4],')*',x[3], '+', x[2])
+  }, MARGIN = 1
+  )
+  
+  dist_args <- paste(fun_dist, collapse=',',sep='')
+  tdist_args <- paste0(fun_tdist,collapse=',')
+  args <- ifelse(tdist_args!='',paste(dist_args,tdist_args,sep=','),dist_args)
+  
+  weights <- c(distdf[,5],tdist[,5])
+  mixString <- paste('distr::UnivarMixingDistribution(',
+                     args,',mixCoeff=weights)',sep='')
+  mixDist <- eval(parse(text=mixString))
+  
+  return(mixDist)
+}

### 2022-03-01 manuscript.tex
save manuscript

--- 2022-02-24 draft2.tex
@@
 
+\section{...}
+
+Tools for creating a discrete mixture distribution as well as constructing an 
+ensemble model from several mixture distributions are
+
+\subsection{Tools for a discrete mixture}
+
+\section*{MakeDist}
+The MakeDist function is applied function over an R dataframe and returns an 
+object of class "UnivarMixingDistribution"
+
+\subsection*{Usage}
+MakeDist(df)
+
+Variables of R dataframe to b used in making mixture distribution 
+\begin{center}
+    \begin{tabular}{ | l | p{4cm} | p{7cm} |}
+    \hline
+    Argument & Summary & Options \\ \hline
+    dist & A string specifying a distribution family.  & “Beta”, “Cauchy”, 
+    “Lnorm”, “Logis”, “Unif”, “Lst” (location scale t distribution), 
+    “Weibull”, “Fd”, “Norm”,  “Chisq”, 
+    “Gammad”, “Exp”
+	 “Binom”, “Dirac”, “Pois”, “Hyper”, “Nbinom”, “Geom” \\ \hline
+    param1 & A real number specifying the first parameter value of the 
+    distribution. & Beta: shape1; 
+	Cauchy: location; 
+	Lnorm: meanlog; 
+	Logis: location; 
+	Unif: min; 
+	Lst: location; 
+	Weibull: shape;
+	Fd: df1;
+	Norm: mean;
+	Chisq: df;
+	Gammad: scale;
+	Exp: rate; 
+	Binom: size;
+	Dirac: location;
+	Pois: lambda;
+	Hyper: m;
+	Nbinom: n;
+	Geom: prob
+     \\ \hline
+    param2 & A real number specifying the second parameter value of the 
+    distribution. & Beta: shape2; 
+	Cauchy: scale; 
+	Lnorm: slog; 
+	Logis: scale; 
+	Unif: Max; 
+	Lst: scale; 
+	Weibull: scale; 
+	Fd: df2; 
+	Norm: sd; 
+	Chisq: ncp; 
+	Gammad: shape; 
+	Binom: prob; 
+	Hyper: n; 
+	Nbinom: p \\
+    \hline
+    param3 & A real number specifying the third parameter value of the 
+    distribution. & Lst: df;
+	Hyper: k \\
+	\hline
+	weight & A real number between 0 and 1 specifying the weight given to the 
+	distribution in the overall mixture distribution. The sum of the weight 
+	column should equal 1. & ...
+	\\
+	\hline
+    \end{tabular}
+\end{center}
+
+\newpage
+% \begin{adjustwidth}{-3cm}{-1cm}
+\begin{center}
+% \caption{MakeDist parameter options}
+    \begin{tabular}{ l l  p{2cm}  p{2cm}  p{2cm}}
+    \hline
+    \textbf{Distribution} & \textbf{dist} & \textbf{param1} & \textbf{param2} & 
+    \textbf{param3} \newline \\ \hline
+    Beta & Beta & shape1 & shape2 &  \\ 
+    Cauch & Cauchy & location & scale &  \\
+    Log-normal & Lnorm & meanlog & slog &  \\
+    Logistic & Logis & location & scale &  \\
+    Uniform & Unif & min & max &  \\
+    Location Scale T & Lst & location & scale & df \\
+    Weibull & Weibull & shape & scale &  \\
+    F & Fd & df1 & df2 &  \\
+    Normal & Norm & mean & sd &  \\
+    Chisqure & Chisq & df &  &  \\
+    Gamma & Gammad & scale & shape &  \\
+    Exponential & Exp & rate &  &  \\
+    Binomial & Binom & size & prob &  \\
+    Dirac & Dirac & location &  &  \\
+    Poisson & Pois & lambda &  &  \\
+    Hypergeometric & Hyper & m & n & k \\
+    Negative binomial & Nbinom & n & p &  \\
+    Geometric & Geom & prob &  &  \\ \hline
+    \end{tabular}
+\end{center}
+% \end{adjustwidth}
+
 \newpage

### 2022-03-01 manuscript.tex
more additions to manuscript and references

@@
 \makeatother
-
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
 
@@
 \begin{table}[h!]
+\label{tab:pstor}
 \centering
@@
 \begin{table}[h!]
+\label{tab:dstor}
 \centering
-\label{tab:dbins}
  \begin{tabular}{|c|c|} 
@@
 \end{table}
-Submitted as a forecast prediction, the distribution in table \ref{tab:dbins} 
+Submitted as a forecast prediction, the distribution in table \ref{tab:dstor} 
 includes 82 pieces of data. For parts 
@@
 to fit a mixture distribution to probability models with the other 
-representations discussed. Further discussion on methods for fitting mixture 
+representations discussed. According to McLachlan and Peel, a finite mixture of 
+normal densities with common variance can be used to approximate abitrarily well
+any continuous distribution \cite{peel2000finite} (see also 
+\cite{nguyen2019approximations}). Thus, for any unconventional probability
+distribution -such as MCMC posterior samples- it may be reasonable to 
+approximate the distribution by a mixture of normals.
+Further discussion on methods for fitting mixture 
 distributions to different types of model representations is included in this 
@@
 
-Tools for creating a discrete mixture distribution as well as constructing an 
-ensemble model from several mixture distributions are
-
-\subsection{Tools for a discrete mixture}
-
-\section*{MakeDist}
-The MakeDist function is applied function over an R dataframe and returns an 
-object of class "UnivarMixingDistribution"
-
-\subsection*{Usage}
-MakeDist(df)
+The CDC and the COVID-19 Forecast Hub as well as other collaborative projects
+have their own established systems for receiving, 
+evaluating and constructing ensemble forecasts. A transition from using binned 
+distributions or quantile forecasts to using mixture distributions would require
+a few adjustments to those systems. In this section we outline how some of these
+adjustments may be implemented as well as present some tools which may be used
+to evaluate forecasts and construct ensemble forecasts from multiple models.
+
+\subsection{Submission format}
+For a collaborative forecast project to run smoothly, model submissions from all 
+modelers should all follow the same format. For both the CDC flu forecasting and
+the COVID-19 Forecast Hub, teams are provided a csv spreadsheet with columns 
+similar to those in tables \ref{tab:dstor} and \ref{tab:qstor}. Additionally
+columns for Location, Target, Type and Unit are included which serve as
+indicators of the specific prediction. The values for all variables except 
+Value come from a specified list from the forecast center. Value is the 
+probability assigned to a bin when the Type is Bin.
+
+\begin{table}[h!]
+\label{tab:dstan}
+\centering
+ \begin{tabular}{|c|c|c|c|c|c|}
+ \hline
+    Location & Target & Type & Unit & Bin & Value  \\ \hline
+    US National & Season Onset & Point & week & NA & . \\
+    US National & Season Onset & Bin & week & 0.0 & . \\
+    US National & Season Onset & Bin & week & 0.1 & . \\
+    ... & ... & ... & ... & ... & ... \\
+ \hline
+ \end{tabular}
+\end{table}
+
+For the quantile forecasts of the Forecast Hub, the possible values for Type 
+are Point and Quantile, and rather than using a Bin variable Quantile is used
+with values specified by the Hub. Then Value rather than a probability is the
+forecasted value for the specified quantile. Per prediction there may be a 
+couple dozen rows, up to 24 in the Forecast Hub, or over 100 rows as in some
+flu forecasts.
+
+An adjustment may be made to the format of table \ref{tab:dstan} where each row
+represents a compnonent in a mixture distribution.
+The variables Bin/Quantile and Value are removed and replaced with Family,
+Param1, Param2, Param3 and Weight where Family is the distribution family,
+Params are the parameters for the component distribution and Weight is the 
+weight $w_i$ for that component.
+
+\begin{table}[h!]
+\label{tab:mstan}
+\centering
+ \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+ \hline
+    Location & Target & Type & Unit & Family & Param1 & Param2 & Param3 & Weight
+    \\ \hline
+    US National & Season Onset & Dist & week & norm & mean & sd & NA & .  \\
+    US National & Season Onset & Dist & week & lnorm & meanlog & sdlog & NA & . \\
+    ... & ... & ... & ... & ... & ... & ... & ... & .\\
+ \hline
+ \end{tabular}
+\end{table}
+
+A forecast center may want to limit the number of components allowed per 
+prediction. For a reference, a mixture distribution prediction with 16 
+components would require $16 \times 9 = 144$ cells submitted. This is the same 
+number of cells
+submitted for a Forecast Hub forecast with 23 quantiles and a point prediction.
+
+\subsection{Mixture construction and scoring tools}
+
+From a submitted forecast, a prediction may be found by Location, Target and 
+Unit (or whatever other indication variables are used) and evaluated. We found
+the \texttt{distr} \cite{camphausen2007distr}
+useful for constructing a mixture distribution given
+information like that from table \ref{tab:mstan}.
+
+The function 
+\texttt{UnivarMixingDistribution} takes as arguments a list of distributions
+and a vector of weights for each distribution and a object pf a class called 
+\texttt{AbscontDistribution} is returned. Functions for density, distribution
+and quantile functions as well as for random sampling may then be used on the
+mixture distribution object for evaluation. Using those functions and the 
+created object, LogS and CRPS are easily calculable.
+
+We wrote a function \texttt{MakeDist} which takes on a data frame with variables
+Family, Param1, Param2, Param3 and Weight and returns a mixture distribution 
+of component distributions specified in the rows.
+
+\subsection{Ensemble construction}
+
+To construct an ensemble distribution from multiple mixture distributions, the 
+\texttt{UnivarMixingDistribution} is again a useful tool. Two or more 
+\texttt{AbscontDistribution} objects may be
 

### 2022-03-02 manuscript.tex
Include all references within a single \cite{}

@@
 on calibration, sharpness and scoring of a forecast pertains to parametric 
-distribution forecasts (see for example 
-\cite{gneiting2007probabilistic},
-\cite{gneiting2013combining} \cite{baran2018combining}).
+distribution forecasts
+\cite[see, e.g.]{gneiting2007probabilistic,gneiting2013combining,baran2018combining}).
 Other common representations include samples \cite{krueger2016probabilistic}, 

### 2022-03-08 manuscript.tex
beginning of discussion section and updated images

@@
 \usepackage{amsfonts}
+\usepackage{listings}
+\usepackage[svgnames]{xcolor}
+
+\lstset{language=R,
+    basicstyle=\small\ttfamily,
+    stringstyle=\color{DarkGreen},
+    otherkeywords={0,1,2,3,4,5,6,7,8,9},
+    morekeywords={TRUE,FALSE},
+    deletekeywords={data,frame,length,as,character},
+    keywordstyle=\color{blue},
+    commentstyle=\color{DarkGreen},
+}
 \makeatletter
@@
 \subsubsection{Parametric distributions}
+\label{section:pardist}
 A parametric distribution is a discrete or continuous probability distribution 
@@
 From a submitted forecast, a prediction may be found by Location, Target and 
-Unit (or whatever other indication variables are used) and evaluated. We found
+Unit (or whatever other indication variables are used by collaborators) and 
+evaluated. We found
 the \texttt{distr} \cite{camphausen2007distr}
@@
 and a vector of weights for each distribution and a object pf a class called 
-\texttt{AbscontDistribution} is returned. Functions for density, distribution
+\texttt{AbscontDistribution} is returned. The object is in essence a mixture
+distribution of the form from (\ref{eq:dmd}). Functions for density, 
+distribution
 and quantile functions as well as for random sampling may then be used on the
@@
 
-We wrote a function \texttt{MakeDist} which takes on a data frame with variables
+We wrote a function \texttt{MakeDist} (see appendix)
+which takes on a data frame with variables
 Family, Param1, Param2, Param3 and Weight and returns a mixture distribution 
@@
 To construct an ensemble distribution from multiple mixture distributions, the 
-\texttt{UnivarMixingDistribution} is again a useful tool. Two or more 
-\texttt{AbscontDistribution} objects may be
-
-Variables of R dataframe to b used in making mixture distribution 
-\begin{center}
-    \begin{tabular}{ | l | p{4cm} | p{7cm} |}
-    \hline
-    Argument & Summary & Options \\ \hline
-    dist & A string specifying a distribution family.  & “Beta”, “Cauchy”, 
-    “Lnorm”, “Logis”, “Unif”, “Lst” (location scale t distribution), 
-    “Weibull”, “Fd”, “Norm”,  “Chisq”, 
-    “Gammad”, “Exp”
-	 “Binom”, “Dirac”, “Pois”, “Hyper”, “Nbinom”, “Geom” \\ \hline
-    param1 & A real number specifying the first parameter value of the 
-    distribution. & Beta: shape1; 
-	Cauchy: location; 
-	Lnorm: meanlog; 
-	Logis: location; 
-	Unif: min; 
-	Lst: location; 
-	Weibull: shape;
-	Fd: df1;
-	Norm: mean;
-	Chisq: df;
-	Gammad: scale;
-	Exp: rate; 
-	Binom: size;
-	Dirac: location;
-	Pois: lambda;
-	Hyper: m;
-	Nbinom: n;
-	Geom: prob
+\texttt{UnivarMixingDistribution} is again a useful tool. The function takes 
+two or more
+\texttt{AbscontDistribution} or mixture distributions and a vector of weights 
+corresponding to each mixture. A new \texttt{AbscontDistribution} object is 
+returned as an ensemble of mixture distributions see (\ref{eq:bma}).
+
+At the onset of a collaborative forecast before the various models can be scored
+based on true observations, it may make sense to assign equal weight to each 
+component distribution in an ensemble. As a project progresses however, 
+assigning weights based on past performance may be desired. As mentioned in 
+section \ref{section:pardist}, weights may be selected by maximizing the
+likelihood of (\ref{eq:bma}) or by minimizing the CRPS. Another method of 
+selecting weights is to use the posterior model probability.
+
+If we have $T$ models ($M_t$) the posterior model probability of $M_t$ is 
+defined as
+
+\begin{equation}
+\label{eq:pmp}
+p(M_t|x) = \frac{p(x|M_t)p(M_t)}{p(x)}
+         = \frac{p(x|M_t)p(M_t)}{\sum_{k=1}^T p(x|M_k)p(M_k)}
+\end{equation}
+where $p(\cdot |M_t) := p_m(\cdot)$ is the density function of the model and 
+$p(M_j)$ is the prior probability assigned to the model. Where the prior
+probabilities for each model are equal or $p(M_t) = 1/T$ for all $t$ 
+(\ref{eq:pmp}) is reduced to
+
+\begin{equation}
+\label{eq:pmpeq}
+p(M_t|x) =  \frac{p(x|M_t)}{\sum_{k=1}^Tp(x|M_k)}
+\end{equation}
+
+The posterior model probability $p(M_t|x^*)$ for an already observed event $x^*$
+are then used as weights for a yet unrealized event being forecasted i.e.
+$w_t := p(M_t|x^*)$ see (\ref{eq:bma}).
+
+\subsection{Toy Example}
+
+In the following example, a toy example is given of constructing two  
+mixture distribution forecast prediction models from separate forecast 
+submissions. The tools presented in this section are used in \texttt{R} code to
+construct the distributions, build an ensemble consisting of both predictions 
+and score the different models. In building the ensemble forecast, weights are
+selected using the posterior model probability with equal prior probabilities
+for both models (\ref{eq:pmpeq}).
+
+Beginning with two forecast submissions of the form of table \ref{tab:mstan}, 
+say we select from each a prediction of an event for the same location, target
+and unit. The following two data frames \texttt{preddf1} and \texttt{preddf2}
+are the resulting predictions.
+
+\begin{table}[h!]
+\label{tab:preddf1}
+\centering
+ \begin{tabular}{|c|c|c|c|c|}
+ \hline
+    family & param1 & param2 & param3 & weight
     \\ \hline
-    param2 & A real number specifying the second parameter value of the 
-    distribution. & Beta: shape2; 
-	Cauchy: scale; 
-	Lnorm: slog; 
-	Logis: scale; 
-	Unif: Max; 
-	Lst: scale; 
-	Weibull: scale; 
-	Fd: df2; 
-	Norm: sd; 
-	Chisq: ncp; 
-	Gammad: shape; 
-	Binom: prob; 
-	Hyper: n; 
-	Nbinom: p \\
-    \hline
-    param3 & A real number specifying the third parameter value of the 
-    distribution. & Lst: df;
-	Hyper: k \\
-	\hline
-	weight & A real number between 0 and 1 specifying the weight given to the 
-	distribution in the overall mixture distribution. The sum of the weight 
-	column should equal 1. & ...
-	\\
+    Lnorm & 2 & 1 & NA & 0.3  \\
+    Norm & 2.1 & 1 & NA & 0.7 \\
  \hline
  \end{tabular}
-\end{center}
+\end{table}
+
+\begin{table}[h!]
+\label{tab:preddf2}
+\centering
+ \begin{tabular}{|c|c|c|c|c|}
+ \hline
+    family & param1 & param2 & param3 & weight
+    \\ \hline
+    Norm & 1.5 & 1 & NA & 0.4  \\
+    Norm & 4 & 2 & NA & 0.6 \\
+ \hline
+ \end{tabular}
+\end{table}
+
+The following code in \texttt{R} will construct mixture distributions, select
+weights for an ensemble based on an observed realization, build the ensemble and 
+score the forecasts using the
+LogS and the CRPS.
 
 \newpage
-% \begin{adjustwidth}{-3cm}{-1cm}
-\begin{center}
-% \caption{MakeDist parameter options}
-    \begin{tabular}{ l l  p{2cm}  p{2cm}  p{2cm}}
-    \hline
-    \textbf{Distribution} & \textbf{dist} & \textbf{param1} & \textbf{param2} & 
-    \textbf{param3} \newline \\ \hline
-    Beta & Beta & shape1 & shape2 &  \\ 
-    Cauch & Cauchy & location & scale &  \\
-    Log-normal & Lnorm & meanlog & slog &  \\
-    Logistic & Logis & location & scale &  \\
-    Uniform & Unif & min & max &  \\
-    Location Scale T & Lst & location & scale & df \\
-    Weibull & Weibull & shape & scale &  \\
-    F & Fd & df1 & df2 &  \\
-    Normal & Norm & mean & sd &  \\
-    Chisqure & Chisq & df &  &  \\
-    Gamma & Gammad & scale & shape &  \\
-    Exponential & Exp & rate &  &  \\
-    Binomial & Binom & size & prob &  \\
-    Dirac & Dirac & location &  &  \\
-    Poisson & Pois & lambda &  &  \\
-    Hypergeometric & Hyper & m & n & k \\
-    Negative binomial & Nbinom & n & p &  \\
-    Geometric & Geom & prob &  &  \\ \hline
-    \end{tabular}
-\end{center}
-% \end{adjustwidth}
+\begin{lstlisting}[language=R]
+
+preddf1
+#  family param1 param2 param3 weights
+#1  Lnorm    2.0      1     NA     0.3
+#2   Norm    2.1      1     NA     0.7
+
+preddf2
+#  family param1 param2 param3 weights
+#1   Norm    1.5      1     NA     0.4
+#2   Norm    4.0      2     NA     0.6
+
+#make mixture distributions from prediction submissions
+mdist1 <- MakeDist(preddf1)
+mdist2 <- MakeDist(preddf2)
+
+#make pdfs for mixture predictions
+dmdist1 <- function(x) {distr::d(mdist1)(x)}
+dmdist2 <- function(x) {distr::d(mdist2)(x)}
+
+#make cdfs for mixture predictions
+pmdist1 <- function(x) {distr::p(mdist1)(x)}
+pmdist2 <- function(x) {distr::p(mdist2)(x)}
+
+#realized observation
+ob <- 3
+
+#posterior model probability for calculating weights
+w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
+w2 <- 1-w1
+#w1 => 0.5286434
+#w1 => 0.4713566
+
+#build ensemble with calculated weights
+ensdist <- distr::UnivarMixingDistribution(mdist1,
+                                           mdist2,
+                                           mixCoeff = c(w1,w2))
+
+#pdf and cdf for ensemble
+densdist <- function(x) {(distr::d(ensdist)(x))}
+pensdist <- function(x) {(distr::p(ensdist)(x))}
+
+#LogS for predictions at the realized observation
+-log(dmdist1(ob)) # => 1.547238
+-log(dmdist2(ob)) # => 1.848796
+-log(densdist(ob)) # => 1.678156
+
+#CRPS for predictions at the realized observation
+CRPS(pmdist1,y=ob) # => 0.6348212
+CRPS(pmdist2,y=ob) # => 0.5306083
+CRPS(pensdist,y=ob) # => 0.5486368
+\end{lstlisting}
+
+Figure \ref{figmixs} below shows the density plots for each of the two mixture
+distribution forecasts and the ensemble from the toy example.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.15]{mix_dists.png}}
+\caption{Figure this out later}
+\label{figmixs}
+\end{figure}
+
+\section{Discussion}
+
+In this paper we have reviewed four representation types commonly used in
+probabilistic 
+forecasting including proper scoring, data storage and ensemble model 
+construction for each type. We presented the discrete mixture distribution
+representation and argue that in terms of model flexibility, storage and 
+ensemble building it is
+comparable to discretized bins and interval forecasts but also provides a 
+forecast with a continuous nominal resolution. Thus we advocate its use in
+future forecasting projects like those done by the CDC and COVID-19 Forecast 
+Hub.
+
+% Variables of R dataframe to b used in making mixture distribution 
+% \begin{center}
+%     \begin{tabular}{ | l | p{4cm} | p{7cm} |}
+%     \hline
+%     Argument & Summary & Options \\ \hline
+%     dist & A string specifying a distribution family.  & “Beta”, “Cauchy”, 
+%     “Lnorm”, “Logis”, “Unif”, “Lst” (location scale t distribution), 
+%     “Weibull”, “Fd”, “Norm”,  “Chisq”, 
+%     “Gammad”, “Exp”
+% 	 “Binom”, “Dirac”, “Pois”, “Hyper”, “Nbinom”, “Geom” \\ \hline
+%     param1 & A real number specifying the first parameter value of the 
+%     distribution. & Beta: shape1; 
+% 	Cauchy: location; 
+% 	Lnorm: meanlog; 
+% 	Logis: location; 
+% 	Unif: min; 
+% 	Lst: location; 
+% 	Weibull: shape;
+% 	Fd: df1;
+% 	Norm: mean;
+% 	Chisq: df;
+% 	Gammad: scale;
+% 	Exp: rate; 
+% 	Binom: size;
+% 	Dirac: location;
+% 	Pois: lambda;
+% 	Hyper: m;
+% 	Nbinom: n;
+% 	Geom: prob
+%      \\ \hline
+%     param2 & A real number specifying the second parameter value of the 
+%     distribution. & Beta: shape2; 
+% 	Cauchy: scale; 
+% 	Lnorm: slog; 
+% 	Logis: scale; 
+% 	Unif: Max; 
+% 	Lst: scale; 
+% 	Weibull: scale; 
+% 	Fd: df2; 
+% 	Norm: sd; 
+% 	Chisq: ncp; 
+% 	Gammad: shape; 
+% 	Binom: prob; 
+% 	Hyper: n; 
+% 	Nbinom: p \\
+%     \hline
+%     param3 & A real number specifying the third parameter value of the 
+%     distribution. & Lst: df;
+% 	Hyper: k \\
+% 	\hline
+% 	weight & A real number between 0 and 1 specifying the weight given to the 
+% 	distribution in the overall mixture distribution. The sum of the weight 
+% 	column should equal 1. & ...
+% 	\\
+% 	\hline
+%     \end{tabular}
+% \end{center}
+
+% \newpage
+% % \begin{adjustwidth}{-3cm}{-1cm}
+% \begin{center}
+% % \caption{MakeDist parameter options}
+%     \begin{tabular}{ l l  p{2cm}  p{2cm}  p{2cm}}
+%     \hline
+%     \textbf{Distribution} & \textbf{dist} & \textbf{param1} & \textbf{param2} & 
+%     \textbf{param3} \newline \\ \hline
+%     Beta & Beta & shape1 & shape2 &  \\ 
+%     Cauch & Cauchy & location & scale &  \\
+%     Log-normal & Lnorm & meanlog & slog &  \\
+%     Logistic & Logis & location & scale &  \\
+%     Uniform & Unif & min & max &  \\
+%     Location Scale T & Lst & location & scale & df \\
+%     Weibull & Weibull & shape & scale &  \\
+%     F & Fd & df1 & df2 &  \\
+%     Normal & Norm & mean & sd &  \\
+%     Chisqure & Chisq & df &  &  \\
+%     Gamma & Gammad & scale & shape &  \\
+%     Exponential & Exp & rate &  &  \\
+%     Binomial & Binom & size & prob &  \\
+%     Dirac & Dirac & location &  &  \\
+%     Poisson & Pois & lambda &  &  \\
+%     Hypergeometric & Hyper & m & n & k \\
+%     Negative binomial & Nbinom & n & p &  \\
+%     Geometric & Geom & prob &  &  \\ \hline
+%     \end{tabular}
+% \end{center}
+% % \end{adjustwidth}
 

### 2022-03-08 code/ensemble_toy.R

@@ -1,29 +1,29 @@
 library(scoringutils)
 
 md1 <- distr::UnivarMixingDistribution(distr::Norm(1.5,1), 
-                                       distr::Norm(2,2),
-                                       mixCoeff = c(.3,.7))
+                                       distr::Norm(4,2),
+                                       mixCoeff = c(.4,.6))
 
 md2 <- distr::UnivarMixingDistribution(distr::Lnorm(2,1),
                                        distr::Norm(2.1,1),
-                                       mixCoeff = c(.4,.6))
+                                       mixCoeff = c(.3,.7))
 
 md2 <- distr::Truncate(md2,lower=0,upper=4)
 
-pmd1 <- function(x) {p(md1)(x)}
-pmd2 <- function(x) {p(md2)(x)}
+pmd1 <- function(x) {distr::p(md1)(x)}
+pmd2 <- function(x) {distr::p(md2)(x)}
+dmd1 <- function(x) {distr::d(md1)(x)}
+dmd2 <- function(x) {distr::d(md2)(x)}
 
+(pmd1(2.2)*.5)/(.5*(pmd1(2.2)+pmd2(2.2)))
+(pmd2(2.2)*.5)/(.5*(pmd1(2.2)+pmd2(2.2)))
 
 crps_integrand <- function(x,dist,y) {(dist(x) - as.numeric(y <= x))^2}
+
 CRPS <- function(y,dist) {
   int <- integrate(crps_integrand,-Inf,Inf,y,dist=dist)
   return(int$value)
 }
-
-CRPS(pmd1,y=4)
-CRPS(pmd2,y=4)
-ens(lw1,x=4)
-CRPS(pmd1+.6*pmd2,y=2.2)
 
 ens <- function(lw1,x) {
   w1 <- boot::inv.logit(lw1)
@@ -33,8 +33,25 @@ ens <- function(lw1,x) {
   return(s)
 }
 
-j <- integrate(dnorm,-Inf,Inf)
-test <- optim(fn=ens,par=c(12),x=4)
+test <- optim(fn=ens,par=c(12),x=3)
+w1 <- inv.logit(test$par)
+w2 <- 1- w1
+
+ense <- distr::UnivarMixingDistribution(md1,md2,mixCoeff = c(w1,w2))
+pense <- function(x) {distr::p(ense)(x)}
[…]

### 2022-03-12 manuscript.tex
discussion additions
abstract added and some pictures updated

@@
 % otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
+% \makeatletter
+% \def\maxwidth{ %
+%   \ifdim\Gin@nat@width>\linewidth
+%     \linewidth
+%   \else
+%     \Gin@nat@width
+%   \fi
+% }
+% \makeatother
 
@@
 \makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+% \newenvironment{kframe}{%
+%  \def\at@end@of@kframe{}%
+%  \ifinner\ifhmode%
+%   \def\at@end@of@kframe{\end{minipage}}%
+%   \begin{minipage}{\columnwidth}%
+%  \fi\fi%
+%  \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+%  \colorbox{shadecolor}{##1}\hskip-\fboxsep
+%      % There is no \\@totalrightmargin, so:
+%      \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+%  \MakeFramed {\advance\hsize-\width
+%    \@totalleftmargin\z@ \linewidth\hsize
+%    \@setminipage}}%
+%  {\par\unskip\endMakeFramed%
+%  \at@end@of@kframe}
+% \makeatother
+
+% \definecolor{shadecolor}{rgb}{.97, .97, .97}
+% \definecolor{messagecolor}{rgb}{0, 0, 0}
+% \definecolor{warningcolor}{rgb}{1, 0, 1}
+% \definecolor{errorcolor}{rgb}{1, 0, 0}
+% \newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
 
@@
 \begin{document}
+
+\section*{Abstract}
+
+Collaboration among multiple teams has played a major role in probabilistic
+forecasting of influenza outbreaks, the COVID-19 pandemic, other disease
+outbreaks and problems in other fields. When collecting forecasts from 
+individual teams, ensuring that each team's model represents forecast
+uncertainty according to the same format allows for direct comparison of 
+forecasts as well as methods of constructing multi-model ensemble forecasts.
+This paper outlines several common probabilistic forecast formats including
+probability density functions, samples, binned distributions and  quantile 
+forecasts and compares
+their usage within the context of collaborative projects. The discrete mixture
+distribution forecast format is presented as an attractive alternative to the 
+former formats due to the flexibility such a forecast may have in shape as well
+as the relatively low loss of information due to limited computer storage.
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[scale=.4]{dens_comp.png}}
+\centerline{\includegraphics[scale=.1]{dens_comp.png}}
 \caption{Figure this out later}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[scale=.4]{cum_comp.png}}
+\centerline{\includegraphics[scale=.1]{cum_comp.png}}
 \caption{Figure this out later}
@@
 construction for each type. We presented the discrete mixture distribution
-representation and argue that in terms of model flexibility, storage and 
+representation and we argue that its use in collaborative probabilistic 
+forecasting is preferable to the other representations.
+In terms of model flexibility, storage and 
 ensemble building it is
@@
 Hub.
+
+For a number of reasons, the adoption of finite mixture distributions as the
+submission format may face hurdles. A forecast hub, along with modelers, using a 
+different representation may simply not want to break from tradition. The 
+implementation of new scoring and ensemble construction methods may be a 
+barrier. One aspect of ensemble construction which received little attention in 
+this paper is the selection of weights for components of an ensemble where each
+of the components is mixture distribution. Computing requirements could become a
+concern in such a problem and further research on this may provide
+ideas of best methods for weight selection.
+
+Another area of recommended research is the use of joint distributions for 
+forecasting. We have only considered here probabilistic forecasting of one 
+event at a time. Number of new infections in one week at one specific location
+for example. This forecast is presented as a marginal distribution for that 
+specific target, time and location. A joint distribution for forecasting 
+multiple targets, times or locations may sometime be desirable and may require
+further consideration on how joint mixture distributions could be used as a 
+format in collaboration.
 

### 2022-03-12 code/make pictures.R

@@ -1,140 +1,0 @@
-
-source('~/Documents/GitTest/mixture_distributions_for_forecasting/simulate_functions.R')
-
-
-set.seed(168)
-# lnorm_params <- getLnormParams(par=c(3,1))
-lnorm_params <- c(1,.4)
-
-x <- seq(0,8,length.out = 1001)
-# y <- dlnorm(x,lnorm_params[1],lnorm_params[2])
-
-y <- EnvStats::dlnormTrunc(x,meanlog = lnorm_params[1],
-                           sdlog = lnorm_params[2],min = x[1],
-                           max=x[length(x)])
-
-yp <- EnvStats::plnormTrunc(x,meanlog = lnorm_params[1],
-                                 sdlog = lnorm_params[2],min = x[1],
-                                 max=x[length(x)])
-
-par(mfrow=c(2,2))
-plot(y~x,col='blue',type='l',main='(a)',
-     ylab = 'p(x)')
-
-wid <- .2
-lnbins <- seq(0,8,by=wid)
-disc_lnorm <- discretizeDist(bins=lnbins,par=lnorm_params,
-                             family='trlnorm',nu=NA)
-
-lnorm_samp <- EnvStats::rlnormTrunc(1000,meanlog = lnorm_params[1],
-                                    sdlog = lnorm_params[2],min = x[1],
-                                    max=x[length(x)])
-hist(lnorm_samp,main='(b)',xlab='x',border='purple',axes=TRUE)
-box()
-
-secdf <- ecdf(lnorm_samp)
-
-
-outl <- disc_lnorm$bins
-plot((disc_lnorm$probs*5)~disc_lnorm$bins,type='s',col='red',xlab='x',lwd=1.5,
-     ylab='Prob',main='(c)')
-lines((disc_lnorm$probs*5)~outl,type='h',col='black')
-lines((disc_lnorm$probs*5)~outl,type='h',col='red')
-
-
-
-quant_23 <- c(0.010, 0.025, 0.050, 0.100, 0.150, 0.200, 0.250, 0.300, 0.350, 
-              0.400, 0.450, 0.500, 0.550, 0.600, 0.650, 0.700,
-              0.750, 0.800, 0.850, 0.900, 0.950, 0.975, 0.990)
-
-quant_7 <- c(0.025, 0.100, 0.250, 0.500, 0.750, 0.900, 0.975)
-quants <- quant_23
-
[…]

### 2022-03-23 manuscript.tex
updates to manuscript

@@
-\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass{article}
+% \usepackage[]{graphicx}\usepackage[]{color}
 % maxwidth is the original width if it is less than linewidth
@@
 \usepackage[svgnames]{xcolor}
+\usepackage{graphicx}
+\usepackage{subfig}
+% \usepackage{geometry}
+% \geometry{legalpaper, margin=1in}
 
@@
 \cite{gneiting2014probabilistic}. Specific problems for 
-which probabilistic forecasts is used include weather forecasting
+which probabilistic forecasting is used include weather forecasting
 \cite{baran2018combining}, economics \cite{groen2013real} and disease outbreaks
@@
 A probabilistic forecast is a forecast to which probabilities are assigned to 
-various possible outcomes. There are a number of ways the probabilities or 
+various possible outcomes. There are a number of ways whereby probabilities or 
 uncertainty may be represented. A common representation is either a continuous 
 or
-discrete parametric distribution function (a pdf or pmf). Much of the literature 
+discrete parametric distribution, given as a probability density/mass function 
+(pdf/pmf). Much of the literature 
 on calibration, sharpness and scoring of a forecast pertains to parametric 
 distribution forecasts
-\cite[see, e.g.]{gneiting2007probabilistic,gneiting2013combining,baran2018combining}).
+\cite[see, e.g.]{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
 Other common representations include samples \cite{krueger2016probabilistic}, 
-discretized bins 
+discretized bins \cite{mcgowan2019collaborative}
 and quantile or interval type forecasts \cite{taylor2021evaluating} 
@@
 appropriate than the others for a given problem but knowing how to interpret, 
-score and contruct ensemble forecasts for a selected representation is a must 
-when multiple forecasts of the same event are involved.
-
-Two projects on forecasting disease outbreaks for which many separate forecasts 
-are used include the United States Center for Disease Control (CDC) hosted
-annual competition for forecasting influenza \cite{cdcflusight}
+score and contruct ensemble forecasts for a selected representation is essential
+when multiple teams collaborate in the same forecasting project.
+
+Two collaborative projects on forecasting disease outbreaks for which many 
+separate forecasts 
+are used include the United States Centers for Disease Control (CDC) hosted
+annual competition for forecasting influenza ??\cite{cdcflusight}
 and the COVID-19 Forecast Hub which has 
@@
 for the different targets also include predictions for one, two, three and 
-four weeks ahead of the prediction time. National flu data is weekly provided 
-to outside academic teams who use that data to construct forecasts however they
-will, but the forecast predictions are always submitted in a discretized bin
-format. Here the binning scheme was on a bounded numeric scale and the 
+four weeks ahead of the prediction time. National flu data is provided weekly 
+to outside academic teams who use that data to construct forecasts using 
+whatever methods they choose. Historically, the forecast predictions must be 
+submitted 
+in a discretized bin
+format. During previous fluw seasons the binning scheme was on a bounded numeric 
+scale and the 
 prediction of a specific target was a set of probabilities assigned to each bin
@@
 parties a chance to collaborate and improve forecasting each season. One 
-proposed way to enhance prediction has been to aggregate the various by team
+proposed way to enhance prediction has been to aggregate the various teams'
 forecasts into a multi-model ensemble forecast \cite{mcgowan2019collaborative}
@@
 models into one model which often yields better predicting power than the 
-individual models \cite{cramer2021evaluation} (and did lead to better average 
-results with flu competition forecasts in \cite{reich2019accuracy}.) 
+individual models \cite{cramer2021evaluation}. Such an ensemble made from 
+multiple influenza competition forecasts did in fact outperform the individual 
+component models \cite{reich2019accuracy}.
 In the COVID-19 Forecast Hub, construction of ensemble forecasts is a main
@@
 
-% Ensemble building has a history in dynamical weather 
-% prediction \cite{lewis2005roots}. In weather forecasting, individual members of 
-% an ensemble are generated from perturbations of initial conditions, see Baran 
-% section 2. Data \cite{baran2018combining} \cite{leutbecher2008ensemble}.
-% \cite{yamana2016superensemble}
-
 \subsection{COVID-19 Forecast Hub}
-In March 2020, at the onset of the COVID-19 pandemic, the Reich Lab in
-association with others founded the COVID-19 Forecast Hub. Borrowing on work and 
-ideas from the CDC annual competition, the Forecast Hub is a central site in 
+In March 2020, at the onset of the COVID-19 pandemic, the COVID-19 Forecast Hub
+was founded. Borrowing on work and 
+ideas from the CDC influenza competition, the Forecast Hub is a central site in 
 which dozens of academic teams collaborate to forecast the ongoing COVID-19 
@@
 forecasts and the ensemble are passed along to the CDC for its use in official
-communication \cite{Cramer2021-hub-dataset}.
+communication \cite{Cramer2021-hub-dataset} see Figure \ref{fig:cdcoff}.
 
@@
 for over one-hundred straight weeks. 
-As well due to the initial lack of understanding of COVID-19 and the time 
+As well due to the initial lack of understanding of the COVID-19 virus and the 
+time 
 pressure of
 creating forecasts, rather than requesting forecasts as binned probabilities
-the forecasts were requested as the predictive mean and 
+the forecasts were requested as the predictive median and 
 predictive intervals for various nominal levels depending on the target to be
 predicted \cite{bracher2021evaluating}. Collecting forecasts in this quantile
-or interval type brings with it differences in how to score, construct ensemble
-models and store the forecasts along with other considerations.
+or interval type format brings with it differences in how to score, construct 
+ensemble
+models and store the forecasts among other differences.
 
@@
 \centerline{\includegraphics[scale=.12]{8_30_21_cvd_deaths.jpeg}}
-\caption{Figure this out later}
-\label{fig}
+\caption{This graphic was published on cdc.gov as official public communication 
+by the CDC shows forecast models for national new weekly deaths due to COVID-19 
+in the top row and cumulative deaths on the bottom row. The plots in the left 
+column show prediction intervals from multiple teams whereas the plots on the 
+right show the intervals for an ensemble forecast model.}
+\label{fig:cdcoff}
 \end{figure}
 
-\subsection{...}
+\subsection{}
 In the context of collaborative forecasting like that of the CDC flu competition
@@
 proven useful and effective. Yet both types come with their drawbacks. Data 
-storage for instance might be a concern if many bins are allowed for a 
-prediction. And scoring methods are limited if forecasts are made of quantiles.
+storage for instance might be a concern if many bins are used for forecasting. 
+And scoring methods are limited if forecasts are made of prediction intervals.
 
@@
 Forecast Hub. In section 2, popular probabilistic forecast representation 
-types will be defined and reviewed. Methods of scoring, storing, building 
+types are defined and reviewed. Methods of scoring, storing, building 
 ensembles and other aspects will be reviewed and compared for each 
@@
 
-Before introducing discrete mixture distributions as a candidate for a
+Before introducing discrete mixture distributions as a representation type for a
 probabilistic forecast, we review representations already commonplace in 
@@
 
-\subsection{Considerations...}
+\subsection{Things to consider}
 \subsubsection{Scoring}
-Scoring rules are used to evaluate numerically a probability forecast. The
-score is a measure on the accuracy of the forecast and where multiple forecasts
-exist may provide a rank for each relative to the others. If a scoring rule is 
-proper, then the highest possible reward is obtained by reporting the true 
+Scoring rules are used to numerically evaluate or score a probability forecast. 
+The
+score is a measure of the accuracy of the forecast and where multiple forecasts
+exist the score for each may be used to compare forecasts. If a scoring rule 
+is proper, then the best possible score is obtained by reporting the true 
 distribution. The rule is strictly proper if that value is unique. 
@@
 submission \cite{gneiting2007strictly}. This makes proper scoring rules ideal
-for grading forecasts. We will limit our review of scoring methods to rules
+for evaluating forecasts. We will limit our review of scoring methods to rules
 which are proper.
@@
 \subsubsection{Storage}
-For a forecast hub collecting many predictions, computer storage is something
-that needs to be addressed. For a project involving many researchers, the 
-number of forecast predictions can add up. For example, the repository for the
-COVID-19 Forecast Hub predictions contained 85.4 million predictions as of 
-February 5, 2022! (cite zoltar??)
+For a collaborative forecast project where many researchers are involved and 
+many predictions are collected, computer storage may be something
+that needs to be addressed. As an example of required computer storage, the 
+repository for the
+COVID-19 Forecast Hub predictions contained 85 million predictions as of 
+February 5, 2022 which required more than 11.6 gigabytes of storage!
+(cite zoltar??)
 When determining the goals of a forecast project, there should be consideration 
-of the storage required for different representations.
+of the storage required for different forecast representation types.
 
@@
 A multi-model ensemble is a statistical model made by combining information from
-2 or more individual statistical models. Private and public decisions are 
+two or more individual statistical models. Private and public decisions are 
 regularly made after combining information from multiple sources. For any given
-situation, information from one source may shed light on a subject which other
-sources fail to capture. Likewise one statistical model may provide perspective
+situation, information from one source may provide insight on a subject which 
+other
+sources fail to capture. Likewise one statistical model may provide insight
 that another model does not, so that when they are combined in an ensemble the 
-resulting model is superior.
+ensemble model outperforms the individual components.
 
@@
 Multi-model ensembles allow for an incorporation of multiple signals -
-often from differing data sources- and for individual model biases being canceled
-out or reduced by biases in others (\cite{reich2019accuracy} see references
+often from differing data sources- and sometimes individual model biases are 
+canceled
+out or reduced by biases in others (\cite{reich2019accuracy} ??see references
 therein). 
@@
 
-\subsection{Representations}
+\subsection{Probabilistic Forecast Representation Types}
 \subsubsection{Parametric distributions}
@@
 on $x$ in the space of the random variable. In the continuous case 
-$P(D = x) = 0$ for all $x$, but the probability 
+$P(X = x) = 0$ for all $x$, but the probability 
 that $X$ falls within an interval $(a,b)$ is calculated as
@@
 \begin{equation}
+\label{eq:prob}
   P(a < X < b) = \int_a^b p(x) dx
@@
 \begin{equation}
+\label{eq:ccdf}
   F_X(x) = P(X \leq b) = \int_{-\infty}^x p(t) dt
@@
 \begin{equation}
+\label{eq:quant}
   Q(p) = \inf \{ y \in \mathbb{R} : p \leq F_X(x) \}
@@
 \cite{alves2013ncep} and the interval/Brier 
-score \cite{gneiting2007strictly} among 
+score (IS) \cite{gneiting2007strictly} among 
 others. See also \cite{gneiting2014probabilistic}
@@
 \begin{equation}
+\label{eq:logs}
   LS(p_m,x*) = -log\;p_m(x^*)
 \end{equation}
-The goal is to minimize the LogS, so that a forecast $p{'}_m(x^*)$ is deemed 
+The goal is to minimize the LogS, so that a forecast $p^{'}_m(x^*)$ is considered 
 superior to $p_m$ if
-$LS(p{'}_m, x^*) < LS(p_m, x^*)$.
-The LogS is strictly limited to scoring forecasts with density functions and
+$LS(p^{'}_m, x^*) < LS(p_m, x^*)$.
+The LogS is limited to scoring forecasts with density functions and
 evaluating those densities only at the point $x^*$.
@@
 and so 
-can be used a bit more extensively than the LogS which is limited to 
-distributions which carry a density. For the CDF $F_m$, the CRPS is defined as
+can be used a more extensively than the LogS. 
+For the CDF $F_m$, the CRPS is defined as
 
@@
 
-Besides evaluating forecasts, the CRPS is also used in optimizing weights used
-to build ensembles. Considered the state-of-the-art techniques for combining 
+Besides evaluating forecasts, the CRPS may also be used for optimizing weights 
+used
+to build ensembles using Bayesian model averaging (BMA). Considered the state-of-the-art techniques for combining 
 component distributions
 into a multi-model ensemble are nonhomogeneous regression (NR), also known as
-ensemble model output statistics (EMOS), and ensemble Bayesian model averaging
-(BMA), both of which will be defined as in \cite{gneiting2014probabilistic}.
+ensemble model output statistics (EMOS), and ensemble
+BMA, both of which are defined in \cite{gneiting2014probabilistic}.
 
 In the context of an ensemble made from component models submitted from various
-sources, contructed with different methods and with potentially different data,
+sources,
 BMA is the better option. In BMA, the final model does not have to be specified
 beforehand and the resulting forecast will be a discrete mixture distribution
-of all component forecasts. The general form for the ensemble distribution $p^E$
+of all component forecasts. The general form for an ensemble distribution $p^E$
 is
@@
 \label{eq:bma}
-  p^E(x) = \sum_{jm=1}^M w_mp_m(x)
-\end{equation}
-where $p_m$ is the $j^{th}$ component forecast distribution and 
-$0 \leq w_m \leq 1$ is a weight assigned to each component where $\sum w_m = 1$.
+  p^E(x) = \sum_{m=1}^M w_mp_m(x)
+\end{equation}
+where $p_m$ is the $m^{th}$ component forecast distribution and 
+$0 \leq w_m \leq 1$ is a weight assigned to that component where $\sum w_m = 1$.
 Methods for estimating weights include Maximum Likelihood estimation
@@
 of weights)
-and minimizing the CRPS as in 
+and minimizing the ensemble CRPS as in 
 \cite{baran2018combining}.
@@
 Generally computation and evaluation of parametric distributions is not hard. 
-For most commonly used parametric distributions -Normal, Lognorm, Poisson,
+For most commonly used parametric distributions -Normal, Lognormal, Poisson,
 Gamma, etc.- there is software readily available to compute density, 
 distribution and quantile values. Likewise, requirements for storage are low 
-compared to other uncertainty representations we will discuss. The most common
+compared to other representation types that will be discussed. The most common
 parametric distributions can be fully defined with three or pieces of data.
-The distribution family and two or three parameters. Below shows a table with
+The distribution family and two or three parameters. Table \ref{table:pstor} 
+contains
 enough information to completely define a $Lognormal(1,0.4)$ distribution.
@@
 \begin{table}[h!]
-\label{tab:pstor}
+
 \centering
@@
  \hline
- Family & param1 & param2 \\ [0.5ex] 
+ family & param1 & param2 \\ [0.5ex] 
  \hline
@@
  \end{tabular}
+ \caption{lognormal distribution with parameters $\mu = $ 1 and $\sigma =$ 0.4}
+ \label{table:pstor}
 \end{table}
@@
 \subsubsection{Sample Distributions}
-Some forecast model builders may want more flexibility than a parametric 
-distribution can provide. Some methods such as sampling from a posterior 
-distribution or resampling methods like Bootstrap will produce forecasts of
-sample distributions.
-
-A sample distribution is built of a sample of random variables 
+Some forecast model builders may want more flexibility in modeling than a 
+parametric 
+distribution can provide. Methods that require sampling from a posterior 
+distribution or Bootstrap sampling to obtain a sample distribution are examples
+where parametric distributions may not be appropriate for modeling.
+
+A sample distribution is made of a sample of random variables 
 $(X_1,...,X_n)$ where $X_i \sim D$ and $D$ is a distribution. From this, sample
@@
 According to the Strong Law of Large numbers, the sample mean will converge to
-the expected value of distribution as $n \rightarrow \infty$ as long as the 
+the expected value of the distribution as $n \rightarrow \infty$ as long as the 
 expected value of that distribution exists. Likewise by the same law the 
@@
 distribution function as $n \rightarrow \infty$. Thus, if a sufficiently large 
-sample is generated from a distribution, the sample will closely approximate the 
+sample is generated from a distribution with an expectation, 
+the sample will closely approximate the 
 true distribution.
@@
 For common distribution families it is easy to generate large samples using 
-existing functions in R and other programming platforms. For some distributions 
+existing functions in \texttt{R} and other programming platforms. For some 
+distributions 
 for which the mathematical formula is unkown or is not in closed form, more 
@@
 So the options that a researcher has for constructing a forecast are more than
-if they are asked to submit a parametric distribution and the characterisitcs 
-and potential shapes of distributions is much larger.
+if they are asked to submit a parametric distribution and the range 
+characterisitcs 
+and shapes of distributions is larger.
 In the last few decades, increased computing power and improvements in MCMC
 sampling have greatly contributed to growth in the use of
-predictive distributions \cite{gneiting2007strictly}. (See examples listed in
+predictive distributions \cite{gneiting2007strictly}. ??(See examples listed in
 \cite{krueger2016probabilistic}).
@@
 and LogS may be used. The CRPS has the advantage here of scoring the sample 
-distribution directly since the CDF in  (\ref{eq:crps}) may be replaced by 
+distribution directly since the CDF in  (\ref{eq:crps}) may be replaced by the 
+ECDF 
 (\ref{eq:ecdf}). To use the LogS to score a forecast, a density function for the 
@@
 construction from (\ref{eq:bma}) would work only replacing $p_m$ with 
-$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$. Here as well the optimal weights 
+$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$ -approximate KD and GA densities. 
+Here as well the optimal weights 
 $w_m$ may be estimated by maximizing the likelihood or minimizing CRPS. Then 
@@
 
-\subsection{Discretized bin distributions}
+\subsubsection{Discretized bin distributions}
 An alternative to parametric distributions and sample distributions which allows
-for high flexibility in distribution shape but is more manageable in terms of 
-storage is a discretized bin distribution.
+for higher flexibility in distribution shape than a parametric distribution and 
+will usually require less storage space than samples is a discretized bin 
+distribution.
 
@@
 where $B_i = [b_{i-1}, b_i)$ and $\cup_{i=1}^{K} B_i = A$. Based on the problem
-to be forecasted, a forecast hub will determine the possible values for $A$ and 
-select the number of bins and the sizes for each. It may be the case
+to be forecasted, researchers will determine the possible range $A$ and 
+select the number of bins and the sizes for each bin. It may be the case
 that a forecast hub will set the width of all bins to be equal so that 
@@
 $\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$. The 
-cumulative distribution may be
+cumulative distribution may be calculated as
 
@@
 
-The CDC has used a discretized distribution representation as the representation
+The CDC has used a discretized bin distribution representation as the 
+representation
 for their annual influenza forecasting competition and other disease outbreaks.
 In that context it has become the standard representation 
-\cite{brooks2020comparing}. A decent amount of work has been done in evaluating 
+\cite{brooks2020comparing}. Much work has been done in evaluating 
 and constructing ensemble models on influenza forecasts represented by 
@@
 construction. Reich et. al used BMA to combine multiple forecasts from the flu 
-competition. There built and compared ensemble models with different weighting
+competition. They built and compared ensemble models with different weighting
 schemes including equally weighted components $w_j = 1/J$ and estimating weights
@@
 In the CDC flu contest, a forecast could have 131 bins between 0\% and 13\% 
--bins having increments of 0.1- with 
-corresponding probabilities in each. That makes 262 pieces of information per
+-bins having increments of 0.1 or 0.001\%- with 
+corresponding probabilities in each. That made 262 pieces of information per
 prediction. For any binning scheme of more than two bins, the information 
 requirement for discretized bins will be higher than for parametric distrbutions.
-Table \ref{tab:dbins} illustrates what a discretized 
+Table \ref{table:dbins} illustrates what a discretized 
 Lognormal$(1,0.4)$ distribution truncated over $[0,8]$
@@
 \begin{table}[h!]
-\label{tab:dstor}
+
 \centering
@@
  \hline
+
  \end{tabular}
+  \caption{This table displays subset of bins and probabilities in each for a Lognormal distribution
+with $\mu = 1$ and $\sigma = 0.4$ after discretization}
+\label{table:dbins}
 \end{table}
-Submitted as a forecast prediction, the distribution in table \ref{tab:dstor} 
+Submitted as a forecast prediction, the distribution in table \ref{table:dbins} 
 includes 82 pieces of data. For parts 
 of the CDC influenza competition some forecasts included upt to 262. This is 
-much more manageable than possible thousands of samples from a samle 
+requires much less storage than possible thousands of draws from a sample 
 distribution but is 
@@
 Depending on what is known about the problem to be solved, creating the right 
-binning scheme might be a challenge. Because there must be a finite number of
-bins, forecast distributions must have a finite support. Where the range of 
-possible outcomes to a problem is little known, the right binning scheme may be
+binning scheme may be a challenge. Because there must be a finite number of
+bins, forecast distributions often have a finite support. Where the range of 
+possible outcomes to a problem is not well known, the right binning scheme may 
+be
 hard to produce.
 
-\subsection{Quantile representation}
+\subsubsection{Quantile representation}
 When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
@@
 The Forecast Hub requires predictions to be submitted as 11 or 3 nominal 
-intervals -depending on the specific target- and a median.
-Using this interval or quantile representation lead to a number of changes in 
-the evaluation and aggregation of forecasts.
+intervals -depending on the specific target and unit to forecast- and a median.
+Using this interval or quantile representation leads to a number of changes in 
+the scoring and ensemble building of forecasts.
 
 A quantile forecast is constructed as follows.
-For $N$ given quantiles $\alpha_1,..., \alpha_N$, $q_1,..., q_N$ are the values
+For $N$ given quantiles $\alpha_1,..., \alpha_N$; $q_1,..., q_N$ are the values
 such that
@@
 \begin{equation}
+\label{eq:quantiles}
   P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ..., 
@@
 \end{equation}
-When the quantiles are reported as prediction intervals we have more 
-specifically
-
-\begin{equation}
+When the quantiles are reported as prediction intervals we have
+
+\begin{equation}
+\label{eq:intervals}
   P(Y \leq q_1) = \alpha_1, P(Y \leq q_2) = \alpha_2, ...,
-  P(Y \leq q_{N-1}) = 1 - \alpha_{N-1}, P(Y \leq q_N) = 1 - \alpha_N
-\end{equation}
-
-The quantile or interval format is somewhat unique among forecast 
-representations discussed in this paper. What is possible for scoring forecasts
+  P(Y \leq q_{N-1}) = 1 - \alpha_2, P(Y \leq q_N) = 1 - \alpha_1
+\end{equation}
+
+What is possible for scoring forecasts
 or building ensemble models in other representations is often not possible with
 quantile forecasts. The shape of a distribution is also not known and in fact,
-nothing is known about the tails of the uncertainty or ouside of the most 
+nothing is known about the tails or the uncertainty or ouside of the most 
 extreme reported quantile values. In the Forecast Hub predictions, nothing 
-is said about the range below the $1^{st}$ quantile or above the $99^{ths}$.
+is said about the range below the $1^{st}$ quantile or above the $99^{th}$.
 Yet the quantile representation has its advantages.
@@
 
-To score predictions from a prediction interval, 
+To score predictions from a quantile or prediction interval format, 
 neither the LogS nor the CRPS may be used, 
-but another proper scoring rule the interval score (IS) may be.
+but another proper scoring rule the interval score (IS) may be used.
 For an observed outcome $x^*$ and a prediction interval $(l,r)$ 
@@
 
-When an interval forecast is made up of more than one interval with different
-$\alpha$ levels, a weighted interval score (WIS) may be evaluated. Bracher et.
+When an interval forecast is made up of multiple intervals each with different
+$\alpha$ levels, the weighted interval score (WIS) may be evaluated. Bracher et.
 al use the WIS to evaluate COVID-19 inverval forecasts 
@@
 which are described by Bracher et. al- but that used in the COVID-19 Forecast
-Hub is defined as follows
-
-\begin{equation}
+Hub for a forecast of $K$ intervals is defined as follows
+
+\begin{equation}
+\label{eq:wis}
   WIS_{0,K}(F_m,y^*) = \frac{1}{K + 1/2} \times (w_0, \times |y^*-med|+
@@
 \end{equation}
-$w_k = \alpha_k/2$ is the weight on
-intervals which was used. With that choice of weights, it may be shown that the
+where $w_k = \alpha_k/2$ is the weight on the $k^{th}$
+interval. With that choice of weights, it may be shown that the
 WIS approximates CRPS see S1 Text  \cite{bracher2021evaluating}
@@
 Bogner, Liechti and Zappa compared scoring forecasts of quantiles with the 
-Quantile Score similar to the interval score and scoring distribution functions
+Quantile Score (QS) similar to the interval score and scoring distribution functions
 fit to those quantiles using CRPS \cite{bogner2017combining}. The CRPS 
@@
 the distribution and especially in the tails past the end points of quantiles
-used in QS or IS.
+used in QS or IS. Thus there may be something lost in terms of scoring when the 
+WIS is used.
 
@@
 ensemble forecast.
-
 The ensemble forecast constructed by the COVID-19 Forecast Hub was made as an
@@
 to outperform equally-weighted mean construction. To come up with optimal 
-weights, they select values $\nu_m$ from \ref{eq:qa} which minimize the WIS of 
+weights, they select values $\nu_m$ from (\ref{eq:qa}) which minimize the WIS of 
 the ensemble forecast.
 
-Averaging quantiles in this way the same as quantile averaging or Vincentization
+Averaging quantiles in this way is the same as quantile averaging or Vincentization
 only with an incomplete quantile function. It thus carries with it many of the
@@
 where $F_m^{-1} (\alpha) = \inf \{y:F_m(y) \geq \alpha\}$ for 
-$0 < \alpha \leq 1$. Some notable characteristics are that it is more likely
-to be unimodal than linear averaging of densities like BMA 
+$0 < \alpha \leq 1$. Some notable characteristics are that it is more likely for
+the ensemble distribution
+to be unimodal than it is under linear averaging of densities like BMA 
 \cite{busetti2017quantile} (this paper is a comparison of QMA and 
@@
 depend on the desired clarity of resolution. For the COVID-19 forecasts 
-submitted to the forecast hub, twenty-three quantile values are requested for 
+submitted to the Forecast Hub, twenty-three quantile values are requested for 
 the quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This included a 
@@
 storage, this is an improvement over requirements for the flu contest. Table
-\ref{tab:qstor} shows what a submission of 23 quantiles from a 
+\ref{table:qstor} shows what a submission of 23 quantiles from a 
 Lognormal $(1,0.4)$ looks like.
@@
 \centering
-\label{tab:qstor}
+
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
@@
  \end{tabular}
+ \caption{A table showing a subset of quantiles and values of a Lognormal
+ distribution with $\mu=1$ and $\sigma = 0.4$}
+ \label{table:qstor}
 \end{table}
@@
 \subsection{Discrete mixture of parametric distributions}
-In a parametric setting, forecasters may be permitted to submit a forecast as a
-discrete mixture. Such a distribution may be constructed in the same way as the
-ensemble described under Parametric distributions (\ref{eq:bma}) 
+A discrete mixture of parametric distributions forecast representation may be an
+attractive alternative to the four types already discussed. A discrete mixture 
+would allow for many distribution shapes, a high resolution, storage comparable
+to that of discretized bins and quantile representations and the use of the more
+common methods for scoring and ensemble building.
+
+A discrete mixture distribution may be constructed in the same way as the
+ensemble described under section \ref{section:pardist} in equation 
+(\ref{eq:bma}) 
 where for $T$ distributions
@@
 Like the standard parametric model, a discrete mixture is easily evaluated with
-exisiting software (like distr R package \cite{camphausen2007distr}). And 
+exisiting software (like distr \texttt{R} package \cite{camphausen2007distr}). 
+And 
 scoring may be done by 
-using the LogS, CRPS and IS. The resolution of a discrete mixture is high 
+using the LogS, CRPS and IS. The resolution of a discrete mixture is continuous 
 and the support need not be limited by submission requirements.
@@
 \end{table}
+
+% \begin{figure}[h]
+% \caption{Write the caption here.}
+% % \vspace{0.0cm} \centering
+% \centering
+%     \subfloat[label 1]{{\includegraphics[width=1cm]{flu_fit_img/_flu_fit_1_10_2_.png} }}
+%     \qquad
+%     \subfloat[label 2]{{\includegraphics[width=1cm]{flu_fit_img/_flu_fit_1_10_6_.png} }}
+%     \caption{2 Figures side by side}
+%     \label{fig:example}
+% % \includegraphics[height=5.4cm]{flu_fit_img/_flu_fit_1_10_2_.png}
+% % \includegraphics[height=5.4cm]{flu_fit_img/_flu_fit_1_10_6_.png}
+% % \includegraphics[height=5.4cm]{flu_fit_img/_flu_fit_3_11_2_.png}
+% % \includegraphics[height=5.4cm]{flu_fit_img/_flu_fit_3_11_4_.png}
+% % \includegraphics[height=5.4cm]{allimages/fig3.eps}
+% % \includegraphics[height=5.4cm]{allimages/fig4.eps}
+% % \includegraphics[height=5.4cm]{allimages/fig5.eps}
+% % \includegraphics[height=5.4cm]{allimages/fig6.eps}
+% \end{figure}
+% \begin{adjustwidth}{-3cm}{-1cm}
+% \begin{figure}[htbp]
+% 
+%     \centering
+%     \subfloat[1]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_1_10_2_.png}}}
+%     \hfill
+%     \subfloat[2]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_1_10_6_.png}}}
+%     \hfill
+%     \subfloat[1]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_3_11_2_.png}}}
+%     \hfill
+%     \subfloat[2]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_3_11_4_.png}}}
+% 
+%     \subfloat[1]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_5_6_1_.png}}}
+%     \hfill
+%     \subfloat[2]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_5_6_2_.png}}}
+%     \hfill
+%     \subfloat[1]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_5_10_4_.png}}}
+%     \hfill
+%     \subfloat[2]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_5_10_6_.png}}}    
+%     \caption{graphs}%
+% 
+% \end{figure}
+% \end{adjustwidth}
 

### 2022-03-30 manuscript/Preface/abstract.tex
ISU thesis format CC all contained in manuscript folder

\specialchapt{ABSTRACT}

Collaboration among multiple teams has played a major role in probabilistic
forecasting of influenza outbreaks, the COVID-19 pandemic, other disease
outbreaks and problems in many other fields. When collecting forecasts from 
individual teams, ensuring that each team's model represents forecast
uncertainty according to the same format allows for direct comparison of 
forecasts as well as methods of constructing multi-model ensemble forecasts.
This paper outlines several common probabilistic forecast formats including
probability densities, samples, binned distributions and  quantile 
forecasts and compares
their usage within the context of collaborative projects. We propose the use of
a discrete mixture distribution format in collaborative forecasting in place of
other formats. The flexibility in distribution shape, the ease for scoring and 
building ensemble models and the reasonably low level of computer storage 
required to save such a format make the discrete mixture distribution an 
attractive alternative to the other mentioned formats.

### 2022-03-30 manuscript/Preface/acknowl.tex
ISU thesis format CC all contained in manuscript folder

\specialchapt{ACKNOWLEDGMENTS}

% I would like to take this opportunity to express my thanks to those
% who helped me with various aspects of conducting research and the writing
% of this thesis.
% First and foremost, Dr. Susan D. Ross for her guidance, patience and support
% throughout this research and the writing of this thesis.
% Her insights and words of encouragement have often inspired me and renewed
% my hopes for completing my graduate education.
% I would also like to thank my committee members for their efforts
% and contributions to this work: Dr. August Tanner and
% Dr. Lewis Hargrave.
% I would additionally like to thank
% Dr. Tanner for his guidance throughout the initial stages of my
% graduate career and Dr. Hargrave for his inspirational teaching style.

### 2022-03-30 manuscript/thesis.Rnw
ISU thesis format CC all contained in manuscript folder

--- 2022-03-23 manuscript.tex
@@
-\documentclass{article}
-% \usepackage[]{graphicx}\usepackage[]{color}
-% maxwidth is the original width if it is less than linewidth
-% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-% \makeatletter
-% \def\maxwidth{ %
-%   \ifdim\Gin@nat@width>\linewidth
-%     \linewidth
-%   \else
-%     \Gin@nat@width
-%   \fi
-% }
-% \makeatother
+% Template file for a standard thesis
+\documentclass[11pt,notitlepage]{isuthesis}
+% notitlepage is used because \begin{abstract} uses titlepage by default, which resets the page numbers
+
+\usepackage[pdftex]{graphicx}
 
@@
 \usepackage{subfig}
-% \usepackage{geometry}
-% \geometry{legalpaper, margin=1in}
-
+% Standard, old-style thesis
+\usepackage{isutraditional}   
+\chaptertitle
+% Old-style, thesis numbering down to subsubsection
+\alternate
+\nochap
+\usepackage{rotating}
+% Bibliography without numbers or labels
+\usepackage{natbib}
+% Use the following line if you want square brackets and numbering system
+%\usepackage[square, numbers]{natbib}
 \lstset{language=R,
@@
 \makeatletter
-% \newenvironment{kframe}{%
-%  \def\at@end@of@kframe{}%
-%  \ifinner\ifhmode%
-%   \def\at@end@of@kframe{\end{minipage}}%
-%   \begin{minipage}{\columnwidth}%
-%  \fi\fi%
-%  \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
-%  \colorbox{shadecolor}{##1}\hskip-\fboxsep
-%      % There is no \\@totalrightmargin, so:
-%      \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
-%  \MakeFramed {\advance\hsize-\width
-%    \@totalleftmargin\z@ \linewidth\hsize
-%    \@setminipage}}%
-%  {\par\unskip\endMakeFramed%
-%  \at@end@of@kframe}
-% \makeatother
-
-% \definecolor{shadecolor}{rgb}{.97, .97, .97}
-% \definecolor{messagecolor}{rgb}{0, 0, 0}
-% \definecolor{warningcolor}{rgb}{1, 0, 1}
-% \definecolor{errorcolor}{rgb}{1, 0, 0}
-% \newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-
-\usepackage{apacite}
+
+\renewcommand{\bibfont}{\setstretch{1}\selectfont}
+\setlength{\bibsep}{13.2pt}
+
+\usepackage{chapterbib}
+%\renewcommand\bibsection{\section*{\ref name}}
+%\renewcommand\bibsection{\section*}
+\renewcommand{\bibsection}{\section{References}}
+
+%\bibliographystyle{apa}  % changed from apa, abbrv, unsrtnat
+%\includeonly{titletoc,chapter1}
+%Optional Package to add PDF bookmarks and hypertext links
+\usepackage[pdftex,hypertexnames=false,linktocpage=true]{hyperref}
+\hypersetup{colorlinks=true,linkcolor=blue,anchorcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue,bookmarksnumbered=true,pdfview=FitB}
+
+%\usepackage{titletoc}
+\usepackage{hyperref}
+
+% \usepackage{subfig} %% Use this package instead of the subcaptions package for subfigures. Please see at the end of this file, an example of how to use the package.
+
+\overfullrule=0pt
+%%%%%%%%%%%%%%%%%%%%%
+
+% The following piece of code removes extra space on the top of each chapter
+%  that is default of latex report class documents
+
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd{\@makechapterhead}{50\p@}{0pt}{}{}
+\patchcmd{\@makeschapterhead}{50\p@}{0pt}{}{}
+\makeatother
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% Removing Bold characters in the Table of Contents
+% % Alternatively to this the isuthesis.cls file has been changed by default in the
+% % line section \renewcommand{\l@chapter}[2]{\addpenalty{-\@highpenalty}....
+%\titlecontents{chapter}
+%[0pt]                                               % left margin
+%{}%
+%{\contentsmargin{0pt}                               % numbered entry format
+%    \thecontentslabel\enspace%
+%    \large}
+%{\contentsmargin{0pt}\large}                        % unnumbered entry format
+%{\titlerule*[.5pc]{.}\contentspage}                 % filler-page format (e.g dots)
+%[]                                                  % below code (e.g vertical space)
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% In order to change space between the Table of contents items go to isuthesis.cls
+% line  \renewcommand{\l@chapter}[2]{\addpenalty{-\@highpenalty}....
+% change \vkip values
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% This is to minimize orphan lines. Might not be possible to entirely remove them
+% Method 1 of doing this
+\widowpenalty100000
+\clubpenalty100000
+
+% Method 2 of doing this
+\usepackage[all]{nowidow}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% control bibliography spacings
+% \newlength{\bibitemsep}\setlength{\bibitemsep}{\baselineskip}
+% % plus .05\baselineskip minus .05\baselineskip}
+% \newlength{\bibparskip}\setlength{\bibparskip}{0pt}
+% \let\oldthebibliography\thebibliography
+% \renewcommand\thebibliography[1]{%
+%   \oldthebibliography{#1}%
+%   \setlength{\parskip}{\bibitemsep}%
+%   \setlength{\itemsep}{\bibparskip}%
+% }
+% \usepackage{setspace}
+% \setlength{\bibsep}{2sp}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %% aligning lof captions
+% \usepackage{tocloft}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Set the margins in the whole document
+\geometry{letterpaper, left=1in, top=1in, right=1in, bottom=1in, includehead=true} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{amssymb}
+\usepackage[intoc, english]{nomencl}
 
 \begin{document}
-
-\section*{Abstract}
-
-Collaboration among multiple teams has played a major role in probabilistic
-forecasting of influenza outbreaks, the COVID-19 pandemic, other disease
-outbreaks and problems in other fields. When collecting forecasts from 
-individual teams, ensuring that each team's model represents forecast
-uncertainty according to the same format allows for direct comparison of 
-forecasts as well as methods of constructing multi-model ensemble forecasts.
-This paper outlines several common probabilistic forecast formats including
-probability density functions, samples, binned distributions and  quantile 
-forecasts and compares
-their usage within the context of collaborative projects. The discrete mixture
-distribution forecast format is presented as an attractive alternative to the 
-former formats due to the flexibility such a forecast may have in shape as well
-as the relatively low loss of information due to limited computer storage.
+\SweaveOpts{concordance=TRUE}
+\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
+%\begin{singlespace}
+\def\@makechapterheada{\vspace*{-2cm}\titlepage} % in order to reduce the space between margin and heading in titlepage
+\include{Preface/titlepage}
+%\end{singlespace}
+
+% Left-justified setting for all sections including
+% dedication, nomenclature, acknowledgement, abstract and all chapters
+% Re-position the two lines below will change all the section
+% being compiled after those two lines
+\raggedright
+\parindent 0.25 in % set all paragraphs in the document to have indent
+
+% Optional thesis dedication
+\include{Preface/dedication}
+% Table of Contents, List of Tables and List of Figures
+{
+\pdfbookmark[1]{TABLE OF CONTENTS}{table}
+\tableofcontents
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The line below adds the word "Page" over the page numbers in TOC, LOT, LOF
+\addtocontents{toc}{~\hfill\textbf{Page}\par}
+\addtocontents{lot}{~\hfill\textbf{Page}\par}
+\addtocontents{lof}{~\hfill\textbf{Page}\par}
+%%
+\addtocontents{toc}{\def\protect\@chapapp{}} \cleardoublepage \phantomsection
+\pagebreak
+\addcontentsline{toc}{chapter}{LIST OF TABLES}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\listoftables
+\cleardoublepage \phantomsection \addcontentsline{toc}{chapter}{LIST OF FIGURES}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\listoffigures
+
+%Optional Nomenclature
+\cleardoublepage \phantomsection
+\include{Preface/nomenclature}
+
+% Comment out the next line if NOT using chaptertitle
+\addtocontents{toc}{\def\protect\@chapapp{CHAPTER\ }}
+
+%Optional Acknowledgements
+\cleardoublepage \phantomsection
+\include{Preface/acknowl}
+%Optional thesis abstract
+\cleardoublepage \phantomsection
+\include{Preface/abstract}
+\newpage
+\pagenumbering{arabic}
 
@@
 distribution forecasts
-\cite[see, e.g.]{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
+\cite{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
 Other common representations include samples \cite{krueger2016probabilistic}, 
@@
 are used include the United States Centers for Disease Control (CDC) hosted
-annual competition for forecasting influenza ??\cite{cdcflusight}
+annual competition for forecasting influenza \cite{cdcflusight}
 and the COVID-19 Forecast Hub which has 
@@
 in a discretized bin
-format. During previous fluw seasons the binning scheme was on a bounded numeric 
+format. During previous flu seasons the binning scheme was on a bounded numeric 
 scale and the 
@@
 proposed way to enhance prediction has been to aggregate the various teams'
-forecasts into a multi-model ensemble forecast \cite{mcgowan2019collaborative}
-\cite{mcandrew2019adaptively} \cite{reich2019accuracy}.
-
-A multi-model ensemble forecast is combination of several component forecast 
+forecasts into a multi-model ensemble forecast 
+\cite{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy}.
+
+A multi-model ensemble forecast is a combination of several component forecast 
 models into one model which often yields better predicting power than the 
@@
 forecasts and the ensemble are passed along to the CDC for its use in official
-communication \cite{Cramer2021-hub-dataset} see Figure \ref{fig:cdcoff}.
+communication \cite{Cramer2021-hub-dataset}. See Figure \ref{fig:cdcoff}.
 
@@
 been operating continuously since it first began, so forecasts have been made
-for over one-hundred straight weeks. 
+for over 100 straight weeks. 
 As well due to the initial lack of understanding of the COVID-19 virus and the 
@@
 creating forecasts, rather than requesting forecasts as binned probabilities
-the forecasts were requested as the predictive median and 
+the forecasts are requested as the predictive median and 
 predictive intervals for various nominal levels depending on the target to be
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[scale=.12]{8_30_21_cvd_deaths.jpeg}}
-\caption{This graphic was published on cdc.gov as official public communication 
-by the CDC shows forecast models for national new weekly deaths due to COVID-19 
+\centerline{\includegraphics[scale=.12]{Images/8_30_21_cvd_deaths.jpeg}}
+\caption[Official CDC COVID-19 deaths report August 2021]{This image, 
+published on cdc.gov as official public communication 
+by the CDC, shows forecast models for national new weekly deaths due to COVID-19 
 in the top row and cumulative deaths on the bottom row. The plots in the left 
@@
 of forecasting for projects similar to the CDC flu competition or the COVID-19
-Forecast Hub. In section 2, popular probabilistic forecast representation 
+Forecast Hub. In section \ref{section:representations}, 
+popular probabilistic forecast representation 
 types are defined and reviewed. Methods of scoring, storing, building 
@@
 representation type.
-Section 3 is a retrospective study of the CDC flu competition and COVID-19 
+In section \ref{section:conmixforc}, details for using discrete mixture 
+distributions in a collaborative forecast project are presented as well as tools
+which may be used for scoring and ensemble building.
+Section \ref{section:retrostud} is a retrospective study of the CDC flu 
+competition and COVID-19 
 forecast predictions and an attempt to assess whether any predictions 
-approximately come from well known continuous distributions.
+approximately come from well known continuous distributions. This paper is 
+concluded with a discussion.
 
 \section{Probabilistic Forecast Representations}
+\label{section:representations}
 
@@
 should be considered. With each representation presented, 
-commmon application of 
-scoring, data storage and ensemble construction will be considered for each type
+commmon applications of 
+scoring, data storage and ensemble construction will be considered for
 as well as other notable properties.
 
-\subsection{Things to consider}
+\subsection{Representation properties to consider in collaborative projects}
 \subsubsection{Scoring}
@@
 For a collaborative forecast project where many researchers are involved and 
-many predictions are collected, computer storage may be something
-that needs to be addressed. As an example of required computer storage, the 
+many predictions are collected, computer storage may need to be addressed. 
+As an example of required computer storage, the 
 repository for the
@@
 that another model does not, so that when they are combined in an ensemble the 
-ensemble model outperforms the individual components.
+ensemble model outperforms the individual component models.
 
@@
 modeling. Multi-model ensembles have been used extensively in weather and
-climate modeling see \cite{baran2018combining}, 
+climate modeling \cite[for example]{baran2018combining}, 
 and they have been used increasingly in modeling infectious disease outbreaks
-see for example \cite{yamana2016superensemble}. 
+see \cite[for example]{yamana2016superensemble}. 
 Multi-model ensembles allow for an incorporation of multiple signals -
@@
 canceled
-out or reduced by biases in others (\cite{reich2019accuracy} ??see references
-therein). 
+out or reduced by biases in others \cite[see references
+therein]{reich2019accuracy}. 
 In several disease outbreak studies, multi-model ensemble forecasts have been 
-shown to outperform individual model forecasts (\cite{cramer2021evaluation} see
-references therein).
+shown to outperform individual model forecasts 
+\cite[see
+references therein]{cramer2021evaluation}.
 
@@
 described by a known function $p(x) := p(x|\theta)$ -pmf in the discrete case or 
-pdf in the continuous case. $\theta$ is a vector of known or unkown parameters 
+pdf in the continuous case. Here $\theta$ is a vector of known or unkown 
+parameters 
 contained in a parameter space.
@@
 \label{eq:ccdf}
-  F_X(x) = P(X \leq b) = \int_{-\infty}^x p(t) dt
+  F(x) = P(X \leq b) = \int_{-\infty}^x p(t) dt
 \end{equation}
@@
 \label{eq:dcdf}
-  F_X(x) = P(X \leq b) = \sum_{k=1}^n p(x_k) dt
+  F(x) = P(X \leq b) = \sum_{k=1}^n p(x_k) dt
 \end{equation}
@@
 \label{eq:quant}
-  Q(p) = \inf \{ y \in \mathbb{R} : p \leq F_X(x) \}
+  Q(p) = \inf \{ y \in \mathbb{R} : p \leq F(x) \}
 \end{equation}
@@
 others. See also \cite{gneiting2014probabilistic}
-section 3 for on proper scoring functions. Unless otherwise noted, the following
-definitions/reviews can be found in the review by Krueger.
-
-For a forecast with pdf/pmf $p_m(x)$, the Logarithmic score evaluates the 
+section 3 for more on proper scoring functions. Unless otherwise noted, the 
+following
+definitions can be found in the review by Krueger.
+
+For a forecast with pdf/pmf $p_m(x)$, the LogS evaluates the 
 probability of the observed value $x^*$. It is defined as
@@
 \end{equation}
-The goal is to minimize the LogS, so that a forecast $p^{'}_m(x^*)$ is considered 
-superior to $p_m$ if
+The goal is to minimize the LogS, so a forecast $p^{'}_m(x^*)$ is considered 
+superior to $p_m(x^*)$ if
 $LS(p^{'}_m, x^*) < LS(p_m, x^*)$.
@@
 The CRPS is a function of a CDF $F$
-and so 
-can be used a more extensively than the LogS. 
+and so it may
+be used more extensively than the LogS. 
 For the CDF $F_m$, the CRPS is defined as
@@
 used
-to build ensembles using Bayesian model averaging (BMA). Considered the state-of-the-art techniques for combining 
+to build ensembles under Bayesian model averaging (BMA). Considered the 
+state-of-the-art techniques for combining 
 component distributions
@@
 \cite{raftery2005using}, MCMC 
-sampling see \cite{vrugt2008ensemble} (also in this paper it talks about how 
-EM can get difficult as parameters i.e. number of distributions increase, and 
-shows MCMC may be better with that high dimensionality and gives full posterior
-of weights)
-and minimizing the ensemble CRPS as in 
+sampling see \cite{vrugt2008ensemble}
+and minimizing the ensemble CRPS see
 \cite{baran2018combining}.
@@
 difficult to compute. For example, when the forecast is a mixture of a 
-Truncated Normal distribution (TN) and a Truncated Lognormal (TL) the CRPS is 
+truncated normal distribution (TN) and a truncated lognormal (TL) the CRPS is 
 not available in closed form \cite{baran2018combining}.
@@
 Generally computation and evaluation of parametric distributions is not hard. 
-For most commonly used parametric distributions -Normal, Lognormal, Poisson,
-Gamma, etc.- there is software readily available to compute density, 
+For most commonly used parametric distributions -normal, lognormal, Poisson,
+gamma, etc.- there is software readily available to compute density, 
 distribution and quantile values. Likewise, requirements for storage are low 
 compared to other representation types that will be discussed. The most common
-parametric distributions can be fully defined with three or pieces of data.
-The distribution family and two or three parameters. Table \ref{table:pstor} 
+parametric distributions can be fully defined with three or pieces of data
+including
+the distribution family and two or three parameters. Table \ref{table:pstor} 
 contains
@@
  \end{tabular}
- \caption{lognormal distribution with parameters $\mu = $ 1 and $\sigma =$ 0.4}
+ \caption[Parametric distribution storage]{Storage example of parametric 
+ lognormal 
+ distribution with 
+ parameters $\mu = $ 1 and $\sigma =$ 0.4}
  \label{table:pstor}
@@
 models is limited to what is available in software, so certain distributional
-shapes may unattainable. The distribution may assign probability to values
+shapes may unattainable. The distribution may also assign probability to values
 outside the range of the forecast. There are remedies for this such as 
@@
 ECDF will converge to the true CDF 
-distribution function as $n \rightarrow \infty$. Thus, if a sufficiently large 
+as $n \rightarrow \infty$. Thus, if a sufficiently large 
 sample is generated from a distribution with an expectation, 
@@
 
-So the options that a researcher has for constructing a forecast are more than
+Under the samle distribution format, the options that a researcher has for 
+constructing a forecast are more than
 if they are asked to submit a parametric distribution and the range 
@@
 sampling have greatly contributed to growth in the use of
-predictive distributions \cite{gneiting2007strictly}. ??(See examples listed in
-\cite{krueger2016probabilistic}).
+predictive distributions \cite{gneiting2007strictly}
+\cite[see examples listed therein]{krueger2016probabilistic}.
 
@@
 distribution directly since the CDF in  (\ref{eq:crps}) may be replaced by the 
-ECDF 
+ECDF in
 (\ref{eq:ecdf}). To use the LogS to score a forecast, a density function for the 
@@
 
-KD is defined in Kruger as
+KD is defined by Krueger et. al as
 
@@
 where $\Phi$ is the standard normal CDF and $\hat{\mu}_n$ and $\hat{\sigma}_n$
-are the empirical mean and standard deviation of the sample $(X_i)$. (See
-\cite{krueger2016probabilistic} for definitions of \ref{eq:kd} and \ref{eq:ga}).
-
-Kruger et. al compare scoring of MCMC drawn forecast distributions using CRPS 
+are the empirical mean and standard deviation of the sample $(X_i)$
+\cite{krueger2016probabilistic}.
+
+Krueger et. al compare scoring of MCMC drawn forecast distributions using CRPS 
 and LogS over samples directly using ECDF or over density approximations using
@@
 To build an ensemble model from sample distribution forecasts, the BMA 
-construction from (\ref{eq:bma}) would work only replacing $p_m$ with 
+construction from (\ref{eq:bma}) may be used only replacing $p_m$ with 
 $\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$ -approximate KD and GA densities. 
@@
 
-A potentially big issue with using sample distributions is the amount of storage
+A potentially large issue with using sample distributions is the amount of storage
 it would require. For example when making MCMC draws from a posterior 
@@
 select the number of bins and the sizes for each bin. It may be the case
-that a forecast hub will set the width of all bins to be equal so that 
-$\Delta = b_i - b_{i-1}$ is the width for all $i$ see for example
-\cite{mcgowan2019collaborative}.
+that a collaborative project will set the width of all bins to be equal so that 
+$\Delta = b_i - b_{i-1}$ is the same width for all $i$ 
+\cite[see for example]{mcgowan2019collaborative}.
 To complete the construction, a probability $p_i$ is assigned to each $b_i$ 
@@
 the cumulative distribution are done the same as for a discrete parametric 
-distribution. For a random variable X from a binned distribution to calculate
+distribution. For a random variable $X$ from a binned distribution to calculate
 the $j^{th}$ moment we may use
@@
 \end{equation}
-where $\beta_i$ is a value related to the bin $B_i$ such as $\beta_i = b_i$,
-$\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$. The 
+where $\beta_i$ is a value corresponding to bin $B_i$ (such as $\beta_i = b_i$,
+$\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$). The 
 cumulative distribution may be calculated as
@@
 The CDC has used a discretized bin distribution representation as the 
-representation
-for their annual influenza forecasting competition and other disease outbreaks.
+format
+for their annual influenza forecasting competition and other disease outbreak
+forecast projects.
 In that context it has become the standard representation 
@@
 and constructing ensemble models on influenza forecasts represented by 
-discretized bins \cite{mcgowan2019collaborative}, \cite{mcandrew2019adaptively}
-\cite{reich2019collaborative}.
+discretized bins \cite{mcgowan2019collaborative, mcandrew2019adaptively,reich2019collaborative}.
 
@@
 according to the model specification. To estimate weights they used the 
-Expectation Maximization (EM) algorithm \cite{reich2019accuracy}. See the
-supplementary material for details.
+Expectation Maximization (EM) algorithm 
+\cite[see
+supplementary material within for details]{reich2019accuracy}.
 
 The exact amount of information required for a discretized bin forecast will 
-vary depending on permitted range of the forecast and the desired resolution. 
-In the CDC flu contest, a forecast could have 131 bins between 0\% and 13\% 
+vary depending on the permitted range of the forecast and the desired 
+resolution. 
+In the CDC flu contest, a forecast might have 131 bins between 0\% and 13\% 
 -bins having increments of 0.1 or 0.001\%- with 
-corresponding probabilities in each. That made 262 pieces of information per
+corresponding probabilities in each. This makes 262 pieces of information per
 prediction. For any binning scheme of more than two bins, the information 
@@
 where $p^{TL}$ is the pdf of a truncated Lognormal$(1,0.4)$. This is similar
-to Methodology-IV from Chakraborty \cite{chakraborty2015generating}
- \cite{kemp2004classes}.
+to Methodology-IV from Chakraborty 
+\cite{chakraborty2015generating,kemp2004classes}.
 
@@
  \end{tabular}
-  \caption{This table displays subset of bins and probabilities in each for a Lognormal distribution
-with $\mu = 1$ and $\sigma = 0.4$ after discretization}
+  \caption[Discretized bin distribution storage]{Storage example of discretized
+  lognormal with $\mu = 1$ and $\sigma = 0.4$}
 \label{table:dbins}
@@
 includes 82 pieces of data. For parts 
-of the CDC influenza competition some forecasts included upt to 262. This is 
-requires much less storage than possible thousands of draws from a sample 
+of the CDC influenza competition some forecasts included up to 262. This is 
+far less storage than the possible thousands of draws from a sample 
 distribution but is 
-still much larger than the 3 or 5 data pieces required to report a lognormal
+still much larger than the three or five data pieces required to report a 
+lognormal
 or truncated lognormal distribution.
@@
 the time pressure of generating forecasts and the consideration of the large
-range for possible outcomes contributed to the COVID-19 Forecast Hub decision
+range for possible outcomes both contributed to the COVID-19 Forecast Hub 
+decision
 to forego trying to create the right binning scheme and use sets of prediction
@@
 
-The Forecast Hub requires predictions to be submitted as 11 or 3 nominal 
+The Forecast Hub requires predictions to be submitted as 11 or three nominal 
 intervals -depending on the specific target and unit to forecast- and a median.
@@
 quantile forecasts. The shape of a distribution is also not known and in fact,
-nothing is known about the tails or the uncertainty or ouside of the most 
+nothing is known about the tails or the uncertainty beyond the most 
 extreme reported quantile values. In the Forecast Hub predictions, nothing 
-is said about the range below the $1^{st}$ quantile or above the $99^{th}$.
+is reported about the range below the $1^{st}$ quantile or above the $99^{th}$.
 Yet the quantile representation has its advantages.
@@
 -e.g. quantile function for parametric functions or calculating sample 
-quantiles- we consider quantile forecasts to have high flexbility in terms of 
+quantiles- we consider quantile forecasts to be highly flexible in terms of 
 what methods forecasters may employ in modeling.
@@
 neither the LogS nor the CRPS may be used, 
-but another proper scoring rule the interval score (IS) may be used.
+but another proper scoring rule the IS may be used.
 For an observed outcome $x^*$ and a prediction interval $(l,r)$ 
@@
 There are multiple versions of the WIS -some of 
-which are described by Bracher et. al- but that used in the COVID-19 Forecast
+which are described in Bracher et. al- but the version used by the COVID-19 
+Forecast
 Hub for a forecast of $K$ intervals is defined as follows
@@
 interval. With that choice of weights, it may be shown that the
-WIS approximates CRPS see S1 Text  \cite{bracher2021evaluating}
+WIS approximates the CRPS \cite[see S1 Text therein]{bracher2021evaluating}.
 
@@
 Quantile Score (QS) similar to the interval score and scoring distribution functions
-fit to those quantiles using CRPS \cite{bogner2017combining}. The CRPS 
+fit to those quantiles using the CRPS \cite{bogner2017combining}. The CRPS 
 corresponds to the integral of the QS over all possible thresholds rather than
-just specific quantiles, it more effectively reveals deficiencies in parts of 
+just specific quantiles, so it more effectively reveals deficiencies in parts of 
 the distribution and especially in the tails past the end points of quantiles
@@
 all models corresponding to the same quantile \cite{ray2020ensemble}. For $M$ 
-models each with $K$ quantiles, the $k^{th}$ ensemble quantile $q_k$ is 
+models each with $K$ quantiles, the $k^{th}$ ensemble quantile $q^E_k$ is 
 calculated as
@@
 \label{eq:qa}
-  q_k = \sum_{m=1}^M \nu_m q_k^m 
+  q^E_k = \sum_{m=1}^M \nu_m q_k^m 
 \end{equation}
@@
 In their report, they show that weighted means and median constructions tend
-to outperform equally-weighted mean construction. To come up with optimal 
+to outperform an equally-weighted mean construction. To come up with optimal 
 weights, they select values $\nu_m$ from (\ref{eq:qa}) which minimize the WIS of 
@@
 to be unimodal than it is under linear averaging of densities like BMA 
-\cite{busetti2017quantile} (this paper is a comparison of QMA and 
-linear or log averaging. Under some circumstances, such as when member
+\cite{busetti2017quantile} Under some circumstances, such as when member
 distributions are exponential, Weibull or logisitic the aggregated distribution
@@
 depend on the desired clarity of resolution. For the COVID-19 forecasts 
-submitted to the Forecast Hub, twenty-three quantile values are requested for 
+submitted to the Forecast Hub, 23 quantile values are requested for 
 the quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This included a 
 median along with eleven confidence intervals \cite{bracher2021evaluating}. This
-requires forecasters to submit forty-six values in each short-term forecast 
+requires forecasters to submit 46 values in each short-term forecast 
 (some of the longer term forecasts only include seven quantiles). In terms of 
@@
 \ref{table:qstor} shows what a submission of 23 quantiles from a 
-Lognormal $(1,0.4)$ looks like.
-
-% \begin{table}[h!]
-% \centering
-%  \begin{tabular}{|c|c|} 
-%  \hline
-%     quantile & value \\ \hline
-%     0.01 & 1.07137 \\
-%     0.025 & 1.2404 \\
-%     0.05 & 1.40689 \\
-%     0.01 & 1.62675 \\
-%     ...  & ... \\
-%     0.9 & 4.50667 \\
-%     0.95 & 5.18328 \\
-%     0.975 & 5.82391 \\
-%     0.99 & 6.58783 \\
-%  \hline
-%  \end{tabular}
-% \end{table}
+$Lognormal(1,0.4)$ looks like.
 
@@
 
- \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
- % \begin{tabular}{|c|c|}
+ \begin{tabular}{|c||c|c|c|c|c|c|c|c|c|}
  \hline
@@
     5.82391 & 6.58783 \\
-    % quantile & value \\ \hline
-    % 0.01 & 1.07137 \\
-    % 0.025 & 1.2404 \\
-    % 0.05 & 1.40689 \\
-    % 0.01 & 1.62675 \\
-    % ...  & ... \\
-    % 0.9 & 4.50667 \\
-    % 0.95 & 5.18328 \\
-    % 0.975 & 5.82391 \\
-    % 0.99 & 6.58783 \\
+
  \hline
  \end{tabular}
- \caption{A table showing a subset of quantiles and values of a Lognormal
- distribution with $\mu=1$ and $\sigma = 0.4$}
+ \caption[Quantile/interval and values storage]{Storage example of quantiles 
+ and values of lognormal with $\mu = 1$ and $\sigma = 0.4$}
  \label{table:qstor}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[scale=.1]{dens_comp.png}}
-\caption{Figure this out later}
-\label{fig}
-\end{figure}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[scale=.1]{cum_comp.png}}
-\caption{Figure this out later}
-\label{fig}
+\centerline{\includegraphics[scale=.1]{Images/dens_cum_comp.png}}
+\caption[Density/CDF comparison between parametric distribution, sample 
+distribution, discretized bin distribution and quantiles]{This figure compares 
+the
+densities and CDFs of forecast representation types discussed in the left and 
+right columns respectively. Each is generated from a lognorma(1,0.4) 
+distribution. Blue shows the density and CDF functions. Purple shows a 
+histogram and ECDF of 1,000 samples. Red shows bin probabilities and the CDF
+function. Green shows quantiles/intervals with corresponding values.}
+\label{fig:denscomp}
 \end{figure}
@@
 A discrete mixture distribution may be constructed in the same way as the
-ensemble described under section \ref{section:pardist} in equation 
+ensemble described in section \ref{section:pardist} in equation 
 (\ref{eq:bma}) 
@@
 
-Like the standard parametric model, a discrete mixture is easily evaluated with
+Like the standard parametric model, a discrete mixture may be evaluated with
 exisiting software (like distr \texttt{R} package \cite{camphausen2007distr}). 
@@
 scoring may be done by 
-using the LogS, CRPS and IS. The resolution of a discrete mixture is continuous 
+using the LogS, CRPS and IS. The resolution of a discrete mixture is infinite 
 and the support need not be limited by submission requirements.
 
-A mixture distribution may be much more flexible than a simple parametric in 
-terms of distributional shape. But as it is essentially parametric, forecasters
-mays still be limited in how they construct their models. But it may be possible
-to fit a mixture distribution to probability models with the other 
-representations discussed. According to McLachlan and Peel, a finite mixture of 
-normal densities with common variance can be used to approximate abitrarily well
+A mixture distribution may be much more flexible than a single component 
+parametric distribution in 
+terms of distributional shape. According to 
+McLachlan and Peel, a finite mixture of 
+normal densities with common variance can be used to approximate arbitrarily 
+well
 any continuous distribution \cite{peel2000finite} (see also 
-\cite{nguyen2019approximations}). Thus, for any unconventional probability
+\cite{nguyen2019approximations}). Thus, for an unconventional probability
 distribution -such as MCMC posterior samples- it may be reasonable to 
-approximate the distribution by a mixture of normals.
-Further discussion on methods for fitting mixture 
-distributions to different types of model representations is included in this 
-paper.
+approximate the distribution by constructing a mixture of normals.
+% See section \ref{section:conmix} for an example.
 
 An ensemble model may be built by using (\ref{eq:bma}) only replacing $p_m$
-with $p^M$. Solving for weights may also be done similarly, though with the 
-added complexity of component models being mixture distributions, the 
-computation is likely to get more expensive. An example where this may be
+with $p_m^M$ in \ref{eq:dmd}. Solving for weights may also be done similarly, 
+though with the 
+added complexity of component models being mixture distributions the 
+computation is likely to be more expensive. An example where this may be
 especially true is when minimizing of CRPS, but the exact mixture doesn't 
-result in CRPS in closed form \cite{baran2018combining}.
+result in CRPS in closed form \cite{baran2018combining}. In large projects like
+the COVID-19 Forecast Hub, if an equal weight is not assigned to each component,
+it may be determined that models not reaching a certain standard of predictive
+performance are
+assigned an ensemble weight of 0. This would simplify an ensemble model to 
+include only the best performing forecasts.
 
@@
 forecast, the amount of storage per forecast might be as little as for a 
-parametric forecast and as much as a forecast hub will allow. For modelers whose
-models produce distributions with irregular shapes, it may be that those
-distributions can be closely approximated by the right mixture distribution.
+parametric forecast and as much as a forecast hub will allow. In section
+\ref{section:conmixforc} we show how a mixture distribution may be constructed,
+scored and used to construct an ensemble using software available in 
+\texttt{R}.
+
+Table \ref{table:repscomp} shows how a discrete mixture distribution forecast 
+compares with the other formats discussed in terms of methods for scoring,
+information and resolution provided, methods for ensemble building and computer
+storage requirement.
 
 \begin{flushleft}
-    \begin{adjustwidth}{-3cm}{-1cm}
-    \begin{tabular}{ | p{2.4cm} | p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
-    \hline
-    Representation & Scoring & Flexibility/Information & Ensemble &
-    Storage Requirement
+  \begin{table}
+    % \begin{adjustwidth}{-3cm}{-1cm}
+    \begin{tabular}{ | p{2.4cm} || p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
+    \hline
+    \textbf{Representation} & \textbf{Scoring} & 
+    \textbf{Flexibility/Information} & \textbf{Ensemble} &
+    \textbf{Storage Requirement}
+    \\ \hline \hline
+
+    Parametric & LogS, CRPS, IS & Limited to common distribution families. 
+    Infinite resolution
+    & BMA & Low 3-6 values per prediction \\ \hline
+
+    Samples & CRPS and IS. LogS after smoothing & Any shape. Resolution may be
+    very high but depends on sample size & BMA after smoothing. Resampling 
+    otherwise & 
+    Hundreds or thousands of values per prediction
     \\ \hline
 
-    Parametric & LogS, CRPS, IS & Limited to common distribution families. 
-    Infinite resoution
-    & BMA & Low 3-6 values/prediction \\ \hline
-
-    Samples & CRPS and IS. LogS after smoothing & Any shape. Resolution may be
-    high but depends on sample size & BMA after smoothing. Resampling otherwise& 
-    Hundreds or thousands of values/prediction
-    \\ \hline
-
     Discretized bins & LogS, CRPS, IS &
-    Any shape allowed, but limited by binning scheme & BMA &
+    Any shape allowed, but limited by binning scheme. Range also may be limited
+    & BMA &
     Depends on binning scheme but dozens to hundreds of values
@@
 
-    Quantiles & IS, WIS & Shape unknown but may still have much info with 
-    enough quantiles. No tail information & Quantile averaging & Depends on 
-    quantiles requested but dozens of values
+    Quantiles & IS, WIS & Shape unknown but with enough quantiles there is still
+    a decent amount of information. No tail information & 
+    Quantile averaging & Depends on 
+    requested quantiles. Perhaps dozens of values
     \\ \hline
 
-    Discrete Mixture & LogS, CRPS, IS. May be more limited by computation & Can
-    take on many shapes/approximate most & BMA 
-    & 3 to limit values permitted
+    Discrete Mixture & LogS, CRPS, IS. May be more limited by computation & With
+    enough component distributions may
+    approximate any distribution shape. Infinite resolution& BMA 
+    & 3 values to dozens per forecast depending on number of components
     \\ \hline
@@
 	 \end{tabular}
-	 \end{adjustwidth}
+	 % \end{adjustwidth}
+   \caption[Forecast representation comparison]{This table compares scoring,
+   information, ensemble building and storage requirements for the different
+   forecast representations discussed.}
+   \label{table:repscomp}
+   \end{table}
+
 \end{flushleft}
 
-% bin & -6.5 & -6.4 & -6.3 $ ... & 6.3 & 6.4 & 6.5 \\  
-%  prob & 3.75e-11 & 1 7.11e-11 & 1.33e-10 & ... & 7.11e-11 & 3.75e-11 & 1.96e-11\\
-
-\newpage
+\section{Mixture distributions in a collaborative forecast project}
+\label{section:conmixforc}
+
+The CDC and the COVID-19 Forecast Hub as well as other collaborative projects
+have their own established systems for receiving, 
+evaluating and constructing ensemble forecasts. A transition from using binned 
+distributions or quantile forecasts to using discrete mixture distributions 
+nwould require
+a few adjustments to those systems. In this section we outline how some of these
+adjustments may be implemented as well as present some tools which may be used
+to evaluate forecasts and construct ensemble forecasts from multiple models.
+
+\subsection{Submission format}
+For a collaborative forecast project to run smoothly, model submissions from all 
+modelers should all follow the same format. For both the CDC flu forecasting and
+the COVID-19 Forecast Hub, teams are provided a .csv spreadsheet with columns 
+similar to those in tables \ref{table:dbins} and \ref{table:qstor}. Additionally
+columns for Location, Target, Type and Unit are included which serve as
+indicators of the specific prediction. The values for all variables except 
+Value come from a specified list from the forecast center. Value is the 
+probability assigned to a bin when the Type is Bin.
+
+\begin{table}[h!]
+\label{tab:dstan}
+\centering
+ \begin{tabular}{|c|c|c|c|c|c|}
+ \hline
+    Location & Target & Type & Unit & Bin & Value  \\ \hline
+    US National & Season Onset & Point & week & NA & . \\
+    US National & Season Onset & Bin & week & 0.0 & . \\
+    US National & Season Onset & Bin & week & 0.1 & . \\
+    ... & ... & ... & ... & ... & ... \\
+ \hline
+ \end{tabular}
+ \caption[Influenza competition submission example]{Example of a submission file
+ for an discretized forecast like those in the CDC influenza forecast 
+ competition. To match a quantile submission format as used by
+ the COVID-19 Forecast Hub, possible values for the variable Type are Point and
+ Quantile, the Bin column is replaced with a Quantile column and Value is 
+ the value of the specified quantile in the forecast.}
+ \label{table:dstan}
+\end{table}
+
+For the quantile forecasts of the Forecast Hub, the main changes to table
+\ref{tab:dstan} are that the possible values for Type 
+are Point and Quantile, and rather than using a Bin variable Quantile is used
+with values specified by the Hub. Then Value rather than a probability is the
+forecasted value for the specified quantile. Per prediction there may be a 
+couple dozen rows, up to 24 in the Forecast Hub, or over 100 rows as in some
+flu forecasts.
+
+In the discrete mixture format, an adjustment may be made to the format of table 
+\ref{table:dstan} where each 
+row
+represents a component in a mixture distribution.
+The variables Bin/Quantile and Value are removed and replaced with Family,
+Param1, Param2 and Weight where Family is the distribution family,
+Params are the parameters for the component distribution and Weight is the 
+weight $w_i$ for that component.
+
+\begin{table}[h!]
+\centering
+ \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+ \hline
+    Location & Target & Type & Unit & Family & Param1 & Param2 & Weight
+    \\ \hline
+    US National & Season Onset & Dist & week & norm & $\mu_n$ & $\sigma_n$ & .\\
+    US National & Season Onset & Dist & week & lnorm & $\mu_l$ & $\sigma_l$ &.\\
+    ... & ... & ... & ... & ... & ... & ... & .\\
+ \hline
+ \end{tabular}
+ \caption[Mixture distribution forecast submission example]{Example of a 
+ submission file
+ for a disease outbreak forecast using mixture distribution representation}
+ \label{table:dstan}
+\end{table}
+
+A forecast center may want to limit the number of components allowed per 
+prediction. For reference, a mixture distribution prediction following the 
+format in table \ref{table:dstan} with 18 
+components would require $18 \times 8 = 144$ cells submitted. This is the same 
+number of cells
+submitted for a Forecast Hub forecast with 23 quantiles and a point prediction 
+according to the format in table \ref{table:dstan}.
+
+Throughout the remainder of this section, explanations of how to work with 
+mixture distributions along with \texttt{R} code which will be given to 
+demonstrate constructing a mixture distribution from a forecast submission, 
+scoring the forecast and building an ensemble forecast.
+
+\subsection{Mixture construction and scoring tools}
+\label{section:tools}
+
+From a submitted forecast, a prediction may be found by Location, Target and 
+Unit (or whatever other indication variables are used by collaborators) and 
+evaluated. We found
+the \texttt{distr} package \cite{camphausen2007distr}
+useful for constructing a mixture distribution given
+information like that from table \ref{table:dstan}.
+
+The function 
+\texttt{UnivarMixingDistribution} takes as arguments a list of distributions
+and a vector of weights for each distribution and a object of class 
+\texttt{AbscontDistribution} is returned. The object is in essence a mixture
+distribution of the form of (\ref{eq:dmd}). Functions for density, 
+distribution
+and quantile functions as well as for random sampling may then be used on the
+mixture distribution object for evaluation. Using those functions and the 
+created object, LogS and CRPS are easily calculable.
+
+We wrote a function \texttt{MakeDist} (see Appendix)
+which takes on a data frame with variables
+Family, Param1, Param2, Param3 and Weight and returns a mixture distribution 
+of component distributions specified in the rows.
+
+Beginning with two forecast submissions of the form of table \ref{table:dstan}, 
+say we select from each a prediction of an event for the same location, target
+and unit. The following two data frames \texttt{preddf1} and \texttt{preddf2}
+are the resulting predictions.
+
+\begin{table}[h!]
+\centering
+ \begin{tabular}{|c|c|c|c|c|}
+ \hline
+    family & param1 & param2 & param3 & weight
+    \\ \hline
+    Lnorm & 2 & 1 & NA & 0.3  \\
+    Norm & 2.1 & 1 & NA & 0.7 \\
+ \hline
+ \end{tabular}
+ \caption[Toy prediction 1]{Toy prediction 1}
+ \label{tab:preddf1}
+\end{table}
+
+\begin{table}[h!]
+\centering
+ \begin{tabular}{|c|c|c|c|c|}
+ \hline
+    family & param1 & param2 & param3 & weight
+    \\ \hline
+    Norm & 1.5 & 1 & NA & 0.4  \\
+    Norm & 4 & 2 & NA & 0.6 \\
+ \hline
+ \end{tabular}
+ \caption[Toy prediction 2]{Toy prediction 2}
+ \label{tab:preddf2}
+\end{table}
+
+The code here shows these two data frames and how the \texttt{MakeDist} 
+function is used to create the distributions in \texttt{R}. Once the 
+distributions are created as \texttt{AbscontDistribution} classes, then 
+functions for evaluating a pdf and a CDF for each are created.
+
+<<eval = FALSE>>=
+preddf1
+#  family param1 param2 param3 weights
+#1  Lnorm    2.0      1     NA     0.3
+#2   Norm    2.1      1     NA     0.7
+
+preddf2
+#  family param1 param2 param3 weights
+#1   Norm    1.5      1     NA     0.4
+#2   Norm    4.0      2     NA     0.6
+
+#make mixture distributions from prediction submissions
+mdist1 <- MakeDist(preddf1)
+mdist2 <- MakeDist(preddf2)
+
+#make pdfs for mixture predictions
+dmdist1 <- function(x) {distr::d(mdist1)(x)}
+dmdist2 <- function(x) {distr::d(mdist2)(x)}
+
+#make cdfs for mixture predictions
+pmdist1 <- function(x) {distr::p(mdist1)(x)}
+pmdist2 <- function(x) {distr::p(mdist2)(x)}
+@
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.15]{Images/toyfors12.png}}
+\caption[Toy mixture distributions]{These plots show the density functions of
+the two toy mixture distribution forecasts along with the component density
+functions scaled by the corresponding weights}
+\label{fig:toymixs}
+\end{figure}
+
+The LogS or the CRPS may then be calculated for each forecast using the pdf
+and cdf functions respectively. Here will will assume that the realized value
+which both forecasts attempted to predict was 3. The \texttt{CRPS()} function 
+here is 
+included in the appendix of this manuscript. It can be seen here that by the 
+LogS, the forecast from table \ref{tab:preddf1} outperforms that from table
+\ref{tab:preddf2}. Yet under the CRPS the performance is the other way around.
+
+<<eval=FALSE>>=
+#realized observation
+ob <- 3
+
+#LogS for predictions at the realized observation
+-log(dmdist1(ob)) # => 1.547238
+-log(dmdist2(ob)) # => 1.848796
+
+#CRPS for predictions at the realized observation
+CRPS(pmdist1,y=ob) # => 0.6348212
+CRPS(pmdist2,y=ob) # => 0.5306083
+@
+
+\subsection{Ensemble construction}
+
+To construct an ensemble distribution from multiple mixture distributions, the 
+\texttt{UnivarMixingDistribution} is again a useful tool. The function takes 
+two or more
+\texttt{AbscontDistribution} or mixture distributions and a vector of weights 
+corresponding to each mixture. A new \texttt{AbscontDistribution} object is 
+returned as an ensemble of mixture distributions see (\ref{eq:bma}).
+
+At the onset of a collaborative forecast before the various models can be scored
+based on true observations, it may make sense to assign equal weight to each 
+component distribution in an ensemble. As a project progresses however, 
+assigning weights based on past performance may be desired. As mentioned in 
+section \ref{section:pardist}, weights may be selected by maximizing the
+likelihood of (\ref{eq:bma}) or by minimizing the CRPS. Another method of 
+selecting weights is to use the posterior model probability.
+
+If we have $T$ models ($M_t$) the posterior model probability of $M_t$ is 
+defined as
+
+\begin{equation}
+\label{eq:pmp}
+p(M_t|x) = \frac{p(x|M_t)p(M_t)}{p(x)}
+         = \frac{p(x|M_t)p(M_t)}{\sum_{k=1}^T p(x|M_k)p(M_k)}
+\end{equation}
+where $p(\cdot |M_t) := p_m(\cdot)$ is the density function of the model and 
+$p(M_j)$ is the prior probability assigned to the model. Where the prior
+probabilities for each model are equal or $p(M_t) = 1/T$ for all $t$ 
+(\ref{eq:pmp}) is reduced to
+
+\begin{equation}
+\label{eq:pmpeq}
+p(M_t|x) =  \frac{p(x|M_t)}{\sum_{k=1}^Tp(x|M_k)}
+\end{equation}
+
+The posterior model probability $p(M_t|x^*)$ for an already observed event $x^*$
+are then used as weights for a yet unrealized event being forecasted i.e.
+$w_t := p(M_t|x^*)$ see (\ref{eq:bma}).
+
+From the same toy problem in the previous section, the following code shows how
+to use the posterior model probability to select weights and construct an 
+ensemble distribution and score the ensemble forecast. The ensemble distribution
+with components is show in figure \ref{fig:mixense}.
+
+<<eval=FALSE>>=
+#posterior model probability for calculating weights
+w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
+w2 <- 1-w1
+#w1 => 0.5286434
+#w2 => 0.4713566
+
+#build ensemble with calculated weights
+ensdist <- distr::UnivarMixingDistribution(mdist1,
+                                           mdist2,
+                                           mixCoeff = c(w1,w2))
+
+#pdf and cdf for ensemble
+densdist <- function(x) {(distr::d(ensdist)(x))}
+pensdist <- function(x) {(distr::p(ensdist)(x))}
+
+#LogS for predictions at the realized observation
+-log(densdist(ob)) # => 1.678156
+
+#CRPS for predictions at the realized observation
+CRPS(pensdist,y=ob) # => 0.5486368
+@
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.15]{Images/mix_ense.png}}
+\caption[Toy ensemble forecast]{Toy ensemble forecast with component mixture
+distributions shown}
+\label{fig:mixense}
+\end{figure}
+
+% \subsection{Mixture approximation of sample distribution}
 
 \section{Retrospective Analysis}
+\label{section:retrostud}
+
+For large collaborative forecast projects having already established the 
+representation formats for forecasting, it may be difficult for individual
+forecast teams to adjust to a discrete mixture distribution format. Exact 
+methods for modeling and forecasting may not cater well to submitting a forecast
+as a discrete parametric mixture distribution.
+
+In this section we attempt to assess whether or not any forecasts from the CDC
+influenza forecast competition and the COVID-19 Forecast Hub were generated from
+common continuous parametric distributions. The forecasts we assess are in the 
+forms of discretized bin predictions or sets of predictive intervals. In these
+formats, not knowing anything about distributions or samples,  formal 
+statistical methods for fitting to parametric distributions 
+and assessing fit do not exist. Thus any results stated here may not be stated
+in terms of statistical certainty.
 
@@
 The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
-850,000 probabilistic ILI predictions for all combinations of of eleven regions 
+850,000 probabilistic influenza-like illness predictions for all combinations
+of eleven regions 
 in the United States and seven targets from twenty-seven different models. These
@@
 
-We wanted to determine whether or not some or any of these binned forecasts may
-have come from known continuous distribution families such as Uniform, Normal, 
-Lognormal or Gamma families. The process we followed for making such a claim was
-to "fit" a distribution to the probabilities provided in the forecast by
+We wanted to determine whether or not some or any of these binned forecasts were
+generated from known uniform, normal, 
+lognormal or gamma continuous distribution families. 
+The process we followed for making such a claim was
+to fit a distribution to the probabilities provided in the forecast by
 minimizing
@@
   \sum_{i=1}^K (p_i - [F(b_i; \theta) - F(b_{i-1}; \theta)])^2
+  \label{eq:mds}
 \end{equation}
@@
 [F(b_i; \theta) - F(b_{i-1}; \theta)])^2
-\end{equation}
-
-If well known continuous distribution was fit to the submitted binned prediction
-and the mean sum of squared differences fell below a specified cutoff value, we
+\label{eq:discfit}
+\end{equation}
+
+If a well known continuous distribution was fit to the submitted binned 
+prediction
+and the mean sum of squared differences (MSD) or \ref{eq:msd} fell below a 
+specified cutoff value, we
 considered that the binned predictions were plausibly discretized from the 
@@
 binned distributions were discretized from known continuous distributions, 
-parameters were fit to the binned distrubtions and the mean sum of squared 
-differences was calculated.
-
-For each of Uniform, Truncated Normal (TN), Truncated Lognormal (TL) and 
-Truncated Gamma (TG) distributions the following was
+parameters were fit to the binned distrubtions and the MSD was calculated.
+
+For each of uniform, truncated normal (TN), truncated lognormal (TL) and 
+truncated gamma (TG) distributions the following was
 done 1,000 times. A set of 131 bins with interval lengths of 
@@
 the center and scale parameters of a TN distribution. 
-For Uniform, TL and TG family
+For uniform, TL and TG family
 distributions, model parameters were solved for so that $\mu$ and $\sigma$ 
 were roughly the mean and standard deviation. The minimization was done using 
-the `optim` function in the R `stats` package.
+the \texttt{optim} function in the \texttt{R} \texttt{stats} package.
 Had we accounted for the changes
@@
 With a known distribution, probabilities $p_i =F(b_i; \theta) - F(b_{i-1})$ were
-calculated for each bin. A Uniform or truncated distribution from the same
-family was fit to the bins by minimizing (equation number) with the resulting
-distribution function $F(\cdot; \hat{theta})$. From the fitted distribution
+calculated for each bin. A uniform or truncated distribution from the same
+family was fit to the bins by minimizing \ref{eq:msd} with the resulting
+distribution function $F(\cdot; \hat{\theta})$. From the fitted distribution
 $\hat{p_i} = F(b_i; \hat{\theta}) - F(b_{i-1}; \hat{\theta})$ was computed for 
 each of the 131 bins. Finally the mean sum of squared probability differences
-$\frac{1}{K}\sum_{i=1}^K (\hat{p_i} - p_i)^2$ was calculated. Table (table number)
-below shows MSD value for which 95\% of all 1,000 MSDs fell below. Other than in
-the case of the Uniform distribution family, those values were selected as the 
+$\frac{1}{K}\sum_{i=1}^K (\hat{p_i} - p_i)^2$ was calculated. 
+Table \ref{table:bincutoffs}
+below shows MSD value for which 95\% of all 1,000 MSDs fell below. Those values 
+were selected as the 
 cutoff values for declaring whether or not a binned distribution was discretized
@@
   \begin{tabular}{l*{6}{c}r}
-  Distribution          & Mean Square Difference 95\%  \\
+  Distribution          & MSD 95\%  \\
   \hline
@@
   \end{tabular}
+  \caption[Discretized bin distribution cutoff values]{If a binned 
+  distribution is fit to a parametric distribution and the MSD is smaller than
+  the corresponding cutoff value listed here, we consider that binned 
+  distribution to have been discretized from the fit parametric distribution.}
+  \label{table:bincutoffs}
 \end{table}
@@
 distribution with the lowest MSD was considered the best fit and if the MSD fell
-below the corresponding cutoff value listed in (table number) we consider that 
-the prediction approximately follows the fit distribution. The results for the
-11,715 fit distributions are seen below.
+below the corresponding cutoff value listed in \ref{table:bincutoffs} we 
+considered that 
+the prediction was discretized from the fit distribution.
+
+Of the 11,715 binned distributions fit to continuous parametric distributions,
+2,502 of those fits producted MSD values below the values listed in table
+\ref{table:bincutoffs}. Thus we conclude that a proportion of 0.214 of those
+forecasts were generated from a common parametric distribution. The results for 
+the
+11,715 fit distributions, which families the binned distributions were best
+fit to and whether or not the fits produce an MSD below the cutoff value, 
+are seen in table \ref{table:cdcresults}. Figure \ref{fig:binparamfits} is an
+example of
+the best fit distributions to the same binned probability distribution.
 
@@
   \begin{tabular}{l*{6}{c}r}
-  Distribution Family   & Total    & Total Below MSD Cutoff \\
-  \hline
-  Uniform               & 896      & 669    \\
-  Truncated Normal      & 3,804    & 198    \\
-  Truncated Lognormal   & 4,501    & 1,340  \\
-  Truncated Gamma       & 2,514    & 295    \\
+  Distribution Family   & Total    & Total below MSD cutoff value 
+  & Proportion from parametric distribution\\
+  \hline
+  Uniform               & 896      & 669  & 0.747  \\
+  Truncated Normal      & 3,804    & 198  & 0.052  \\
+  Truncated Lognormal   & 4,501    & 1,340 & 0.289 \\
+  Truncated Gamma       & 2,514    & 295   & 0.117 \\
   \end{tabular}
+  \caption[CDC influenza retro analysis results]{Results for CDC influenza
+  forecast retro analysis}
+  \label{table:cdcresults}
 \end{table}
 
-% \begin{figure}[h]
-% \caption{Write the caption here.}
-% % \vspace{0.0cm} \centering
-% \centering
-%     \subfloat[label 1]{{\includegraphics[width=1cm]{flu_fit_img/_flu_fit_1_10_2_.png} }}
-%     \qquad
-%     \subfloat[label 2]{{\includegraphics[width=1cm]{flu_fit_img/_flu_fit_1_10_6_.png} }}
-%     \caption{2 Figures side by side}
-%     \label{fig:example}
-% % \includegraphics[height=5.4cm]{flu_fit_img/_flu_fit_1_10_2_.png}
-% % \includegraphics[height=5.4cm]{flu_fit_img/_flu_fit_1_10_6_.png}
-% % \includegraphics[height=5.4cm]{flu_fit_img/_flu_fit_3_11_2_.png}
-% % \includegraphics[height=5.4cm]{flu_fit_img/_flu_fit_3_11_4_.png}
-% % \includegraphics[height=5.4cm]{allimages/fig3.eps}
-% % \includegraphics[height=5.4cm]{allimages/fig4.eps}
-% % \includegraphics[height=5.4cm]{allimages/fig5.eps}
-% % \includegraphics[height=5.4cm]{allimages/fig6.eps}
-% \end{figure}
-% \begin{adjustwidth}{-3cm}{-1cm}
-% \begin{figure}[htbp]
-% 
-%     \centering
-%     \subfloat[1]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_1_10_2_.png}}}
-%     \hfill
-%     \subfloat[2]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_1_10_6_.png}}}
-%     \hfill
-%     \subfloat[1]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_3_11_2_.png}}}
-%     \hfill
-%     \subfloat[2]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_3_11_4_.png}}}
-% 
-%     \subfloat[1]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_5_6_1_.png}}}
-%     \hfill
-%     \subfloat[2]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_5_6_2_.png}}}
-%     \hfill
-%     \subfloat[1]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_5_10_4_.png}}}
-%     \hfill
-%     \subfloat[2]{{\includegraphics[width=0.5\textwidth]{flu_fit_img/_flu_fit_5_10_6_.png}}}    
-%     \caption{graphs}%
-% 
-% \end{figure}
-% \end{adjustwidth}
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.15]{Images/flu_fit_17_10_3.png}}
+\caption[Parametric distribution fits to binned distribution]{This figure shows
+the plots of fits from each a uniform, truncated normal, truncated lognormal
+and truncated gamma distributions to the same binned probability distribution.
+In this case, the fit to the normal distribution produced an MSD below the 
+normal cutoff value, so we conclude that the binned distribution may have been
+discretized froma truncated normal.}
+\label{fig:binparamfits}
+\end{figure}
 
@@
 for these predictions is the quantile representation where a point estimated is
-submitted along with a number of confidence intervals -three or eleven for most
-targets. So the predictions typically include seven or twenty-three quantiles.
-
-To assess whether or not a quantile based forecast was formulated from a well
-known continuous distribution, we minimized the MSE between the cumulative
-density function and the given quantiles. The estimated parameters are the 
+submitted along with a number of confidence intervals -three or 11 for most
+targets. So the predictions typically include seven or 23 quantiles.
+
+To assess whether or not a quantile based forecast was calculated from a well
+known continuous distribution, we minimized the mean square error (MSE) between 
+the CDF and the given quantiles. The estimated parameters are the 
 solution to $argmin_{\theta} \sum_{i=1}^m (q_i - F(y; \theta))$ where $q_i$ is
@@
 
-For each prediction used, we fit the quantiles to a Uniform, Normal, Lognormal,
-Gamma and Location-scale T CDF. We included the T distribution in case of any
-symmetric forecasts with tails heavier than in a Normal distribution.
+For each prediction used, we fit the quantiles to a uniform, normal, lognormal,
+gamma and location-scale t CDF. We included the t distribution in case of any
+symmetric forecasts with heavier tails than in a normal distribution.
 
@@
 
-A decision was made on creating a quantile distribution with 7 quantiles or 23
+A decision was randomly made on creating a quantile distribution with seven 
+quantiles or 23
 quantiles with probabilities 1/3 and 2/3 respectively. This was done because 
-in the COVID-19 Forecast Hub certain targets require 7 quantiles and others 
+in the COVID-19 Forecast Hub certain targets require seven quantiles and others 
 require 23. After that decision was made, a random value $\mu$ was drawn from
@@
 proper transformations computed to find model parameters corresponding to the 
-distribution. Quantile values were calculated for each quantile. When using an 
-LST distribution, a value for degrees of freedom was drawn from a 
+distribution. Quantile values were calculated for each quantile. When using a 
+t distribution, a value for degrees of freedom was drawn from a 
 $Uniform(2,35)$ distribution. A CDF
 was fit by minimizing $\sum_{i=1}^m (q_i - F(y; \theta))$ over the parameter
-vector $\theta$ and the MSD value $\sum_{i=1}^m (q_i - F(y; \hat{\theta}))$ was 
-calculated. The MSD value for which 95\% of the 1,000 simulated distributions
-fell below was considered the cutoff and is seen in the table below.
+vector $\theta$ and the MSE value $\sum_{i=1}^m (q_i - F(y; \hat{\theta}))$ was 
+calculated. The MSE value for which 95\% of the 1,000 simulated distributions
+fell below was considered the cutoff and is seen in table 
+\ref{table:quantcutoffs}.
 
@@
   \begin{tabular}{l*{6}{c}r}
-  Distribution          & Mean Square Difference 95\%  \\
+  Distribution          & Mean Square Error 95\%  \\
   \hline
@@
   \end{tabular}
+  \caption[Quantile cutoff values]{If a set of quantiles
+  is fit to a parametric distribution CDF and the MSE is smaller than
+  the corresponding cutoff value listed here, we consider the quantiles to 
+  have been calculated parametric distribution.}
+  \label{table:quantcutoffs}
 \end{table}
@@
 specified above, we considered that the quantile prediction was approximately
-from the same distribution as the fit distribution. The results are below.
+from the same distribution as the fit distribution. Of the 2,504 fits, 99 of 
+them produced an MSE value below the corresponding cutoff. Results for fits by
+distribution are seen in table \ref{table:cresults}.
+Figures \ref{fig:qqfits} and \ref{fig:cdffits} show the QQ plots and CDF plots
+for different distribution fits to the same set of quantiles.
 
@@
   \begin{tabular}{l*{6}{c}r}
-  Distribution Family   & Total    & Total Below MSD Cutoff \\
-  \hline
-  Uniform               & 239      & 0        \\
-  Normal                & 609      & 74       \\
-  Lognormal             & 694      & 0        \\
-  Gamma                 & 597      & 0        \\
-  Location-scale T      & 365      & 25       \\
+  Distribution Family   & Total    & Total below MSE cutoff 
+  & Proportion from parametric distribution\\
+  \hline
+  Uniform               & 239      & 0    & 0    \\
+  Normal                & 609      & 74   & 0.122    \\
+  Lognormal             & 694      & 0    & 0    \\
+  Gamma                 & 597      & 0    & 0    \\
+  Location-scale T      & 365      & 25   & 0.068    \\
   \end{tabular}
+  \caption[COVID-19 Forecast Hub results]{Results for COVID-19 Forecast Hub
+  retro analysis}
+  \label{table:cresults}
 \end{table}
 
-\section{...}
-
-The CDC and the COVID-19 Forecast Hub as well as other collaborative projects
-have their own established systems for receiving, 
-evaluating and constructing ensemble forecasts. A transition from using binned 
-distributions or quantile forecasts to using mixture distributions would require
-a few adjustments to those systems. In this section we outline how some of these
-adjustments may be implemented as well as present some tools which may be used
-to evaluate forecasts and construct ensemble forecasts from multiple models.
-
-\subsection{Submission format}
-For a collaborative forecast project to run smoothly, model submissions from all 
-modelers should all follow the same format. For both the CDC flu forecasting and
-the COVID-19 Forecast Hub, teams are provided a csv spreadsheet with columns 
-similar to those in tables \ref{tab:dstor} and \ref{tab:qstor}. Additionally
-columns for Location, Target, Type and Unit are included which serve as
-indicators of the specific prediction. The values for all variables except 
-Value come from a specified list from the forecast center. Value is the 
-probability assigned to a bin when the Type is Bin.
-
-\begin{table}[h!]
-\label{tab:dstan}
-\centering
- \begin{tabular}{|c|c|c|c|c|c|}
- \hline
-    Location & Target & Type & Unit & Bin & Value  \\ \hline
-    US National & Season Onset & Point & week & NA & . \\
-    US National & Season Onset & Bin & week & 0.0 & . \\
-    US National & Season Onset & Bin & week & 0.1 & . \\
-    ... & ... & ... & ... & ... & ... \\
- \hline
- \end{tabular}
-\end{table}
-
-For the quantile forecasts of the Forecast Hub, the possible values for Type 
-are Point and Quantile, and rather than using a Bin variable Quantile is used
-with values specified by the Hub. Then Value rather than a probability is the
-forecasted value for the specified quantile. Per prediction there may be a 
-couple dozen rows, up to 24 in the Forecast Hub, or over 100 rows as in some
-flu forecasts.
-
-An adjustment may be made to the format of table \ref{tab:dstan} where each row
-represents a compnonent in a mixture distribution.
-The variables Bin/Quantile and Value are removed and replaced with Family,
-Param1, Param2, Param3 and Weight where Family is the distribution family,
-Params are the parameters for the component distribution and Weight is the 
-weight $w_i$ for that component.
-
-\begin{table}[h!]
-\label{tab:mstan}
-\centering
- \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
- \hline
-    Location & Target & Type & Unit & Family & Param1 & Param2 & Param3 & Weight
-    \\ \hline
-    US National & Season Onset & Dist & week & norm & mean & sd & NA & .  \\
-    US National & Season Onset & Dist & week & lnorm & meanlog & sdlog & NA & . \\
-    ... & ... & ... & ... & ... & ... & ... & ... & .\\
- \hline
- \end{tabular}
-\end{table}
-
-A forecast center may want to limit the number of components allowed per 
-prediction. For a reference, a mixture distribution prediction with 16 
-components would require $16 \times 9 = 144$ cells submitted. This is the same 
-number of cells
-submitted for a Forecast Hub forecast with 23 quantiles and a point prediction.
-
-\subsection{Mixture construction and scoring tools}
-
-From a submitted forecast, a prediction may be found by Location, Target and 
-Unit (or whatever other indication variables are used by collaborators) and 
-evaluated. We found
-the \texttt{distr} \cite{camphausen2007distr}
-useful for constructing a mixture distribution given
-information like that from table \ref{tab:mstan}.
-
-The function 
-\texttt{UnivarMixingDistribution} takes as arguments a list of distributions
-and a vector of weights for each distribution and a object pf a class called 
-\texttt{AbscontDistribution} is returned. The object is in essence a mixture
-distribution of the form from (\ref{eq:dmd}). Functions for density, 
-distribution
-and quantile functions as well as for random sampling may then be used on the
-mixture distribution object for evaluation. Using those functions and the 
-created object, LogS and CRPS are easily calculable.
-
-We wrote a function \texttt{MakeDist} (see appendix)
-which takes on a data frame with variables
-Family, Param1, Param2, Param3 and Weight and returns a mixture distribution 
-of component distributions specified in the rows.
-
-\subsection{Ensemble construction}
-
-To construct an ensemble distribution from multiple mixture distributions, the 
-\texttt{UnivarMixingDistribution} is again a useful tool. The function takes 
-two or more
-\texttt{AbscontDistribution} or mixture distributions and a vector of weights 
-corresponding to each mixture. A new \texttt{AbscontDistribution} object is 
-returned as an ensemble of mixture distributions see (\ref{eq:bma}).
-
-At the onset of a collaborative forecast before the various models can be scored
-based on true observations, it may make sense to assign equal weight to each 
-component distribution in an ensemble. As a project progresses however, 
-assigning weights based on past performance may be desired. As mentioned in 
-section \ref{section:pardist}, weights may be selected by maximizing the
-likelihood of (\ref{eq:bma}) or by minimizing the CRPS. Another method of 
-selecting weights is to use the posterior model probability.
-
-If we have $T$ models ($M_t$) the posterior model probability of $M_t$ is 
-defined as
-
-\begin{equation}
-\label{eq:pmp}
-p(M_t|x) = \frac{p(x|M_t)p(M_t)}{p(x)}
-         = \frac{p(x|M_t)p(M_t)}{\sum_{k=1}^T p(x|M_k)p(M_k)}
-\end{equation}
-where $p(\cdot |M_t) := p_m(\cdot)$ is the density function of the model and 
-$p(M_j)$ is the prior probability assigned to the model. Where the prior
-probabilities for each model are equal or $p(M_t) = 1/T$ for all $t$ 
-(\ref{eq:pmp}) is reduced to
-
-\begin{equation}
-\label{eq:pmpeq}
-p(M_t|x) =  \frac{p(x|M_t)}{\sum_{k=1}^Tp(x|M_k)}
-\end{equation}
-
-The posterior model probability $p(M_t|x^*)$ for an already observed event $x^*$
-are then used as weights for a yet unrealized event being forecasted i.e.
-$w_t := p(M_t|x^*)$ see (\ref{eq:bma}).
-
-\subsection{Toy Example}
-
-In the following example, a toy example is given of constructing two  
-mixture distribution forecast prediction models from separate forecast 
-submissions. The tools presented in this section are used in \texttt{R} code to
-construct the distributions, build an ensemble consisting of both predictions 
-and score the different models. In building the ensemble forecast, weights are
-selected using the posterior model probability with equal prior probabilities
-for both models (\ref{eq:pmpeq}).
-
-Beginning with two forecast submissions of the form of table \ref{tab:mstan}, 
-say we select from each a prediction of an event for the same location, target
-and unit. The following two data frames \texttt{preddf1} and \texttt{preddf2}
-are the resulting predictions.
-
-\begin{table}[h!]
-\label{tab:preddf1}
-\centering
- \begin{tabular}{|c|c|c|c|c|}
- \hline
-    family & param1 & param2 & param3 & weight
-    \\ \hline
-    Lnorm & 2 & 1 & NA & 0.3  \\
-    Norm & 2.1 & 1 & NA & 0.7 \\
- \hline
- \end{tabular}
-\end{table}
-
-\begin{table}[h!]
-\label{tab:preddf2}
-\centering
- \begin{tabular}{|c|c|c|c|c|}
- \hline
-    family & param1 & param2 & param3 & weight
-    \\ \hline
-    Norm & 1.5 & 1 & NA & 0.4  \\
-    Norm & 4 & 2 & NA & 0.6 \\
- \hline
- \end{tabular}
-\end{table}
-
-The following code in \texttt{R} will construct mixture distributions, select
-weights for an ensemble based on an observed realization, build the ensemble and 
-score the forecasts using the
-LogS and the CRPS.
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.15]{Images/qq_11_12_5.png}}
+\caption[QQ plot for quantile fit]{This figure shows qq plots for a set of
+submitted quantiles against the quantiles the continuous distribution to which
+it was fit. In no case here was the MSE below the cutoff value of the 
+corresponding distribution.}
+\label{fig:qqfits}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.15]{Images/cdf_11_12_5.png}}
+\caption[CDF plot for quantile fit]{This figure shows the CDF plots for 
+distributions fit to a set of quantiles. The grey line is a line of connected 
+dots from the submitted quantiles and values. 
+In no case here was the MSE below the cutoff value of the 
+corresponding distribution.}
+\label{fig:cdffits}
+\end{figure}
+
+The results in the previous two studies suggest that in some cases, forecasters
+are using methods which produce simple parametric distribution forecasts. Many
+likely are not. To improve upon these studies, one could fit the binned 
+influenza forecasts or the COVID-19 quantile forecasts to discrete mixture 
+distributions with multiple components. Forecasts that are very close to 
+a mixture distribution may suggest that the forecasters already have models that
+make transition to a discrete mixture distribution forecast format easy or
+straightforward.
 
 \newpage
-\begin{lstlisting}[language=R]
-
-preddf1
-#  family param1 param2 param3 weights
-#1  Lnorm    2.0      1     NA     0.3
-#2   Norm    2.1      1     NA     0.7
-
-preddf2
-#  family param1 param2 param3 weights
-#1   Norm    1.5      1     NA     0.4
-#2   Norm    4.0      2     NA     0.6
-
-#make mixture distributions from prediction submissions
-mdist1 <- MakeDist(preddf1)
-mdist2 <- MakeDist(preddf2)
-
-#make pdfs for mixture predictions
-dmdist1 <- function(x) {distr::d(mdist1)(x)}
-dmdist2 <- function(x) {distr::d(mdist2)(x)}
-
-#make cdfs for mixture predictions
-pmdist1 <- function(x) {distr::p(mdist1)(x)}
-pmdist2 <- function(x) {distr::p(mdist2)(x)}
-
-#realized observation
-ob <- 3
-
-#posterior model probability for calculating weights
-w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
-w2 <- 1-w1
-#w1 => 0.5286434
-#w1 => 0.4713566
-
-#build ensemble with calculated weights
-ensdist <- distr::UnivarMixingDistribution(mdist1,
-                                           mdist2,
-                                           mixCoeff = c(w1,w2))
-
-#pdf and cdf for ensemble
-densdist <- function(x) {(distr::d(ensdist)(x))}
-pensdist <- function(x) {(distr::p(ensdist)(x))}
-
-#LogS for predictions at the realized observation
--log(dmdist1(ob)) # => 1.547238
--log(dmdist2(ob)) # => 1.848796
--log(densdist(ob)) # => 1.678156
-
-#CRPS for predictions at the realized observation
-CRPS(pmdist1,y=ob) # => 0.6348212
-CRPS(pmdist2,y=ob) # => 0.5306083
-CRPS(pensdist,y=ob) # => 0.5486368
-\end{lstlisting}
-
-Figure \ref{figmixs} below shows the density plots for each of the two mixture
-distribution forecasts and the ensemble from the toy example.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[scale=.15]{mix_dists.png}}
-\caption{Figure this out later}
-\label{figmixs}
-\end{figure}
 
@@
 comparable to discretized bins and interval forecasts but also provides a 
-forecast with a continuous nominal resolution. Thus we advocate its use in
+forecast with a infinite nominal resolution. Thus we advocate its use in
 future forecasting projects like those done by the CDC and COVID-19 Forecast 
@@
 For a number of reasons, the adoption of finite mixture distributions as the
-submission format may face hurdles. A forecast hub, along with modelers, using a 
+submission format may face hurdles. A collaborative forecast center, along with 
+forecasters, using a 
 different representation may simply not want to break from tradition. The 
@@
 
-% Variables of R dataframe to b used in making mixture distribution 
-% \begin{center}
-%     \begin{tabular}{ | l | p{4cm} | p{7cm} |}
-%     \hline
-%     Argument & Summary & Options \\ \hline
-%     dist & A string specifying a distribution family.  & “Beta”, “Cauchy”, 
-%     “Lnorm”, “Logis”, “Unif”, “Lst” (location scale t distribution), 
-%     “Weibull”, “Fd”, “Norm”,  “Chisq”, 
-%     “Gammad”, “Exp”
-% 	 “Binom”, “Dirac”, “Pois”, “Hyper”, “Nbinom”, “Geom” \\ \hline
-%     param1 & A real number specifying the first parameter value of the 
-%     distribution. & Beta: shape1; 
-% 	Cauchy: location; 
-% 	Lnorm: meanlog; 
-% 	Logis: location; 
-% 	Unif: min; 
-% 	Lst: location; 
-% 	Weibull: shape;
-% 	Fd: df1;
-% 	Norm: mean;
-% 	Chisq: df;
-% 	Gammad: scale;
-% 	Exp: rate; 
-% 	Binom: size;
-% 	Dirac: location;
-% 	Pois: lambda;
-% 	Hyper: m;
-% 	Nbinom: n;
-% 	Geom: prob
-%      \\ \hline
-%     param2 & A real number specifying the second parameter value of the 
-%     distribution. & Beta: shape2; 
-% 	Cauchy: scale; 
-% 	Lnorm: slog; 
-% 	Logis: scale; 
-% 	Unif: Max; 
-% 	Lst: scale; 
-% 	Weibull: scale; 
-% 	Fd: df2; 
-% 	Norm: sd; 
-% 	Chisq: ncp; 
-% 	Gammad: shape; 
-% 	Binom: prob; 
-% 	Hyper: n; 
-% 	Nbinom: p \\
-%     \hline
-%     param3 & A real number specifying the third parameter value of the 
-%     distribution. & Lst: df;
-% 	Hyper: k \\
-% 	\hline
-% 	weight & A real number between 0 and 1 specifying the weight given to the 
-% 	distribution in the overall mixture distribution. The sum of the weight 
-% 	column should equal 1. & ...
-% 	\\
-% 	\hline
-%     \end{tabular}
-% \end{center}
-
-% \newpage
-% % \begin{adjustwidth}{-3cm}{-1cm}
-% \begin{center}
-% % \caption{MakeDist parameter options}
-%     \begin{tabular}{ l l  p{2cm}  p{2cm}  p{2cm}}
-%     \hline
-%     \textbf{Distribution} & \textbf{dist} & \textbf{param1} & \textbf{param2} & 
-%     \textbf{param3} \newline \\ \hline
-%     Beta & Beta & shape1 & shape2 &  \\ 
-%     Cauch & Cauchy & location & scale &  \\
-%     Log-normal & Lnorm & meanlog & slog &  \\
-%     Logistic & Logis & location & scale &  \\
-%     Uniform & Unif & min & max &  \\
-%     Location Scale T & Lst & location & scale & df \\
-%     Weibull & Weibull & shape & scale &  \\
-%     F & Fd & df1 & df2 &  \\
-%     Normal & Norm & mean & sd &  \\
-%     Chisqure & Chisq & df &  &  \\
-%     Gamma & Gammad & scale & shape &  \\
-%     Exponential & Exp & rate &  &  \\
-%     Binomial & Binom & size & prob &  \\
-%     Dirac & Dirac & location &  &  \\
-%     Poisson & Pois & lambda &  &  \\
-%     Hypergeometric & Hyper & m & n & k \\
-%     Negative binomial & Nbinom & n & p &  \\
-%     Geometric & Geom & prob &  &  \\ \hline
-%     \end{tabular}
-% \end{center}
-% % \end{adjustwidth}
-
-\newpage
-
-\section*{everything below here is just notes for now}
-
-Even as computing power and memory storage continue to improve, 
-A single probabilistic forecast can range from only a few pieces of data, such 
-as a well known distribution family and two given parameters, to thousands or
-tens of thousands of MCMC draws from a posterior distribution. When a repository
-of forecasts contains many millions of individual prediction distributions, such
-as the COVID-19 Forecast Hub \cite{Cramer2021-hub-dataset}, large file type forecasts can become a 
-problem. (Say something about MechBayes posterior samples vs. quantile version
-of the forecast).
-Something about ensemble storage...
-
-Bogner, Liechti and Zappa compared scoring forecasts of quantiles with the 
-Quantile Score similar to the interval score and scoring distribution functions
-fit to those quantiles using CRPS \cite{bogner2017combining}. 
-The CRPS proves more effective than QS in 
-revealing model issues especially in the tails.
-
-Depending on the forecast representation, certain scoring rules may not work to 
-assess a forecast. For example, for a quantile or interval representation, LogS
-and CPRS may not be used. The weighted interval score was used by Bracher et. al
-to evaluate forecasts collected by the COVID-19 Forecast Hub. 
-\cite{bracher2021evaluating}
-
-As the number of quantiles required increases, so does the per forecast storage 
-requirment. In the COVID-19 Forecast Hub, $23\times 2 = 46$ pieces of 
-information are required for certain targets. And because quantiles are easily 
-obtained from most methods of probabilistic modeling, teams have much 
-flexibility in the type of modeling they perform.
-
-Ensemble modeling under quantiles is done by averaging each quantile over all 
-forecast models. Weighting the models based on past performance may be done, but
-may not always prove worth the effort. (cite??) A shortcoming of quantile
-averaging is the limit that ensemble distributions shapes may take. It has been
-shown that quantile averaging may only produce quantiles for distributions which
-are unimodal. (cite??) Another shortcoming is that not all proper scoring
-methods are appropriate in scoring quantile forecasts. The log-score may not be 
-used for example. There are, however, alternatives for scoring such as the
-weighted interval score. (cite??)
-
-\subsection*{Above quantiles below bins}
-
-Thus point estimates and
-probabilities are easily calculated and proper scoring of each forecast may be 
-done with the usual methods.
-
-To build an ensemble forecast from several individual forecasts, each bin may be
-averaged over all forecasts. This may be done with or without weighting of the 
-various models and the weights if selected may be assigned using the same 
-methods that may be used for parametric distribution forecasts.
-
-The discretized representation can provide distributions with reasonably high
-resolution but with some cost. As the width of the bins decreases, the 
-resolution increases but the storage increases. The number of bins may range 
-from a few dozen to hundreds requiring just as many rows in a data table and at 
-least two columns. The CDC for example reuqired participants to submit 
-probabilities for 51 bins per forecast in the influenza forecasting competition. 
-Each team then, had to submit $51\times2 = 102$ pieces of information.
-
-\subsection*{Above bins, below pdfs}
-
-Where a forecast hub requests a parametric distribution as a forecast, a 
-submission of three or four cells of data per forecast may suffice making this
-representation very efficient for storage. (See table ??)
-That little information is enough to provide a high resolution forecast over
-all possible values of the forecast. Evaluation of parametric forecasts may be 
-done using most proper scoring methods such as the log-scoring method
-\cite{gneiting2007strictly}
-or modifications of the log-scoring method such as that used by the CDC in 
-influenza forecasting \cite{reich2019collaborative}.
-
-In building an ensemble forecast, a discrete mixture distribution may be used.  
-To construct a mixture distribution suppose there are $J$ forecasts represented
-by parametric distributions with probability density functions $p_j(y|\theta)$ 
-for $j = 1,..,J$. A mixture distribution of the $J$ forecasts is
-
-$$p^{E}(y|\theta) = \sum_{j=1}^{J} w_j p_j(y|\theta)$$
-where $w_j > 0$ and $\sum_{j=1}^{J} = 1$ are weights assigned to each to each 
-component. Equal weights may be assigned to each forecast so $w_j = 1/J$ for all
-$j$ or they may be determined by the accuracy and precision of the individual
-forecast. Bayesian model averaging \cite{raftery2005using}
-is one reasonable way to select weights, though there are
-
-A drawback of representing a forecast in a parametric distribution is the lack 
-of flexibility in the model selection. Easy computation and evaluation of these 
-models is limited to what is available in software, so certain distributional
-shapes may unattainable. The distribution may assign probability to values
-outside the range of the forecast. There are remedies for this such as 
-truncation, but these increase the complexity in evaluation and scoring.
-Requiring a parametric forecast also bars the use of some statistical methods
-which might be used including certain Bayesian methods.
-
-\begin{table}[h!]
-\centering
- \begin{tabular}{||c c c c||} 
- \hline
- Family & param1 & param2 & param3 \\ [0.5ex] 
- \hline\hline
- normal & $\hat{\mu}$ & $\hat{\sigma}$ & NA \\ 
- lst & $\hat{\mu}$ & $\hat{\sigma}$ & $\hat{\nu}$ \\ [1ex] 
- \hline
- \end{tabular}
-\end{table}
-
-\subsection*{Information}
-
-\newpage    
-\bibliographystyle{apacite}
-\bibliography{references}
+% \include{Body/ch1/ch1_main}
+% \include{Body/ch2/ch2_main}
+% \include{Body/ch3/ch3_main}
+% \include{Body/ch4/ch4_main}
+% \include{Body/ch5/ch5_main}
+%\include{Body/ch6/ch6_future_and_conclusions}
+
+%\bibliographystyle{acm} % use for numbered citations along with options given in preamble. Look at the main thesis.tex file
+\bibliographystyle{apa}
+\bibliography{master_bib}
+
+\section{Appendix}
+
+The following is the code to make the \texttt{MakeDist()} function introduced 
+in \ref{section:tools}.
+<<eval=FALSE>>=
+MakeDist <- function(distsdf){
+
+  distdf <- distsdf[distsdf[,1] != 'Lst',]
+  tdist <- distsdf[distsdf[,1] == 'Lst',]
+
+  fun_dist <- 
+    apply(distdf, FUN=function(x) {
+      paste('distr::',x[1], '(', 
+            ifelse(!is.na(x[2]) & (!is.na(x[3]) | !is.na(x[4])),
+                   paste(x[2],',',sep=''),
+                   ifelse(!is.na(x[2]) & is.na(x[3]) & is.na(x[4]),
+                          x[2], '')), 
+            ifelse(!is.na(x[3]) & !is.na(x[4]),
+                   paste(x[3],',',sep=''),
+                   ifelse(!is.na(x[3]) & is.na(x[4]), x[3],'')), 
+            ifelse(!is.na(x[4]),x[4],''), ')',sep='')
+    }, MARGIN = 1
+    )
+
+  fun_tdist <- apply(tdist, FUN=function(x) {
+    paste0('distr::Td(',x[4],')*',x[3], '+', x[2])
+  }, MARGIN = 1
+  )
+
+  dist_args <- paste(fun_dist, collapse=',',sep='')
+  tdist_args <- paste0(fun_tdist,collapse=',')
+  args <- ifelse(tdist_args!='',paste(dist_args,tdist_args,sep=','),dist_args)
+
+  weights <- c(distdf[,5],tdist[,5])
+  mixString <- paste('distr::UnivarMixingDistribution(',
+                     args,',mixCoeff=weights)',sep='')
+  mixDist <- eval(parse(text=mixString))
+
+  return(mixDist)
+}
+@
+
+The following is the code used to make the function \texttt{CRPS()} used in
+section \ref{section:tools}.
+<<eval=FALSE>>=
+crps_integrand <- function(x,dist,y) {(dist(x) - as.numeric(y <= x))^2}
+
+CRPS <- function(y,dist) {
+  int <- integrate(crps_integrand,-Inf,Inf,y,dist=dist)
+  return(int$value)
+}
+@
+
+% \section{Bibliography}
+% \bibliographystyle{apa}
+% % \vspace{-20pt}
+% \begingroup
+%     \setlength{\bibsep}{13.2pt}
+%     \linespread{1}\selectfont
+%     \bibliography{master_bib}
+% \endgroup
+% \clearpage
+% \pagebreak
+
+%%%%%% bibliographies
+
+%\clearpage
+%% \nocite{*}
+%\unappendixtitle
+%\newpage
+%% % \phantomsection
+%\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
+%\section*{BIBLIOGRAPHY}
+%\bibliographystyle{apa}
+%\vspace{-20pt}
+%\begingroup
+%    \setlength{\bibsep}{14.5pt}
+%    \linespread{1}\selectfont
+    % \bibliography{master_bib}
+%\endgroup
+
+% Renders the citations but does not show the bibliography at the end of the thesis
+%\newsavebox\mytempbib
+%\savebox\mytempbib{\parbox{\textwidth}{\bibliography{master_bib}}}
+
+\clearpage
+\pagebreak
+
+%% Only within chapter appendix is allowed for Journal style writing
+%\include{Appendix/appendix1} % Instruction for single appendix look below
+%\include{Appendix/appendix2}
 \end{document}
+
+% use \isucaption{} for all captions of figures and tables, where the captions are not too long.
+
+% Use \isucaption[]{} with the square brackets for short caption of figure or table that goes into the list of tables and list of figures, and the curly brackets can have long captions which go with the figure/ table.
+
+% IMPORTANT NOTES
+% TABLE OF CONTENTS :
+% TOPIC 1:  If you need a page break follow the steps below
+% step1
+% check before which chapter in the table of contents you want a page break
+% step 2
+% go the folder "body". There open the chapter tex file that you noted needed page break in the table of contents..
+% step 3
+% insert  \addtocontents{toc}{\protect\newpage} before the first line i.e. before the line \chapter{RESULTS}.
+
+%%%%%%%%%%%%%%
+% use \isucaption{} for all captions of figures and tables, where the captions are not too long.
+
+% Use \isucaption[]{} with the square brackets for short caption of figure or table that goes into the list of tables and list of figures, and the curly brackets can have long captions which go with the figure/ table.
+
+%%%%%% Using sub figures 
+% %%% In preamble include : \usepackage{subfig}
+% \begin{figure}[htbp]
+% 	\centering
+% 	\subfloat[first caption.\label{fig:2a}]{\includegraphics[width=0.2\textwidth]{Images/dc5.jpg}}\hfill
+%     \subfloat[second caption.\label{fig:2b}] {\includegraphics[width=0.2\textwidth]{Images/dc5.jpg}}\hfill
+% 	\isucaption{Sub-figure test}
+% 	\label{fig:subfigure-test}
+% \end{figure}
+
+% Subfloat reference: Fig \ref{fig:2a}
+
+% Figure reference: Fig \ref{fig:subfigure-test}

### 2022-03-30 manuscript/thesis.tex
ISU thesis format CC all contained in manuscript folder

--- 2022-03-30 manuscript/thesis.Rnw
@@
 
+\usepackage{Sweave}
 \begin{document}
-\SweaveOpts{concordance=TRUE}
+\input{thesis-concordance}
 \DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
@@
 
-<<eval = FALSE>>=
-preddf1
-#  family param1 param2 param3 weights
-#1  Lnorm    2.0      1     NA     0.3
-#2   Norm    2.1      1     NA     0.7
-
-preddf2
-#  family param1 param2 param3 weights
-#1   Norm    1.5      1     NA     0.4
-#2   Norm    4.0      2     NA     0.6
-
-#make mixture distributions from prediction submissions
-mdist1 <- MakeDist(preddf1)
-mdist2 <- MakeDist(preddf2)
-
-#make pdfs for mixture predictions
-dmdist1 <- function(x) {distr::d(mdist1)(x)}
-dmdist2 <- function(x) {distr::d(mdist2)(x)}
-
-#make cdfs for mixture predictions
-pmdist1 <- function(x) {distr::p(mdist1)(x)}
-pmdist2 <- function(x) {distr::p(mdist2)(x)}
-@
+\begin{Schunk}
+\begin{Sinput}
+> preddf1
+> #  family param1 param2 param3 weights
+> #1  Lnorm    2.0      1     NA     0.3
+> #2   Norm    2.1      1     NA     0.7
+> 
+> preddf2
+> #  family param1 param2 param3 weights
+> #1   Norm    1.5      1     NA     0.4
+> #2   Norm    4.0      2     NA     0.6
+> 
+> 
+> 
+> #make mixture distributions from prediction submissions
+> mdist1 <- MakeDist(preddf1)
+> mdist2 <- MakeDist(preddf2)
+> #make pdfs for mixture predictions
+> dmdist1 <- function(x) {distr::d(mdist1)(x)}
+> dmdist2 <- function(x) {distr::d(mdist2)(x)}
+> #make cdfs for mixture predictions
+> pmdist1 <- function(x) {distr::p(mdist1)(x)}
+> pmdist2 <- function(x) {distr::p(mdist2)(x)}
+\end{Sinput}
+\end{Schunk}
 
@@
 
-<<eval=FALSE>>=
-#realized observation
-ob <- 3
-
-#LogS for predictions at the realized observation
--log(dmdist1(ob)) # => 1.547238
--log(dmdist2(ob)) # => 1.848796
-
-#CRPS for predictions at the realized observation
-CRPS(pmdist1,y=ob) # => 0.6348212
-CRPS(pmdist2,y=ob) # => 0.5306083
-@
+\begin{Schunk}
+\begin{Sinput}
+> #realized observation
+> ob <- 3
+> #LogS for predictions at the realized observation
+> -log(dmdist1(ob)) # => 1.547238
+> -log(dmdist2(ob)) # => 1.848796
+> #CRPS for predictions at the realized observation
+> CRPS(pmdist1,y=ob) # => 0.6348212
+> CRPS(pmdist2,y=ob) # => 0.5306083
+\end{Sinput}
+\end{Schunk}
 
@@
 
-<<eval=FALSE>>=
-#posterior model probability for calculating weights
-w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
-w2 <- 1-w1
-#w1 => 0.5286434
-#w2 => 0.4713566
-
-#build ensemble with calculated weights
-ensdist <- distr::UnivarMixingDistribution(mdist1,
-                                           mdist2,
-                                           mixCoeff = c(w1,w2))
-
-#pdf and cdf for ensemble
-densdist <- function(x) {(distr::d(ensdist)(x))}
-pensdist <- function(x) {(distr::p(ensdist)(x))}
-
-#LogS for predictions at the realized observation
--log(densdist(ob)) # => 1.678156
-
-#CRPS for predictions at the realized observation
-CRPS(pensdist,y=ob) # => 0.5486368
-@
+\begin{Schunk}
+\begin{Sinput}
+> #posterior model probability for calculating weights
+> w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
+> w2 <- 1-w1
+> #w1 => 0.5286434
+> #w2 => 0.4713566
+> 
+> #build ensemble with calculated weights
+> ensdist <- distr::UnivarMixingDistribution(mdist1,
++                                            mdist2,
++                                            mixCoeff = c(w1,w2))
+> #pdf and cdf for ensemble
+> densdist <- function(x) {(distr::d(ensdist)(x))}
+> pensdist <- function(x) {(distr::p(ensdist)(x))}
+> #LogS for predictions at the realized observation
+> -log(densdist(ob)) # => 1.678156
+> #CRPS for predictions at the realized observation
+> CRPS(pensdist,y=ob) # => 0.5486368
+\end{Sinput}
+\end{Schunk}
 
@@
 in \ref{section:tools}.
-<<eval=FALSE>>=
-MakeDist <- function(distsdf){
-
-  distdf <- distsdf[distsdf[,1] != 'Lst',]
-  tdist <- distsdf[distsdf[,1] == 'Lst',]
-
-  fun_dist <- 
-    apply(distdf, FUN=function(x) {
-      paste('distr::',x[1], '(', 
-            ifelse(!is.na(x[2]) & (!is.na(x[3]) | !is.na(x[4])),
-                   paste(x[2],',',sep=''),
-                   ifelse(!is.na(x[2]) & is.na(x[3]) & is.na(x[4]),
-                          x[2], '')), 
-            ifelse(!is.na(x[3]) & !is.na(x[4]),
-                   paste(x[3],',',sep=''),
-                   ifelse(!is.na(x[3]) & is.na(x[4]), x[3],'')), 
-            ifelse(!is.na(x[4]),x[4],''), ')',sep='')
-    }, MARGIN = 1
-    )
-
-  fun_tdist <- apply(tdist, FUN=function(x) {
-    paste0('distr::Td(',x[4],')*',x[3], '+', x[2])
-  }, MARGIN = 1
-  )
-
-  dist_args <- paste(fun_dist, collapse=',',sep='')
-  tdist_args <- paste0(fun_tdist,collapse=',')
-  args <- ifelse(tdist_args!='',paste(dist_args,tdist_args,sep=','),dist_args)
-
-  weights <- c(distdf[,5],tdist[,5])
-  mixString <- paste('distr::UnivarMixingDistribution(',
-                     args,',mixCoeff=weights)',sep='')
-  mixDist <- eval(parse(text=mixString))
-
-  return(mixDist)
-}
-@
+\begin{Schunk}
+\begin{Sinput}
+> MakeDist <- function(distsdf){
++   
++   distdf <- distsdf[distsdf[,1] != 'Lst',]
++   tdist <- distsdf[distsdf[,1] == 'Lst',]
++   
++   fun_dist <- 
++     apply(distdf, FUN=function(x) {
++       paste('distr::',x[1], '(', 
++             ifelse(!is.na(x[2]) & (!is.na(x[3]) | !is.na(x[4])),
++                    paste(x[2],',',sep=''),
++                    ifelse(!is.na(x[2]) & is.na(x[3]) & is.na(x[4]),
++                           x[2], '')), 
++             ifelse(!is.na(x[3]) & !is.na(x[4]),
++                    paste(x[3],',',sep=''),
++                    ifelse(!is.na(x[3]) & is.na(x[4]), x[3],'')), 
++             ifelse(!is.na(x[4]),x[4],''), ')',sep='')
++     }, MARGIN = 1
++     )
++   
++   fun_tdist <- apply(tdist, FUN=function(x) {
++     paste0('distr::Td(',x[4],')*',x[3], '+', x[2])
++   }, MARGIN = 1
++   )
++   
++   dist_args <- paste(fun_dist, collapse=',',sep='')
++   tdist_args <- paste0(fun_tdist,collapse=',')
++   args <- ifelse(tdist_args!='',paste(dist_args,tdist_args,sep=','),dist_args)
++   
++   weights <- c(distdf[,5],tdist[,5])
++   mixString <- paste('distr::UnivarMixingDistribution(',
++                      args,',mixCoeff=weights)',sep='')
++   mixDist <- eval(parse(text=mixString))
++   
++   return(mixDist)
++ }
+\end{Sinput}
+\end{Schunk}
 
@@
 section \ref{section:tools}.
-<<eval=FALSE>>=
-crps_integrand <- function(x,dist,y) {(dist(x) - as.numeric(y <= x))^2}
-
-CRPS <- function(y,dist) {
-  int <- integrate(crps_integrand,-Inf,Inf,y,dist=dist)
-  return(int$value)
-}
-@
+\begin{Schunk}
+\begin{Sinput}
+> crps_integrand <- function(x,dist,y) {(dist(x) - as.numeric(y <= x))^2}
+> CRPS <- function(y,dist) {
++   int <- integrate(crps_integrand,-Inf,Inf,y,dist=dist)
++   return(int$value)
++ }
+\end{Sinput}
+\end{Schunk}
 

### 2022-03-31 manuscript/thesis.Rnw
revisions to section 1

@@
 \alternate
-\nochap
+% \nochap
 \usepackage{rotating}
@@
 % Use the following line if you want square brackets and numbering system
-%\usepackage[square, numbers]{natbib}
-\lstset{language=R,
-    basicstyle=\small\ttfamily,
-    stringstyle=\color{DarkGreen},
-    otherkeywords={0,1,2,3,4,5,6,7,8,9},
-    morekeywords={TRUE,FALSE},
-    deletekeywords={data,frame,length,as,character},
-    keywordstyle=\color{blue},
-    commentstyle=\color{DarkGreen},
-}
+% \usepackage[square, numbers]{natbib}
+% \lstset{language=R,
+%     basicstyle=\small\ttfamily,
+%     stringstyle=\color{DarkGreen},
+%     otherkeywords={0,1,2,3,4,5,6,7,8,9},
+%     morekeywords={TRUE,FALSE},
+%     deletekeywords={data,frame,length,as,character},
+%     keywordstyle=\color{blue},
+%     commentstyle=\color{DarkGreen},
+% }
 \makeatletter
@@
 %\renewcommand\bibsection{\section*}
-\renewcommand{\bibsection}{\section{References}}
+\renewcommand{\bibsection}{\section*{}}
 
@@
 \usepackage[intoc, english]{nomencl}
-
+\renewcommand{\chaptername}{}
 \begin{document}
@@
 
-\section{Introduction}
+\chapter{Introduction}
+
 Predicting the outcomes of prospective events is the object of much scientific
@@
 which probabilistic forecasting is used include weather forecasting
-\cite{baran2018combining}, economics \cite{groen2013real} and disease outbreaks
+\cite{baran2018combining}, economics \cite{groen2013real}, and disease outbreaks
 \cite{yamana2016superensemble}.
@@
 (pdf/pmf). Much of the literature 
-on calibration, sharpness and scoring of a forecast pertains to parametric 
+on calibration, sharpness, and scoring of a forecast pertains to parametric 
 distribution forecasts
@@
 Other common representations include samples \cite{krueger2016probabilistic}, 
-discretized bins \cite{mcgowan2019collaborative}
-and quantile or interval type forecasts \cite{taylor2021evaluating} 
-\cite{bracher2021evaluating}. Each representation may be more or less 
+discretized bin distributions \cite{mcgowan2019collaborative},
+and quantile forecasts \cite{taylor2021evaluating, bracher2021evaluating}. 
+Each representation may be more or less 
 appropriate than the others for a given problem but knowing how to interpret, 
-score and contruct ensemble forecasts for a selected representation is essential
-when multiple teams collaborate in the same forecasting project.
+score, and contruct ensemble forecasts for a selected representation is 
+essential when multiple teams collaborate in the same forecasting project.
 
@@
 separate forecasts 
-are used include the United States Centers for Disease Control (CDC) hosted
-annual competition for forecasting influenza \cite{cdcflusight}
+are used include the United States Centers for Disease Control (CDC)
+annual competition for forecasting the influenza outbreak \cite{cdcflusight}
 and the COVID-19 Forecast Hub which has 
@@
 
-\subsection{CDC Influenza Like Illness}
+\section{CDC flu competition}
 
 Since the 2013-14 flu season, the CDC has hosted an annual competition for 
-predicting the timing, peak and intensity of the year's flu season. Forecasts
-for the different targets also include predictions for one, two, three and 
+forecasting the timing, peak, and intensity of the year's flu 
+season. The specific events to be forecasted are known as \emph{targets}.
+Forecasts
+for these different targets also include forecasts for one, two, three, and 
 four weeks ahead of the prediction time. National flu data is provided weekly 
-to outside academic teams who use that data to construct forecasts using 
-whatever methods they choose. Historically, the forecast predictions must be 
+to academic teams not directly affiliated with the CDC who use that data to 
+construct forecasts using 
+whatever methods they choose. Historically, the forecasts must be 
 submitted 
-in a discretized bin
-format. During previous flu seasons the binning scheme was on a bounded numeric 
-scale and the 
+in a discretized bin distribution
+format. A \emph{bin distribution} is a probability distribution represented by
+breaking the numeric range of an event into intervals or \emph{bins} and
+directly assigning the probability that the event falls within each bin.
+During previous flu seasons the \emph{binning scheme} or the assignment of 
+bin values was on a numeric 
+scale with a bounded range and the 
 prediction of a specific target was a set of probabilities assigned to each bin
 \cite{mcgowan2019collaborative}.
-These forecasts are then evaluated against actual flu activity, and at 
-the end of the season a winning team is declared \cite{cdcflusight}.
-
-This competition has provided the CDC, competing teams and other interested
-parties a chance to collaborate and improve forecasting each season. One 
+These forecasts were then evaluated against actual flu activity, and at 
+the end of the season a winning team was declared \cite{cdcflusight}.
+
+This competition has provided the CDC, competing teams, and other interested
+parties a chance to collaborate and improve their forecasting from season to
+season. One 
 proposed way to enhance prediction has been to aggregate the various teams'
-forecasts into a multi-model ensemble forecast 
-\cite{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy}.
-
-A multi-model ensemble forecast is a combination of several component forecast 
+forecasts into a \emph{multi-model ensemble forecast} 
+\cite{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy},
+refered to hereafter as an ensemble forecast.
+
+An \emph{ensemble forecast} is a combination of several component forecast 
 models into one model which often yields better predicting power than the 
@@
 component models \cite{reich2019accuracy}.
-In the COVID-19 Forecast Hub, construction of ensemble forecasts is a main
-priority.
-
-\subsection{COVID-19 Forecast Hub}
+In the COVID-19 Forecast Hub, construction of ensemble forecasts to improve
+predicting power has been a priority.
+
+\section{COVID-19 Forecast Hub}
 In March 2020, at the onset of the COVID-19 pandemic, the COVID-19 Forecast Hub
-was founded. Borrowing on work and 
-ideas from the CDC influenza competition, the Forecast Hub is a central site in 
+was founded. Borrowing from the work done in the CDC flu competition, the 
+COVID-19 Forecast Hub is a central site in 
 which dozens of academic teams collaborate to forecast the ongoing COVID-19 
@@
 Every week relevant
-pandemic data is provided to these teams who build probabilistic models for 
-their use in
-forecasting cases, hospitalizations and deaths due to COVID-19. Forecasts are 
+pandemic data is provided to these teams who construct forecasts models to 
+predict the targets cases, hospitalizations, and deaths due to COVID-19. 
+Forecasts are 
 made on the US county,
-state and national level with predictions for days, weeks and months ahead.
-These forecasts are combined into a single ensemble forecast. The model data,
-forecasts and the ensemble are passed along to the CDC for its use in official
+state, and national levels and for days, weeks, and months ahead.
+These forecasts are aggregated into a single ensemble forecast. The model data,
+forecasts, and the ensemble forecast are passed along to the CDC for its use in 
+official
 communication \cite{Cramer2021-hub-dataset}. See Figure \ref{fig:cdcoff}.
 
-Though similar to the forecasting in the influenza competition, the format of 
+Though similar to the forecasting in the CDC flu competition, the format of 
 the COVID-19 Forecast Hub has some key distinctions. For one this project has
@@
 pressure of
-creating forecasts, rather than requesting forecasts as binned probabilities
+creating forecasts, rather than requesting forecasts as bin distributions
 the forecasts are requested as the predictive median and 
 predictive intervals for various nominal levels depending on the target to be
-predicted \cite{bracher2021evaluating}. Collecting forecasts in this quantile
-or interval type format brings with it differences in how to score, construct 
-ensemble
-models and store the forecasts among other differences.
+predicted \cite{bracher2021evaluating}. Each value in a predictive interval
+is a value for a quantile at a specified nominal level. This makes a set of 
+predicitve intervals a \emph{quantile forecast} or a forecast made up of a set
+of quantiles and corresponding values.
+Collecting forecasts as quantile forecasts instead of bin forecasts brings with 
+it differences in how to score, construct an 
+ensemble forecast, and store the forecasts among other differences.
 
 \begin{figure}[htbp]
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \centerline{\includegraphics[scale=.12]{Images/8_30_21_cvd_deaths.jpeg}}
 \caption[Official CDC COVID-19 deaths report August 2021]{This image, 
-published on cdc.gov as official public communication 
+published on www.cdc.gov in August 2021 as official public communication 
 by the CDC, shows forecast models for national new weekly deaths due to COVID-19 
@@
 \label{fig:cdcoff}
+\end{minipage}
+\end{center}
 \end{figure}
 
-\subsection{}
+\section{Outline}
 In the context of collaborative forecasting like that of the CDC flu competition
-or the COVID-19 Forecast Hub, discretized bins and quantile forecasts have 
-proven useful and effective. Yet both types come with their drawbacks. Data 
+or the COVID-19 Forecast Hub, bin forecasts and quantile forecasts have become
+important representations to those involved in the projects. Yet both 
+representation types come 
+with their drawbacks. Data 
 storage for instance might be a concern if many bins are used for forecasting. 
-And scoring methods are limited if forecasts are made of prediction intervals.
+And scoring methods are limited if forecasts are quantile forecasts.
 
 In this paper, we propose the use of discrete mixture distributions as a means 
-of forecasting for projects similar to the CDC flu competition or the COVID-19
-Forecast Hub. In section \ref{section:representations}, 
+of forecasting for collaborative projects similar to the CDC flu competition or 
+the COVID-19
+Forecast Hub. In Section \ref{section:representations}, 
 popular probabilistic forecast representation 
-types are defined and reviewed. Methods of scoring, storing, building 
-ensembles and other aspects will be reviewed and compared for each 
+types are defined and reviewed. Methods of scoring, storing, constructing 
+ensembles, and other aspects will be reviewed and compared for each 
 representation type.
-In section \ref{section:conmixforc}, details for using discrete mixture 
+In Section \ref{section:conmixforc}, details for using discrete mixture 
 distributions in a collaborative forecast project are presented as well as tools
-which may be used for scoring and ensemble building.
+which may be used for scoring and constructing an ensemble.
 Section \ref{section:retrostud} is a retrospective study of the CDC flu 
-competition and COVID-19 
-forecast predictions and an attempt to assess whether any predictions 
-approximately come from well known continuous distributions. This paper is 
-concluded with a discussion.
-
-\section{Probabilistic Forecast Representations}
+competition and COVID-19 Forecast Hub
+forecast and an attempt to assess whether any forecast models
+may be approximated by known continuous distributions. We conclude this 
+paper with a discussion.
+
+\chapter{Probabilistic forecast representations}
 \label{section:representations}
 
-Before introducing discrete mixture distributions as a representation type for a
-probabilistic forecast, we review representations already commonplace in 
+In this section we review four forecast representations already commonplace in 
 forecasting. In a collaborative setting, certain aspects of each representation
-should be considered. With each representation presented, 
-commmon applications of 
-scoring, data storage and ensemble construction will be considered for
-as well as other notable properties.
-
-\subsection{Representation properties to consider in collaborative projects}
-\subsubsection{Scoring}
+should be considered including scoring, computer storage, and how to construct
+an ensemble forecast. For each representation presented, applications of each of 
+those aspects are also presented.
+
+\section{Representation aspects to consider in collaborative projects}
+\subsection{Scoring}
 Scoring rules are used to numerically evaluate or score a probability forecast. 
@@
 
-\subsubsection{Storage}
+\subsection{Storage}
 For a collaborative forecast project where many researchers are involved and 
@@
 
-\subsubsection{Ensemble Modeling}
+\subsection{Ensemble Modeling}
 A multi-model ensemble is a statistical model made by combining information from
@@
 
-\subsection{Probabilistic Forecast Representation Types}
-\subsubsection{Parametric distributions}
+\section{Probabilistic Forecast Representation Types}
+\subsection{Parametric distributions}
 \label{section:pardist}
@@
 
-\subsubsection{Sample Distributions}
+\subsection{Sample Distributions}
 Some forecast model builders may want more flexibility in modeling than a 
@@
 
-\subsubsection{Discretized bin distributions}
+\subsection{Discretized bin distributions}
 An alternative to parametric distributions and sample distributions which allows
@@
 
-\subsubsection{Quantile representation}
+\subsection{Quantile representation}
 When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
@@
 
-\subsection{Discrete mixture of parametric distributions}
+\section{Discrete mixture of parametric distributions}
 A discrete mixture of parametric distributions forecast representation may be an
@@
 
-\section{Mixture distributions in a collaborative forecast project}
+\chapter{Mixture distributions in a collaborative forecast project}
 \label{section:conmixforc}
@@
 have their own established systems for receiving, 
-evaluating and constructing ensemble forecasts. A transition from using binned 
-distributions or quantile forecasts to using discrete mixture distributions 
-nwould require
+scoring, and constructing ensemble forecasts. A transition from using bin or 
+quantile forecasts to using mixture distribution forecasts
+would require
 a few adjustments to those systems. In this section we outline how some of these
 adjustments may be implemented as well as present some tools which may be used
-to evaluate forecasts and construct ensemble forecasts from multiple models.
-
-\subsection{Submission format}
+to score forecasts and construct ensembles from multiple models.
+
+\section{Submission format}
 For a collaborative forecast project to run smoothly, model submissions from all 
-modelers should all follow the same format. For both the CDC flu forecasting and
-the COVID-19 Forecast Hub, teams are provided a .csv spreadsheet with columns 
+modelers should follow the same format. For both the CDC flu competition and
+the COVID-19 Forecast Hub, teams provide a \texttt{.csv} spreadsheet with 
+columns 
 similar to those in tables \ref{table:dbins} and \ref{table:qstor}. Additionally
-columns for Location, Target, Type and Unit are included which serve as
-indicators of the specific prediction. The values for all variables except 
-Value come from a specified list from the forecast center. Value is the 
-probability assigned to a bin when the Type is Bin.
+columns for \texttt{location}, \texttt{target}, \texttt{type}, and \texttt{unit} 
+are included.
+Here \texttt{location} defines the specific county, state, or country of the 
+forecast. The \texttt{target} variable defines what is forecasted for example
+season onset, deaths, hospitalizations, etc. The \texttt{type} variable defines
+the type for the \texttt{value} variable, \texttt{bin} or \texttt{quantile}.
+The \texttt{unit} variable defines the time frame of the forecast: week,
+two weeks, four weeks, etc. And the \texttt{value} variable is a number that 
+either gives probability for a bin or the value for a quantile. Table
+\ref{table:dstan} show what a few rows of a forecast 
+submission file for the CDC flu competition look like.
+For the quantile forecasts of the Forecast Hub, the main changes to Table
+\ref{table:dstan} are that the possible values for \texttt{type} 
+quantile, and rather than using a \texttt{bin} variable \texttt{quantile} is 
+used
+with values specified by the Hub. This is seen in Table \ref{table:qstan}
+
+A single submission may include many forecasts each aimed at predicting a 
+different combination of \texttt{location}, \texttt{target}, and \texttt{unit}. 
+A set of rows which share
+the same specific combination of \texttt{location}, \texttt{target}, and 
+\texttt{unit} constitute a single forecast. One forecast for the CDC flu
+competition may require up to 131 rows whereas in the COVID-19 Forecast Hub one 
+forecast may require up to 23 rows.
 
 \begin{table}[h!]
-\label{tab:dstan}
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \centering
@@
  \hline
-    Location & Target & Type & Unit & Bin & Value  \\ \hline
-    US National & Season Onset & Point & week & NA & . \\
-    US National & Season Onset & Bin & week & 0.0 & . \\
-    US National & Season Onset & Bin & week & 0.1 & . \\
+    location & target & type & unit & bin & value  \\ \hline
+    % US National & Season Onset & Point & week & NA & . \\
+    us national & season onset & bin & week & 0.0 & . \\
+    us national & season onset & bin & week & 0.1 & . \\
     ... & ... & ... & ... & ... & ... \\
@@
  \end{tabular}
- \caption[Influenza competition submission example]{Example of a submission file
- for an discretized forecast like those in the CDC influenza forecast 
- competition. To match a quantile submission format as used by
- the COVID-19 Forecast Hub, possible values for the variable Type are Point and
- Quantile, the Bin column is replaced with a Quantile column and Value is 
- the value of the specified quantile in the forecast.}
+ \caption[Influenza competition submission example]{This shows a few rows of a 
+ submission file
+ for a discretized forecast like those in the CDC influenza forecast 
+ competition. A set of rows which share the same combination of 
+ \texttt{location}, \texttt{target}, and \texttt{unit} make up a
+ single forecast. One submission may include many forecasts specified by 
+ differing combinations of those three columns.}
  \label{table:dstan}
+ \end{minipage}
+ \end{center}
 \end{table}
 
-For the quantile forecasts of the Forecast Hub, the main changes to table
-\ref{tab:dstan} are that the possible values for Type 
-are Point and Quantile, and rather than using a Bin variable Quantile is used
-with values specified by the Hub. Then Value rather than a probability is the
-forecasted value for the specified quantile. Per prediction there may be a 
-couple dozen rows, up to 24 in the Forecast Hub, or over 100 rows as in some
-flu forecasts.
-
-In the discrete mixture format, an adjustment may be made to the format of table 
-\ref{table:dstan} where each 
+\begin{table}[h!]
+\begin{center}
+\begin{minipage}{11cm}
+\captionsetup{font=scriptsize}
+\centering
+ \begin{tabular}{|c|c|c|c|c|c|}
+ \hline
+    location & target & type & unit & quantile & value  \\ \hline
+    % US National & Season Onset & Point & week & NA & . \\
+    us national & season onset & quantile & week & 0.01 & . \\
+    us national & season onset & quantile & week & 0.025 & . \\
+    ... & ... & ... & ... & ... & ... \\
+ \hline
+ \end{tabular}
+ \caption[COVID-19 Forecast Hub competition submission example]{This shows
+ a few rows of a 
+ submission file
+ for a quantile forecast like those in the COVID-19 Forecast Hub. 
+ A set of rows which share the same combination of 
+ \texttt{location}, \texttt{target}, and \texttt{unit} make up a
+ single forecast. One submission may include many forecasts specified by 
+ differing combinations of those three columns.}
+ \label{table:qstan}
+ \end{minipage}
+ \end{center}
+\end{table}
+
+In the mixture distribution format, an adjustment may be made to the format of 
+Tables
+\ref{table:dstan} and \ref{table:qstan} where each 
 row
@@
  \hline
-    Location & Target & Type & Unit & Family & Param1 & Param2 & Weight
+    location & target & type & unit & family & param1 & param2 & weight
     \\ \hline
@@
  for a disease outbreak forecast using mixture distribution representation}
- \label{table:dstan}
+ \label{table:mstan}
 \end{table}
@@
 
-\subsection{Mixture construction and scoring tools}
+\section{Mixture construction and scoring tools}
 \label{section:tools}
@@
 
-\subsection{Ensemble construction}
+\section{Ensemble construction}
 
@@
 
-\section{Retrospective Analysis}
+\chapter{Retrospective Analysis}
 \label{section:retrostud}
@@
 
-\subsection{CDC Influenza like Illness}
+\section{CDC Influenza like Illness}
 The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
@@
 
-\subsection{COVID-19 Forecast Hub}
+\section{COVID-19 Forecast Hub}
 
@@
 
-\newpage
-
-\section{Discussion}
+\chapter{Discussion}
 
@@
 %\bibliographystyle{acm} % use for numbered citations along with options given in preamble. Look at the main thesis.tex file
+
+% \bibliographystyle{apa}
+% \bibliography{master_bib}
+
+% \section{Bibliography}
+% \bibliographystyle{apa}
+% % \vspace{-20pt}
+% \begingroup
+%     \setlength{\bibsep}{13.2pt}
+%     \linespread{1}\selectfont
+%     \bibliography{master_bib}
+% \endgroup
+% \clearpage
+% \pagebreak
+
+%%%%%% bibliographies
+
+\clearpage
+\nocite{*}
+\unappendixtitle
+\newpage
+\phantomsection
+\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
+\section*{BIBLIOGRAPHY}
 \bibliographystyle{apa}
+\vspace{-20pt}
+\begingroup
+   \setlength{\bibsep}{14.5pt}
+   \linespread{1}\selectfont
 \bibliography{master_bib}
-
-\section{Appendix}
+\endgroup
+
+\appendix
+
+\specialchapt{APPENDIX}
 
@@
 
-% \section{Bibliography}
-% \bibliographystyle{apa}
-% % \vspace{-20pt}
-% \begingroup
-%     \setlength{\bibsep}{13.2pt}
-%     \linespread{1}\selectfont
-%     \bibliography{master_bib}
-% \endgroup
-% \clearpage
-% \pagebreak
-
-%%%%%% bibliographies
-
-%\clearpage
-%% \nocite{*}
-%\unappendixtitle
-%\newpage
-%% % \phantomsection
-%\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
-%\section*{BIBLIOGRAPHY}
-%\bibliographystyle{apa}
-%\vspace{-20pt}
-%\begingroup
-%    \setlength{\bibsep}{14.5pt}
-%    \linespread{1}\selectfont
-    % \bibliography{master_bib}
-%\endgroup
-
 % Renders the citations but does not show the bibliography at the end of the thesis

### 2022-03-31 manuscript/thesis.tex
additional edits up to quantile forecasts

@@
 
+\usepackage{amsmath}
 \usepackage{amssymb}
 \usepackage[intoc, english]{nomencl}
-
+\renewcommand{\chaptername}{}
 \usepackage{Sweave}
@@
 repository for the
-COVID-19 Forecast Hub predictions contained 85 million predictions as of 
+COVID-19 Forecast Hub contained 85 million forecasts as of 
 February 5, 2022 which required more than 11.6 gigabytes of storage!
@@
 
-\subsubsection{Ensemble Modeling}
+\subsection{Ensemble construction}
 A multi-model ensemble is a statistical model made by combining information from
@@
 sources fail to capture. Likewise one statistical model may provide insight
-that another model does not, so that when they are combined in an ensemble the 
-ensemble model outperforms the individual component models.
+that another model does not so that when they are combined into an ensemble the 
+ensemble outperforms the individual component models.
 
 As probabilistic forecasting becomes more commonplace, so too does ensemble 
-modeling. Multi-model ensembles have been used extensively in weather and
-climate modeling \cite[for example]{baran2018combining}, 
+modeling. Ensembles have been used extensively in weather and
+climate modeling \cite{baran2018combining}, 
 and they have been used increasingly in modeling infectious disease outbreaks
-see \cite[for example]{yamana2016superensemble}. 
-Multi-model ensembles allow for an incorporation of multiple signals -
+\cite{yamana2016superensemble}. 
+Ensembles allow for an incorporation of multiple signals -
 often from differing data sources- and sometimes individual model biases are 
 canceled
-out or reduced by biases in others \cite[see references
+out or reduced by biases from other models \cite[see references
 therein]{reich2019accuracy}. 
-In several disease outbreak studies, multi-model ensemble forecasts have been 
+In several disease outbreak studies, ensemble forecasts have been 
 shown to outperform individual model forecasts 
@@
 Construction of an ensemble may be done by combining individual forecast 
-distributions using weighted averages. This has been called stacking 
+models using weighted averages. This has been called stacking 
 \cite{wolpert1992stacked} or weighted density ensembles 
@@
 
-\subsection{Probabilistic Forecast Representation Types}
-\subsubsection{Parametric distributions}
+\section{Probabilistic forecast representation types}
+\subsection{Parametric distributions}
 \label{section:pardist}
 A parametric distribution is a discrete or continuous probability distribution 
-described by a known function $p(x) := p(x|\theta)$ -pmf in the discrete case or 
-pdf in the continuous case. Here $\theta$ is a vector of known or unkown 
-parameters 
-contained in a parameter space.
+described by a known function $p(x) := p(x|\theta)$. The function $p(x)$ is 
+called a pmf if the distribution is discrete and is called a
+pdf if the distribution is continuous. Here $\theta$ is a vector of known or 
+unkown parameters contained in the parameter space of the distribution.
 
@@
 $P(X = x) = 0$ for all $x$, but the probability 
-that $X$ falls within an interval $(a,b)$ is calculated as
-
-\begin{equation}
-\label{eq:prob}
+that $X$ falls within an interval $(a,b)$ is calculated by 
+\eqref{equation:prob}.
+
+\begin{equation}
+\label{equation:prob}
   P(a < X < b) = \int_a^b p(x) dx
@@
 distribution function (CDF) and the inverse CDF or quantile function. The CDF 
-in the continuous case is defined as
+in the continuous case is defined in \eqref{eq:ccdf} and is defined in the 
+discrete case in \eqref{eq:dcdf}. Here $x_n$ is the largest value of X less than 
+or equal to $x$.
+The quantile function is defined in \eqref{eq:quant} which returns a quantile 
+value where $p$ is a given probability such that $0\leq p \leq 1$.
 
@@
 \end{equation}
-or in the discrete case
 
@@
 \end{equation}
-where $x_n$ is the largest value of X less than or equal to $x$.
-The quantile function is defined as
+
 \begin{equation}
@@
 \end{equation}
-returning a quantile value where $p$ is a given probability $0\leq p \leq 1$.
-
-% \subsubsubsection{Scoring}
-For a forecast represented as a parametric function with pmf/pdf $p_m(x)$, 
-the accuracy of the forecast may be measured as how likely realized value $x^*$
+
+For a forecast represented as a parametric function with pmf/pdf $p_m(\cdot)$, 
+the accuracy of the forecast may be measured by how likely realized value $x^*$
 is to occur. Commonly used proper scoring rules for parametric distributions
-include the Logarithmic score (LogS), 
+include the logarithmic score (LogS), the
 continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
-\cite{alves2013ncep} and the interval/Brier 
+\cite{alves2013ncep}, and the interval/Brier 
 score (IS) \cite{gneiting2007strictly} among 
 others. See also \cite{gneiting2014probabilistic}
-section 3 for more on proper scoring functions. Unless otherwise noted, the 
-following
-definitions can be found in the review by Krueger.
-
-For a forecast with pdf/pmf $p_m(x)$, the LogS evaluates the 
-probability of the observed value $x^*$. It is defined as
+Section 3 for more on proper scoring functions. The definitions 
+\eqref{eq:logs} and \eqref{eq:crps} are found in the review by Krueger.
+
+For a forecast with pdf/pmf $p_m(\cdot)$, the LogS evaluates the 
+probability of the observed value $x^*$. It is defined in \eqref{eq:logs}.
 
@@
 \label{eq:logs}
-  LS(p_m,x*) = -log\;p_m(x^*)
-\end{equation}
-The goal is to minimize the LogS, so a forecast $p^{'}_m(x^*)$ is considered 
+  LogS(p_m,x*) = -log\;p_m(x^*)
+\end{equation}
+The goal for a forecaster is to minimize the LogS, so a forecast $p^{'}_m(x^*)$ 
+is considered 
 superior to $p_m(x^*)$ if
-$LS(p^{'}_m, x^*) < LS(p_m, x^*)$.
+$LogS(p^{'}_m, x^*) < LogS(p_m, x^*)$.
 The LogS is limited to scoring forecasts with density functions and
@@
 be used more extensively than the LogS. 
-For the CDF $F_m$, the CRPS is defined as
+For the CDF $F_m$, the CRPS is defined in \eqref{eq:crps}.
+Here too a smaller score indicates a more accurate forecast.
 
@@
 \end{equation}
-Here too a smaller score indicates a better forecast.
 
@@
 component distributions
-into a multi-model ensemble are nonhomogeneous regression (NR), also known as
+into an ensemble distribution are nonhomogeneous regression (NR), also known as
 ensemble model output statistics (EMOS), and ensemble
@@
 sources,
-BMA is the better option. In BMA, the final model does not have to be specified
+BMA may be preferrable because it does not require that modeling methods for 
+individual components be the same. 
+In BMA, the final model does not have to be specified
 beforehand and the resulting forecast will be a discrete mixture distribution
 of all component forecasts. The general form for an ensemble distribution $p^E$
-is
-
-\begin{equation}
-\label{eq:bma}
-  p^E(x) = \sum_{m=1}^M w_mp_m(x)
-\end{equation}
-where $p_m$ is the $m^{th}$ component forecast distribution and 
+is in \eqref{eq:bma}. Here $p_m$ is the $m^{th}$ component forecast 
+distribution and 
 $0 \leq w_m \leq 1$ is a weight assigned to that component where $\sum w_m = 1$.
@@
 \cite{raftery2005using}, MCMC 
-sampling see \cite{vrugt2008ensemble}
-and minimizing the ensemble CRPS see
+sampling \cite{vrugt2008ensemble},
+and minimizing the CRPS of the ensemble
 \cite{baran2018combining}.
 
-For selecting distribution weights, the CRPS has some nice properties, but can 
-sometimes be
+\begin{equation}
+\label{eq:bma}
+  p^E(x) = \sum_{m=1}^M w_mp_m(x)
+\end{equation}
+
+For selecting distribution weights, minimizing the CRPS has some nice 
+properties, but it can also be
 difficult to compute. For example, when the forecast is a mixture of a 
@@
 
-Generally computation and evaluation of parametric distributions is not hard. 
+Generally computation and evaluation of parametric distribution functions is not 
+hard. 
 For most commonly used parametric distributions -normal, lognormal, Poisson,
 gamma, etc.- there is software readily available to compute density, 
-distribution and quantile values. Likewise, requirements for storage are low 
+distribution, and quantile values. 
+A completely defined continuous parametric distribution may be evaluated at a
+continuously
+infinite number of values. We will call this an infinite resolution.
+And requirements for storage are low 
 compared to other representation types that will be discussed. The most common
@@
 including
-the distribution family and two or three parameters. Table \ref{table:pstor} 
+the distribution family and two parameters. Table \ref{table:pstor} 
 contains
-enough information to completely define a $Lognormal(1,0.4)$ distribution.
+enough information to completely define a $\mbox{Lognormal(1,0.4)}$ 
+distribution.
 
 \begin{table}[h!]
-
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \centering
@@
  \end{tabular}
- \caption[Parametric distribution storage]{Storage example of parametric 
- lognormal 
+ \caption[Parametric distribution storage]{This is an example of data required
+ for a lognormal 
  distribution with 
@@
  \label{table:pstor}
+ \end{minipage}
+ \end{center}
 \end{table}
-
-A completely defined continuous parametric distribution can be evaluated at an
-infinite number of values. We will call this an infinite resolution.
 
@@
 models is limited to what is available in software, so certain distributional
-shapes may unattainable. The distribution may also assign probability to values
-outside the range of the forecast. There are remedies for this such as 
-truncation, but these increase the complexity in evaluation and scoring.
+shapes may unattainable.
 Requiring a parametric forecast also bars the use of some statistical methods
@@
 
-\subsubsection{Sample Distributions}
-Some forecast model builders may want more flexibility in modeling than a 
+\subsection{Sample distributions}
+Forecast model builders may want more flexibility in modeling than a 
 parametric 
@@
 distribution or Bootstrap sampling to obtain a sample distribution are examples
-where parametric distributions may not be appropriate for modeling.
+where parametric distributions may not be appropriate for modeling because of 
+the lack of flexibility in distribution shape.
 
 A sample distribution is made of a sample of random variables 
-$(X_1,...,X_n)$ where $X_i \sim D$ and $D$ is a distribution. From this, sample
-statistics such as mean, median, variance and quantiles may be calculated. 
+$(X_1,...,X_n)$ where $X_i \sim D$ and $D$ is some distribution. From this 
+sample,
+statistics such as mean, median, variance, and quantiles may be calculated. 
 An empirical cumulative distribution function (ECDF) may also be calculated as
+in \eqref{eq:ecdf}.
 
@@
 \label{eq:ecdf}
-  F_n(x) = \frac{1}{n} \sum_{i=1}^n \mathbb{I}(X_i \leq x)
+  ECDF = F_n(x) = \frac{1}{n} \sum_{i=1}^n \mathbb{I}(X_i \leq x)
 \end{equation}
@@
 as $n \rightarrow \infty$. Thus, if a sufficiently large 
-sample is generated from a distribution with an expectation, 
+sample is generated from a distribution with for which an expectation exists, 
 the sample will closely approximate the 
@@
 sophisticated methods may be required to generate samples. Bayesian analyses may 
-require a Gibbs or Metropolis-Hastings algorithm, among others, to generate a 
+require a Gibbs sampling or a Metropolis-Hastings algorithm, among others, 
+to generate a 
 sample. Such samples are useful in that the true distribution may be closely 
@@
 
-Under the samle distribution format, the options that a researcher has for 
-constructing a forecast are more than
-if they are asked to submit a parametric distribution and the range 
-characterisitcs 
-and shapes of distributions is larger.
+Under the sample distribution representation, the options that a researcher has 
+for constructing a forecast are more than
+if they are asked to submit a parametric distribution, and the range of possible 
+shapes for a distribution is larger.
 In the last few decades, increased computing power and improvements in MCMC
 sampling have greatly contributed to growth in the use of
-predictive distributions \cite{gneiting2007strictly}
+sample distributions for forecasting \cite{gneiting2007strictly}
 \cite[see examples listed therein]{krueger2016probabilistic}.
@@
 and LogS may be used. The CRPS has the advantage here of scoring the sample 
-distribution directly since the CDF in  (\ref{eq:crps}) may be replaced by the 
+distribution directly since the CDF in  (\ref{eq:crps}) may be replaced with the 
 ECDF in
@@
 
-KD is defined by Krueger et. al as
+The KD in \eqref{eq:kd} is defined by Krueger et. al 
+where $K$ is a kernel function, and $h_n$ is a suitable bandwidth. The GA is 
+defined in \eqref{eq:ga} where $\Phi$ is the standard normal CDF and 
+$\hat{\mu}_n$ and $\hat{\sigma}_n$
+are the empirical mean and standard deviation of the sample $(X_i)$
+\cite[see also for a comparison of scoring MCMC drawn forecasts between the CRPS 
+and the LogS]{krueger2016probabilistic}.
 
@@
 \end{equation}
-where $K$ is a kernel function, and $h_n$ is a suitable bandwidth. GA is defined
-as
 
@@
 \end{equation}
-where $\Phi$ is the standard normal CDF and $\hat{\mu}_n$ and $\hat{\sigma}_n$
-are the empirical mean and standard deviation of the sample $(X_i)$
-\cite{krueger2016probabilistic}.
-
-Krueger et. al compare scoring of MCMC drawn forecast distributions using CRPS 
-and LogS over samples directly using ECDF or over density approximations using
-KD or GA.
 
 To build an ensemble model from sample distribution forecasts, the BMA 
-construction from (\ref{eq:bma}) may be used only replacing $p_m$ with 
-$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$ -approximate KD and GA densities. 
+construction from (\ref{eq:bma}) may be used only replacing $p_m$ with the
+approximate KD or GA pdf functions
+-$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$  
 Here as well the optimal weights 
-$w_m$ may be estimated by maximizing the likelihood or minimizing CRPS. Then 
-the ensemble distribution would take the form of a continuous or discrete
-probability mixture distribution. If the desire is that the ensemble still be
+$w_m$ may be estimated by maximizing the likelihood or minimizing CRPS. 
+If the desire is that the ensemble still be
 a sample distribution, after selecting weights, a sample may be selected by 
@@
 
-\subsubsection{Discretized bin distributions}
+\subsection{Bin distributions}
 An alternative to parametric distributions and sample distributions which allows
 for higher flexibility in distribution shape than a parametric distribution and 
-will usually require less storage space than samples is a discretized bin 
+will usually require less storage space than samples is a bin 
 distribution.
 
-A discretized bin probability distribution may be constructed over a set 
+A bin distribution may be constructed over a set 
 $A = [a, b]$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
@@
 $\Delta = b_i - b_{i-1}$ is the same width for all $i$ 
-\cite[see for example]{mcgowan2019collaborative}.
-To complete the construction, a probability $p_i$ is assigned to each $b_i$ 
+\cite{mcgowan2019collaborative}.
+To complete the construction, a probability $p_i$ is assigned to each $B_i$ 
 where $\sum_{i=1}^{K}p_i = 1$. These probabilities are determined by the 
 forecasters. 
-This discrete representation with a given bin and assigned probability is in
-essence a probability mass function in that the calculation of moments and the 
+This representation with a given bin and assigned probability may be 
+treated like a discrete distribution with a pmf in that the calculations of 
+moments and of the 
 the cumulative distribution are done the same as for a discrete parametric 
-distribution. For a random variable $X$ from a binned distribution to calculate
-the $j^{th}$ moment we may use
+distribution. For a random variable $X$ from a binned distribution 
+the $j^{th}$ moment may be calculated as in \eqref{eq:bev}. 
+Here $\beta_i$ is a value corresponding to bin $B_i$ (such as $\beta_i = b_i$,
+$\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$). The 
+cumulative distribution may be calculated as in \eqref{eq:bcdf}.
+Here $p_n$ is the probability for the bin $B_n$ where $b \in B_n$.
 
@@
 \end{equation}
-where $\beta_i$ is a value corresponding to bin $B_i$ (such as $\beta_i = b_i$,
-$\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$). The 
-cumulative distribution may be calculated as
 
@@
 \end{equation}
-where $p_n$ is the probability for the bin $B_n$ where $b \in B_n$.
-
-If the value to be forecasted takes on discrete values, a common discrete 
+
+If the value to be forecasted takes on discrete values a common discrete 
 distribution, such as a binary or Poisson distribution, may sometimes be used to 
@@
 
-The CDC has used a discretized bin distribution representation as the 
-format
-for their annual influenza forecasting competition and other disease outbreak
+The CDC flu competition has used a bin distributions as the forecast 
+representation. The CDC has also used it for other disease outbreak
 forecast projects.
@@
 resolution. 
-In the CDC flu contest, a forecast might have 131 bins between 0\% and 13\% 
--bins having increments of 0.1 or 0.001\%- with 
+In the CDC flu contest, a forecast might have 131 bins between 0\% and 13.1\% 
+-bins having increments of 0.1 or 0.01\%- with 
 corresponding probabilities in each. This makes 262 pieces of information per
 prediction. For any binning scheme of more than two bins, the information 
-requirement for discretized bins will be higher than for parametric distrbutions.
+requirement for bin distributions will be higher than for parametric 
+distributions.
 Table \ref{table:dbins} illustrates what a discretized 
-Lognormal$(1,0.4)$ distribution truncated over $[0,8]$
-looks like in 41 equally spaced discretized bins. The discretization was done
-such that
+$\mbox{Lognormal(1,0.4)}$ distribution truncated over $[0,8]$
+looks like in 41 equally spaced bins. The discretization was done
+such that the probabilities $p_i$ are calculated as in \eqref{eq:disc}
+where $p^{TL}$ is the pdf of a truncated $\mbox{Lognormal(1,0.4)}$. This is 
+similar
+to Methodology-IV from Chakraborty 
+\cite{chakraborty2015generating,kemp2004classes}.
 
@@
 \end{equation}
-where $p^{TL}$ is the pdf of a truncated Lognormal$(1,0.4)$. This is similar
-to Methodology-IV from Chakraborty 
-\cite{chakraborty2015generating,kemp2004classes}.
+
+Submitted as a forecast prediction, the distribution illustrated in table 
+\ref{table:dbins} 
+includes 82 pieces of data. For parts 
+of the CDC influenza competition some forecasts included up to 262. This is 
+far less storage than the possible thousands of draws from a sample 
+distribution but is 
+still much larger than the three or five data pieces required to report a 
+lognormal
+or truncated lognormal distribution.
 
 \begin{table}[h!]
-
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \centering
@@
  \end{tabular}
-  \caption[Discretized bin distribution storage]{Storage example of discretized
-  lognormal with $\mu = 1$ and $\sigma = 0.4$}
+  \caption[Discretized bin distribution storage]{This is a storage example of a
+  discretized
+  lognormal with $\mu = 1$ and $\sigma = 0.4$ truncated over $[0,8]$.}
 \label{table:dbins}
+\end{minipage}
+\end{center}
 \end{table}
-Submitted as a forecast prediction, the distribution in table \ref{table:dbins} 
-includes 82 pieces of data. For parts 
-of the CDC influenza competition some forecasts included up to 262. This is 
-far less storage than the possible thousands of draws from a sample 
-distribution but is 
-still much larger than the three or five data pieces required to report a 
-lognormal
-or truncated lognormal distribution.
-
-Depending on what is known about the problem to be solved, creating the right 
+
+Besides potentially large amount of information required per forecast,
+creating the right 
 binning scheme may be a challenge. Because there must be a finite number of
-bins, forecast distributions often have a finite support. Where the range of 
+bins, forecast distributions often have a finite support. And where the range of 
 possible outcomes to a problem is not well known, the right binning scheme may 
 be
-hard to produce.
-
-\subsubsection{Quantile representation}
+hard to produce. This may depend on the details of the event to be forecasted, 
+but in the case of the COVID-19 outbreak choosing the right set of bins posed
+a few problems.
+
+\subsection{Quantile representation}
 When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
-the time pressure of generating forecasts and the consideration of the large
+the time pressure of generating forecasts and the large
 range for possible outcomes both contributed to the COVID-19 Forecast Hub 
 decision
-to forego trying to create the right binning scheme and use sets of prediction
-intervals to represent uncertainty in predictions \cite{bracher2021evaluating}.
-
-The Forecast Hub requires predictions to be submitted as 11 or three nominal 
+to forego trying to create the right binning scheme and use quantile forecasts
+to forecast the COVID-19 pandemic \cite{bracher2021evaluating}.
+The COVID-19 Forecast Hub requires predictions to be submitted as 11 or three 
+nominal 
 intervals -depending on the specific target and unit to forecast- and a median.
@@
 
-A quantile forecast is constructed as follows.
-For $N$ given quantiles $\alpha_1,..., \alpha_N$; $q_1,..., q_N$ are the values
-such that
+A quantile forecast is constructed as in \eqref{eq:quantiles}.
+Here for $N$ given quantiles $\alpha_1,..., \alpha_N$; $q_1,..., q_N$ are the 
+values such that 
+When the quantiles are reported as prediction intervals we have 
+\eqref{eq:intervals}.
 
@@
 \end{equation}
-When the quantiles are reported as prediction intervals we have
 
@@
 What is possible for scoring forecasts
-or building ensemble models in other representations is often not possible with
+or constructing ensemble in other representations is often not possible with
 quantile forecasts. The shape of a distribution is also not known and in fact,
 nothing is known about the tails or the uncertainty beyond the most 
-extreme reported quantile values. In the Forecast Hub predictions, nothing 
+extreme reported quantile values. In the COVID-19 Forecast Hub predictions, 
+nothing 
 is reported about the range below the $1^{st}$ quantile or above the $99^{th}$.
@@
 
-Quantile representation allows for forecasters to submit fairly detailed
+Quantile FORECASTS allows for forecasters to submit fairly detailed
 forecasts without restricting the range of possible values.
 Since quantiles are easily calculated from any regular distribution type
--e.g. quantile function for parametric functions or calculating sample 
+-using the quantile function for parametric functions or calculating sample 
 quantiles- we consider quantile forecasts to be highly flexible in terms of 
@@
 
-To score predictions from a quantile or prediction interval format, 
+To score a quantile forecast, 
 neither the LogS nor the CRPS may be used, 
@@
 where $l$ and $r$ are the $\alpha/2$ and $(1-\alpha/2)$ quantiles that bound
-the central $(1-\alpha)$ prediction interval the IS is defined as
-
-\begin{equation}
-\label{eq:is}
-  IS_{\alpha}(l,r; x^*) = (r-l) + \frac{2}{\alpha}(l-x^*)1\{x^*<l\} 
-  + \frac{2}{\alpha}(y-r)1\{x^* > r\}
-\end{equation}
+the central $(1-\alpha)$ prediction interval the IS is defined in \eqref{eq:is}.
 This is a sum -weighted by 
@@
 
-When an interval forecast is made up of multiple intervals each with different
-$\alpha$ levels, the weighted interval score (WIS) may be evaluated. Bracher et.
-al use the WIS to evaluate COVID-19 inverval forecasts 
+\begin{equation}
+\label{eq:is}
+  IS_{\alpha}(l,r; x^*) = (r-l) + \frac{2}{\alpha}(l-x^*)1\{x^*<l\} 
+  + \frac{2}{\alpha}(y-r)1\{x^* > r\}
+\end{equation}
+
+When an quantile forecast is made up of multiple intervals each with different
+$\alpha$ levels, the weighted interval score (WIS) may be used as it was by
+Bracher et.
+al use the WIS to score COVID-19 quantile forecasts 
 \cite{bracher2021evaluating}.
@@
 Forecast
-Hub for a forecast of $K$ intervals is defined as follows
+Hub for a forecast of $K$ intervals is defined in \eqref{eq:wis}.
+Here $w_k = \alpha_k/2$ is the weight on the $k^{th}$
+interval. With that selection of weights, it may be shown that the
+WIS approximates the CRPS \cite[see S1 Text therein]{bracher2021evaluating}.
 
@@
 \end{equation}
-where $w_k = \alpha_k/2$ is the weight on the $k^{th}$
-interval. With that choice of weights, it may be shown that the
-WIS approximates the CRPS \cite[see S1 Text therein]{bracher2021evaluating}.
 
@@
 models each with $K$ quantiles, the $k^{th}$ ensemble quantile $q^E_k$ is 
-calculated as
-
-\begin{equation}
-\label{eq:qa}
-  q^E_k = \sum_{m=1}^M \nu_m q_k^m 
-\end{equation}
+calculated as in \eqref{eq:qa}
 where $\nu_m$ is the weight assigned to each forecast and $\sum \nu_m = 1$. In
-the Forecast Hub model, $\nu_m = \nu = 1/M$. Where the overall mean or a
-weighted mean may be used, the median may also be used.
+the COVID-19 Forecast Hub model, $\nu_m = \nu = 1/M$. Where the overall mean or 
+a weighted mean may be used, the median may also be used.
 Brooks et. al compare performance of the COVID-19 ensemble
-between equally-weighted means, weighted means and median value constructions.
-\cite{brooks2020comparing} (is is appropriate to cite this blog??)
+using equally-weighted means, weighted means, and median value constructions
+\cite{brooks2020comparing}.
 In their report, they show that weighted means and median constructions tend
@@
 the ensemble forecast.
-
 Averaging quantiles in this way is the same as quantile averaging or Vincentization
@@
 same characteristics.
+
+\begin{equation}
+\label{eq:qa}
+  q^E_k = \sum_{m=1}^M \nu_m q_k^m 
+\end{equation}
+
 Quantile averaging or Vincentization for a complete distribution is defined as
-
-\begin{equation}
-\label{eq:vinc}
-  F_v^{-1}(\alpha) = \sum_{m=i}^M w_m F_m^{-1} (\alpha)
-\end{equation}
+in \eqref{eq:vinc}
 where $F_m^{-1} (\alpha) = \inf \{y:F_m(y) \geq \alpha\}$ for 
@@
 to be unimodal than it is under linear averaging of densities like BMA 
-\cite{busetti2017quantile} Under some circumstances, such as when member
-distributions are exponential, Weibull or logisitic the aggregated distribution
-is the same \cite{ratcliff1979group}. It produces smoother
+\cite{busetti2017quantile}. Under some circumstances, such as when member
+distributions are exponential, Weibull, or logisitic the aggregated distribution
+is of the same family \cite{ratcliff1979group}. Quantile averagin produces 
+smoother
 distributions than BMA according to Schepen and Wang \cite{schepen2015model}.
-Lichtendahl et. al conclude that quantile averaging produces sharper forecasts
-and tends to perform better in scoring than probability averaging
+And Lichtendahl et. al conclude that quantile averaging produces sharper 
+forecasts
+and tends to perform better in scoring than probability averaging, BMA,
 \cite{lichtendahl2013better}.
 
-As in sample distributions and binned distributions, 
+\begin{equation}
+\label{eq:vinc}
+  F_v^{-1}(\alpha) = \sum_{m=i}^M w_m F_m^{-1} (\alpha)
+\end{equation}
+
+As in sample distributions and bin distributions, 
 data storage for interval forecasts will
 depend on the desired clarity of resolution. For the COVID-19 forecasts 
-submitted to the Forecast Hub, 23 quantile values are requested for 
-the quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This included a 
-median along with eleven confidence intervals \cite{bracher2021evaluating}. This
-requires forecasters to submit 46 values in each short-term forecast 
+submitted to the COVID-19 Forecast Hub, 23 quantile values are requested for 
+quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This includes a 
+median along with 11 predictive intervals \cite{bracher2021evaluating}. 
+Forecasters are thus required to submit 46 values in each short-term forecast 
 (some of the longer term forecasts only include seven quantiles). In terms of 
@@
 \ref{table:qstor} shows what a submission of 23 quantiles from a 
-$Lognormal(1,0.4)$ looks like.
+$\mbox{Lognormal(1,0.4)}$ might look like.
 
@@
 \centering
+\begin{center}
+
+\captionsetup{font=scriptsize}
 
@@
  \end{tabular}
+ \begin{minipage}{10cm}
  \caption[Quantile/interval and values storage]{Storage example of quantiles 
@@
  \label{table:qstor}
+ \end{minipage}
+ \end{center}
 \end{table}

### 2022-04-01 manuscript/thesis.tex
revisions to sections 2 and 3

@@
 sources,
-BMA may be preferrable because it does not require that modeling methods for 
+BMA may be preferable because it does not require that modeling methods for 
 individual components be the same. 
@@
  \begin{minipage}{10cm}
- \caption[Quantile/interval and values storage]{Storage example of quantiles 
- and values of lognormal with $\mu = 1$ and $\sigma = 0.4$}
+ \caption[Quantiles and values storage]{This shows six quantiles
+ and values from a lognormal distribution with $\mu = 1$ and $\sigma = 0.4$}
  \label{table:qstor}
@@
 
+Figure \ref{fig:denscomp} illustrates how the densities and CDFs compare 
+between parametric distributions, sample distributions, bin distributions, and
+quantiles.
+
 \begin{figure}[htbp]
+\begin{center}
+
+\captionsetup{font=scriptsize}
 \centerline{\includegraphics[scale=.1]{Images/dens_cum_comp.png}}
+\begin{minipage}{10cm}
 \caption[Density/CDF comparison between parametric distribution, sample 
@@
 densities and CDFs of forecast representation types discussed in the left and 
-right columns respectively. Each is generated from a lognorma(1,0.4) 
+right columns respectively. Each is generated from a Lognorma(1,0.4) 
 distribution. Blue shows the density and CDF functions. Purple shows a 
 histogram and ECDF of 1,000 samples. Red shows bin probabilities and the CDF
-function. Green shows quantiles/intervals with corresponding values.}
+function for a bin distribution. Green shows quantiles
+with corresponding values.}
 \label{fig:denscomp}
+\end{minipage}
+\end{center}
 \end{figure}
 
-\section{Discrete mixture of parametric distributions}
-A discrete mixture of parametric distributions forecast representation may be an
-attractive alternative to the four types already discussed. A discrete mixture 
+\newpage
+
+\section{Mixture distributions}
+A discrete mixture of parametric distributions forecast -which we will refer to
+as a mixture distribution forecast- representation is an
+attractive alternative to the four representations already discussed. 
+A mixture distribution forecast
 would allow for many distribution shapes, a high resolution, storage comparable
-to that of discretized bins and quantile representations and the use of the more
-common methods for scoring and ensemble building.
-
-A discrete mixture distribution may be constructed in the same way as the
-ensemble described in section \ref{section:pardist} in equation 
+to that of bin and quantile forecasts, and the more common methods for scoring
+and ensemble construction may be used.
+
+A mixture distribution may be constructed in the same way as the
+ensemble described in section \ref{section:pardist} 
 (\ref{eq:bma}) 
 where for $T$ distributions
-with pdfs $p_t(x)$ and $z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$
+with pdfs $p_t(x)$ and $z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$ we have 
+\eqref{eq:dmd}.
 
@@
 
-Like the standard parametric model, a discrete mixture may be evaluated with
-exisiting software (like distr \texttt{R} package \cite{camphausen2007distr}). 
+Like the parametric, a mixture distribution may be evaluated with
+existing software like \texttt{distr} package in \texttt{R} 
+\cite{camphausen2007distr}. 
 And 
-scoring may be done by 
-using the LogS, CRPS and IS. The resolution of a discrete mixture is infinite 
-and the support need not be limited by submission requirements.
+scoring may be done  
+using the LogS, CRPS and IS. A mixture distribution, like its parametric 
+distribution components, has an infinite resolution.
 
@@
 distribution -such as MCMC posterior samples- it may be reasonable to 
-approximate the distribution by constructing a mixture of normals.
-% See section \ref{section:conmix} for an example.
-
-An ensemble model may be built by using (\ref{eq:bma}) only replacing $p_m$
-with $p_m^M$ in \ref{eq:dmd}. Solving for weights may also be done similarly, 
-though with the 
+approximate the distribution by fitting those samples to a mixture of normal
+distributions.
+Depending on the number of components a forecaster includes in a mixture 
+forecast, the amount of storage per forecast might be as little as for a 
+parametric forecast or as permitted in the specific forecast project.
+
+An ensemble model may be built by using \eqref{eq:bma} only replacing $p_m$
+with $p_m^M$ in \eqref{eq:dmd}. Solving for weights may also be done by 
+maximizing
+the likelihood of the forecast or minimizing the CRPS. However with the 
 added complexity of component models being mixture distributions the 
-computation is likely to be more expensive. An example where this may be
-especially true is when minimizing of CRPS, but the exact mixture doesn't 
-result in CRPS in closed form \cite{baran2018combining}. In large projects like
+computation is likely to be more expensive. An example where this is
+true is when trying to minimize the CRPS but the exact mixture doesn't 
+produce a closed form CRPS \cite{baran2018combining}. In large projects like
 the COVID-19 Forecast Hub, if an equal weight is not assigned to each component,
@@
 
-Depending on the number of components a forecaster includes in a mixture 
-forecast, the amount of storage per forecast might be as little as for a 
-parametric forecast and as much as a forecast hub will allow. In section
+Table \ref{table:repscomp} shows how a discrete mixture distribution forecast 
+compares with the other formats discussed in terms of methods for scoring,
+information and resolution provided, methods for ensemble building, and computer
+storage requirement. To summarize, a continuous mixture distribution has the 
+infinite resolution of a parametric distribution with the flexibility of a bin
+distribution, a sample distribution, and a set of quantiles. The common proper
+scoring rules LogS and CRPS may be used to score it. The storage requirement is
+comparable to that of a bin distribution or a set of quantiles. And BMA may be 
+used for building an ensemble.
+In Section
 \ref{section:conmixforc} we show how a mixture distribution may be constructed,
@@
 
-Table \ref{table:repscomp} shows how a discrete mixture distribution forecast 
-compares with the other formats discussed in terms of methods for scoring,
-information and resolution provided, methods for ensemble building and computer
-storage requirement.
-
 \begin{flushleft}
+
   \begin{table}
-    % \begin{adjustwidth}{-3cm}{-1cm}
+    \begin{center}
+    \captionsetup{font=scriptsize}
     \begin{tabular}{ | p{2.4cm} || p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
@@
 
-    Parametric & LogS, CRPS, IS & Limited to common distribution families. 
+    Parametric distribution & LogS, CRPS, IS & Limited to common 
+    distribution families. 
     Infinite resolution
@@
 
-    Samples & CRPS and IS. LogS after smoothing & Any shape. Resolution may be
+    Sample distribution & CRPS and IS. LogS after smoothing & Any shape. 
+    Resolution may be
     very high but depends on sample size & BMA after smoothing. Resampling 
@@
 
-    Discretized bins & LogS, CRPS, IS &
+    Bin distribution & LogS, CRPS, IS &
     Any shape allowed, but limited by binning scheme. Range also may be limited
@@
 
-    Discrete Mixture & LogS, CRPS, IS. May be more limited by computation & With
+    Mixture distribution & LogS, CRPS, IS. May be more limited by computation & 
+    With
     enough component distributions may
@@
 	 % \end{adjustwidth}
+    \begin{minipage}{14cm}
    \caption[Forecast representation comparison]{This table compares scoring,
-   information, ensemble building and storage requirements for the different
-   forecast representations discussed.}
+   information, ensemble building, and storage requirements for the different
+   forecast representations discussed. To summarize 
+   a continuous mixture distribution has the 
+infinite resolution of a parametric distribution with the flexibility of a bin
+distribution, a sample distribution, and a set of quantiles. The common proper
+scoring rules LogS and CRPS may be used to score it. The storage requirement is
+comparable to that of a bin distribution or a set of quantiles. And BMA may be 
+used for building an ensemble.}
    \label{table:repscomp}
+   \end{minipage}
+   \end{center}
    \end{table}
@@
 
-The CDC and the COVID-19 Forecast Hub as well as other collaborative projects
+The CDC flu competition and the COVID-19 Forecast Hub as well as other 
+collaborative projects
 have their own established systems for receiving, 
@@
 adjustments may be implemented as well as present some tools which may be used
-to score forecasts and construct ensembles from multiple models.
+to build forecasts from submissions, score those forecasts, and construct 
+ensembles from them.
 
 \section{Submission format}
-For a collaborative forecast project to run smoothly, model submissions from all 
-modelers should follow the same format. For both the CDC flu competition and
-the COVID-19 Forecast Hub, teams provide a \texttt{.csv} spreadsheet with 
-columns 
-similar to those in tables \ref{table:dbins} and \ref{table:qstor}. Additionally
-columns for \texttt{location}, \texttt{target}, \texttt{type}, and \texttt{unit} 
-are included.
+For a collaborative forecast project to run smoothly, forecast submissions from 
+all forecasters 
+should follow the same format. For both the CDC flu competition and
+the COVID-19 Forecast Hub, teams provide a \texttt{.csv} spreadsheet which 
+contains the distributional information for one or multiple forecasts. Tables
+\ref{table:dstan} and \ref{table:qstan} show what variables are included and a
+couple rows to illustrate possible values.
+The column variables include \texttt{location}, \texttt{target}, \texttt{type},
+\texttt{unit}, \texttt{bin} or \texttt{quantile} and \texttt{value}.
 Here \texttt{location} defines the specific county, state, or country of the 

### 2022-04-01 manuscript/thesis.tex
further revisions of section 3

@@
 The column variables include \texttt{location}, \texttt{target}, \texttt{type},
-\texttt{unit}, \texttt{bin} or \texttt{quantile} and \texttt{value}.
+\texttt{unit}, \texttt{bin} or \texttt{quantile}, and \texttt{value}.
 Here \texttt{location} defines the specific county, state, or country of the 
-forecast. The \texttt{target} variable defines what is forecasted for example
+forecast. The \texttt{target} variable defines what is forecasted with levels
 season onset, deaths, hospitalizations, etc. The \texttt{type} variable defines
-the type for the \texttt{value} variable, \texttt{bin} or \texttt{quantile}.
-The \texttt{unit} variable defines the time frame of the forecast: week,
-two weeks, four weeks, etc. And the \texttt{value} variable is a number that 
-either gives probability for a bin or the value for a quantile. Table
-\ref{table:dstan} show what a few rows of a forecast 
-submission file for the CDC flu competition look like.
-For the quantile forecasts of the Forecast Hub, the main changes to Table
-\ref{table:dstan} are that the possible values for \texttt{type} 
-quantile, and rather than using a \texttt{bin} variable \texttt{quantile} is 
-used
-with values specified by the Hub. This is seen in Table \ref{table:qstan}
-
-A single submission may include many forecasts each aimed at predicting a 
-different combination of \texttt{location}, \texttt{target}, and \texttt{unit}. 
+the type for the \texttt{value} variable with levels of \texttt{point}, 
+bin, or quantile.
+The \texttt{unit} variable defines the time frame of the forecast with levels of
+week,
+two weeks, four weeks, etc. The variables \texttt{bin} and \texttt{quantile}
+give a specific bin or a specific quantile. And the \texttt{value} variable is a 
+number that 
+either gives the probability associated with a bin or the value associated 
+with a quantile.
+
+A single submission may include many forecasts aimed at forecasting a 
+different combinations of \texttt{location}, \texttt{target}, and \texttt{unit}. 
 A set of rows which share
@@
 
-In the mixture distribution format, an adjustment may be made to the format of 
-Tables
-\ref{table:dstan} and \ref{table:qstan} where each 
-row
-represents a component in a mixture distribution.
-The variables Bin/Quantile and Value are removed and replaced with Family,
-Param1, Param2 and Weight where Family is the distribution family,
-Params are the parameters for the component distribution and Weight is the 
+Table \ref{table:mstan} illustrates adjustments made to the submission formats
+from 
+Tables \ref{table:dstan} and \ref{table:qstan} which make a useable submission 
+format for mixture distribution forecasts. In such a format, each row represents
+a component used in a mixture distribution.
+The variables \texttt{bin} or \texttt{quantile} and \texttt{value} are removed 
+and replaced with \texttt{family},
+\texttt{param1}, \texttt{param2}, and \texttt{weight} where \texttt{family} is 
+the distribution family of the component,
+\texttt{param1} and \texttt{param2} are the parameters for the component 
+distribution, and \texttt{weight} is the 
 weight $w_i$ for that component.
@@
     \\ \hline
-    US National & Season Onset & Dist & week & norm & $\mu_n$ & $\sigma_n$ & .\\
-    US National & Season Onset & Dist & week & lnorm & $\mu_l$ & $\sigma_l$ &.\\
-    ... & ... & ... & ... & ... & ... & ... & .\\
+    US National & Season Onset & Dist & week & norm & $a_n$ & $b_n$ & $w_1$\\
+    US National & Season Onset & Dist & week & lnorm & $a_l$ & $b_l$ & $w_2$\\
+    ... & ... & ... & ... & ... & ... & ... & ...\\
  \hline
  \end{tabular}
- \caption[Mixture distribution forecast submission example]{Example of a 
+ \begin{minipage}{11cm}
+\captionsetup{font=scriptsize}
+ \caption[Mixture distribution forecast submission example]{This is an example 
+ of a 
  submission file
- for a disease outbreak forecast using mixture distribution representation}
+ for a disease outbreak forecast using a mixture distribution representation.
+ Each row represents a component of a mixture distribution. The variables
+ location, target, and unit specify what is being forecasted. The variable type
+ specifies that the row represents a parametric distribution. The variables
+ family, param1, and param2 specify the exact distribution. And the variable 
+ weight specifies the weight $w_i$ that the component distribution has in the
+ mixture distribution. Here two components are shown with distributions
+ Normal$(a_n, b_n)$, Lognormal$(a_l, b_l)$ and weights $w_1$ and $w_2$.}
  \label{table:mstan}
+ \end{minipage}
 \end{table}
 
-A forecast center may want to limit the number of components allowed per 
-prediction. For reference, a mixture distribution prediction following the 
-format in table \ref{table:dstan} with 18 
-components would require $18 \times 8 = 144$ cells submitted. This is the same 
-number of cells
-submitted for a Forecast Hub forecast with 23 quantiles and a point prediction 
-according to the format in table \ref{table:dstan}.
+For reasons of storage and computation, a forecast project may have a limit to 
+the number of components allowed per forecast.
+For reference, a mixture distribution forecast following the 
+format in table \ref{table:dstan} with 17
+components would require $17 \times 8 = 136$ cells submitted per forecast. 
+A submission to the COVID-19 Forecast Hub forecast 23 quantiles
+according to the format in table \ref{table:dstan} requires
+$23 \times 6 = 138$ cells. Thus if the COVID-19 Forecast Hub were to change the
+forecast representation from quantile forecasts to mixture forecasts but 
+continue allowing the same amount of data per forecast, 
+a mixture distribution with 17 components could be used in one forecast. That
+many components could allow for a large range of distribution shapes and 
+flexible forecasts.
 
 Throughout the remainder of this section, explanations of how to work with 
-mixture distributions along with \texttt{R} code which will be given to 
-demonstrate constructing a mixture distribution from a forecast submission, 
-scoring the forecast and building an ensemble forecast.
+mixture distributions submitted according to Table \ref{table:mstan} is 
+given. Also given is
+\texttt{R} code which 
+demonstrates constructing a mixture distribution from a forecast submission, 
+scoring the forecast, and building an ensemble from two separate submissions.
 
@@
 
-From a submitted forecast, a prediction may be found by Location, Target and 
-Unit (or whatever other indication variables are used by collaborators) and 
-evaluated. We found
-the \texttt{distr} package \cite{camphausen2007distr}
-useful for constructing a mixture distribution given
-information like that from table \ref{table:dstan}.
-
-The function 
-\texttt{UnivarMixingDistribution} takes as arguments a list of distributions
+A single \texttt{.csv} submission file of the format in Table \ref{table:mstan} 
+may contain multiple forecasts forecasting different combinations of location,
+target, and unit. Selecting only rows which share a specific combination of 
+location, target, and unit will produce a table representing a single forecast.
+That table may look like Tables \ref{tab:preddf1} and 
+\ref{tab:preddf1}. If the table is saved as a standard \texttt{data.frame} in 
+\texttt{R}, then tools based on the \texttt{distr} package 
+\cite{camphausen2007distr} may be used for evaluating a mixture distribution 
+with the components in the table.
+
+The \texttt{distr} package contains a function 
+\texttt{UnivarMixingDistribution()} takes as arguments a list of distributions
 and a vector of weights for each distribution and a object of class 
-\texttt{AbscontDistribution} is returned. The object is in essence a mixture
-distribution of the form of (\ref{eq:dmd}). Functions for density, 
-distribution
-and quantile functions as well as for random sampling may then be used on the
-mixture distribution object for evaluation. Using those functions and the 
-created object, LogS and CRPS are easily calculable.
-
-We wrote a function \texttt{MakeDist} (see Appendix)
-which takes on a data frame with variables
-Family, Param1, Param2, Param3 and Weight and returns a mixture distribution 
-of component distributions specified in the rows.
-
-Beginning with two forecast submissions of the form of table \ref{table:dstan}, 
-say we select from each a prediction of an event for the same location, target
-and unit. The following two data frames \texttt{preddf1} and \texttt{preddf2}
-are the resulting predictions.
+\texttt{AbscontDistribution} is returned. An \texttt{AbscontDistribution} class
+is a mother class which defines a random number generator, pdf,
+CDF, and quantile function for continuous distributions from common
+families contained in the \texttt{distr} and for mixture distributions with 
+component distributions from those families.
+We wrote a function \texttt{MakeDist()} (see APPENDIX)
+which takes on a \texttt{data.frame} with variables
+family, param1, param2, param3, and weight and where each row represents a
+component distribution in a mixture distribution. The function 
+\texttt{MakeDist()} calls on the \texttt{UnivarMixingDistribution()} function
+and returns a mixture distribution object of class \texttt{AbscontDistribution}.
+
+If a forecast such as in Table \ref{tab:preddf1} is taken as an argument in 
+\texttt{MakeDist()}, the resulting mixture distribution may then be evaluated 
+with functions for the pdf, CDF, quantile function, and random samples from the
+mixture distribution may be drawn. Thus the distribution may be scored using the
+LogS or CRPS.
 
@@
  \end{tabular}
- \caption[Toy prediction 1]{Toy prediction 1}
+ \caption[Illustrative forecast 1]{Toy prediction 1}
  \label{tab:preddf1}
@@
  \end{tabular}
- \caption[Toy prediction 2]{Toy prediction 2}
+ \caption[Illustrative forecast 2]{Toy prediction 2}
  \label{tab:preddf2}
@@
 
-The code here shows these two data frames and how the \texttt{MakeDist} 
+Here we include code to illustrate the process of constructing and scoring two 
+separate forecasts. We suppose that Table \ref{tab:preddf1} represents a 
+submitted forecast from one forecaster and Table \ref{tab:preddf2} represents
+a forecast of the same event from a second forecaster.
+Note the additional \texttt{param3} variable
+in Tables \ref{tab:preddf1} and \ref{tab:preddf1}. This variable is included
+in the table because of the functionality of the \texttt{MakeDist()} function
+which allows for component distributions of three parameters.
+The code here shows these two forecasts as \texttt{data.frame}s and how the 
+\texttt{MakeDist()} 
 function is used to create the distributions in \texttt{R}. Once the 
-distributions are created as \texttt{AbscontDistribution} classes, then 
+distributions are created as \texttt{AbscontDistribution} objects, then 
 functions for evaluating a pdf and a CDF for each are created.
@@
 \specialchapt{APPENDIX}
+\label{section:append}
 

### 2022-04-01 manuscript/thesis.tex
revisions to sections 3 and 4

@@
 \usepackage[svgnames]{xcolor}
+
 \usepackage{graphicx}
@@
 \renewcommand{\chaptername}{}
+
 \usepackage{Sweave}
@@
 \input{thesis-concordance}
+\DefineVerbatimEnvironment{Sinput}{Verbatim} {xleftmargin=2em,
+                                              frame=single}
+\DefineVerbatimEnvironment{Soutput}{Verbatim}{xleftmargin=2em,
+                                              frame=single}
 \DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
+
 %\begin{singlespace}
@@
     \\ \hline
-    US National & Season Onset & Dist & week & norm & $a_n$ & $b_n$ & $w_1$\\
-    US National & Season Onset & Dist & week & lnorm & $a_l$ & $b_l$ & $w_2$\\
+    us national & season onset & dist & week & norm & $a_n$ & $b_n$ & $w_1$\\
+    us national & season onset & dist & week & lnorm & $a_l$ & $b_l$ & $w_2$\\
     ... & ... & ... & ... & ... & ... & ... & ...\\
@@
  \end{tabular}
- \caption[Illustrative forecast 1]{Toy prediction 1}
+  \begin{minipage}{11cm}
+\captionsetup{font=scriptsize}
+ \caption[Illustrative forecast 1]{This is an illustrative example of a
+ mixture distribution
+ forecast where the distribution is described in a data frame. The first 
+ component is a Lognormal$(2,1)$ with a weight of 0.3 in the mixture and the 
+ second component is a Normal$(2.1,1)$ with a weight of 0.7.}
  \label{tab:preddf1}
+ \end{minipage}
 \end{table}
@@
  \end{tabular}
- \caption[Illustrative forecast 2]{Toy prediction 2}
+  \begin{minipage}{11cm}
+\captionsetup{font=scriptsize}
+ \caption[Illustrative forecast 2]{This is a second
+ illustrative example of a mixture distribution
+ forecast where the distribution is described in a data frame. The first 
+ component is a Normal$(1.5,1)$ with a weight of 0.4 in the mixture and the 
+ second component is a Normal$(4,2)$ with a weight of 0.6.}
  \label{tab:preddf2}
+ \end{minipage}
 \end{table}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.15]{Images/toyfors12.png}}
+\begin{center}
+ \begin{minipage}{11cm}
+\captionsetup{font=scriptsize}
+\caption[Example mixture distributions]{These plots show the density functions 
+of
+the two example mixture distribution forecasts along with the component density
+functions scaled by the corresponding weights}
+\label{fig:toymixs}
+\end{minipage}
+\end{center}
+\end{figure}
 
@@
 submitted forecast from one forecaster and Table \ref{tab:preddf2} represents
-a forecast of the same event from a second forecaster.
+a forecast of the same event from a second forecaster. Table \ref{fig:toymixs}
+shows plots of the pdfs for both mixture forecasts.
 Note the additional \texttt{param3} variable
@@
 in the table because of the functionality of the \texttt{MakeDist()} function
-which allows for component distributions of three parameters.
+which allows for component distributions of up to three parameters.
 The code here shows these two forecasts as \texttt{data.frame}s and how the 
@@
 > preddf1
-> #  family param1 param2 param3 weights
-> #1  Lnorm    2.0      1     NA     0.3
-> #2   Norm    2.1      1     NA     0.7
-> 
+\end{Sinput}
+\begin{Soutput}
+  family param1 param2 param3 weights
+1  Lnorm    2.0      1     NA     0.3
+2   Norm    2.1      1     NA     0.7
+\end{Soutput}
+\begin{Sinput}
 > preddf2
-> #  family param1 param2 param3 weights
-> #1   Norm    1.5      1     NA     0.4
-> #2   Norm    4.0      2     NA     0.6
-> 
-> 
-> 
+\end{Sinput}
+\begin{Soutput}
+  family param1 param2 param3 weights
+1   Norm    1.5      1     NA     0.4
+2   Norm    4.0      2     NA     0.6
+\end{Soutput}
+\begin{Sinput}
 > #make mixture distributions from prediction submissions
@@
 > mdist2 <- MakeDist(preddf2)
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
 > #make pdfs for mixture predictions
@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics[scale=.15]{Images/toyfors12.png}}
-\caption[Toy mixture distributions]{These plots show the density functions of
-the two toy mixture distribution forecasts along with the component density
-functions scaled by the corresponding weights}
-\label{fig:toymixs}
-\end{figure}
-
 The LogS or the CRPS may then be calculated for each forecast using the pdf
-and cdf functions respectively. Here will will assume that the realized value
-which both forecasts attempted to predict was 3. The \texttt{CRPS()} function 
-here is 
-included in the appendix of this manuscript. It can be seen here that by the 
-LogS, the forecast from table \ref{tab:preddf1} outperforms that from table
-\ref{tab:preddf2}. Yet under the CRPS the performance is the other way around.
+and CDF functions respectively. Here will will assume that the realized value
+which both forecasts attempted to predict was \texttt{3}. 
+The \texttt{CRPS()} function
+here is one that we wrote and is
+included in the APPENDIX. It is seen in the code below that under the
+LogS, forecast 1 from table \ref{tab:preddf1} outperforms forecast 2 from table
+\ref{tab:preddf2} with scores of 1.547 and 
+1.849 respectively. 
+However, under the CRPS forecast 2 outperforms forecast 1
+with scores 0.635 and 
+0.635 respectively. We continue to use these same
+forecasts in Section \ref{section:enscon} to construct an ensemble forecast.
 
@@
 > #LogS for predictions at the realized observation
-> -log(dmdist1(ob)) # => 1.547238
-> -log(dmdist2(ob)) # => 1.848796
+> -log(dmdist1(ob))
+\end{Sinput}
+\begin{Soutput}
+[1] 1.547238
+\end{Soutput}
+\begin{Sinput}
+> -log(dmdist2(ob))
+\end{Sinput}
+\begin{Soutput}
+[1] 1.848796
+\end{Soutput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
 > #CRPS for predictions at the realized observation
-> CRPS(pmdist1,y=ob) # => 0.6348212
-> CRPS(pmdist2,y=ob) # => 0.5306083
+> CRPS(pmdist1,y=ob)
 \end{Sinput}
+\begin{Soutput}
+[1] 0.6348212
+\end{Soutput}
+\begin{Sinput}
+> CRPS(pmdist2,y=ob)
+\end{Sinput}
+\begin{Soutput}
+[1] 0.5306083
+\end{Soutput}
 \end{Schunk}
@@
 \section{Ensemble construction}
+\label{section:enscon}
 
 To construct an ensemble distribution from multiple mixture distributions, the 
-\texttt{UnivarMixingDistribution} is again a useful tool. The function takes 
+\texttt{UnivarMixingDistribution()} is again a useful tool. The function takes 
 two or more
-\texttt{AbscontDistribution} or mixture distributions and a vector of weights 
-corresponding to each mixture. A new \texttt{AbscontDistribution} object is 
-returned as an ensemble of mixture distributions see (\ref{eq:bma}).
-
-At the onset of a collaborative forecast before the various models can be scored
-based on true observations, it may make sense to assign equal weight to each 
+\texttt{AbscontDistribution} distribution objects and a vector of weights 
+corresponding to each object. A new \texttt{AbscontDistribution} object is 
+returned as an ensemble of mixture distributions as in (\ref{eq:bma}). 
+Since they are \texttt{AbscontDistribution} objects \texttt{mdist1} and 
+\texttt{mdist2} created in the code
+in Section \ref{section:tools} may be input as arguments into the function
+\texttt{UnivarMixingDistribution()}, but weights for each object need to also
+be determined.
+
+At the onset of a collaborative forecast before there are true event 
+observations which the forecasts can be scored on, 
+it may make sense to assign an equal weight to each 
 component distribution in an ensemble. As a project progresses however, 
@@
 If we have $T$ models ($M_t$) the posterior model probability of $M_t$ is 
-defined as
+defined as in \eqref{eq:pmp} where $p(\cdot |M_t) := p_m(\cdot)$ is the density 
+function of the model and 
+$p(M_j)$ is the prior probability assigned to the model. A common approach is to
+assume the prior
+probabilities for each model are equal or $p(M_t) = 1/T$ for all $t$ in which 
+case
+(\ref{eq:pmp}) is reduced to \eqref{eq:pmpeq}. In this case the posterior model 
+probability for model $t$ is equal to the exponential of its negative LogS or
+$p(M_t|x) = e^{-LogS(p(M_t|x))}$, so the performance of a forecast based on the
+LogS is directly related to posterior model probability and may be used as an 
+ensemble weight. For an observed event $x^*$, ensemble weights $(w_t)$ from 
+\eqref{eq:bma} may be defined as $w_t := p(M_t|x^*)$.
 
@@
 \end{equation}
-where $p(\cdot |M_t) := p_m(\cdot)$ is the density function of the model and 
-$p(M_j)$ is the prior probability assigned to the model. Where the prior
-probabilities for each model are equal or $p(M_t) = 1/T$ for all $t$ 
-(\ref{eq:pmp}) is reduced to
 
@@
 
-The posterior model probability $p(M_t|x^*)$ for an already observed event $x^*$
-are then used as weights for a yet unrealized event being forecasted i.e.
-$w_t := p(M_t|x^*)$ see (\ref{eq:bma}).
-
-From the same toy problem in the previous section, the following code shows how
+Using the illustrative example from Section \ref{section:tools}, 
+the following code shows how
 to use the posterior model probability to select weights and construct an 
-ensemble distribution and score the ensemble forecast. The ensemble distribution
+ensemble distribution and score the ensemble forecast. Here again we take the 
+observed value to be \texttt{3}.
+The ensemble distribution
 with components is show in figure \ref{fig:mixense}.
@@
 > w2 <- 1-w1
-> #w1 => 0.5286434
-> #w2 => 0.4713566
-> 
+> w1
+\end{Sinput}
+\begin{Soutput}
+[1] 0.5286434
+\end{Soutput}
+\begin{Sinput}
+> w2
+\end{Sinput}
+\begin{Soutput}
+[1] 0.4713566
+\end{Soutput}
+\begin{Sinput}
 > #build ensemble with calculated weights
@@
 > #LogS for predictions at the realized observation
-> -log(densdist(ob)) # => 1.678156
+> -log(densdist(ob))
+\end{Sinput}
+\begin{Soutput}
+[1] 1.678156
+\end{Soutput}
+\begin{Sinput}
 > #CRPS for predictions at the realized observation
-> CRPS(pensdist,y=ob) # => 0.5486368
+> CRPS(pensdist,y=ob)
 \end{Sinput}
+\begin{Soutput}
+[1] 0.5486368
+\end{Soutput}
 \end{Schunk}
@@
 \centerline{\includegraphics[scale=.15]{Images/mix_ense.png}}
-\caption[Toy ensemble forecast]{Toy ensemble forecast with component mixture
-distributions shown}
+\caption[Toy ensemble forecast]{Ensemble forecast made from forecast 1 and 
+forecast 2 from Section \ref{section:tools}. The green line is the density 
+component of mixture forecast 1 with weight 0.529. The 
+red line is the density component of mixture forecast 2 with weight 
+0.471. The blue line is the density of the ensemble.}
 \label{fig:mixense}
@@
 
-\chapter{Retrospective Analysis}
+\chapter{Retrospective analysis}
 \label{section:retrostud}
@@
 representation formats for forecasting, it may be difficult for individual
-forecast teams to adjust to a discrete mixture distribution format. Exact 
-methods for modeling and forecasting may not cater well to submitting a forecast
-as a discrete parametric mixture distribution.
-
+forecast teams to adjust to a mixture distribution format. There may be several
+reasons for this, including that not all 
+forecast modeling methods will produce forecasts which may conveniently be
+represented by a mixture distribution.
 In this section we attempt to assess whether or not any forecasts from the CDC
-influenza forecast competition and the COVID-19 Forecast Hub were generated from
-common continuous parametric distributions. The forecasts we assess are in the 
-forms of discretized bin predictions or sets of predictive intervals. In these
-formats, not knowing anything about distributions or samples,  formal 
-statistical methods for fitting to parametric distributions 
-and assessing fit do not exist. Thus any results stated here may not be stated
-in terms of statistical certainty.
-
-\section{CDC Influenza like Illness}
+flu competition and the COVID-19 Forecast Hub were generated from one component
+mixture distribution models. We do this by fitting one component mixture 
+distributions to the forecasts and assessing how well the fit models represent
+the forecasts.
+
+Forecasters in both the CDC flu competition and the COVID-19 Forecast Hub do 
+not include with their forecast submissions information about modeling methods 
+or 
+distributional assumptions. Thus the only information we have for fitting
+distributions are bin
+forecasts and quantile forecasts. We are unaware of formal statistical 
+methods for fitting parametric distributions or mixture distributions to bin
+distributions. Methods of fitting a distribution to quantiles 
+include Bayesian Quantile Matching
+\cite{nirwan2020bayesian}, step interpolation with exponential tails 
+\cite{quinonero2005evaluating},
+and the Method of Simulated Quantiles 
+\cite{dominicy2013method}. These studies however lack claims that the methods
+for fitting are statistically formal.
+Because of this it should be noted that any conclusions made in 
+this section may not be 
+stated in terms of statistical certainty.
+
+\section{CDC flu competition}
 The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
-850,000 probabilistic influenza-like illness predictions for all combinations
-of eleven regions 
-in the United States and seven targets from twenty-seven different models. These
-include predictions during Influenza season between October 2010 and December
-2018. All predictions are in the form of discretized probability bins.
-
-We wanted to determine whether or not some or any of these binned forecasts were
-generated from known uniform, normal, 
-lognormal or gamma continuous distribution families. 
-The process we followed for making such a claim was
-to fit a distribution to the probabilities provided in the forecast by
-minimizing
-
-\begin{equation}
-  \sum_{i=1}^K (p_i - [F(b_i; \theta) - F(b_{i-1}; \theta)])^2
-  \label{eq:mds}
-\end{equation}
-
-Here $F(\cdot; \hat{\theta})$ is a CDF, $p_i$ is the reported probability for 
+869,638 probabilistic influenza-like illness forecasts for all combinations
+of 11 regions 
+in the United States and seven targets from 27 different modeling teams. These
+include forecasts made during all flu seasons between October 2010 and December
+2018. All forecasts are represented by bin distributions. 
+We wanted to determine whether or not any of these forecasts were
+generated from one component mixture distributions of continuous uniform, 
+truncated normal (TN), truncated
+lognormal (TL), or truncated gamma (TG) distribution families.
+The process we followed for determining if a forecast was generated by one of
+these common families was to first fit a distribution of that family to the bin
+forecast and then measure close the fit was. The decsion to fit truncated 
+distributions was due to all bin forecasts being assessed having a finite 
+support.
+
+To fit a distribution to a forecast we first minimize \eqref{eq:msd}. We call
+\eqref{eq:msd} the mean square difference (MSD).
+Here $F(\cdot| \hat{\theta})$ is a CDF, $p_i$ is the reported probability for 
 the $i^{th}$ bin $B_i := [b_{i-1}, b_i)$ and $K$ is the number of bins.
 The fitted parameter vector $\hat{\theta}$ is the solution to 
-
-\begin{equation}
-\arg\min_{\theta}\sum_{i=1}^K (p_i - 
+\eqref{eq:discfit}.
+If a distribution was fit to the submitted binned 
+prediction
+and the MSD was less than a 
+specified cutoff value, we
+concluded that the bin forecast may have been discretized from the 
+distribution.
+
+\begin{equation}
+  MSD = \sum_{i=1}^K (p_i - [F(b_i| \hat{\theta}) - F(b_{i-1}| \hat{\theta})])^2
+  \label{eq:msd}
+\end{equation}
+
+\begin{equation}
+\hat{\theta} = \arg\min_{\theta}\sum_{i=1}^K (p_i - 
 [F(b_i; \theta) - F(b_{i-1}; \theta)])^2
@@
 
-If a well known continuous distribution was fit to the submitted binned 
-prediction
-and the mean sum of squared differences (MSD) or \ref{eq:msd} fell below a 
-specified cutoff value, we
-considered that the binned predictions were plausibly discretized from the 
-continuous distribution.
-
 To determine what values to use as cutoffs we conducted a study where 
-binned distributions were discretized from known continuous distributions, 
-parameters were fit to the binned distrubtions and the MSD was calculated.
-
-For each of uniform, truncated normal (TN), truncated lognormal (TL) and 
-truncated gamma (TG) distributions the following was
-done 1,000 times. A set of 131 bins with interval lengths of 
-0.1 between 0 and 13.1 was constructed. 
-A value $\mu$ was selected from a $Uniform(a,b)$ distribution and $\sigma$ from 
-a $Uniform(.05,1.6)$ distribution. $\mu$ and $\sigma$ were taken as respectively 
+bin distributions were discretized from known distributions, 
+parameters were fit to the binned distrubtions and the MSD was calculated. This 
+was done 1,000 times for the four distrubtion families considered and the cutoff 
+value for each family was set as the value under which 95\% of MSD values fell.
+The exact process is as follows.
+
+For each of uniform, TN, TL, and 
+TG distributions the following was
+done 1,000 times. A set of 131 bins with interval widths of 
+0.1 between 0 and 13 was constructed. 
+A value $u$ was selected from a $\mbox{Unif(0,13)}$ distribution and $y$ from 
+a $\mbox{Unif(.05,1.6)}$ distribution. 
+$u$ and $y$ were taken as respectively 
 the center and scale parameters of a TN distribution. 
-For uniform, TL and TG family
-distributions, model parameters were solved for so that $\mu$ and $\sigma$ 
-were roughly the mean and standard deviation. The minimization was done using 
+For uniform, TL, and TG family
+distributions, model parameters were solved for so that $u$ and $y$ 
+were roughly the mean and standard deviation.
+% Had we accounted for the changes
+% in moment values from the truncation, the means and standard deviations could 
+% have been exactly $\mu$ and $\sigma$. But we considered the differences small 
+% enough that it didn't matter for our purpose.
+With a known distribution with $\theta = (u,y)$, 
+probabilities $p_i =F(b_i| \theta) - F(b_{i-1})$ 
+where, were
+calculated for each bin. A distribution from the same
+family was fit to the bins by minimizing \eqref{eq:msd} with the resulting
+distribution function $F(\cdot| \hat{\theta})$. 
+The minimization was done using 
 the \texttt{optim} function in the \texttt{R} \texttt{stats} package.
-Had we accounted for the changes
-in moment values from the truncation, the means and standard deviations could 
-have been exactly $\mu$ and $\sigma$. But we considered the differences small 
-enough that it didn't matter for our purpose.
-
-With a known distribution, probabilities $p_i =F(b_i; \theta) - F(b_{i-1})$ were
-calculated for each bin. A uniform or truncated distribution from the same
-family was fit to the bins by minimizing \ref{eq:msd} with the resulting
-distribution function $F(\cdot; \hat{\theta})$. From the fitted distribution
+From the fit distribution
 $\hat{p_i} = F(b_i; \hat{\theta}) - F(b_{i-1}; \hat{\theta})$ was computed for 
-each of the 131 bins. Finally the mean sum of squared probability differences
-$\frac{1}{K}\sum_{i=1}^K (\hat{p_i} - p_i)^2$ was calculated. 
+each of the 131 bins. Finally the MSD was calculated. 
 Table \ref{table:bincutoffs}
@@
 were selected as the 
-cutoff values for declaring whether or not a binned distribution was discretized
-from a common continuous distribution.
+cutoff values for declaring whether or not a bin distribution was discretized
+from from a one component mixture distribution of that family.
 
@@
   \end{tabular}
-  \caption[Discretized bin distribution cutoff values]{If a binned 
-  distribution is fit to a parametric distribution and the MSD is smaller than
-  the corresponding cutoff value listed here, we consider that binned 
-  distribution to have been discretized from the fit parametric distribution.}
+  \begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
+  \caption[Bin distribution cutoff values]{If a binned 
+  one component mixture distribution is fit to a bin forecast
+  and the MSD is smaller than
+  the corresponding cutoff value listed here, we consider that bin 
+  distribution to have been discretized from the fit mixture distribution.}
   \label{table:bincutoffs}
+  \end{minipage}
+  \end{center}
 \end{table}
@@
 Of the 869,638 predictions from the CDC Retrospective Forecast project, we fit
-each of Uniform, TN, TL and TG distributions to 11,715 of the individual 
-predictions. The MSD between the prediction probabilities and the fit
-discretized probabilities was calcuated. For each prediction, the fitted 
-distribution with the lowest MSD was considered the best fit and if the MSD fell
+each of uniform, TN, TL, and TG distributions to 11,715 of the individual 
+predictions. From each of the 27 teams represented, we randomly selected 1,944
+forecasts to fit. In many cases the \texttt{optim} function used to fit the 
+distributions failed to converge, so of all forecasts we were only able to 
+successfully fit distributions to 11,715 of them.
+We calculated the MSD, and for each forecast the fit
+distribution with the lowest of the four MSDs was considered the best fit. If 
+the MSD from the best fit fell
 below the corresponding cutoff value listed in \ref{table:bincutoffs} we 
-considered that 
-the prediction was discretized from the fit distribution.
-
-Of the 11,715 binned distributions fit to continuous parametric distributions,
-2,502 of those fits producted MSD values below the values listed in table
+concluded that 
+the forecast was discretized from the fit distribution.
+
+Table \ref{table:bincutoffs} shows the results of this analysis. 
+Of the 11,715 binned distributions fit to the mixture distributions,
+2,502 of those fits had MSD values below the values listed in Table
 \ref{table:bincutoffs}. Thus we conclude that a proportion of 0.214 of those
@@
 example of
-the best fit distributions to the same binned probability distribution.
+the fit distributions to the same bin forecast.
 
@@
   \end{tabular}
-  \caption[CDC influenza retro analysis results]{Results for CDC influenza
-  forecast retro analysis}
+  \begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
+  \caption[CDC flu retro analysis results]{Of the 11,715
+forecasts 864 were best fit by a uniform distribution, 3,804 by a TN, 
+4,501 by a TL, and 2,514 by a TG. Of those forecasts, 669 appear to have
+come from a uniform distribution, 198 from a TN, 1,340 from a TL, and 295 from
+a TG.
+}
   \label{table:cdcresults}
+  \end{minipage}
+  \end{center}
 \end{table}
@@
 normal cutoff value, so we conclude that the binned distribution may have been
-discretized froma truncated normal.}
+discretized froma truncated normal. Proportions of distributions with MSDs 
+below the cutoff values are also included.}
 \label{fig:binparamfits}
@@
 
-As of January 24, 2022 there were nearly 85,000,000 prediction distributions 
-from 114 different models submitted to the COVID-19 Forecast Hub (cite??). These 
-distributions covered all combinations of 3,202 municipalities (mostly counties) 
+As of April 1, 2022 there were 89.8 million forecasts  
+from 117 different modeling teams submitted to the COVID-19 Forecast Hub (cite??). 
+These 
+forecasts covered all combinations of 3,202 municipalities (mostly counties) 
 in the United States with 441 targets. The first of these forecasts was 
-submitted in March of 2020 shortly after the initial outbreak of the virus in 
-the US and forecasts had been received weekly since. The forecast representation
-for these predictions is the quantile representation where a point estimated is
-submitted along with a number of confidence intervals -three or 11 for most
-targets. So the predictions typically include seven or 23 quantiles.
-
-To assess whether or not a quantile based forecast was calculated from a well
-known continuous distribution, we minimized the mean square error (MSE) between 
-the CDF and the given quantiles. The estimated parameters are the 
-solution to $argmin_{\theta} \sum_{i=1}^m (q_i - F(y; \theta))$ where $q_i$ is
-the $i^{th}$ given quantile value and $F(y; \theta)$ is the CDF with parameter
-$\theta$. This least squares estimating is a more common way to fit a model but
-other methods have been presented including Bayesian Quantile Matching
-\cite{nirwan2020bayesian}, step interpolation with exponential tails 
-\cite{quinonero2005evaluating}
-and the Method of Simulated Quantiles 
-\cite{dominicy2013method}.
-
-For each prediction used, we fit the quantiles to a uniform, normal, lognormal,
-gamma and location-scale t CDF. We included the t distribution in case of any
+submitted in March of 2020 shortly after the initial outbreak of the COVID-19 
+virus in 
+the US and forecasts have been received weekly since. 
+The forecasts are all quantile forecasts made up of three or 11 predictive 
+intervals -depending on the specific time frame for the forecast-
+and a median. In the forecasts include seven or 23 quantiles.
+
+To assess whether or not a quantile forecast was calculated from a well
+known continuous distribution, we minimized the mean square error (MSE)  
+in \eqref{eq:mse} between where $q_i$ is
+the $i^{th}$ quantile value from a forecast and $F(y| \theta)$ is a fit CDF with 
+parameter $\hat{\theta}$. The parameter $\hat{\theta}$ is the solution to 
+\eqref{eq:minithet}.
+a fit CDF and the given quantiles.
+
+\begin{equation}
+  MSE = \sum_{i=1}^m (q_i - F(y| \hat{\theta}))
+  \label{eq:mse}
+\end{equation}
+
+\begin{equation}
+  \hat{\theta} = \arg\min_{\theta} \sum_{i=1}^m (q_i - F(y| \theta))
+  \label{eq:minthet}
+\end{equation}
+
+For each forecast assessed, we fit the quantiles to a uniform, normal, 
+lognormal,
+gamma, and location-scale t CDF. Unlike in the previous section, we felt no need
+to the distributions as truncated because there is no range limit to these 
+forecasts. We included the t distribution to account for any
 symmetric forecasts with heavier tails than in a normal distribution.
-
 If the MSE between a given forecast and a fit CDF fell below a certain cutoff,
@@
 quantiles with probabilities 1/3 and 2/3 respectively. This was done because 
-in the COVID-19 Forecast Hub certain targets require seven quantiles and others 
-require 23. After that decision was made, a random value $\mu$ was drawn from
-a $Uniform(2,000,\; 25,000)$ distribution and another value $\sigma$ was drawn
+in the COVID-19 Forecast Hub certain target/time frame combinations require 
+seven quantiles and others 
+require 23. After that decision was made, a random value $u$ was drawn from
+a $\mbox{Unif(2,000,\; 25,000)}$ distribution and another value $v$ was drawn
 from a $Uniform(3, 200)$ distribution. These values were taken as the mean and
-standard deviation and for each of the distribution families considered, the
+standard deviation and for each of the distribution families considered. The
 proper transformations computed to find model parameters corresponding to the 
-distribution. Quantile values were calculated for each quantile. When using a 
-t distribution, a value for degrees of freedom was drawn from a 
-$Uniform(2,35)$ distribution. A CDF
-was fit by minimizing $\sum_{i=1}^m (q_i - F(y; \theta))$ over the parameter
-vector $\theta$ and the MSE value $\sum_{i=1}^m (q_i - F(y; \hat{\theta}))$ was 
+distribution. Quantile values were calculated for then each quantile. When using 
+a t distribution, a value for degrees of freedom was drawn from a 
+$\mbox{Unif(2,35)}$ distribution. A CDF
+was fit by minimizing \eqref{eq:minthet} over the parameter
+vector $\theta$ and the MSE value from \eqref{eq:mse} was 
 calculated. The MSE value for which 95\% of the 1,000 simulated distributions
-fell below was considered the cutoff and is seen in table 
-\ref{table:quantcutoffs}.
+fell below was considered the cutoff for that family and is seen in table 
+\ref{table:quantcutoffs}. It is immediately noticeable that the cutoff value 
+for the location-scale t family is several orders of magnitude higher than for 
+the other distribution families. We believe this is related to the fact that 
+that is a three parameter family where as the other four families are two 
+parameter families. Thus influencing the optimization methods used enough to 
+make such a difference in the cutoff value.
 
@@
   \end{tabular}
+  \begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
   \caption[Quantile cutoff values]{If a set of quantiles
@@
   \label{table:quantcutoffs}
+  \end{minipage}
+  \end{center}
 \end{table}
@@
   \end{tabular}
+  \begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
   \caption[COVID-19 Forecast Hub results]{Results for COVID-19 Forecast Hub
@@
   \label{table:cresults}
+  \end{minipage}
+  \end{center}
 \end{table}

### 2022-04-02 manuscript/thesis.tex
revisions to sections 3 and 4

@@
   \begin{tabular}{l*{6}{c}r}
-  Distribution          & MSD 95\%  \\
+  Distribution          & MSD 95\% Cutoff \\
   \hline
@@
 each of uniform, TN, TL, and TG distributions to 11,715 of the individual 
-predictions. From each of the 27 teams represented, we randomly selected 1,944
-forecasts to fit. In many cases the \texttt{optim} function used to fit the 
+predictions. From each of the 27 teams represented, there is a list of forecast
+submissions from which we randomly selected 12. From each submission, we 
+we randomly selected six forecasts.
+In many cases the \texttt{optim} function used to fit the 
 distributions failed to converge, so of all forecasts we were only able to 
@@
 \caption[Parametric distribution fits to binned distribution]{This figure shows
-the plots of fits from each a uniform, truncated normal, truncated lognormal
-and truncated gamma distributions to the same binned probability distribution.
+the plots of fits from each a uniform, TN, TL,
+and TG distributions to the same bin distribution. The title of this forecast
+given by the submission team is Bayesian Model Averaging. This forecast was
+submitted to the CDC on May 15, 2017 and is a three week ahead forecast of
+percent of hospital patients due to an influenza like illness for a specific
+region of the United States.
 In this case, the fit to the normal distribution produced an MSD below the 
-normal cutoff value, so we conclude that the binned distribution may have been
-discretized froma truncated normal. Proportions of distributions with MSDs 
+TN cutoff value, so we conclude that the bin forecast may have been
+discretized from a TN. Proportions of distributions with MSDs 
 below the cutoff values are also included.}
@@
 The forecasts are all quantile forecasts made up of three or 11 predictive 
-intervals -depending on the specific time frame for the forecast-
+intervals -depending on the specific unit for the forecast-
 and a median. In the forecasts include seven or 23 quantiles.
@@
 quantiles with probabilities 1/3 and 2/3 respectively. This was done because 
-in the COVID-19 Forecast Hub certain target/time frame combinations require 
+in the COVID-19 Forecast Hub certain target/unit combinations require 
 seven quantiles and others 
@@
 a $\mbox{Unif(2,000,\; 25,000)}$ distribution and another value $v$ was drawn
-from a $Uniform(3, 200)$ distribution. These values were taken as the mean and
+from a $\mbox{Unif(3, 200)}$ distribution. These values were taken as the mean 
+and
 standard deviation and for each of the distribution families considered. The
@@
   \begin{tabular}{l*{6}{c}r}
-  Distribution          & Mean Square Error 95\%  \\
+  Distribution          & MSE 95\% Cutoff \\
   \hline
@@
 \captionsetup{font=scriptsize}
-  \caption[Quantile cutoff values]{If a set of quantiles
-  is fit to a parametric distribution CDF and the MSE is smaller than
-  the corresponding cutoff value listed here, we consider the quantiles to 
-  have been calculated parametric distribution.}
+  \caption[Quantile cutoff values]{If a one component mixture distribution of a
+  certain distribution family
+  is fit to a quantile forecast and the MSE is smaller than
+  the corresponding cutoff value listed here, we conclude the quantiles to 
+  have been calculated from the fit distribution.}
   \label{table:quantcutoffs}
@@
 
-With these cutoff values selected, models were then fit to quantile forecasts
-from the COVID-19 Forecasts on zoltardata.com. This was a computationally more
-difficult problem than fitting distributions to the binned forecasts of the 
-influenza project, so the number of predictions fit is much smaller. The 
-predictions fit were selected from each of the 115 models with model weeks, 
-targets and units selected randomly. In total 2,504 predictions were fit to each
-of the five distributions, the MSE was calculated for each and the fit with the
+With these cutoff values selected, distributions were then fit to quantile 
+forecasts
+from the COVID-19 Forecasts on zoltardata.com.?? 
+From 115 modeling teams we randomly selected four forecast submissions. From 
+those submissions we randomly selected three units and attempted to assess
+forecasts for all targets under than unit.
+This was a computationally more
+difficult problem than fitting distributions to the bin forecasts from the CDC
+flu competition, so the number of forecasts where convergence for fitting was
+met was much smaller. In total distributions from all five families of interest
+were fit to 2,504 forecasts. 
+The MSE was calculated for each and the fit with the
 lowest MSE was selected as the closest fit. If the MSE fell below the cutoff
-specified above, we considered that the quantile prediction was approximately
-from the same distribution as the fit distribution. Of the 2,504 fits, 99 of 
-them produced an MSE value below the corresponding cutoff. Results for fits by
-distribution are seen in table \ref{table:cresults}.
+specified above, we concluded that the quantile forecast was approximately
+from the same distribution as the fit distribution.
+
+Table \ref{table:cresults} show the results of the analysis by distribution
+family.
+Of the 2,504 fits, 99 of 
+them had an MSE value below the corresponding cutoff listed in Table
+\ref{table:quantcutoffs}. Thus we conclude that a proportion of 0.04 of the 
+forecasts assessed came from distributions fit to them.
+Results for fits by
+distribution are seen in Table \ref{table:cresults}.
 Figures \ref{fig:qqfits} and \ref{fig:cdffits} show the QQ plots and CDF plots
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[scale=.15]{Images/qq_11_12_5.png}}
+\centerline{\includegraphics[scale=.15]{Images/qq_gleam_110121_1wkincdeath_st16.png}}
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \caption[QQ plot for quantile fit]{This figure shows qq plots for a set of
 submitted quantiles against the quantiles the continuous distribution to which
-it was fit. In no case here was the MSE below the cutoff value of the 
+it was fit. 
+The name of this forecast given by the team who submitted it is Gleam COVID-19.
+This forecast was submitted to the C0VID-19 Forecast Hub on November 1, 2021
+and is forecasting deaths one in the next week in a certain US state due to the
+virus.
+In no case here was the MSE below the cutoff value of the 
 corresponding distribution.}
 \label{fig:qqfits}
+\end{minipage}
+\end{center}
 \end{figure}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[scale=.15]{Images/cdf_11_12_5.png}}
+\centerline{\includegraphics[scale=.15]{Images/cdf_gleam_110121_1wkincdeath_st16.png}}
+% i=11,j=12,k=5
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \caption[CDF plot for quantile fit]{This figure shows the CDF plots for 
 distributions fit to a set of quantiles. The grey line is a line of connected 
-dots from the submitted quantiles and values. 
+dots from the submitted quantiles and values and is the same in all four plots.
+This is the same set of forecasts as is \ref{fig:qqfits}.
 In no case here was the MSE below the cutoff value of the 
@@
 \label{fig:cdffits}
+\end{minipage}
+\end{center}
 \end{figure}
 
-The results in the previous two studies suggest that in some cases, forecasters
-are using methods which produce simple parametric distribution forecasts. Many
-likely are not. To improve upon these studies, one could fit the binned 
-influenza forecasts or the COVID-19 quantile forecasts to discrete mixture 
+The results from these two studies suggest that in some cases, forecasters
+are using methods which produce may produce one component mixture distribution
+forecasts. Many
+likely are not. To expand upon these studies, one could attempt to fit the 
+bin forecasts or the quantile forecasts to mixture 
 distributions with multiple components. Forecasts that are very close to 
@@
 probabilistic 
-forecasting including proper scoring, data storage and ensemble model 
-construction for each type. We presented the discrete mixture distribution
+forecasting including proper scoring, data storage, and ensemble model 
+construction for each type. We presented the mixture distribution
 representation and we argue that its use in collaborative probabilistic 
 forecasting is preferable to the other representations.
-In terms of model flexibility, storage and 
+In terms of model flexibility, storage, and 
 ensemble building it is
-comparable to discretized bins and interval forecasts but also provides a 
-forecast with a infinite nominal resolution. Thus we advocate its use in
-future forecasting projects like those done by the CDC and COVID-19 Forecast 
-Hub.
+comparable to discretized bins and quantile forecasts but also provides a 
+forecast with a infinite nominal resolution. Based on a retrospective analysis,
+we argue that among the teams participating in the CDC flu
+competition and the COVID-19 Forecast Hub, there are already some which produce
+forecasts already resembling single component mixture distributions making the 
+transition from past and current formats to a mixture distribution format 
+straightforward.
+We thus advocate for the use of mixture distributions in
+future forecasting projects like those done in the CDC flu competition or in the
+COVID-19 Forecast Hub.
 
 For a number of reasons, the adoption of finite mixture distributions as the
-submission format may face hurdles. A collaborative forecast center, along with 
+submission format may be avoided. A collaborative forecast center, along with 
 forecasters, using a 
@@
 implementation of new scoring and ensemble construction methods may be a 
-barrier. One aspect of ensemble construction which received little attention in 
+barrier. Development of tools beyond what was used in Section 
+\ref{section:tools} would assist in making a transition to using mixture 
+distributions more straightforward.
+One aspect of ensemble construction which received little attention in 
 this paper is the selection of weights for components of an ensemble where each
@@
 
-Another area of recommended research is the use of joint distributions for 
+Another area of recommended research is the use of joint mixture distributions 
+for 
 forecasting. We have only considered here probabilistic forecasting of one 
@@
 for example. This forecast is presented as a marginal distribution for that 
-specific target, time and location. A joint distribution for forecasting 
+specific target, time, and location. A joint distribution for forecasting 
 multiple targets, times or locations may sometime be desirable and may require

### 2022-04-05 manuscript/Preface/abstract.tex
final draft maybe

@@
 Collaboration among multiple teams has played a major role in probabilistic
-forecasting of influenza outbreaks, the COVID-19 pandemic, other disease
-outbreaks and problems in many other fields. When collecting forecasts from 
+forecasting events of influenza outbreaks, the COVID-19 pandemic, other disease
+outbreaks, and in many other fields. When collecting forecasts from 
 individual teams, ensuring that each team's model represents forecast
@@
 forecasts as well as methods of constructing multi-model ensemble forecasts.
-This paper outlines several common probabilistic forecast formats including
-probability densities, samples, binned distributions and  quantile 
+This paper outlines several common probabilistic forecast representation formats 
+including
+probability densities, samples, binned distributions, and  quantile 
 forecasts and compares
-their usage within the context of collaborative projects. We propose the use of
+their use in the context of collaborative projects. We propose the use of
 a discrete mixture distribution format in collaborative forecasting in place of
 other formats. The flexibility in distribution shape, the ease for scoring and 
-building ensemble models and the reasonably low level of computer storage 
+building ensemble models, and the reasonably low level of computer storage 
 required to save such a format make the discrete mixture distribution an 
-attractive alternative to the other mentioned formats.
+attractive alternative to the other representation formats.

### 2022-04-05 manuscript/thesis.tex
final draft maybe

@@
 account for uncertainty in predicted quantities or events 
-\cite{gneiting2014probabilistic}. Specific problems for 
+\cite[]{gneiting2014probabilistic}. Specific problems for 
 which probabilistic forecasting is used include weather forecasting
-\cite{baran2018combining}, economics \cite{groen2013real}, and disease outbreaks
-\cite{yamana2016superensemble}.
+\cite[]{baran2018combining}, economics \cite[]{groen2013real}, and disease outbreaks
+\cite[]{yamana2016superensemble}.
 
@@
 or
-discrete parametric distribution, given as a probability density/mass function 
-(pdf/pmf). Much of the literature 
+discrete parametric distribution, given as a probability density/mass function. 
+Much of the literature 
 on calibration, sharpness, and scoring of a forecast pertains to parametric 
 distribution forecasts
-\cite{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
-Other common representations include samples \cite{krueger2016probabilistic}, 
-discretized bin distributions \cite{mcgowan2019collaborative},
-and quantile forecasts \cite{taylor2021evaluating, bracher2021evaluating}. 
+\cite[]{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
+Other common representations include samples \cite[]{krueger2016probabilistic}, 
+discretized bin distributions \cite[]{mcgowan2019collaborative},
+and quantile forecasts \cite[]{taylor2021evaluating, bracher2021evaluating}. 
 Each representation may be more or less 
@@
 are used include the United States Centers for Disease Control (CDC)
-annual competition for forecasting the influenza outbreak \cite{cdcflusight}
+annual competition for forecasting the influenza outbreak \cite[]{cdcflusight}
 and the COVID-19 Forecast Hub which has 
 continuously operated since the start of the COVID-19 pandemic in the US in 
-early 2020 \cite{Cramer2021-hub-dataset}.
+early 2020 \cite[]{Cramer2021-hub-dataset}.
 
@@
 format. A \emph{bin distribution} is a probability distribution represented by
-breaking the numeric range of an event into intervals or \emph{bins} and
+breaking the numeric range of an outcome into intervals or \emph{bins} and
 directly assigning the probability that the event falls within each bin.
@@
 prediction of a specific target was a set of probabilities assigned to each bin
-\cite{mcgowan2019collaborative}.
+\cite[]{mcgowan2019collaborative}.
 These forecasts were then evaluated against actual flu activity, and at 
-the end of the season a winning team was declared \cite{cdcflusight}.
+the end of the season a winning team was declared \cite[]{cdcflusight}.
 
@@
 forecasts into a \emph{multi-model ensemble forecast} 
-\cite{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy},
+\cite[]{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy},
 refered to hereafter as an ensemble forecast.
@@
 models into one model which often yields better predicting power than the 
-individual models \cite{cramer2021evaluation}. Such an ensemble made from 
+individual models \cite[]{cramer2021evaluation}. Such an ensemble made from 
 multiple influenza competition forecasts did in fact outperform the individual 
-component models \cite{reich2019accuracy}.
-In the COVID-19 Forecast Hub, construction of ensemble forecasts to improve
-predicting power has been a priority.
+component models \cite[]{reich2019accuracy}.
 
@@
 official
-communication \cite{Cramer2021-hub-dataset}. See Figure \ref{fig:cdcoff}.
+communication \cite[]{Cramer2021-hub-dataset}. Figure \ref{fig:cdcoff} is an 
+official CDC report from August 2021 showing forecasts from the COVID-19 
+Forecast Hub of increment deaths and cumulative deaths due to COVID-19.
 
@@
 predictive intervals for various nominal levels depending on the target to be
-predicted \cite{bracher2021evaluating}. Each value in a predictive interval
+predicted \cite[]{bracher2021evaluating}. Each value in a predictive interval
 is a value for a quantile at a specified nominal level. This makes a set of 
-predicitve intervals a \emph{quantile forecast} or a forecast made up of a set
+predictve intervals a \emph{quantile forecast} or a forecast made up of a set
 of quantiles and corresponding values.
@@
 ensemble forecast, and store the forecasts among other differences.
+Ray et. al show that ensemble forecasts in the COVID-19 Forecast Hub provide
+precise short-term forecasts which decline in accuracy in longer term forecasts
+approaching four weeks \cite[]{ray2020ensemble}.
 
 \begin{figure}[htbp]
+\centerline{\includegraphics[scale=.24]{Images/8_30_21_cvd_deaths.jpeg}}
 \begin{center}
@@
 \captionsetup{font=scriptsize}
-\centerline{\includegraphics[scale=.12]{Images/8_30_21_cvd_deaths.jpeg}}
 \caption[Official CDC COVID-19 deaths report August 2021]{This image, 
@@
 column show prediction intervals from multiple teams whereas the plots on the 
-right show the intervals for an ensemble forecast model.}
+right show the intervals for an ensemble forecast model with gray lines
+predicting individual model point forecasts.}
 \label{fig:cdcoff}
@@
 representation types come 
-with their drawbacks. Data 
-storage for instance might be a concern if many bins are used for forecasting. 
-And scoring methods are limited if forecasts are quantile forecasts.
-
-In this paper, we propose the use of discrete mixture distributions as a means 
+with their drawbacks. Computer
+storage for instance might be a concern if many bin distributions are used for 
+forecasting, 
+and scoring methods are limited if forecasts are quantile forecasts.
+
+In this paper, we propose the use of finite mixture distributions as a means 
 of forecasting for collaborative projects similar to the CDC flu competition or 
 the COVID-19
-Forecast Hub. In Section \ref{section:representations}, 
+Forecast Hub. A finite mixture distribution -which we will refer to as a
+\emph{mixture distribution}- is distribution constructed by combining a finite 
+collection of other distributions. In this paper, we focus on the case where the
+collection of distributions are parametric distributions.
+
+In Section \ref{section:representations}, 
 popular probabilistic forecast representation 
@@
 representation type.
-In Section \ref{section:conmixforc}, details for using discrete mixture 
+In Section \ref{section:conmixforc}, details for using mixture 
 distributions in a collaborative forecast project are presented as well as tools
@@
 competition and COVID-19 Forecast Hub
-forecast and an attempt to assess whether any forecast models
-may be approximated by known continuous distributions. We conclude this 
-paper with a discussion.
+forecasts and an attempt to assess whether forecast models
+may be approximated by one component mixture distributions.
 
@@
 \subsection{Scoring}
-Scoring rules are used to numerically evaluate or score a probability forecast. 
+Scoring rules are used to numerically evaluate or \emph{score} a probability 
+forecast. 
 The
@@
 exist the score for each may be used to compare forecasts. If a scoring rule 
-is proper, then the best possible score is obtained by reporting the true 
+is \emph{proper}, then the best possible score is obtained by reporting the true 
 distribution. The rule is strictly proper if that value is unique. 
@@
 scoring rules, a forecaster has no incentive to be dishonest in their 
-submission \cite{gneiting2007strictly}. This makes proper scoring rules ideal
+submission \cite[]{gneiting2007strictly}. This makes proper scoring rules ideal
 for evaluating forecasts. We will limit our review of scoring methods to rules
@@
 COVID-19 Forecast Hub contained 85 million forecasts as of 
-February 5, 2022 which required more than 11.6 gigabytes of storage!
-(cite zoltar??)
+April 4, 2022 which required more than 11.7 gigabytes of storage!
+\cite[]{covidgithub}.
 When determining the goals of a forecast project, there should be consideration 
@@
 modeling. Ensembles have been used extensively in weather and
-climate modeling \cite{baran2018combining}, 
+climate modeling \cite[]{baran2018combining}, 
 and they have been used increasingly in modeling infectious disease outbreaks
-\cite{yamana2016superensemble}. 
+\cite[]{yamana2016superensemble}. 
 Ensembles allow for an incorporation of multiple signals -
@@
 \cite[see
-references therein]{cramer2021evaluation}.
+references therein]{ray2020ensemble, cramer2021evaluation}.
 
@@
 models using weighted averages. This has been called stacking 
-\cite{wolpert1992stacked} or weighted density ensembles 
-\cite{ray2018prediction}.
+\cite[]{wolpert1992stacked} or weighted density ensembles 
+\cite[]{ray2018prediction}.
 
@@
 described by a known function $p(x) := p(x|\theta)$. The function $p(x)$ is 
-called a pmf if the distribution is discrete and is called a
-pdf if the distribution is continuous. Here $\theta$ is a vector of known or 
+called a probability mass function (pmf) if the distribution is discrete and 
+is called a probability density function
+(pdf) if the distribution is continuous. Here $\theta$ is a vector of known or 
 unkown parameters contained in the parameter space of the distribution.
@@
 \begin{equation}
+\label{eq:dcdf}
+  F(x) = P(X \leq b) = \sum_{x \in X} p(x)
+\end{equation}
+
+\begin{equation}
 \label{eq:ccdf}
   F(x) = P(X \leq b) = \int_{-\infty}^x p(t) dt
-\end{equation}
-
-\begin{equation}
-\label{eq:dcdf}
-  F(x) = P(X \leq b) = \sum_{k=1}^n p(x_k) dt
 \end{equation}
@@
 include the logarithmic score (LogS), the
-continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
-\cite{alves2013ncep}, and the interval/Brier 
-score (IS) \cite{gneiting2007strictly} among 
-others. See also \cite{gneiting2014probabilistic}
+continuous rank probability score (CRPS) \cite[]{hersbach2000decomposition}
+\cite[]{alves2013ncep}, and the interval/Brier 
+score (IS) \cite[]{gneiting2007strictly} among 
+others. See also \cite[]{gneiting2014probabilistic}
 Section 3 for more on proper scoring functions. The definitions 
@@
 used
-to build ensembles under Bayesian model averaging (BMA). Considered the 
+to build ensembles under model averaging (MA). Considered the 
 state-of-the-art techniques for combining 
@@
 ensemble model output statistics (EMOS), and ensemble
-BMA, both of which are defined in \cite{gneiting2014probabilistic}.
+MA, both of which are defined in \cite[]{gneiting2014probabilistic}.
 
@@
 sources,
-BMA may be preferable because it does not require that modeling methods for 
+MA may be preferable because it does not require that modeling methods for 
 individual components be the same. 
-In BMA, the final model does not have to be specified
-beforehand and the resulting forecast will be a discrete mixture distribution
+In MA, the final model does not have to be specified
+beforehand and the resulting forecast will be a mixture distribution
 of all component forecasts. The general form for an ensemble distribution $p^E$
@@
 $0 \leq w_m \leq 1$ is a weight assigned to that component where $\sum w_m = 1$.
-Methods for estimating weights include Maximum Likelihood estimation
-\cite{raftery2005using}, MCMC 
-sampling \cite{vrugt2008ensemble},
+Methods for estimating weights include maximum likelihood estimation
+\cite[]{raftery2005using}, MCMC 
+sampling \cite[]{vrugt2008ensemble},
 and minimizing the CRPS of the ensemble
-\cite{baran2018combining}.
+\cite[]{baran2018combining}.
 
@@
 truncated normal distribution (TN) and a truncated lognormal (TL) the CRPS is 
-not available in closed form \cite{baran2018combining}.
+not available in closed form \cite[]{baran2018combining}.
 
@@
 sampling have greatly contributed to growth in the use of
-sample distributions for forecasting \cite{gneiting2007strictly}
+sample distributions for forecasting \cite[]{gneiting2007strictly}
 \cite[see examples listed therein]{krueger2016probabilistic}.
@@
 
-To build an ensemble model from sample distribution forecasts, the BMA 
+To build an ensemble model from sample distribution forecasts, the MA 
 construction from (\ref{eq:bma}) may be used only replacing $p_m$ with the
@@
 A bin distribution may be constructed over a set 
-$A = [a, b]$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
+$A = [a, b)$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
 where $B_i = [b_{i-1}, b_i)$ and $\cup_{i=1}^{K} B_i = A$. Based on the problem
@@
 $\Delta = b_i - b_{i-1}$ is the same width for all $i$ 
-\cite{mcgowan2019collaborative}.
+\cite[]{mcgowan2019collaborative}.
 To complete the construction, a probability $p_i$ is assigned to each $B_i$ 
@@
 forecast distribution. There are a number of possible ways to do this including
-those outlined by Chakraborty and Subrata \cite{chakraborty2015generating}.
+those outlined by Chakraborty and Subrata \cite[]{chakraborty2015generating}.
 
@@
 In that context it has become the standard representation 
-\cite{brooks2020comparing}. Much work has been done in evaluating 
+\cite[]{brooks2020comparing}. Much work has been done in evaluating 
 and constructing ensemble models on influenza forecasts represented by 
-discretized bins \cite{mcgowan2019collaborative, mcandrew2019adaptively,reich2019collaborative}.
+discretized bins 
+\cite[]{mcgowan2019collaborative, mcandrew2019adaptively,reich2019collaborative}.
 
@@
 already 
-discussed -LogS and CRPS- are useable and BMA is valid method for ensemble 
-construction. Reich et. al used BMA to combine multiple forecasts from the flu 
+discussed -LogS and CRPS- are useable and MA is valid method for ensemble 
+construction. Reich et. al used MA to combine multiple forecasts from the flu 
 competition. They built and compared ensemble models with different weighting
@@
 according to the model specification. To estimate weights they used the 
-Expectation Maximization (EM) algorithm 
+expectation maximization (EM) algorithm 
 \cite[see
@@
 to Methodology-IV from Chakraborty 
-\cite{chakraborty2015generating,kemp2004classes}.
+\cite[]{chakraborty2015generating,kemp2004classes}.
 
@@
 to forego trying to create the right binning scheme and use quantile forecasts
-to forecast the COVID-19 pandemic \cite{bracher2021evaluating}.
+to forecast the COVID-19 pandemic \cite[]{bracher2021evaluating}.
 The COVID-19 Forecast Hub requires predictions to be submitted as 11 or three 
@@
 
-Quantile FORECASTS allows for forecasters to submit fairly detailed
+Quantile forecasts allow for forecasters to submit fairly detailed
 forecasts without restricting the range of possible values.
@@
 interval and the distance between $x^*$ and the interval (if $x^*$ is not 
-captured in the interval) \cite{gneiting2014probabilistic}. 
+captured in the interval) \cite[]{gneiting2014probabilistic}. 
 The IS requires only a single central 
@@
 al use the WIS to score COVID-19 quantile forecasts 
-\cite{bracher2021evaluating}.
+\cite[]{bracher2021evaluating}.
 There are multiple versions of the WIS -some of 
-which are described in Bracher et. al- but the version used by the COVID-19 
+which are described in Bracher et. al, but the version used by the COVID-19 
 Forecast
 Hub for a forecast of $K$ intervals is defined in \eqref{eq:wis}.
-Here $w_k = \alpha_k/2$ is the weight on the $k^{th}$
+Here $median$ refers to the predictive median and $w_k = \alpha_k/2$ is the 
+weight on the $k^{th}$
 interval. With that selection of weights, it may be shown that the
@@
 \label{eq:wis}
-  WIS_{0,K}(F_m,y^*) = \frac{1}{K + 1/2} \times (w_0, \times |y^*-med|+
-  \sum_{k=1}^K \{ w_k \times IS_{\alpha_k}(F_m,y) \} )
+  WIS_{0,K}(F_m,x^*) = \frac{1}{K + 1/2} \times (w_0, \times |x^*-median|+
+  \sum_{k=1}^K \{ w_k \times IS_{\alpha_k}(F_m,x^*) \} )
 \end{equation}
@@
 Quantile Score (QS) similar to the interval score and scoring distribution functions
-fit to those quantiles using the CRPS \cite{bogner2017combining}. The CRPS 
+fit to those quantiles using the CRPS \cite[]{bogner2017combining}. The CRPS 
 corresponds to the integral of the QS over all possible thresholds rather than
@@
 specifically, each quantile value of the ensemble was the average of values from
-all models corresponding to the same quantile \cite{ray2020ensemble}. For $M$ 
+all models corresponding to the same quantile \cite[]{ray2020ensemble}. For $M$ 
 models each with $K$ quantiles, the $k^{th}$ ensemble quantile $q^E_k$ is 
@@
 using equally-weighted means, weighted means, and median value constructions
-\cite{brooks2020comparing}.
+\cite[]{brooks2020comparing}.
 In their report, they show that weighted means and median constructions tend
@@
 the ensemble forecast.
-Averaging quantiles in this way is the same as quantile averaging or Vincentization
-only with an incomplete quantile function. It thus carries with it many of the
-same characteristics.
 
@@
 the ensemble distribution
-to be unimodal than it is under linear averaging of densities like BMA 
-\cite{busetti2017quantile}. Under some circumstances, such as when member
+to be unimodal than it is under linear averaging of densities like MA 
+\cite[]{busetti2017quantile}. Under some circumstances, such as when member
 distributions are exponential, Weibull, or logisitic the aggregated distribution
-is of the same family \cite{ratcliff1979group}. Quantile averagin produces 
+is of the same family \cite[]{ratcliff1979group}. Quantile averagin produces 
 smoother
-distributions than BMA according to Schepen and Wang \cite{schepen2015model}.
+distributions than MA according to Schepen and Wang \cite[]{schepen2015model}.
 And Lichtendahl et. al conclude that quantile averaging produces sharper 
 forecasts
-and tends to perform better in scoring than probability averaging, BMA,
-\cite{lichtendahl2013better}.
+and tends to perform better in scoring than probability averaging, MA,
+\cite[]{lichtendahl2013better}.
 
@@
 quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This includes a 
-median along with 11 predictive intervals \cite{bracher2021evaluating}. 
+median along with 11 predictive intervals \cite[]{bracher2021evaluating}. 
 Forecasters are thus required to submit 46 values in each short-term forecast 
@@
 \section{Mixture distributions}
-A discrete mixture of parametric distributions forecast -which we will refer to
-as a mixture distribution forecast- representation is an
+A mixture distribution forecast representation is an
 attractive alternative to the four representations already discussed. 
@@
 existing software like \texttt{distr} package in \texttt{R} 
-\cite{camphausen2007distr}. 
+\cite[]{camphausen2007distr}. 
 And 
@@
 terms of distributional shape. According to 
-McLachlan and Peel, a finite mixture of 
+McLachlan and Peel, a mixture of 
 normal densities with common variance can be used to approximate arbitrarily 
 well
-any continuous distribution \cite{peel2000finite} (see also 
-\cite{nguyen2019approximations}). Thus, for an unconventional probability
+any continuous distribution \cite[]{peel2000finite} (see also 
+\cite[]{nguyen2019approximations}). Thus, for an unconventional probability
 distribution -such as MCMC posterior samples- it may be reasonable to 
@@
 true is when trying to minimize the CRPS but the exact mixture doesn't 
-produce a closed form CRPS \cite{baran2018combining}. In large projects like
+produce a closed form CRPS \cite[]{baran2018combining}. In large projects like
 the COVID-19 Forecast Hub, if an equal weight is not assigned to each component,
@@
 
-Table \ref{table:repscomp} shows how a discrete mixture distribution forecast 
-compares with the other formats discussed in terms of methods for scoring,
+Table \ref{table:repscomp} shows how a mixture distribution forecast 
+compared with the other formats discussed in terms of methods for scoring,
 information and resolution provided, methods for ensemble building, and computer
@@
 scoring rules LogS and CRPS may be used to score it. The storage requirement is
-comparable to that of a bin distribution or a set of quantiles. And BMA may be 
+comparable to that of a bin distribution or a set of quantiles. And MA may be 
 used for building an ensemble.
@@
   \begin{table}
-    \begin{center}
-    \captionsetup{font=scriptsize}
-    \begin{tabular}{ | p{2.4cm} || p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
+   \begin{adjustwidth}{-1cm}{-1cm}
+    \begin{tabular}{ | p{2.9cm} || p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
     \hline
@@
     Infinite resolution
-    & BMA & Low 3-6 values per prediction \\ \hline
+    & MA & Low 3-6 values per prediction \\ \hline
 
@@
     Resolution may be
-    very high but depends on sample size & BMA after smoothing. Resampling 
+    very high but depends on sample size & MA after smoothing. Resampling 
     otherwise & 
@@
     Any shape allowed, but limited by binning scheme. Range also may be limited
-    & BMA &
+    & MA &
     Depends on binning scheme but dozens to hundreds of values
@@
     enough component distributions may
-    approximate any distribution shape. Infinite resolution& BMA 
+    approximate any distribution shape. Infinite resolution& MA 
     & 3 values to dozens per forecast depending on number of components
@@
 	 \end{tabular}
-	 % \end{adjustwidth}
+	 \end{adjustwidth}
+	  \begin{center}
     \begin{minipage}{14cm}
+    \captionsetup{font=scriptsize}
    \caption[Forecast representation comparison]{This table compares scoring,
@@
 scoring rules LogS and CRPS may be used to score it. The storage requirement is
-comparable to that of a bin distribution or a set of quantiles. And BMA may be 
+comparable to that of a bin distribution or a set of quantiles. And MA may be 
 used for building an ensemble.}
@@
 \texttt{R}, then tools based on the \texttt{distr} package 
-\cite{camphausen2007distr} may be used for evaluating a mixture distribution 
+\cite[]{camphausen2007distr} may be used for evaluating a mixture distribution 
 with the components in the table.
@@
 \centerline{\includegraphics[scale=.15]{Images/mix_ense.png}}
-\caption[Toy ensemble forecast]{Ensemble forecast made from forecast 1 and 
+\caption[Example ensemble forecast]{Ensemble forecast made from forecast 1 and 
 forecast 2 from Section \ref{section:tools}. The green line is the density 
@@
 include Bayesian Quantile Matching
-\cite{nirwan2020bayesian}, step interpolation with exponential tails 
-\cite{quinonero2005evaluating},
+\cite[]{nirwan2020bayesian}, step interpolation with exponential tails 
+\cite[]{quinonero2005evaluating},
 and the Method of Simulated Quantiles 
-\cite{dominicy2013method}. These studies however lack claims that the methods
+\cite[]{dominicy2013method}. These studies however lack claims that the methods
 for fitting are statistically formal.
@@
 \section{CDC flu competition}
-The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
+The CDC Retrospective Forecasts project on zoltrdata.com \cite[]{zoltarflu} 
+contains over
 869,638 probabilistic influenza-like illness forecasts for all combinations
@@
 \centerline{\includegraphics[scale=.15]{Images/flu_fit_17_10_3.png}}
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \caption[Parametric distribution fits to binned distribution]{This figure shows
 the plots of fits from each a uniform, TN, TL,
-and TG distributions to the same bin distribution. The title of this forecast
+and TG distributions to the same bin distribution. Each black vertical line is
+a bin probability $p_i \times 10$. The probabilities are multiplied by 10 to 
+better illustrate fitting a distribution to the probabilities.
+The title of this forecast
 given by the submission team is Bayesian Model Averaging. This forecast was
@@
 \label{fig:binparamfits}
+\end{minipage}
+\end{center}
 \end{figure}
@@
 
-As of April 1, 2022 there were 89.8 million forecasts  
-from 117 different modeling teams submitted to the COVID-19 Forecast Hub (cite??). 
+As of April 4, 2022 there were over 90 million forecasts  
+from 117 different modeling teams submitted to the COVID-19 Forecast Hub 
+\cite[]{zoltarcovid}. 
 These 
@@
 parameter $\hat{\theta}$. The parameter $\hat{\theta}$ is the solution to 
-\eqref{eq:minithet}.
-a fit CDF and the given quantiles.
+\eqref{eq:minthet}.
 
@@
 forecasts
-from the COVID-19 Forecasts on zoltardata.com.?? 
+from the COVID-19 Forecasts on zoltardata.com \cite[]{zoltarcovid}.
 From 115 modeling teams we randomly selected four forecast submissions. From 
@@
 a mixture distribution may suggest that the forecasters already have models that
-make transition to a discrete mixture distribution forecast format easy or
+make transition to a mixture distribution forecast format easy or
 straightforward.
@@
 
-For a number of reasons, the adoption of finite mixture distributions as the
+For a number of reasons, the adoption of mixture distributions as the
 submission format may be avoided. A collaborative forecast center, along with 

### 2022-04-05 code/ensemble_toy.R

@@ -1,4 +1,6 @@
 library(scoringutils)
+library(mixtools)
+library(boot)
 
 md1 <- distr::UnivarMixingDistribution(distr::Norm(1.5,1), 
                                        distr::Norm(4,2),

### 2022-04-05 manuscript/thesis.tex
final draft

@@
 Each representation may be more or less 
-appropriate than the others for a given problem but knowing how to interpret, 
-score, and contruct ensemble forecasts for a selected representation is 
+appropriate than the others for a given problem, but knowing how to interpret, 
+score, and construct ensemble forecasts for a selected representation is 
 essential when multiple teams collaborate in the same forecasting project.
@@
 forecasting the timing, peak, and intensity of the year's flu 
-season. The specific events to be forecasted are known as \emph{targets}.
+season. The specific events to be forecast are known as \emph{targets}.
 Forecasts
@@
 construct forecasts using 
-whatever methods they choose. Historically, the forecasts must be 
+whatever methods they choose. Historically, the forecasts have been
 submitted 
-in a discretized bin distribution
+in a discretized bin distribution or a bin distribution
 format. A \emph{bin distribution} is a probability distribution represented by
 breaking the numeric range of an outcome into intervals or \emph{bins} and
-directly assigning the probability that the event falls within each bin.
+directly assigning to each bin the probability that the event falls 
+within the bin.
 During previous flu seasons the \emph{binning scheme} or the assignment of 
@@
 \cite[]{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy},
-refered to hereafter as an ensemble forecast.
+or an ensemble forecast.
 
@@
 official
-communication \cite[]{Cramer2021-hub-dataset}. Figure \ref{fig:cdcoff} is an 
+communication \cite[]{Cramer2021-hub-dataset}. Figure \ref{fig:cdcoff} is from 
+an 
 official CDC report from August 2021 showing forecasts from the COVID-19 
@@
 column show prediction intervals from multiple teams whereas the plots on the 
-right show the intervals for an ensemble forecast model with gray lines
-predicting individual model point forecasts.}
+right show the intervals for an ensemble forecast model with gray lines that are
+individual model point forecast predictions.}
 \label{fig:cdcoff}
@@
 or the COVID-19 Forecast Hub, bin forecasts and quantile forecasts have become
-important representations to those involved in the projects. Yet both 
+important representations. Yet both 
 representation types come 
@@
 distributions in a collaborative forecast project are presented as well as tools
-which may be used for scoring and constructing an ensemble.
+which may be used for scoring and constructing an ensemble forecast.
 Section \ref{section:retrostud} is a retrospective study of the CDC flu 
@@
 \subsection{Ensemble construction}
-A multi-model ensemble is a statistical model made by combining information from
+An ensemble model is a statistical model made by combining information from
 two or more individual statistical models. Private and public decisions are 
-regularly made after combining information from multiple sources. For any given
-situation, information from one source may provide insight on a subject which 
+regularly made after combining information from multiple sources. For a given
+problem, information from one source may provide insight on a subject which 
 other
@@
 \cite[]{yamana2016superensemble}. 
-Ensembles allow for an incorporation of multiple signals -
-often from differing data sources- and sometimes individual model biases are 
+Ensembles allow for an incorporation of multiple signals -often from differing
+data sources- and sometimes individual model biases are 
 canceled
@@
 distribution function (CDF) and the inverse CDF or quantile function. The CDF 
-in the continuous case is defined in \eqref{eq:ccdf} and is defined in the 
-discrete case in \eqref{eq:dcdf}. Here $x_n$ is the largest value of X less than 
-or equal to $x$.
+in the continuous case is defined in \eqref{eq:ccdf} and in the 
+discrete case is defined in \eqref{eq:dcdf}.
 The quantile function is defined in \eqref{eq:quant} which returns a quantile 
@@
 \begin{equation}
+\label{eq:ccdf}
+  F(x) = P(X \leq b) = \int_{-\infty}^x p(t) dt
+\end{equation}
+
+\begin{equation}
 \label{eq:dcdf}
@@
 \begin{equation}
-\label{eq:ccdf}
-  F(x) = P(X \leq b) = \int_{-\infty}^x p(t) dt
-\end{equation}
-
-\begin{equation}
 \label{eq:quant}
@@
 
-For a forecast represented as a parametric function with pmf/pdf $p_m(\cdot)$, 
+For a forecast represented as a parametric distribution 
+with pmf/pdf $p_m(\cdot)$, 
 the accuracy of the forecast may be measured by how likely realized value $x^*$
@@
 Section 3 for more on proper scoring functions. The definitions 
-\eqref{eq:logs} and \eqref{eq:crps} are found in the review by Krueger.
+\eqref{eq:logs}, \eqref{eq:crps}, and \eqref{eq:is} are found in the review by 
+Krueger.
 
@@
 continuously
-infinite number of values. We will call this an infinite resolution.
-And requirements for storage are low 
+infinite number of values which we call an \emph{infinite resolution}.
+Also, requirements for storage are low 
 compared to other representation types that will be discussed. The most common
-parametric distributions can be fully defined with three or pieces of data
+parametric distributions can be fully defined with three or four pieces of data
 including
@@
 enough information to completely define a $\mbox{Lognormal(1,0.4)}$ 
-distribution.
+truncated on $[0,8]$ distribution. The truncation is done here so as to make a
+direct comparison with the distributions shown later in Tables 
+\ref{table:dbins} and \ref{table:qstor}.
 
@@
 \centering
- \begin{tabular}{|c c c|} 
- \hline
- family & param1 & param2 \\ [0.5ex] 
- \hline
- lnorm & 1 & 0.4 \\ 
+ \begin{tabular}{|c c c c c|} 
+ \hline
+ family & param1 & param2 & lowerlim & upperlim\\ [0.5ex] 
+ \hline
+ lnorm & 1 & 0.4 & 0 & 8 \\ 
  \hline
@@
 \subsection{Sample distributions}
-Forecast model builders may want more flexibility in modeling than a 
+Forecasters may want more flexibility in modeling than a 
 parametric 
 distribution can provide. Methods that require sampling from a posterior 
-distribution or Bootstrap sampling to obtain a sample distribution are examples
+distribution or bootstrap sampling to obtain a sample distribution are examples
 where parametric distributions may not be appropriate for modeling because of 
@@
 as $n \rightarrow \infty$. Thus, if a sufficiently large 
-sample is generated from a distribution with for which an expectation exists, 
+sample is generated from a distribution for which an expectation exists, 
 the sample will closely approximate the 
@@
 distributions 
-for which the mathematical formula is unkown or is not in closed form, more 
+for which the mathematical formula is unknown or is not in closed form, more 
 sophisticated methods may be required to generate samples. Bayesian analyses may 
-require a Gibbs sampling or a Metropolis-Hastings algorithm, among others, 
+require a Gibbs sampling or a Metropolis-Hastings algorithm, among other
+sampling methods, 
 to generate a 
@@
 approximate KD or GA pdf functions
--$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$  
+-$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$ respectively.  
 Here as well the optimal weights 
@@
 
-A potentially large issue with using sample distributions is the amount of storage
-it would require. For example when making MCMC draws from a posterior 
+A potentially large issue with using sample distributions is the amount of 
+storage
+it may require. For example when making MCMC draws from a posterior 
 distribution, the final sample distribution can have a sample size of thousands
@@
 where $B_i = [b_{i-1}, b_i)$ and $\cup_{i=1}^{K} B_i = A$. Based on the problem
-to be forecasted, researchers will determine the possible range $A$ and 
+to be forecast, researchers will determine the possible range $A$ and 
 select the number of bins and the sizes for each bin. It may be the case
-that a collaborative project will set the width of all bins to be equal so that 
+that a collaborative project will set the widths of all bins to be equal so that 
 $\Delta = b_i - b_{i-1}$ is the same width for all $i$ 
@@
 To complete the construction, a probability $p_i$ is assigned to each $B_i$ 
-where $\sum_{i=1}^{K}p_i = 1$. These probabilities are determined by the 
+where $\sum p_i = 1$. These probabilities are determined by the 
 forecasters. 
@@
 
-If the value to be forecasted takes on discrete values a common discrete 
+If the value to be forecast takes on discrete values a common discrete 
 distribution, such as a binary or Poisson distribution, may sometimes be used to 
-assign probabilities to each of the bins. When the values to be forecasted are
+assign probabilities to each of the bins. When the values to be forecast are
 continuous, a forecaster may need to employ a method of discretization to a 
@@
 
-The CDC flu competition has used a bin distributions as the forecast 
+For several flu seasons now, the CDC flu competition has used a bin distribution 
+as the forecast 
 representation. The CDC has also used it for other disease outbreak
@@
 
-Because discretized bins can be seen as a pmf, methods for proper scoring 
+Because a bin distribution can be viewed as a pmf, methods for proper scoring 
 already 
@@
 construction. Reich et. al used MA to combine multiple forecasts from the flu 
-competition. They built and compared ensemble models with different weighting
-schemes including equally weighted components $w_j = 1/J$ and estimating weights
+competition. They constructed and compared ensemble models with different 
+weighting
+schemes including equally weighted components, $w_m = 1/M$,
+and estimating weights
 according to the model specification. To estimate weights they used the 
@@
 
-The exact amount of information required for a discretized bin forecast will 
+The exact amount of information required for a bin forecast will 
 vary depending on the permitted range of the forecast and the desired 
 resolution. 
-In the CDC flu contest, a forecast might have 131 bins between 0\% and 13.1\% 
+In the CDC flu contest, a forecast might have 131 bins between 0\% and 13\% 
 -bins having increments of 0.1 or 0.01\%- with 
@@
 prediction. For any binning scheme of more than two bins, the information 
-requirement for bin distributions will be higher than for parametric 
-distributions.
-Table \ref{table:dbins} illustrates what a discretized 
+requirement for a bin distribution will be higher than for a parametric 
+distribution.
+Table \ref{table:dbins} illustrates what bin distribution which was discretized 
+from a 
 $\mbox{Lognormal(1,0.4)}$ distribution truncated over $[0,8]$
@@
 to Methodology-IV from Chakraborty 
-\cite[]{chakraborty2015generating,kemp2004classes}.
+\cite[]{chakraborty2015generating,kemp2004classes}. The truncation here is done
+because in practice a bin forecast will generally have a finite support.
 
@@
 distribution but is 
-still much larger than the three or five data pieces required to report a 
+still much larger than the three or five pieces of information required to 
+report a 
 lognormal
@@
  \end{tabular}
-  \caption[Discretized bin distribution storage]{This is a storage example of a
+  \caption[Bin distribution storage]{This is a storage example of a
   discretized
@@
 
-Besides potentially large amount of information required per forecast,
+Besides the potentially large amount of information required per forecast,
 creating the right 
@@
 be
-hard to produce. This may depend on the details of the event to be forecasted, 
+hard to produce. This may depend on the details of the event to be forecast, 
 but in the case of the COVID-19 outbreak choosing the right set of bins posed
@@
 
-\subsection{Quantile representation}
+\subsection{Quantiles}
 When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
@@
 nominal 
-intervals -depending on the specific target and unit to forecast- and a median.
-Using this interval or quantile representation leads to a number of changes in 
-the scoring and ensemble building of forecasts.
+intervals -depending on the specific target and unit to be forecast- 
+and a median.
+Using this quantile representation prevents the use of certain methods for 
+scoring and constructing ensemble forecasts.
 
@@
 Here for $N$ given quantiles $\alpha_1,..., \alpha_N$; $q_1,..., q_N$ are the 
-values such that 
+values such that we have \eqref{eq:quantiles}. 
 When the quantiles are reported as prediction intervals we have 
@@
 What is possible for scoring forecasts
-or constructing ensemble in other representations is often not possible with
-quantile forecasts. The shape of a distribution is also not known and in fact,
+or constructing an ensemble in other forecast representations is often not 
+possible when using
+quantile forecasts. The shape of a distribution is also not known, and in fact
 nothing is known about the tails or the uncertainty beyond the most 
-extreme reported quantile values. In the COVID-19 Forecast Hub predictions, 
+extreme reported quantile values. In the COVID-19 Forecast Hub forecasts, 
 nothing 
@@
 where $l$ and $r$ are the $\alpha/2$ and $(1-\alpha/2)$ quantiles that bound
-the central $(1-\alpha)$ prediction interval the IS is defined in \eqref{eq:is}.
+the central $(1-\alpha)$ prediction interval the IS is defined as 
+in \eqref{eq:is}.
 This is a sum -weighted by 
@@
   IS_{\alpha}(l,r; x^*) = (r-l) + \frac{2}{\alpha}(l-x^*)1\{x^*<l\} 
-  + \frac{2}{\alpha}(y-r)1\{x^* > r\}
-\end{equation}
-
-When an quantile forecast is made up of multiple intervals each with different
-$\alpha$ levels, the weighted interval score (WIS) may be used as it was by
+  + \frac{2}{\alpha}(x^*-r)1\{x^* > r\}
+\end{equation}
+
+When a quantile forecast is made up of multiple intervals each with different
+$\alpha$ levels, the weighted interval score (WIS) may be used.
 Bracher et.
@@
 \cite[]{bracher2021evaluating}.
-There are multiple versions of the WIS -some of 
+There are multiple versions of the WIS, some of 
 which are described in Bracher et. al, but the version used by the COVID-19 
@@
 
-Bogner, Liechti and Zappa compared scoring forecasts of quantiles with the 
+Bogner, Liechti, and Zappa compared scoring forecasts of quantiles with the 
 Quantile Score (QS) similar to the interval score and scoring distribution functions
@@
 used in QS or IS. Thus there may be something lost in terms of scoring when the 
-WIS is used.
+WIS is used since it is constructed from the IS.
 
@@
 ensemble forecast.
-The ensemble forecast constructed by the COVID-19 Forecast Hub was made as an
+The ensemble forecast constructed by the COVID-19 Forecast Hub is made as an
 equally-weighted average of forecasts from the component models. More 
-specifically, each quantile value of the ensemble was the average of values from
+specifically, each quantile value of the ensemble is the average of values from
 all models corresponding to the same quantile \cite[]{ray2020ensemble}. For $M$ 
@@
 the COVID-19 Forecast Hub model, $\nu_m = \nu = 1/M$. Where the overall mean or 
-a weighted mean may be used, the median may also be used.
+a weighted mean may be used for averaing, the median may also be used.
 Brooks et. al compare performance of the COVID-19 ensemble
@@
 
-Quantile averaging or Vincentization for a complete distribution is defined as
+More generally, quantile averaging or Vincentization for a complete distribution 
+is defined as
 in \eqref{eq:vinc}
@@
 distributions are exponential, Weibull, or logisitic the aggregated distribution
-is of the same family \cite[]{ratcliff1979group}. Quantile averagin produces 
+is of the same family \cite[]{ratcliff1979group}. Quantile averaging produces 
 smoother
@@
 forecasts
-and tends to perform better in scoring than probability averaging, MA,
+and tends to perform better in scoring than probability averaging like MA
 \cite[]{lichtendahl2013better}.
@@
 (some of the longer term forecasts only include seven quantiles). In terms of 
-storage, this is an improvement over requirements for the flu contest. Table
+storage, this is an improvement over requirements for the CDC flu competition. 
+Table
 \ref{table:qstor} shows what a submission of 23 quantiles from a 
-$\mbox{Lognormal(1,0.4)}$ might look like.
+$\mbox{Lognormal(1,0.4)}$ truncated on $[0,8]$ might look.
 
@@
  \begin{minipage}{10cm}
- \caption[Quantiles and values storage]{This shows six quantiles
+ \caption[Quantile storage]{This shows six quantiles
  and values from a lognormal distribution with $\mu = 1$ and $\sigma = 0.4$}
@@
 right columns respectively. Each is generated from a Lognorma(1,0.4) 
-distribution. Blue shows the density and CDF functions. Purple shows a 
+distribution truncated on $[0,8]$. 
+Blue shows the density and CDF functions. Purple shows a 
 histogram and ECDF of 1,000 samples. Red shows bin probabilities and the CDF
@@
 A mixture distribution forecast
-would allow for many distribution shapes, a high resolution, storage comparable
-to that of bin and quantile forecasts, and the more common methods for scoring
-and ensemble construction may be used.
-
+would allow for a large range of distribution shapes, a high resolution, 
+storage comparable
+to that of bin and quantile forecasts, and ensemble construction using MA.
 A mixture distribution may be constructed in the same way as the
@@
 where for $T$ distributions
-with pdfs $p_t(x)$ and $z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$ we have 
+with pdfs $p_t(x)$ and $z_t > 0$ and $\sum z_t = 1$ we have 
 \eqref{eq:dmd}.
@@
 
-Like the parametric, a mixture distribution may be evaluated with
-existing software like \texttt{distr} package in \texttt{R} 
+Like a parametric distribution, a mixture distribution may be evaluated using
+existing software like the \texttt{distr} package in \texttt{R} 
 \cite[]{camphausen2007distr}. 
@@
 scoring may be done  
-using the LogS, CRPS and IS. A mixture distribution, like its parametric 
+using the LogS, CRPS, and IS. A mixture distribution, like its parametric 
 distribution components, has an infinite resolution.
-
-A mixture distribution may be much more flexible than a single component 
+A mixture distribution may be more flexible than a single component 
 parametric distribution in 
-terms of distributional shape. According to 
+terms of distribution shape. According to 
 McLachlan and Peel, a mixture of 
@@
 forecast, the amount of storage per forecast might be as little as for a 
-parametric forecast or as permitted in the specific forecast project.
-
-An ensemble model may be built by using \eqref{eq:bma} only replacing $p_m$
-with $p_m^M$ in \eqref{eq:dmd}. Solving for weights may also be done by 
+parametric forecast or as much as is permitted permitted in the specific 
+collaborative forecast project.
+
+An ensemble model may be constructed by using \eqref{eq:bma} only replacing 
+$p_m$
+with $p_m^M$ from \eqref{eq:dmd}. Solving for weights may also be done by 
 maximizing
@@
 computation is likely to be more expensive. An example where this is
-true is when trying to minimize the CRPS but the exact mixture doesn't 
+true is when minimizing the CRPS when the exact mixture distribution doesn't 
 produce a closed form CRPS \cite[]{baran2018combining}. In large projects like
@@
 distribution, a sample distribution, and a set of quantiles. The common proper
-scoring rules LogS and CRPS may be used to score it. The storage requirement is
+scoring rules LogS and CRPS may be used to score a mixture forecast. 
+The storage requirement is
 comparable to that of a bin distribution or a set of quantiles. And MA may be 
@@
 \ref{section:conmixforc} we show how a mixture distribution may be constructed,
-scored and used to construct an ensemble using software available in 
+scored, and used to construct an ensemble using software available in 
 \texttt{R}.
@@
     Quantile averaging & Depends on 
-    requested quantiles. Perhaps dozens of values
+    quantiles requested, but dozens of values
     \\ \hline
@@
     Mixture distribution & LogS, CRPS, IS. May be more limited by computation & 
-    With
-    enough component distributions may
+    With a sufficient number of
+    component distributions, it may
     approximate any distribution shape. Infinite resolution& MA 
@@
 a few adjustments to those systems. In this section we outline how some of these
-adjustments may be implemented as well as present some tools which may be used
+adjustments may be implemented. As well we present tools which may be used
 to build forecasts from submissions, score those forecasts, and construct 
@@
 contains the distributional information for one or multiple forecasts. Tables
-\ref{table:dstan} and \ref{table:qstan} show what variables are included and a
+\ref{table:dstan} and \ref{table:qstan} show what variables are included in 
+those submissions and a
 couple rows to illustrate possible values.
@@
 Here \texttt{location} defines the specific county, state, or country of the 
-forecast. The \texttt{target} variable defines what is forecasted with levels
+forecast. The \texttt{target} variable defines what is forecast with levels
 season onset, deaths, hospitalizations, etc. The \texttt{type} variable defines
-the type for the \texttt{value} variable with levels of \texttt{point}, 
+the type for the \texttt{value} variable with levels of point, 
 bin, or quantile.
@@
 two weeks, four weeks, etc. The variables \texttt{bin} and \texttt{quantile}
-give a specific bin or a specific quantile. And the \texttt{value} variable is a 
+give a specific bin or a specific quantile. The \texttt{value} variable is a 
 number that 
@@
 
-A single submission may include many forecasts aimed at forecasting a 
+A single submission may include many forecasts aimed at forecasting 
 different combinations of \texttt{location}, \texttt{target}, and \texttt{unit}. 
@@
  \end{tabular}
- \caption[Influenza competition submission example]{This shows a few rows of a 
+ \caption[Influenza competition submission example]{This table 
+ shows a few rows of a 
  submission file
- for a discretized forecast like those in the CDC influenza forecast 
+ for a bin forecast like those in the CDC flu 
  competition. A set of rows which share the same combination of 
@@
 from 
-Tables \ref{table:dstan} and \ref{table:qstan} which make a useable submission 
+Tables \ref{table:dstan} and \ref{table:qstan} which make a usable submission 
 format for mixture distribution forecasts. In such a format, each row represents
-a component used in a mixture distribution.
+one component distribution used in a mixture distribution.
 The variables \texttt{bin} or \texttt{quantile} and \texttt{value} are removed 
@@
 distribution, and \texttt{weight} is the 
-weight $w_i$ for that component.
+weight $w_i$ for the $i^th$ component.
 
@@
  for a disease outbreak forecast using a mixture distribution representation.
- Each row represents a component of a mixture distribution. The variables
- location, target, and unit specify what is being forecasted. The variable type
+ Each row represents a component distribution
+ of a mixture distribution. The variables
+ location, target, and unit specify what is being forecast. The variable type
  specifies that the row represents a parametric distribution. The variables
- family, param1, and param2 specify the exact distribution. And the variable 
- weight specifies the weight $w_i$ that the component distribution has in the
+ family, param1, and param2 specify the exact component distribution. 
+ And the variable 
+ weight specifies the weight $w_i$ that the $i^th$ component distribution is
+ assigned in the
  mixture distribution. Here two components are shown with distributions
@@
 format in table \ref{table:dstan} with 17
-components would require $17 \times 8 = 136$ cells submitted per forecast. 
-A submission to the COVID-19 Forecast Hub forecast 23 quantiles
+components would require $17 \times 8 = 136$ pieces of information
+submitted per forecast. 
+A submission to the COVID-19 Forecast Hub forecast with 23 quantiles
 according to the format in table \ref{table:dstan} requires
@@
 
-Throughout the remainder of this section, explanations of how to work with 
-mixture distributions submitted according to Table \ref{table:mstan} is 
+In the remainder of this section, explanations of how to work with 
+mixture distributions submitted according to Table \ref{table:mstan} are 
 given. Also given is
@@
 That table may look like Tables \ref{tab:preddf1} and 
-\ref{tab:preddf1}. If the table is saved as a standard \texttt{data.frame} in 
+\ref{tab:preddf2}. If the table is saved as a standard \texttt{data.frame} in 
 \texttt{R}, then tools based on the \texttt{distr} package 
 \cite[]{camphausen2007distr} may be used for evaluating a mixture distribution 
-with the components in the table.
+with the component distributions in the table.
 
 The \texttt{distr} package contains a function 
-\texttt{UnivarMixingDistribution()} takes as arguments a list of distributions
+\texttt{UnivarMixingDistribution()} which takes as arguments a list of 
+distributions
 and a vector of weights for each distribution and a object of class 
@@
 CDF, and quantile function for continuous distributions from common
-families contained in the \texttt{distr} and for mixture distributions with 
+families contained in the \texttt{distr} package
+and for mixture distributions with 
 component distributions from those families.
@@
 with functions for the pdf, CDF, quantile function, and random samples from the
-mixture distribution may be drawn. Thus the distribution may be scored using the
+mixture distribution may be drawn. The distribution may then be scored using the
 LogS or CRPS.
@@
  component is a Lognormal$(2,1)$ with a weight of 0.3 in the mixture and the 
- second component is a Normal$(2.1,1)$ with a weight of 0.7.}
+ second component is a Normal$(2.1,1)$ with a weight of 0.7. The distribution
+ family abbreviations are capitalized here because that is how they will be
+ requested in the \texttt{MakeDist()} function. Refer to Table
+ \ref{table:mixfams} in the APPENDIX for more details. }
  \label{tab:preddf1}
@@
  component is a Normal$(1.5,1)$ with a weight of 0.4 in the mixture and the 
- second component is a Normal$(4,2)$ with a weight of 0.6.}
+ second component is a Normal$(4,2)$ with a weight of 0.6.
+ The distribution
+ family abbreviations are capitalized here because that is how they will be
+ requested in the \texttt{MakeDist()} function. Refer to Table
+ \ref{table:mixfams} in the APPENDIX for more details.}
  \label{tab:preddf2}
@@
 To construct an ensemble distribution from multiple mixture distributions, the 
-\texttt{UnivarMixingDistribution()} is again a useful tool. The function takes 
+\texttt{UnivarMixingDistribution()} function may be used. The function takes 
 two or more
-\texttt{AbscontDistribution} distribution objects and a vector of weights 
+\texttt{AbscontDistribution} distribution objects, including mixture 
+distribution objects, and a vector of weights 
 corresponding to each object. A new \texttt{AbscontDistribution} object is 
 returned as an ensemble of mixture distributions as in (\ref{eq:bma}). 
-Since they are \texttt{AbscontDistribution} objects \texttt{mdist1} and 
+Since they are \texttt{AbscontDistribution} objects, \texttt{mdist1} and 
 \texttt{mdist2} created in the code
@@
 At the onset of a collaborative forecast before there are true event 
-observations which the forecasts can be scored on, 
+observations which the forecasts may be scored on, 
 it may make sense to assign an equal weight to each 
@@
 If we have $T$ models ($M_t$) the posterior model probability of $M_t$ is 
-defined as in \eqref{eq:pmp} where $p(\cdot |M_t) := p_m(\cdot)$ is the density 
-function of the model and 
+defined as in \eqref{eq:pmp} where $p(\cdot |M_t) := p_m(\cdot)$ is the pdf 
+of the model distribution and 
 $p(M_j)$ is the prior probability assigned to the model. A common approach is to
@@
 (\ref{eq:pmp}) is reduced to \eqref{eq:pmpeq}. In this case the posterior model 
-probability for model $t$ is equal to the exponential of its negative LogS or
+probability for the $t^th$ model is equal to the exponential of its negative 
+LogS or
 $p(M_t|x) = e^{-LogS(p(M_t|x))}$, so the performance of a forecast based on the
-LogS is directly related to posterior model probability and may be used as an 
+LogS is directly related to its posterior model probability and may be used 
+as an 
 ensemble weight. For an observed event $x^*$, ensemble weights $(w_t)$ from 
@@
 the following code shows how
-to use the posterior model probability to select weights and construct an 
-ensemble distribution and score the ensemble forecast. Here again we take the 
-observed value to be \texttt{3}.
+to use the posterior model probability to select weights, construct an 
+ensemble distribution, and score the ensemble forecast. Here again we take the 
+observed event value to be \texttt{3}.
 The ensemble distribution
@@
 \centerline{\includegraphics[scale=.15]{Images/mix_ense.png}}
+\begin{center}
+ \begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \caption[Example ensemble forecast]{Ensemble forecast made from forecast 1 and 
@@
 red line is the density component of mixture forecast 2 with weight 
-0.471. The blue line is the density of the ensemble.}
+0.471. The blue line is the density of the ensemble forecast.}
 \label{fig:mixense}
+\end{minipage}
+\end{center}
 \end{figure}
@@
 for fitting are statistically formal.
-Because of this it should be noted that any conclusions made in 
+Nirwan and Bertshinger state that minimizing the mean square error between 
+quantile values and a CDF function has been the most common way to fit a 
+distribution
+to a set of quantiles. This is the method we will use in Section 
+\ref{section:covdretro}.
+Because of the lack of statistically formal methods for fitting a parametric
+distribution to a bin distribution or a set of quantiles, 
+it should be noted that any conclusions made in 
 this section may not be 
@@
 these common families was to first fit a distribution of that family to the bin
-forecast and then measure close the fit was. The decsion to fit truncated 
+forecast and then measure the closeness of that fit. The decision to 
+fit truncated 
 distributions was due to all bin forecasts being assessed having a finite 
@@
 
-To fit a distribution to a forecast we first minimize \eqref{eq:msd}. We call
+In fitting a distribution to a forecast we want minimize \eqref{eq:msd}. We call
 \eqref{eq:msd} the mean square difference (MSD).
 Here $F(\cdot| \hat{\theta})$ is a CDF, $p_i$ is the reported probability for 
-the $i^{th}$ bin $B_i := [b_{i-1}, b_i)$ and $K$ is the number of bins.
+the $i^{th}$ bin $B_i := [b_{i-1}, b_i)$, and $K$ is the number of bins.
 The fitted parameter vector $\hat{\theta}$ is the solution to 
 \eqref{eq:discfit}.
-If a distribution was fit to the submitted binned 
-prediction
+If a distribution was fit to the submitted bin forecast
 and the MSD was less than a 
@@
 bin distributions were discretized from known distributions, 
-parameters were fit to the binned distrubtions and the MSD was calculated. This 
-was done 1,000 times for the four distrubtion families considered and the cutoff 
+parameters were fit to the bin distributions, and the MSDs were calculated. This 
+was done 1,000 times for the four distribution families considered and the 
+cutoff 
 value for each family was set as the value under which 95\% of MSD values fell.
@@
 0.1 between 0 and 13 was constructed. 
-A value $u$ was selected from a $\mbox{Unif(0,13)}$ distribution and $y$ from 
-a $\mbox{Unif(.05,1.6)}$ distribution. 
-$u$ and $y$ were taken as respectively 
+A value $u$ was selected from a $\mbox{Unif(0,13)}$ distribution and $v$ from 
+a $\mbox{Unif(.05,1.6)}$ distribution. The drawn values
+$u$ and $v$ were taken as respectively 
 the center and scale parameters of a TN distribution. 
 For uniform, TL, and TG family
-distributions, model parameters were solved for so that $u$ and $y$ 
+distributions, model parameters were computed such that $u$ and $v$ 
 were roughly the mean and standard deviation.
@@
 % enough that it didn't matter for our purpose.
-With a known distribution with $\theta = (u,y)$, 
-probabilities $p_i =F(b_i| \theta) - F(b_{i-1})$ 
-where, were
+With a known distribution with $\theta = (u,v)$, 
+probabilities $p_i =F(b_i| \theta) - F(b_{i-1})$ were
 calculated for each bin. A distribution from the same
@@
 
-Of the 869,638 predictions from the CDC Retrospective Forecast project, we fit
-each of uniform, TN, TL, and TG distributions to 11,715 of the individual 
-predictions. From each of the 27 teams represented, there is a list of forecast
+Of the 869,638 forecasts from the CDC Retrospective Forecasts project, we fit
+each of uniform, TN, TL, and TG distributions to 11,715 of those
+forecasts. From each of the 27 teams represented, there is a list of forecast
 submissions from which we randomly selected 12. From each submission, we 
@@
 distributions failed to converge, so of all forecasts we were only able to 
-successfully fit distributions to 11,715 of them.
-We calculated the MSD, and for each forecast the fit
+successfully fit distributions to 11,715.
+We calculated the MSD for each of the four fits, and for each forecast the fit
 distribution with the lowest of the four MSDs was considered the best fit. If 
@@
 Of the 11,715 binned distributions fit to the mixture distributions,
-2,502 of those fits had MSD values below the values listed in Table
+2,502 of those fits had MSD values below the cutoff values listed in Table
 \ref{table:bincutoffs}. Thus we conclude that a proportion of 0.214 of those
-forecasts were generated from a common parametric distribution. The results for 
+forecasts were generated from a one component mixture distribution. 
+The results for 
 the
-11,715 fit distributions, which families the binned distributions were best
-fit to and whether or not the fits produce an MSD below the cutoff value, 
+11,715 fit distributions, which families the bin distributions were best
+fit to, and whether or not the fits produce an MSD below the cutoff value, 
 are seen in table \ref{table:cdcresults}. Figure \ref{fig:binparamfits} is an
-example of
-the fit distributions to the same bin forecast.
+image showing a distribution from each of the four distribution families 
+considered
+fit to the same bin forecast.
 
@@
   Distribution Family   & Total    & Total below MSD cutoff value 
-  & Proportion from parametric distribution\\
+  & Proportion from one component mixture\\
   \hline
@@
 \section{COVID-19 Forecast Hub}
+\label{section:covdretro}
 
@@
 forecasts covered all combinations of 3,202 municipalities (mostly counties) 
-in the United States with 441 targets. The first of these forecasts was 
+in the United States with 441 target/unit combinations. 
+The first of these forecasts was 
 submitted in March of 2020 shortly after the initial outbreak of the COVID-19 
 virus in 
-the US and forecasts have been received weekly since. 
+the US, and forecasts have been received weekly since. 
 The forecasts are all quantile forecasts made up of three or 11 predictive 
 intervals -depending on the specific unit for the forecast-
-and a median. In the forecasts include seven or 23 quantiles.
+and a median. Thus each forecasts includes seven or 23 quantiles.
 
@@
 known continuous distribution, we minimized the mean square error (MSE)  
-in \eqref{eq:mse} between where $q_i$ is
-the $i^{th}$ quantile value from a forecast and $F(y| \theta)$ is a fit CDF with 
+in \eqref{eq:mse} where $q_i$ is
+the $i^{th}$ quantile value from a forecast and $F(y| \hat{\theta})$ 
+is a fit CDF with 
 parameter $\hat{\theta}$. The parameter $\hat{\theta}$ is the solution to 
@@
 gamma, and location-scale t CDF. Unlike in the previous section, we felt no need
-to the distributions as truncated because there is no range limit to these 
-forecasts. We included the t distribution to account for any
+to truncate the distributions because there is no range limit to these 
+forecasts. We also included the t distribution to account for any
 symmetric forecasts with heavier tails than in a normal distribution.
-If the MSE between a given forecast and a fit CDF fell below a certain cutoff,
-we considered the quantiles as approximately coming from the fit CDF. To
-determine the cutoff values, for each of the five distribution families the same
+If the MSE between a given forecast and a fit CDF fell below a certain cutoff
+value,
+we considered the quantiles as approximately matching those from the fit CDF. To
+determine the cutoff values, for each of the five distribution families,
+the same
 procedure was followed 1,000 times.
@@
 seven quantiles and others 
-require 23. After that decision was made, a random value $u$ was drawn from
+require 23. The quantiles used matched those used by the COVID-19 Forecast Hub.
+After that decision was made, a random value $u$ was drawn from
 a $\mbox{Unif(2,000,\; 25,000)}$ distribution and another value $v$ was drawn
@@
 and
-standard deviation and for each of the distribution families considered. The
-proper transformations computed to find model parameters corresponding to the 
-distribution. Quantile values were calculated for then each quantile. When using 
+standard deviation for each of the five families and for each the
+proper transformations were computed to find model parameters corresponding to 
+the distribution family. 
+Quantile values were then calculated for each given quantile. When using 
 a t distribution, a value for degrees of freedom was drawn from a 
@@
 the other distribution families. We believe this is related to the fact that 
-that is a three parameter family where as the other four families are two 
+the t distribution is a three parameter family where as the other four families 
+are two 
 parameter families. Thus influencing the optimization methods used enough to 
@@
 The MSE was calculated for each and the fit with the
-lowest MSE was selected as the closest fit. If the MSE fell below the cutoff
+lowest MSE was selected as the best fit. If the MSE fell below the cutoff
 specified above, we concluded that the quantile forecast was approximately
@@
 
-Table \ref{table:cresults} show the results of the analysis by distribution
+Table \ref{table:cresults} shows the results of the analysis by distribution
 family.
@@
 distribution are seen in Table \ref{table:cresults}.
-Figures \ref{fig:qqfits} and \ref{fig:cdffits} show the QQ plots and CDF plots
-for different distribution fits to the same set of quantiles.
+Figures \ref{fig:qqfits} and \ref{fig:cdffits} show the qq plots and thr CDF 
+plots
+for four of the different distribution families fit to the same set of quantiles.
 
@@
   Distribution Family   & Total    & Total below MSE cutoff 
-  & Proportion from parametric distribution\\
+  & Proportion from a one component mixture\\
   \hline
@@
   \caption[COVID-19 Forecast Hub results]{Results for COVID-19 Forecast Hub
-  retro analysis}
+  retro analysis. Here is is seen that 239 of the forecasts were best fit by 
+  a uniform, 609 by a normal, 694 by a lognormal, 597 by a gamma, and 365 by
+  a location-scale t. Of those fits 0, 74, 0, 0, and 25 respectively had an 
+  MSE below the cutoff values give in Table \ref{table:quantcutoffs}.}
   \label{table:cresults}
@@
 The results from these two studies suggest that in some cases, forecasters
-are using methods which produce may produce one component mixture distribution
+are using methods which may produce one component mixture distribution
 forecasts. Many
@@
 probabilistic 
-forecasting including proper scoring, data storage, and ensemble model 
+forecasting and discussed proper scoring, data storage, and ensemble model 
 construction for each type. We presented the mixture distribution
-representation and we argue that its use in collaborative probabilistic 
+representation and argue that its use in collaborative probabilistic 
 forecasting is preferable to the other representations.
 In terms of model flexibility, storage, and 
-ensemble building it is
-comparable to discretized bins and quantile forecasts but also provides a 
+ensemble construction it is
+comparable to bin and quantile forecasts but also provides a 
 forecast with a infinite nominal resolution. Based on a retrospective analysis,
@@
 forecasters, using a 
-different representation may simply not want to break from tradition. The 
+different representation format may simply not want to break from tradition. The 
 implementation of new scoring and ensemble construction methods may be a 
@@
 this paper is the selection of weights for components of an ensemble where each
-of the components is mixture distribution. Computing requirements could become a
+of the components is a mixture distribution. 
+Computing requirements could become a
 concern in such a problem and further research on this may provide
@@
 forecasting. We have only considered here probabilistic forecasting of one 
-event at a time. Number of new infections in one week at one specific location
+event at a time. Number of new infections in one week at one specific location,
 for example. This forecast is presented as a marginal distribution for that 
 specific target, time, and location. A joint distribution for forecasting 
-multiple targets, times or locations may sometime be desirable and may require
+multiple targets, times, or locations may sometimes be desirable and may require
 further consideration on how joint mixture distributions could be used as a 
@@
 The following is the code to make the \texttt{MakeDist()} function introduced 
-in \ref{section:tools}.
+in \ref{section:tools}. Tables \ref{table:mixfams} and \ref{table:mixfamsparams}
+show how distribution family arguments are to be written and what parameters are
+to be used for the distributions in the \texttt{MakeDist()} function.
+
 \begin{Schunk}
@@
 
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | p{4cm} | p{7cm} |}
+    \hline
+    \textbf{Argument} & \textbf{Summary} & \textbf{Options} \\ \hline
+    dist & A string specifying a distribution family.  & Beta, Cauchy,
+    Lnorm, Logis, “Unif, Lst (location scale t distribution),
+    Weibull, Fd, Norm,  Chisq,
+    Gammad, Exp
+	 Binom, Dirac, Pois, Hyper, Nbinom, Geom \\ \hline
+    param1 & A real number specifying the first parameter value of the
+    distribution. & Beta: shape1;
+	Cauchy: location;
+	Lnorm: meanlog;
+	Logis: location;
+	Unif: min;
+	Lst: location;
+	Weibull: shape;
+	Fd: df1;
+	Norm: mean;
+	Chisq: df;
+	Gammad: scale;
+	Exp: rate;
+	Binom: size;
+	Dirac: location;
+	Pois: lambda;
+	Hyper: m;
+	Nbinom: n;
+	Geom: prob
+     \\ \hline
+    param2 & A real number specifying the second parameter value of the
+    distribution. & Beta: shape2;
+	Cauchy: scale;
+	Lnorm: slog;
+	Logis: scale;
+	Unif: Max;
+	Lst: scale;
+	Weibull: scale;
+	Fd: df2;
+	Norm: sd;
+	Chisq: ncp;
+	Gammad: shape;
+	Binom: prob;
+	Hyper: n;
+	Nbinom: p \\
+    \hline
+    param3 & A real number specifying the third parameter value of the
+    distribution. & Lst: df;
+	Hyper: k \\
+	\hline
+	weight & A real number between 0 and 1 specifying the weight given to the
+	distribution in the overall mixture distribution. The sum of the weight
+	column should equal 1. & ...
+	\\
+	\hline
+    \end{tabular}
+    \begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
+  \caption[Arugments of \texttt{MakeDist()} function]{This table describes how
+  each argument may be entered into a data frame entered into the 
+  \texttt{MakeDist()} function, including
+  exactly how the distribution families should appear and what paramaters should
+  be included for each distribution family.}
+  \label{table:mixfams}
+  \end{minipage}
+  \end{center}
+\end{center}
+\end{table}
+
+% \begin{adjustwidth}{-3cm}{-1cm}
+\begin{table}
+\begin{center}
+% \caption{MakeDist parameter options}
+    \begin{tabular}{ l l  p{2cm}  p{2cm}  p{2cm}}
+    \hline
+    \textbf{Distribution} & \textbf{dist} & \textbf{param1} & \textbf{param2} &
+    \textbf{param3} \newline \\ \hline
+    Beta & Beta & shape1 & shape2 &  \\
+    Cauch & Cauchy & location & scale &  \\
+    Log-normal & Lnorm & meanlog & slog &  \\
+    Logistic & Logis & location & scale &  \\
+    Uniform & Unif & min & max &  \\
+    Location Scale T & Lst & location & scale & df \\
+    Weibull & Weibull & shape & scale &  \\
+    F & Fd & df1 & df2 &  \\
+    Normal & Norm & mean & sd &  \\
+    Chisqure & Chisq & df &  &  \\
+    Gamma & Gammad & scale & shape &  \\
+    Exponential & Exp & rate &  &  \\
+    Binomial & Binom & size & prob &  \\
+    Dirac & Dirac & location &  &  \\
+    Poisson & Pois & lambda &  &  \\
+    Hypergeometric & Hyper & m & n & k \\
+    Negative binomial & Nbinom & n & p &  \\
+    Geometric & Geom & prob &  &  \\ \hline
+    \end{tabular}
+        \begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
+  \caption[\texttt{MakeDist()} parameters]{This table shows what parameters
+  may be used for each distribution family used in a data frame for
+  the \texttt{MakeDist()} function or in the 
+  \texttt{UnivarMixingDistribution()} function.}
+  \label{table:mixfamsparams}
+  \end{minipage}
+  \end{center}
+\end{center}
+\end{table}
+% \end{adjustwidth}
+
 The following is the code used to make the function \texttt{CRPS()} used in

### 2022-04-05 manuscript/Preface/abstract.tex
final draft

@@
 including
-probability densities, samples, binned distributions, and  quantile 
-forecasts and compares
+parametric distributions, samples, bin distributions, and  quantiles 
+and compares
 their use in the context of collaborative projects. We propose the use of
@@
 building ensemble models, and the reasonably low level of computer storage 
-required to save such a format make the discrete mixture distribution an 
+required to store such a forecast make the discrete mixture distribution an 
 attractive alternative to the other representation formats.

### 2022-04-05 manuscript/thesis.Rnw
final draft

@@
 
+\usepackage{amsmath}
 \usepackage{amssymb}
@@
 \renewcommand{\chaptername}{}
+
 \begin{document}
 \SweaveOpts{concordance=TRUE}
+\DefineVerbatimEnvironment{Sinput}{Verbatim} {xleftmargin=2em,
+                                              frame=single}
+\DefineVerbatimEnvironment{Soutput}{Verbatim}{xleftmargin=2em,
+                                              frame=single}
 \DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
+
 %\begin{singlespace}
@@
 or
-discrete parametric distribution, given as a probability density/mass function 
-(pdf/pmf). Much of the literature 
+discrete parametric distribution, given as a probability density/mass function. 
+Much of the literature 
 on calibration, sharpness, and scoring of a forecast pertains to parametric 
 distribution forecasts
-\cite{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
-Other common representations include samples \cite{krueger2016probabilistic}, 
-discretized bin distributions \cite{mcgowan2019collaborative},
-and quantile forecasts \cite{taylor2021evaluating, bracher2021evaluating}. 
+\cite[]{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
+Other common representations include samples \cite[]{krueger2016probabilistic}, 
+discretized bin distributions \cite[]{mcgowan2019collaborative},
+and quantile forecasts \cite[]{taylor2021evaluating, bracher2021evaluating}. 
 Each representation may be more or less 
-appropriate than the others for a given problem but knowing how to interpret, 
-score, and contruct ensemble forecasts for a selected representation is 
+appropriate than the others for a given problem, but knowing how to interpret, 
+score, and construct ensemble forecasts for a selected representation is 
 essential when multiple teams collaborate in the same forecasting project.
@@
 construct forecasts using 
-whatever methods they choose. Historically, the forecasts must be 
+whatever methods they choose. Historically, the forecasts have been
 submitted 
-in a discretized bin distribution
+in a discretized bin distribution or a bin distribution
 format. A \emph{bin distribution} is a probability distribution represented by
-breaking the numeric range of an event into intervals or \emph{bins} and
-directly assigning the probability that the event falls within each bin.
+breaking the numeric range of an outcome into intervals or \emph{bins} and
+directly assigning to each bin the probability that the event falls 
+within the bin.
 During previous flu seasons the \emph{binning scheme} or the assignment of 
@@
 forecasts into a \emph{multi-model ensemble forecast} 
-\cite{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy},
-refered to hereafter as an ensemble forecast.
+\cite[]{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy},
+or an ensemble forecast.
 
@@
 official
-communication \cite{Cramer2021-hub-dataset}. See Figure \ref{fig:cdcoff}.
+communication \cite[]{Cramer2021-hub-dataset}. Figure \ref{fig:cdcoff} is from 
+an 
+official CDC report from August 2021 showing forecasts from the COVID-19 
+Forecast Hub of increment deaths and cumulative deaths due to COVID-19.
 
@@
 column show prediction intervals from multiple teams whereas the plots on the 
-right show the intervals for an ensemble forecast model.}
+right show the intervals for an ensemble forecast model with gray lines that are
+individual model point forecast predictions.}
 \label{fig:cdcoff}
@@
 or the COVID-19 Forecast Hub, bin forecasts and quantile forecasts have become
-important representations to those involved in the projects. Yet both 
+important representations. Yet both 
 representation types come 
-with their drawbacks. Data 
-storage for instance might be a concern if many bins are used for forecasting. 
-And scoring methods are limited if forecasts are quantile forecasts.
-
-In this paper, we propose the use of discrete mixture distributions as a means 
+with their drawbacks. Computer
+storage for instance might be a concern if many bin distributions are used for 
+forecasting, 
+and scoring methods are limited if forecasts are quantile forecasts.
+
+In this paper, we propose the use of finite mixture distributions as a means 
 of forecasting for collaborative projects similar to the CDC flu competition or 
 the COVID-19
-Forecast Hub. In Section \ref{section:representations}, 
+Forecast Hub. A finite mixture distribution -which we will refer to as a
+\emph{mixture distribution}- is distribution constructed by combining a finite 
+collection of other distributions. In this paper, we focus on the case where the
+collection of distributions are parametric distributions.
+
+In Section \ref{section:representations}, 
 popular probabilistic forecast representation 
@@
 representation type.
-In Section \ref{section:conmixforc}, details for using discrete mixture 
+In Section \ref{section:conmixforc}, details for using mixture 
 distributions in a collaborative forecast project are presented as well as tools
-which may be used for scoring and constructing an ensemble.
+which may be used for scoring and constructing an ensemble forecast.
 Section \ref{section:retrostud} is a retrospective study of the CDC flu 
 competition and COVID-19 Forecast Hub
-forecast and an attempt to assess whether any forecast models
-may be approximated by known continuous distributions. We conclude this 
-paper with a discussion.
+forecasts and an attempt to assess whether forecast models
+may be approximated by one component mixture distributions.
 
@@
 repository for the
-COVID-19 Forecast Hub predictions contained 85 million predictions as of 
-February 5, 2022 which required more than 11.6 gigabytes of storage!
-(cite zoltar??)
+COVID-19 Forecast Hub contained 85 million forecasts as of 
+April 4, 2022 which required more than 11.7 gigabytes of storage!
+\cite[]{covidgithub}.
 When determining the goals of a forecast project, there should be consideration 
@@
 
-\subsection{Ensemble Modeling}
-A multi-model ensemble is a statistical model made by combining information from
+\subsection{Ensemble construction}
+An ensemble model is a statistical model made by combining information from
 two or more individual statistical models. Private and public decisions are 
-regularly made after combining information from multiple sources. For any given
-situation, information from one source may provide insight on a subject which 
+regularly made after combining information from multiple sources. For a given
+problem, information from one source may provide insight on a subject which 
 other
 sources fail to capture. Likewise one statistical model may provide insight
-that another model does not, so that when they are combined in an ensemble the 
-ensemble model outperforms the individual component models.
+that another model does not so that when they are combined into an ensemble the 
+ensemble outperforms the individual component models.
 
 As probabilistic forecasting becomes more commonplace, so too does ensemble 
-modeling. Multi-model ensembles have been used extensively in weather and
-climate modeling \cite[for example]{baran2018combining}, 
+modeling. Ensembles have been used extensively in weather and
+climate modeling \cite[]{baran2018combining}, 
 and they have been used increasingly in modeling infectious disease outbreaks
-see \cite[for example]{yamana2016superensemble}. 
-Multi-model ensembles allow for an incorporation of multiple signals -
-often from differing data sources- and sometimes individual model biases are 
+\cite[]{yamana2016superensemble}. 
+Ensembles allow for an incorporation of multiple signals -often from differing
+data sources- and sometimes individual model biases are 
 canceled
-out or reduced by biases in others \cite[see references
+out or reduced by biases from other models \cite[see references
 therein]{reich2019accuracy}. 
-In several disease outbreak studies, multi-model ensemble forecasts have been 
+In several disease outbreak studies, ensemble forecasts have been 
 shown to outperform individual model forecasts
 \cite[see
-references therein]{cramer2021evaluation}.
+references therein]{ray2020ensemble, cramer2021evaluation}.
 
 Construction of an ensemble may be done by combining individual forecast 
-distributions using weighted averages. This has been called stacking 
-\cite{wolpert1992stacked} or weighted density ensembles 
-\cite{ray2018prediction}.
-
-\section{Probabilistic Forecast Representation Types}
+models using weighted averages. This has been called stacking 
+\cite[]{wolpert1992stacked} or weighted density ensembles 
+\cite[]{ray2018prediction}.
+
+\section{Probabilistic forecast representation types}
 \subsection{Parametric distributions}
@@
 A parametric distribution is a discrete or continuous probability distribution 
-described by a known function $p(x) := p(x|\theta)$ -pmf in the discrete case or 
-pdf in the continuous case. Here $\theta$ is a vector of known or unkown 
-parameters 
-contained in a parameter space.
+described by a known function $p(x) := p(x|\theta)$. The function $p(x)$ is 
+called a probability mass function (pmf) if the distribution is discrete and 
+is called a probability density function
+(pdf) if the distribution is continuous. Here $\theta$ is a vector of known or 
+unkown parameters contained in the parameter space of the distribution.
 
@@
 distribution function (CDF) and the inverse CDF or quantile function. The CDF 
-in the continuous case is defined as
+in the continuous case is defined in \eqref{eq:ccdf} and in the 
+discrete case is defined in \eqref{eq:dcdf}.
+The quantile function is defined in \eqref{eq:quant} which returns a quantile 
+value where $p$ is a given probability such that $0\leq p \leq 1$.
 
@@
 \label{eq:dcdf}
-  F(x) = P(X \leq b) = \sum_{k=1}^n p(x_k) dt
-\end{equation}
-where $x_n$ is the largest value of X less than or equal to $x$.
-The quantile function is defined as
+  F(x) = P(X \leq b) = \sum_{x \in X} p(x)
+\end{equation}
+
 \begin{equation}
@@
 \end{equation}
-returning a quantile value where $p$ is a given probability $0\leq p \leq 1$.
-
-% \subsubsubsection{Scoring}
-For a forecast represented as a parametric function with pmf/pdf $p_m(x)$, 
-the accuracy of the forecast may be measured as how likely realized value $x^*$
+
+For a forecast represented as a parametric distribution 
+with pmf/pdf $p_m(\cdot)$, 
+the accuracy of the forecast may be measured by how likely realized value $x^*$
 is to occur. Commonly used proper scoring rules for parametric distributions
-include the Logarithmic score (LogS), 
-continuous rank probability score (CRPS) \cite{hersbach2000decomposition}
-\cite{alves2013ncep} and the interval/Brier 
-score (IS) \cite{gneiting2007strictly} among 
-others. See also \cite{gneiting2014probabilistic}
-section 3 for more on proper scoring functions. Unless otherwise noted, the 
-following
-definitions can be found in the review by Krueger.
-
-For a forecast with pdf/pmf $p_m(x)$, the LogS evaluates the 
-probability of the observed value $x^*$. It is defined as
+include the logarithmic score (LogS), the
+continuous rank probability score (CRPS) \cite[]{hersbach2000decomposition}
+\cite[]{alves2013ncep}, and the interval/Brier 
+score (IS) \cite[]{gneiting2007strictly} among 
+others. See also \cite[]{gneiting2014probabilistic}
+Section 3 for more on proper scoring functions. The definitions 
+\eqref{eq:logs}, \eqref{eq:crps}, and \eqref{eq:is} are found in the review by 
+Krueger.
+
+For a forecast with pdf/pmf $p_m(\cdot)$, the LogS evaluates the 
+probability of the observed value $x^*$. It is defined in \eqref{eq:logs}.
 
@@
 used
-to build ensembles under Bayesian model averaging (BMA). Considered the 
+to build ensembles under model averaging (MA). Considered the 
 state-of-the-art techniques for combining 
 component distributions
-into a multi-model ensemble are nonhomogeneous regression (NR), also known as
+into an ensemble distribution are nonhomogeneous regression (NR), also known as
 ensemble model output statistics (EMOS), and ensemble
-BMA, both of which are defined in \cite{gneiting2014probabilistic}.
+MA, both of which are defined in \cite[]{gneiting2014probabilistic}.
 
@@
 sources,
-BMA is the better option. In BMA, the final model does not have to be specified
-beforehand and the resulting forecast will be a discrete mixture distribution
+MA may be preferable because it does not require that modeling methods for 
+individual components be the same. 
+In MA, the final model does not have to be specified
+beforehand and the resulting forecast will be a mixture distribution
 of all component forecasts. The general form for an ensemble distribution $p^E$
-is
+is in \eqref{eq:bma}. Here $p_m$ is the $m^{th}$ component forecast 
+distribution and 
+$0 \leq w_m \leq 1$ is a weight assigned to that component where $\sum w_m = 1$.
+Methods for estimating weights include maximum likelihood estimation
+\cite[]{raftery2005using}, MCMC 
+sampling \cite[]{vrugt2008ensemble},
+and minimizing the CRPS of the ensemble
+\cite[]{baran2018combining}.
 
@@
 \end{equation}
-where $p_m$ is the $m^{th}$ component forecast distribution and 
-$0 \leq w_m \leq 1$ is a weight assigned to that component where $\sum w_m = 1$.
-Methods for estimating weights include Maximum Likelihood estimation
-\cite{raftery2005using}, MCMC 
-sampling see \cite{vrugt2008ensemble}
-and minimizing the ensemble CRPS see
-\cite{baran2018combining}.
-
-For selecting distribution weights, the CRPS has some nice properties, but can 
-sometimes be
+
+For selecting distribution weights, minimizing the CRPS has some nice 
+properties, but it can also be
 difficult to compute. For example, when the forecast is a mixture of a 
 truncated normal distribution (TN) and a truncated lognormal (TL) the CRPS is 
-not available in closed form \cite{baran2018combining}.
-
-Generally computation and evaluation of parametric distributions is not hard. 
+not available in closed form \cite[]{baran2018combining}.
+
+Generally computation and evaluation of parametric distribution functions is not 
+hard. 
 For most commonly used parametric distributions -normal, lognormal, Poisson,
 gamma, etc.- there is software readily available to compute density, 
-distribution and quantile values. Likewise, requirements for storage are low 
+distribution, and quantile values. 
+A completely defined continuous parametric distribution may be evaluated at a
+continuously
+infinite number of values which we call an \emph{infinite resolution}.
+Also, requirements for storage are low 
 compared to other representation types that will be discussed. The most common
-parametric distributions can be fully defined with three or pieces of data
+parametric distributions can be fully defined with three or four pieces of data
 including
-the distribution family and two or three parameters. Table \ref{table:pstor} 
+the distribution family and two parameters. Table \ref{table:pstor} 
 contains
-enough information to completely define a $Lognormal(1,0.4)$ distribution.
+enough information to completely define a $\mbox{Lognormal(1,0.4)}$ 
+truncated on $[0,8]$ distribution. The truncation is done here so as to make a
+direct comparison with the distributions shown later in Tables 
+\ref{table:dbins} and \ref{table:qstor}.
 
 \begin{table}[h!]
-
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \centering
- \begin{tabular}{|c c c|} 
- \hline
- family & param1 & param2 \\ [0.5ex] 
- \hline
- lnorm & 1 & 0.4 \\ 
+ \begin{tabular}{|c c c c c|} 
+ \hline
+ family & param1 & param2 & lowerlim & upperlim\\ [0.5ex] 
+ \hline
+ lnorm & 1 & 0.4 & 0 & 8 \\ 
  \hline
  \end{tabular}
- \caption[Parametric distribution storage]{Storage example of parametric 
- lognormal 
+ \caption[Parametric distribution storage]{This is an example of data required
+ for a lognormal 
  distribution with 
@@
 
-\subsection{Sample Distributions}
-Some forecast model builders may want more flexibility in modeling than a 
+\subsection{Sample distributions}
+Forecasters may want more flexibility in modeling than a 
 parametric 
 distribution can provide. Methods that require sampling from a posterior 
-distribution or Bootstrap sampling to obtain a sample distribution are examples
-where parametric distributions may not be appropriate for modeling.
+distribution or bootstrap sampling to obtain a sample distribution are examples
+where parametric distributions may not be appropriate for modeling because of 
+the lack of flexibility in distribution shape.
 
 A sample distribution is made of a sample of random variables 
-$(X_1,...,X_n)$ where $X_i \sim D$ and $D$ is a distribution. From this, sample
-statistics such as mean, median, variance and quantiles may be calculated. 
+$(X_1,...,X_n)$ where $X_i \sim D$ and $D$ is some distribution. From this 
+sample,
+statistics such as mean, median, variance, and quantiles may be calculated. 
 An empirical cumulative distribution function (ECDF) may also be calculated as
+in \eqref{eq:ecdf}.
 
@@
 as $n \rightarrow \infty$. Thus, if a sufficiently large 
-sample is generated from a distribution with an expectation, 
+sample is generated from a distribution for which an expectation exists, 
 the sample will closely approximate the 
@@
 distributions 
-for which the mathematical formula is unkown or is not in closed form, more 
+for which the mathematical formula is unknown or is not in closed form, more 
 sophisticated methods may be required to generate samples. Bayesian analyses may 
-require a Gibbs or Metropolis-Hastings algorithm, among others, to generate a 
+require a Gibbs sampling or a Metropolis-Hastings algorithm, among other
+sampling methods, 
+to generate a 
 sample. Such samples are useful in that the true distribution may be closely 
@@
 
-Under the samle distribution format, the options that a researcher has for 
-constructing a forecast are more than
-if they are asked to submit a parametric distribution and the range 
-characterisitcs 
-and shapes of distributions is larger.
+Under the sample distribution representation, the options that a researcher has 
+for constructing a forecast are more than
+if they are asked to submit a parametric distribution, and the range of possible 
+shapes for a distribution is larger.
 In the last few decades, increased computing power and improvements in MCMC
 sampling have greatly contributed to growth in the use of
-predictive distributions \cite{gneiting2007strictly}
+sample distributions for forecasting \cite[]{gneiting2007strictly}
 \cite[see examples listed therein]{krueger2016probabilistic}.
@@
 \end{equation}
-where $\Phi$ is the standard normal CDF and $\hat{\mu}_n$ and $\hat{\sigma}_n$
-are the empirical mean and standard deviation of the sample $(X_i)$
-\cite{krueger2016probabilistic}.
-
-Krueger et. al compare scoring of MCMC drawn forecast distributions using CRPS 
-and LogS over samples directly using ECDF or over density approximations using
-KD or GA.
-
-To build an ensemble model from sample distribution forecasts, the BMA 
-construction from (\ref{eq:bma}) may be used only replacing $p_m$ with 
-$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$ -approximate KD and GA densities. 
+
+To build an ensemble model from sample distribution forecasts, the MA 
+construction from (\ref{eq:bma}) may be used only replacing $p_m$ with the
+approximate KD or GA pdf functions
+-$\hat{p}_{n_m}^{KD}$ or $\hat{p}_{n_m}^{GA}$ respectively.  
 Here as well the optimal weights 
-$w_m$ may be estimated by maximizing the likelihood or minimizing CRPS. Then 
-the ensemble distribution would take the form of a continuous or discrete
-probability mixture distribution. If the desire is that the ensemble still be
+$w_m$ may be estimated by maximizing the likelihood or minimizing CRPS. 
+If the desire is that the ensemble still be
 a sample distribution, after selecting weights, a sample may be selected by 
@@
 
-\subsection{Discretized bin distributions}
+\subsection{Bin distributions}
 An alternative to parametric distributions and sample distributions which allows
 for higher flexibility in distribution shape than a parametric distribution and 
-will usually require less storage space than samples is a discretized bin 
+will usually require less storage space than samples is a bin 
 distribution.
 
-A discretized bin probability distribution may be constructed over a set 
-$A = [a, b]$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
+A bin distribution may be constructed over a set 
+$A = [a, b)$ by partitioning $A$ into a set of $K$ bins $\{B_i\}_{i=1}^{K}$
 where $B_i = [b_{i-1}, b_i)$ and $\cup_{i=1}^{K} B_i = A$. Based on the problem
-to be forecasted, researchers will determine the possible range $A$ and 
+to be forecast, researchers will determine the possible range $A$ and 
 select the number of bins and the sizes for each bin. It may be the case
-that a collaborative project will set the width of all bins to be equal so that 
+that a collaborative project will set the widths of all bins to be equal so that 
 $\Delta = b_i - b_{i-1}$ is the same width for all $i$ 
-\cite[see for example]{mcgowan2019collaborative}.
-To complete the construction, a probability $p_i$ is assigned to each $b_i$ 
-where $\sum_{i=1}^{K}p_i = 1$. These probabilities are determined by the 
+\cite[]{mcgowan2019collaborative}.
+To complete the construction, a probability $p_i$ is assigned to each $B_i$ 
+where $\sum p_i = 1$. These probabilities are determined by the 
 forecasters. 
-This discrete representation with a given bin and assigned probability is in
-essence a probability mass function in that the calculation of moments and the 
+This representation with a given bin and assigned probability may be 
+treated like a discrete distribution with a pmf in that the calculations of 
+moments and of the 
 the cumulative distribution are done the same as for a discrete parametric 
-distribution. For a random variable $X$ from a binned distribution to calculate
-the $j^{th}$ moment we may use
+distribution. For a random variable $X$ from a binned distribution 
+the $j^{th}$ moment may be calculated as in \eqref{eq:bev}. 
+Here $\beta_i$ is a value corresponding to bin $B_i$ (such as $\beta_i = b_i$,
+$\beta_i = b_{i-1}$ or $\beta_i$ is the mean or mid value in $B_i$). The 
+cumulative distribution may be calculated as in \eqref{eq:bcdf}.
+Here $p_n$ is the probability for the bin $B_n$ where $b \in B_n$.
 
@@
 \end{equation}
-where $p_n$ is the probability for the bin $B_n$ where $b \in B_n$.
-
-If the value to be forecasted takes on discrete values, a common discrete 
+
+If the value to be forecast takes on discrete values a common discrete 
 distribution, such as a binary or Poisson distribution, may sometimes be used to 
-assign probabilities to each of the bins. When the values to be forecasted are
+assign probabilities to each of the bins. When the values to be forecast are
 continuous, a forecaster may need to employ a method of discretization to a 
 forecast distribution. There are a number of possible ways to do this including
-those outlined by Chakraborty and Subrata \cite{chakraborty2015generating}.
-
-The CDC has used a discretized bin distribution representation as the 
-format
-for their annual influenza forecasting competition and other disease outbreak
+those outlined by Chakraborty and Subrata \cite[]{chakraborty2015generating}.
+
+For several flu seasons now, the CDC flu competition has used a bin distribution 
+as the forecast 
+representation. The CDC has also used it for other disease outbreak
 forecast projects.
 In that context it has become the standard representation 
-\cite{brooks2020comparing}. Much work has been done in evaluating 
+\cite[]{brooks2020comparing}. Much work has been done in evaluating 
 and constructing ensemble models on influenza forecasts represented by 
-discretized bins \cite{mcgowan2019collaborative, mcandrew2019adaptively,reich2019collaborative}.
-
-Because discretized bins can be seen as a pmf, methods for proper scoring 
+discretized bins 
+\cite[]{mcgowan2019collaborative, mcandrew2019adaptively,reich2019collaborative}.
+
+Because a bin distribution can be viewed as a pmf, methods for proper scoring 
 already 
-discussed -LogS and CRPS- are useable and BMA is valid method for ensemble 
-construction. Reich et. al used BMA to combine multiple forecasts from the flu 
-competition. They built and compared ensemble models with different weighting
-schemes including equally weighted components $w_j = 1/J$ and estimating weights
+discussed -LogS and CRPS- are useable and MA is valid method for ensemble 
+construction. Reich et. al used MA to combine multiple forecasts from the flu 
+competition. They constructed and compared ensemble models with different 
+weighting
+schemes including equally weighted components, $w_m = 1/M$,
+and estimating weights
 according to the model specification. To estimate weights they used the 
-Expectation Maximization (EM) algorithm 
+expectation maximization (EM) algorithm 
 \cite[see
@@
 
-The exact amount of information required for a discretized bin forecast will 
+The exact amount of information required for a bin forecast will 
 vary depending on the permitted range of the forecast and the desired 
@@
 In the CDC flu contest, a forecast might have 131 bins between 0\% and 13\% 
--bins having increments of 0.1 or 0.001\%- with 
+-bins having increments of 0.1 or 0.01\%- with 
 corresponding probabilities in each. This makes 262 pieces of information per
 prediction. For any binning scheme of more than two bins, the information 
-requirement for discretized bins will be higher than for parametric distrbutions.
-Table \ref{table:dbins} illustrates what a discretized 
-Lognormal$(1,0.4)$ distribution truncated over $[0,8]$
-looks like in 41 equally spaced discretized bins. The discretization was done
-such that
+requirement for a bin distribution will be higher than for a parametric 
+distribution.
+Table \ref{table:dbins} illustrates what bin distribution which was discretized 
+from a 
+$\mbox{Lognormal(1,0.4)}$ distribution truncated over $[0,8]$
+looks like in 41 equally spaced bins. The discretization was done
+such that the probabilities $p_i$ are calculated as in \eqref{eq:disc}
+where $p^{TL}$ is the pdf of a truncated $\mbox{Lognormal(1,0.4)}$. This is 
+similar
+to Methodology-IV from Chakraborty 
+\cite[]{chakraborty2015generating,kemp2004classes}. The truncation here is done
+because in practice a bin forecast will generally have a finite support.
 
@@
 \end{equation}
-where $p^{TL}$ is the pdf of a truncated Lognormal$(1,0.4)$. This is similar
-to Methodology-IV from Chakraborty 
-\cite{chakraborty2015generating,kemp2004classes}.
+
+Submitted as a forecast prediction, the distribution illustrated in table 
+\ref{table:dbins} 
+includes 82 pieces of data. For parts 
+of the CDC influenza competition some forecasts included up to 262. This is 
+far less storage than the possible thousands of draws from a sample 
+distribution but is 
+still much larger than the three or five pieces of information required to 
+report a 
+lognormal
+or truncated lognormal distribution.
 
 \begin{table}[h!]
-
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \centering
@@
  \end{tabular}
-  \caption[Discretized bin distribution storage]{Storage example of discretized
-  lognormal with $\mu = 1$ and $\sigma = 0.4$}
+  \caption[Bin distribution storage]{This is a storage example of a
+  discretized
+  lognormal with $\mu = 1$ and $\sigma = 0.4$ truncated over $[0,8]$.}
 \label{table:dbins}
+\end{minipage}
+\end{center}
 \end{table}
-Submitted as a forecast prediction, the distribution in table \ref{table:dbins} 
-includes 82 pieces of data. For parts 
-of the CDC influenza competition some forecasts included up to 262. This is 
-far less storage than the possible thousands of draws from a sample 
-distribution but is 
-still much larger than the three or five data pieces required to report a 
-lognormal
-or truncated lognormal distribution.
-
-Depending on what is known about the problem to be solved, creating the right 
+
+Besides the potentially large amount of information required per forecast,
+creating the right 
 binning scheme may be a challenge. Because there must be a finite number of
-bins, forecast distributions often have a finite support. Where the range of 
+bins, forecast distributions often have a finite support. And where the range of 
 possible outcomes to a problem is not well known, the right binning scheme may 
 be
-hard to produce.
-
-\subsection{Quantile representation}
+hard to produce. This may depend on the details of the event to be forecast, 
+but in the case of the COVID-19 outbreak choosing the right set of bins posed
+a few problems.
+
+\subsection{Quantiles}
 When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
-the time pressure of generating forecasts and the consideration of the large
+the time pressure of generating forecasts and the large
 range for possible outcomes both contributed to the COVID-19 Forecast Hub 
 decision
-to forego trying to create the right binning scheme and use sets of prediction
-intervals to represent uncertainty in predictions \cite{bracher2021evaluating}.
-
-The Forecast Hub requires predictions to be submitted as 11 or three nominal 
-intervals -depending on the specific target and unit to forecast- and a median.
-Using this interval or quantile representation leads to a number of changes in 
-the scoring and ensemble building of forecasts.
-
-A quantile forecast is constructed as follows.
-For $N$ given quantiles $\alpha_1,..., \alpha_N$; $q_1,..., q_N$ are the values
-such that
+to forego trying to create the right binning scheme and use quantile forecasts
+to forecast the COVID-19 pandemic \cite[]{bracher2021evaluating}.
+The COVID-19 Forecast Hub requires predictions to be submitted as 11 or three 
+nominal 
+intervals -depending on the specific target and unit to be forecast- 
+and a median.
+Using this quantile representation prevents the use of certain methods for 
+scoring and constructing ensemble forecasts.
+
+A quantile forecast is constructed as in \eqref{eq:quantiles}.
+Here for $N$ given quantiles $\alpha_1,..., \alpha_N$; $q_1,..., q_N$ are the 
+values such that we have \eqref{eq:quantiles}. 
+When the quantiles are reported as prediction intervals we have 
+\eqref{eq:intervals}.
 
@@
 What is possible for scoring forecasts
-or building ensemble models in other representations is often not possible with
-quantile forecasts. The shape of a distribution is also not known and in fact,
+or constructing an ensemble in other forecast representations is often not 
+possible when using
+quantile forecasts. The shape of a distribution is also not known, and in fact
 nothing is known about the tails or the uncertainty beyond the most 
-extreme reported quantile values. In the Forecast Hub predictions, nothing 
+extreme reported quantile values. In the COVID-19 Forecast Hub forecasts, 
+nothing 
 is reported about the range below the $1^{st}$ quantile or above the $99^{th}$.
@@
 
-Quantile representation allows for forecasters to submit fairly detailed
+Quantile forecasts allow for forecasters to submit fairly detailed
 forecasts without restricting the range of possible values.
 Since quantiles are easily calculated from any regular distribution type
--e.g. quantile function for parametric functions or calculating sample 
+-using the quantile function for parametric functions or calculating sample 
 quantiles- we consider quantile forecasts to be highly flexible in terms of 
@@
 the central $(1-\alpha)$ prediction interval the IS is defined as 
-
-\begin{equation}
-\label{eq:is}
-  IS_{\alpha}(l,r; x^*) = (r-l) + \frac{2}{\alpha}(l-x^*)1\{x^*<l\} 
-  + \frac{2}{\alpha}(y-r)1\{x^* > r\}
-\end{equation}
+in \eqref{eq:is}.
 This is a sum -weighted by 
@@
 
-When an interval forecast is made up of multiple intervals each with different
-$\alpha$ levels, the weighted interval score (WIS) may be evaluated. Bracher et.
-al use the WIS to evaluate COVID-19 inverval forecasts 
-\cite{bracher2021evaluating}.
-There are multiple versions of the WIS -some of 
-which are described in Bracher et. al- but the version used by the COVID-19 
+\begin{equation}
+\label{eq:is}
+  IS_{\alpha}(l,r; x^*) = (r-l) + \frac{2}{\alpha}(l-x^*)1\{x^*<l\} 
+  + \frac{2}{\alpha}(x^*-r)1\{x^* > r\}
+\end{equation}
+
+When a quantile forecast is made up of multiple intervals each with different
+$\alpha$ levels, the weighted interval score (WIS) may be used.
+Bracher et.
+al use the WIS to score COVID-19 quantile forecasts 
+\cite[]{bracher2021evaluating}.
+There are multiple versions of the WIS, some of 
+which are described in Bracher et. al, but the version used by the COVID-19 
 Forecast
-Hub for a forecast of $K$ intervals is defined as follows
+Hub for a forecast of $K$ intervals is defined in \eqref{eq:wis}.
+Here $median$ refers to the predictive median and $w_k = \alpha_k/2$ is the 
+weight on the $k^{th}$
+interval. With that selection of weights, it may be shown that the
+WIS approximates the CRPS \cite[see S1 Text therein]{bracher2021evaluating}.
 
@@
 \label{eq:wis}
-  WIS_{0,K}(F_m,y^*) = \frac{1}{K + 1/2} \times (w_0, \times |y^*-med|+
-  \sum_{k=1}^K \{ w_k \times IS_{\alpha_k}(F_m,y) \} )
-\end{equation}
-where $w_k = \alpha_k/2$ is the weight on the $k^{th}$
-interval. With that choice of weights, it may be shown that the
-WIS approximates the CRPS \cite[see S1 Text therein]{bracher2021evaluating}.
-
-Bogner, Liechti and Zappa compared scoring forecasts of quantiles with the 
+  WIS_{0,K}(F_m,x^*) = \frac{1}{K + 1/2} \times (w_0, \times |x^*-median|+
+  \sum_{k=1}^K \{ w_k \times IS_{\alpha_k}(F_m,x^*) \} )
+\end{equation}
+
+Bogner, Liechti, and Zappa compared scoring forecasts of quantiles with the 
 Quantile Score (QS) similar to the interval score and scoring distribution functions
-fit to those quantiles using the CRPS \cite{bogner2017combining}. The CRPS 
+fit to those quantiles using the CRPS \cite[]{bogner2017combining}. The CRPS 
 corresponds to the integral of the QS over all possible thresholds rather than
@@
 ensemble forecast.
-The ensemble forecast constructed by the COVID-19 Forecast Hub was made as an
+The ensemble forecast constructed by the COVID-19 Forecast Hub is made as an
 equally-weighted average of forecasts from the component models. More 
-specifically, each quantile value of the ensemble was the average of values from
-all models corresponding to the same quantile \cite{ray2020ensemble}. For $M$ 
+specifically, each quantile value of the ensemble is the average of values from
+all models corresponding to the same quantile \cite[]{ray2020ensemble}. For $M$ 
 models each with $K$ quantiles, the $k^{th}$ ensemble quantile $q^E_k$ is 
-calculated as
-
-\begin{equation}
-\label{eq:qa}
-  q^E_k = \sum_{m=1}^M \nu_m q_k^m 
-\end{equation}
+calculated as in \eqref{eq:qa}
 where $\nu_m$ is the weight assigned to each forecast and $\sum \nu_m = 1$. In
-the Forecast Hub model, $\nu_m = \nu = 1/M$. Where the overall mean or a
-weighted mean may be used, the median may also be used.
+the COVID-19 Forecast Hub model, $\nu_m = \nu = 1/M$. Where the overall mean or 
+a weighted mean may be used for averaing, the median may also be used.
 Brooks et. al compare performance of the COVID-19 ensemble
-between equally-weighted means, weighted means and median value constructions.
-\cite{brooks2020comparing} (is is appropriate to cite this blog??)
+using equally-weighted means, weighted means, and median value constructions
+\cite[]{brooks2020comparing}.
 In their report, they show that weighted means and median constructions tend
@@
 
-Averaging quantiles in this way is the same as quantile averaging or Vincentization
-only with an incomplete quantile function. It thus carries with it many of the
-same characteristics.
-Quantile averaging or Vincentization for a complete distribution is defined as
-
-\begin{equation}
-\label{eq:vinc}
-  F_v^{-1}(\alpha) = \sum_{m=i}^M w_m F_m^{-1} (\alpha)
-\end{equation}
+\begin{equation}
+\label{eq:qa}
+  q^E_k = \sum_{m=1}^M \nu_m q_k^m 
+\end{equation}
+
+More generally, quantile averaging or Vincentization for a complete distribution 
+is defined as
+in \eqref{eq:vinc}
 where $F_m^{-1} (\alpha) = \inf \{y:F_m(y) \geq \alpha\}$ for 
@@
 the ensemble distribution
-to be unimodal than it is under linear averaging of densities like BMA 
-\cite{busetti2017quantile} Under some circumstances, such as when member
-distributions are exponential, Weibull or logisitic the aggregated distribution
-is the same \cite{ratcliff1979group}. It produces smoother
-distributions than BMA according to Schepen and Wang \cite{schepen2015model}.
-Lichtendahl et. al conclude that quantile averaging produces sharper forecasts
-and tends to perform better in scoring than probability averaging
-\cite{lichtendahl2013better}.
-
-As in sample distributions and binned distributions, 
+to be unimodal than it is under linear averaging of densities like MA 
+\cite[]{busetti2017quantile}. Under some circumstances, such as when member
+distributions are exponential, Weibull, or logisitic the aggregated distribution
+is of the same family \cite[]{ratcliff1979group}. Quantile averaging produces 
+smoother
+distributions than MA according to Schepen and Wang \cite[]{schepen2015model}.
+And Lichtendahl et. al conclude that quantile averaging produces sharper 
+forecasts
+and tends to perform better in scoring than probability averaging like MA
+\cite[]{lichtendahl2013better}.
+
+\begin{equation}
+\label{eq:vinc}
+  F_v^{-1}(\alpha) = \sum_{m=i}^M w_m F_m^{-1} (\alpha)
+\end{equation}
+
+As in sample distributions and bin distributions, 
 data storage for interval forecasts will
 depend on the desired clarity of resolution. For the COVID-19 forecasts 
-submitted to the Forecast Hub, 23 quantile values are requested for 
-the quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This included a 
-median along with eleven confidence intervals \cite{bracher2021evaluating}. This
-requires forecasters to submit 46 values in each short-term forecast 
+submitted to the COVID-19 Forecast Hub, 23 quantile values are requested for 
+quantiles (0.01, 0.025, 0.05, 0.10, …, 0.95, 0.975, 0.99). This includes a 
+median along with 11 predictive intervals \cite[]{bracher2021evaluating}. 
+Forecasters are thus required to submit 46 values in each short-term forecast 
 (some of the longer term forecasts only include seven quantiles). In terms of 
-storage, this is an improvement over requirements for the flu contest. Table
+storage, this is an improvement over requirements for the CDC flu competition. 
+Table
 \ref{table:qstor} shows what a submission of 23 quantiles from a 
-$Lognormal(1,0.4)$ looks like.
+$\mbox{Lognormal(1,0.4)}$ truncated on $[0,8]$ might look.
 
@@
  \end{tabular}
- \caption[Quantile/interval and values storage]{Storage example of quantiles 
- and values of lognormal with $\mu = 1$ and $\sigma = 0.4$}
+ \begin{minipage}{10cm}
+ \caption[Quantile storage]{This shows six quantiles
+ and values from a lognormal distribution with $\mu = 1$ and $\sigma = 0.4$}
  \label{table:qstor}
+ \end{minipage}
+ \end{center}
 \end{table}
 
+Figure \ref{fig:denscomp} illustrates how the densities and CDFs compare 
+between parametric distributions, sample distributions, bin distributions, and
+quantiles.
+
 \begin{figure}[htbp]
+\begin{center}
+
+\captionsetup{font=scriptsize}
 \centerline{\includegraphics[scale=.1]{Images/dens_cum_comp.png}}
+\begin{minipage}{10cm}
 \caption[Density/CDF comparison between parametric distribution, sample 
@@
 densities and CDFs of forecast representation types discussed in the left and 
-right columns respectively. Each is generated from a lognorma(1,0.4) 
-distribution. Blue shows the density and CDF functions. Purple shows a 
+right columns respectively. Each is generated from a Lognorma(1,0.4) 
+distribution truncated on $[0,8]$. 
+Blue shows the density and CDF functions. Purple shows a 
 histogram and ECDF of 1,000 samples. Red shows bin probabilities and the CDF
-function. Green shows quantiles/intervals with corresponding values.}
+function for a bin distribution. Green shows quantiles
+with corresponding values.}
 \label{fig:denscomp}
+\end{minipage}
+\end{center}
 \end{figure}
 
-\section{Discrete mixture of parametric distributions}
-A discrete mixture of parametric distributions forecast representation may be an
-attractive alternative to the four types already discussed. A discrete mixture 
-would allow for many distribution shapes, a high resolution, storage comparable
-to that of discretized bins and quantile representations and the use of the more
-common methods for scoring and ensemble building.
-
-A discrete mixture distribution may be constructed in the same way as the
-ensemble described in section \ref{section:pardist} in equation 
+\newpage
+
+\section{Mixture distributions}
+A mixture distribution forecast representation is an
+attractive alternative to the four representations already discussed. 
+A mixture distribution forecast
+would allow for a large range of distribution shapes, a high resolution, 
+storage comparable
+to that of bin and quantile forecasts, and ensemble construction using MA.
+A mixture distribution may be constructed in the same way as the
+ensemble described in section \ref{section:pardist} 
 (\ref{eq:bma}) 
 where for $T$ distributions
-with pdfs $p_t(x)$ and $z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$
+with pdfs $p_t(x)$ and $z_t > 0$ and $\sum z_t = 1$ we have 
+\eqref{eq:dmd}.
 
@@
 
-Like the standard parametric model, a discrete mixture may be evaluated with
-exisiting software (like distr \texttt{R} package \cite{camphausen2007distr}). 
+Like a parametric distribution, a mixture distribution may be evaluated using
+existing software like the \texttt{distr} package in \texttt{R} 
+\cite[]{camphausen2007distr}. 
 And 
-scoring may be done by 
-using the LogS, CRPS and IS. The resolution of a discrete mixture is infinite 
-and the support need not be limited by submission requirements.
-
-A mixture distribution may be much more flexible than a single component 
+scoring may be done  
+using the LogS, CRPS, and IS. A mixture distribution, like its parametric 
+distribution components, has an infinite resolution.
+A mixture distribution may be more flexible than a single component 
 parametric distribution in 
-terms of distributional shape. According to 
-McLachlan and Peel, a finite mixture of 
+terms of distribution shape. According to 
+McLachlan and Peel, a mixture of 
 normal densities with common variance can be used to approximate arbitrarily 
 well
-any continuous distribution \cite{peel2000finite} (see also 
-\cite{nguyen2019approximations}). Thus, for an unconventional probability
+any continuous distribution \cite[]{peel2000finite} (see also 
+\cite[]{nguyen2019approximations}). Thus, for an unconventional probability
 distribution -such as MCMC posterior samples- it may be reasonable to 
-approximate the distribution by constructing a mixture of normals.
-% See section \ref{section:conmix} for an example.
-
-An ensemble model may be built by using (\ref{eq:bma}) only replacing $p_m$
-with $p_m^M$ in \ref{eq:dmd}. Solving for weights may also be done similarly, 
-though with the 
+approximate the distribution by fitting those samples to a mixture of normal
+distributions.
+Depending on the number of components a forecaster includes in a mixture 
+forecast, the amount of storage per forecast might be as little as for a 
+parametric forecast or as much as is permitted permitted in the specific 
+collaborative forecast project.
+
+An ensemble model may be constructed by using \eqref{eq:bma} only replacing 
+$p_m$
+with $p_m^M$ from \eqref{eq:dmd}. Solving for weights may also be done by 
+maximizing
+the likelihood of the forecast or minimizing the CRPS. However with the 
 added complexity of component models being mixture distributions the 
-computation is likely to be more expensive. An example where this may be
-especially true is when minimizing of CRPS, but the exact mixture doesn't 
-result in CRPS in closed form \cite{baran2018combining}. In large projects like
+computation is likely to be more expensive. An example where this is
+true is when minimizing the CRPS when the exact mixture distribution doesn't 
+produce a closed form CRPS \cite[]{baran2018combining}. In large projects like
 the COVID-19 Forecast Hub, if an equal weight is not assigned to each component,
@@
 
-Depending on the number of components a forecaster includes in a mixture 
-forecast, the amount of storage per forecast might be as little as for a 
-parametric forecast and as much as a forecast hub will allow. In section
+Table \ref{table:repscomp} shows how a mixture distribution forecast 
+compared with the other formats discussed in terms of methods for scoring,
+information and resolution provided, methods for ensemble building, and computer
+storage requirement. To summarize, a continuous mixture distribution has the 
+infinite resolution of a parametric distribution with the flexibility of a bin
+distribution, a sample distribution, and a set of quantiles. The common proper
+scoring rules LogS and CRPS may be used to score a mixture forecast. 
+The storage requirement is
+comparable to that of a bin distribution or a set of quantiles. And MA may be 
+used for building an ensemble.
+In Section
 \ref{section:conmixforc} we show how a mixture distribution may be constructed,
-scored and used to construct an ensemble using software available in 
+scored, and used to construct an ensemble using software available in 
 \texttt{R}.
 
-Table \ref{table:repscomp} shows how a discrete mixture distribution forecast 
-compares with the other formats discussed in terms of methods for scoring,
-information and resolution provided, methods for ensemble building and computer
-storage requirement.
-
 \begin{flushleft}
+
   \begin{table}
-    % \begin{adjustwidth}{-3cm}{-1cm}
-    \begin{tabular}{ | p{2.4cm} || p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
+   \begin{adjustwidth}{-1cm}{-1cm}
+    \begin{tabular}{ | p{2.9cm} || p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
     \hline
@@
 
-    Parametric & LogS, CRPS, IS & Limited to common distribution families. 
+    Parametric distribution & LogS, CRPS, IS & Limited to common 
+    distribution families. 
     Infinite resolution
-    & BMA & Low 3-6 values per prediction \\ \hline
-
-    Samples & CRPS and IS. LogS after smoothing & Any shape. Resolution may be
-    very high but depends on sample size & BMA after smoothing. Resampling 
+    & MA & Low 3-6 values per prediction \\ \hline
+
+    Sample distribution & CRPS and IS. LogS after smoothing & Any shape. 
+    Resolution may be
+    very high but depends on sample size & MA after smoothing. Resampling 
     otherwise & 
@@
 
-    Discretized bins & LogS, CRPS, IS &
+    Bin distribution & LogS, CRPS, IS &
     Any shape allowed, but limited by binning scheme. Range also may be limited
-    & BMA &
+    & MA &
     Depends on binning scheme but dozens to hundreds of values
@@
     Quantile averaging & Depends on 
-    requested quantiles. Perhaps dozens of values
+    quantiles requested, but dozens of values
     \\ \hline
 
-    Discrete Mixture & LogS, CRPS, IS. May be more limited by computation & With
-    enough component distributions may
-    approximate any distribution shape. Infinite resolution& BMA 
+    Mixture distribution & LogS, CRPS, IS. May be more limited by computation & 
+    With a sufficient number of
+    component distributions, it may
+    approximate any distribution shape. Infinite resolution& MA 
     & 3 values to dozens per forecast depending on number of components
@@
 	 \end{tabular}
-	 % \end{adjustwidth}
+	 \end{adjustwidth}
+	  \begin{center}
+    \begin{minipage}{14cm}
+    \captionsetup{font=scriptsize}
    \caption[Forecast representation comparison]{This table compares scoring,
-   information, ensemble building and storage requirements for the different
-   forecast representations discussed.}
+   information, ensemble building, and storage requirements for the different
+   forecast representations discussed. To summarize 
+   a continuous mixture distribution has the 
+infinite resolution of a parametric distribution with the flexibility of a bin
+distribution, a sample distribution, and a set of quantiles. The common proper
+scoring rules LogS and CRPS may be used to score a mixture forecast. 
+The storage requirement is
+comparable to that of a bin distribution or a set of quantiles. And MA may be 
+used for building an ensemble.}
    \label{table:repscomp}
+   \end{minipage}
+   \end{center}
    \end{table}
@@
 a few adjustments to those systems. In this section we outline how some of these
-adjustments may be implemented as well as present some tools which may be used
-to score forecasts and construct ensembles from multiple models.
+adjustments may be implemented. As well we present tools which may be used
+to build forecasts from submissions, score those forecasts, and construct 
+ensembles from them.
 
 \section{Submission format}
-For a collaborative forecast project to run smoothly, model submissions from all 
-modelers should follow the same format. For both the CDC flu competition and
-the COVID-19 Forecast Hub, teams provide a \texttt{.csv} spreadsheet with 
-columns 
-similar to those in tables \ref{table:dbins} and \ref{table:qstor}. Additionally
-columns for \texttt{location}, \texttt{target}, \texttt{type}, and \texttt{unit} 
-are included.
+For a collaborative forecast project to run smoothly, forecast submissions from 
+all forecasters 
+should follow the same format. For both the CDC flu competition and
+the COVID-19 Forecast Hub, teams provide a \texttt{.csv} spreadsheet which 
+contains the distributional information for one or multiple forecasts. Tables
+\ref{table:dstan} and \ref{table:qstan} show what variables are included in 
+those submissions and a
+couple rows to illustrate possible values.
+The column variables include \texttt{location}, \texttt{target}, \texttt{type},
+\texttt{unit}, \texttt{bin} or \texttt{quantile}, and \texttt{value}.
 Here \texttt{location} defines the specific county, state, or country of the 
-forecast. The \texttt{target} variable defines what is forecasted for example
+forecast. The \texttt{target} variable defines what is forecast with levels
 season onset, deaths, hospitalizations, etc. The \texttt{type} variable defines
-the type for the \texttt{value} variable, \texttt{bin} or \texttt{quantile}.
-The \texttt{unit} variable defines the time frame of the forecast: week,
-two weeks, four weeks, etc. And the \texttt{value} variable is a number that 
-either gives probability for a bin or the value for a quantile. Table
-\ref{table:dstan} show what a few rows of a forecast 
-submission file for the CDC flu competition look like.
-For the quantile forecasts of the Forecast Hub, the main changes to Table
-\ref{table:dstan} are that the possible values for \texttt{type} 
-quantile, and rather than using a \texttt{bin} variable \texttt{quantile} is 
-used
-with values specified by the Hub. This is seen in Table \ref{table:qstan}
-
-A single submission may include many forecasts each aimed at predicting a 
-different combination of \texttt{location}, \texttt{target}, and \texttt{unit}. 
+the type for the \texttt{value} variable with levels of point, 
+bin, or quantile.
+The \texttt{unit} variable defines the time frame of the forecast with levels of
+week,
+two weeks, four weeks, etc. The variables \texttt{bin} and \texttt{quantile}
+give a specific bin or a specific quantile. The \texttt{value} variable is a 
+number that 
+either gives the probability associated with a bin or the value associated 
+with a quantile.
+
+A single submission may include many forecasts aimed at forecasting 
+different combinations of \texttt{location}, \texttt{target}, and \texttt{unit}. 
 A set of rows which share
@@
 
-In the mixture distribution format, an adjustment may be made to the format of 
-Tables
-\ref{table:dstan} and \ref{table:qstan} where each 
-row
-represents a component in a mixture distribution.
-The variables Bin/Quantile and Value are removed and replaced with Family,
-Param1, Param2 and Weight where Family is the distribution family,
-Params are the parameters for the component distribution and Weight is the 
-weight $w_i$ for that component.
+Table \ref{table:mstan} illustrates adjustments made to the submission formats
+from 
+Tables \ref{table:dstan} and \ref{table:qstan} which make a usable submission 
+format for mixture distribution forecasts. In such a format, each row represents
+one component distribution used in a mixture distribution.
+The variables \texttt{bin} or \texttt{quantile} and \texttt{value} are removed 
+and replaced with \texttt{family},
+\texttt{param1}, \texttt{param2}, and \texttt{weight} where \texttt{family} is 
+the distribution family of the component,
+\texttt{param1} and \texttt{param2} are the parameters for the component 
+distribution, and \texttt{weight} is the 
+weight $w_i$ for the $i^th$ component.
 
@@
     \\ \hline
-    US National & Season Onset & Dist & week & norm & $\mu_n$ & $\sigma_n$ & .\\
-    US National & Season Onset & Dist & week & lnorm & $\mu_l$ & $\sigma_l$ &.\\
-    ... & ... & ... & ... & ... & ... & ... & .\\
+    us national & season onset & dist & week & norm & $a_n$ & $b_n$ & $w_1$\\
+    us national & season onset & dist & week & lnorm & $a_l$ & $b_l$ & $w_2$\\
+    ... & ... & ... & ... & ... & ... & ... & ...\\
  \hline
  \end{tabular}
- \caption[Mixture distribution forecast submission example]{Example of a 
+ \begin{minipage}{11cm}
+\captionsetup{font=scriptsize}
+ \caption[Mixture distribution forecast submission example]{This is an example 
+ of a 
  submission file
- for a disease outbreak forecast using mixture distribution representation}
+ for a disease outbreak forecast using a mixture distribution representation.
+ Each row represents a component distribution
+ of a mixture distribution. The variables
+ location, target, and unit specify what is being forecast. The variable type
+ specifies that the row represents a parametric distribution. The variables
+ family, param1, and param2 specify the exact component distribution. 
+ And the variable 
+ weight specifies the weight $w_i$ that the $i^th$ component distribution is
+ assigned in the
+ mixture distribution. Here two components are shown with distributions
+ Normal$(a_n, b_n)$, Lognormal$(a_l, b_l)$ and weights $w_1$ and $w_2$.}
  \label{table:mstan}
+ \end{minipage}
 \end{table}
 
-A forecast center may want to limit the number of components allowed per 
-prediction. For reference, a mixture distribution prediction following the 
-format in table \ref{table:dstan} with 18 
-components would require $18 \times 8 = 144$ cells submitted. This is the same 
-number of cells
-submitted for a Forecast Hub forecast with 23 quantiles and a point prediction 
-according to the format in table \ref{table:dstan}.
-
-Throughout the remainder of this section, explanations of how to work with 
-mixture distributions along with \texttt{R} code which will be given to 
-demonstrate constructing a mixture distribution from a forecast submission, 
-scoring the forecast and building an ensemble forecast.
+For reasons of storage and computation, a forecast project may have a limit to 
+the number of components allowed per forecast.
+For reference, a mixture distribution forecast following the 
+format in table \ref{table:dstan} with 17
+components would require $17 \times 8 = 136$ pieces of information
+submitted per forecast. 
+A submission to the COVID-19 Forecast Hub forecast with 23 quantiles
+according to the format in table \ref{table:dstan} requires
+$23 \times 6 = 138$ cells. Thus if the COVID-19 Forecast Hub were to change the
+forecast representation from quantile forecasts to mixture forecasts but 
+continue allowing the same amount of data per forecast, 
+a mixture distribution with 17 components could be used in one forecast. That
+many components could allow for a large range of distribution shapes and 
+flexible forecasts.
+
+In the remainder of this section, explanations of how to work with 
+mixture distributions submitted according to Table \ref{table:mstan} are 
+given. Also given is
+\texttt{R} code which 
+demonstrates constructing a mixture distribution from a forecast submission, 
+scoring the forecast, and building an ensemble from two separate submissions.
 
@@
 
-From a submitted forecast, a prediction may be found by Location, Target and 
-Unit (or whatever other indication variables are used by collaborators) and 
-evaluated. We found
-the \texttt{distr} package \cite{camphausen2007distr}
-useful for constructing a mixture distribution given
-information like that from table \ref{table:dstan}.
-
-The function 
-\texttt{UnivarMixingDistribution} takes as arguments a list of distributions
+A single \texttt{.csv} submission file of the format in Table \ref{table:mstan} 
+may contain multiple forecasts forecasting different combinations of location,
+target, and unit. Selecting only rows which share a specific combination of 
+location, target, and unit will produce a table representing a single forecast.
+That table may look like Tables \ref{tab:preddf1} and 
+\ref{tab:preddf2}. If the table is saved as a standard \texttt{data.frame} in 
+\texttt{R}, then tools based on the \texttt{distr} package 
+\cite[]{camphausen2007distr} may be used for evaluating a mixture distribution 
+with the component distributions in the table.
+
+The \texttt{distr} package contains a function 
+\texttt{UnivarMixingDistribution()} which takes as arguments a list of 
+distributions
 and a vector of weights for each distribution and a object of class 
-\texttt{AbscontDistribution} is returned. The object is in essence a mixture
-distribution of the form of (\ref{eq:dmd}). Functions for density, 
-distribution
-and quantile functions as well as for random sampling may then be used on the
-mixture distribution object for evaluation. Using those functions and the 
-created object, LogS and CRPS are easily calculable.
-
-We wrote a function \texttt{MakeDist} (see Appendix)
-which takes on a data frame with variables
-Family, Param1, Param2, Param3 and Weight and returns a mixture distribution 
-of component distributions specified in the rows.
-
-Beginning with two forecast submissions of the form of table \ref{table:dstan}, 
-say we select from each a prediction of an event for the same location, target
-and unit. The following two data frames \texttt{preddf1} and \texttt{preddf2}
-are the resulting predictions.
+\texttt{AbscontDistribution} is returned. An \texttt{AbscontDistribution} class
+is a mother class which defines a random number generator, pdf,
+CDF, and quantile function for continuous distributions from common
+families contained in the \texttt{distr} package
+and for mixture distributions with 
+component distributions from those families.
+We wrote a function \texttt{MakeDist()} (see APPENDIX)
+which takes on a \texttt{data.frame} with variables
+family, param1, param2, param3, and weight and where each row represents a
+component distribution in a mixture distribution. The function 
+\texttt{MakeDist()} calls on the \texttt{UnivarMixingDistribution()} function
+and returns a mixture distribution object of class \texttt{AbscontDistribution}.
+
+If a forecast such as in Table \ref{tab:preddf1} is taken as an argument in 
+\texttt{MakeDist()}, the resulting mixture distribution may then be evaluated 
+with functions for the pdf, CDF, quantile function, and random samples from the
+mixture distribution may be drawn. The distribution may then be scored using the
+LogS or CRPS.
 
@@
  \end{tabular}
- \caption[Toy prediction 1]{Toy prediction 1}
+  \begin{minipage}{11cm}
+\captionsetup{font=scriptsize}
+ \caption[Illustrative forecast 1]{This is an illustrative example of a
+ mixture distribution
+ forecast where the distribution is described in a data frame. The first 
+ component is a Lognormal$(2,1)$ with a weight of 0.3 in the mixture and the 
+ second component is a Normal$(2.1,1)$ with a weight of 0.7. The distribution
+ family abbreviations are capitalized here because that is how they will be
+ requested in the \texttt{MakeDist()} function. Refer to Table
+ \ref{table:mixfams} in the APPENDIX for more details. }
  \label{tab:preddf1}
+ \end{minipage}
 \end{table}
@@
  \end{tabular}
- \caption[Toy prediction 2]{Toy prediction 2}
+  \begin{minipage}{11cm}
+\captionsetup{font=scriptsize}
+ \caption[Illustrative forecast 2]{This is a second
+ illustrative example of a mixture distribution
+ forecast where the distribution is described in a data frame. The first 
+ component is a Normal$(1.5,1)$ with a weight of 0.4 in the mixture and the 
+ second component is a Normal$(4,2)$ with a weight of 0.6.
+ The distribution
+ family abbreviations are capitalized here because that is how they will be
+ requested in the \texttt{MakeDist()} function. Refer to Table
+ \ref{table:mixfams} in the APPENDIX for more details.}
  \label{tab:preddf2}
+ \end{minipage}
 \end{table}
 
-The code here shows these two data frames and how the \texttt{MakeDist} 
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=.15]{Images/toyfors12.png}}
+\begin{center}
+ \begin{minipage}{11cm}
+\captionsetup{font=scriptsize}
+\caption[Example mixture distributions]{These plots show the density functions 
+of
+the two example mixture distribution forecasts along with the component density
+functions scaled by the corresponding weights}
+\label{fig:toymixs}
+\end{minipage}
+\end{center}
+\end{figure}
+
+Here we include code to illustrate the process of constructing and scoring two 
+separate forecasts. We suppose that Table \ref{tab:preddf1} represents a 
+submitted forecast from one forecaster and Table \ref{tab:preddf2} represents
+a forecast of the same event from a second forecaster. Table \ref{fig:toymixs}
+shows plots of the pdfs for both mixture forecasts.
+Note the additional \texttt{param3} variable
+in Tables \ref{tab:preddf1} and \ref{tab:preddf1}. This variable is included
+in the table because of the functionality of the \texttt{MakeDist()} function
+which allows for component distributions of up to three parameters.
+The code here shows these two forecasts as \texttt{data.frame}s and how the 
+\texttt{MakeDist()} 
 function is used to create the distributions in \texttt{R}. Once the 
-distributions are created as \texttt{AbscontDistribution} classes, then 
+distributions are created as \texttt{AbscontDistribution} objects, then 
 functions for evaluating a pdf and a CDF for each are created.
 
-<<eval = FALSE>>=
+<<echo=FALSE>>=
+source('../code/makemixdist.R')
+source('../code/crps.R')
+
+preddf1 <- data.frame(family=c('Lnorm','Norm'),param1= c(2,2.1), param2=c(1,1),
+                     param3=NA,weights=c(.3,.7))
+
+preddf2 <- data.frame(family=c('Norm','Norm'),param1= c(1.5,4), param2=c(1,2),
+                     param3=NA,weights=c(.4,.6))
+ob <- 3
+@
+
+<<>>=
 preddf1
-#  family param1 param2 param3 weights
-#1  Lnorm    2.0      1     NA     0.3
-#2   Norm    2.1      1     NA     0.7
-
 preddf2
-#  family param1 param2 param3 weights
-#1   Norm    1.5      1     NA     0.4
-#2   Norm    4.0      2     NA     0.6
 
@@
 mdist2 <- MakeDist(preddf2)
-
+@
+
+<<>>=
 #make pdfs for mixture predictions
@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics[scale=.15]{Images/toyfors12.png}}
-\caption[Toy mixture distributions]{These plots show the density functions of
-the two toy mixture distribution forecasts along with the component density
-functions scaled by the corresponding weights}
-\label{fig:toymixs}
-\end{figure}
-
 The LogS or the CRPS may then be calculated for each forecast using the pdf
-and cdf functions respectively. Here will will assume that the realized value
-which both forecasts attempted to predict was 3. The \texttt{CRPS()} function 
-here is 
-included in the appendix of this manuscript. It can be seen here that by the 
-LogS, the forecast from table \ref{tab:preddf1} outperforms that from table
-\ref{tab:preddf2}. Yet under the CRPS the performance is the other way around.
-
-<<eval=FALSE>>=
+and CDF functions respectively. Here will will assume that the realized value
+which both forecasts attempted to predict was \texttt{3}. 
+The \texttt{CRPS()} function
+here is one that we wrote and is
+included in the APPENDIX. It is seen in the code below that under the
+LogS, forecast 1 from table \ref{tab:preddf1} outperforms forecast 2 from table
+\ref{tab:preddf2} with scores of \Sexpr{round(-log(dmdist1(ob)),3)} and 
+\Sexpr{round(-log(dmdist2(ob)),3)} respectively. 
+However, under the CRPS forecast 2 outperforms forecast 1
+with scores \Sexpr{round(CRPS(pmdist1,y=ob),3)} and 
+\Sexpr{round(CRPS(pmdist1,y=ob),3)} respectively. We continue to use these same
+forecasts in Section \ref{section:enscon} to construct an ensemble forecast.
+
+<<>>=
 #realized observation
@@
 #LogS for predictions at the realized observation
--log(dmdist1(ob)) # => 1.547238
--log(dmdist2(ob)) # => 1.848796
-
+-log(dmdist1(ob))
+-log(dmdist2(ob))
+@
+
+<<>>=
 #CRPS for predictions at the realized observation
-CRPS(pmdist1,y=ob) # => 0.6348212
-CRPS(pmdist2,y=ob) # => 0.5306083
+CRPS(pmdist1,y=ob)
+CRPS(pmdist2,y=ob)
 @
@@
 \section{Ensemble construction}
+\label{section:enscon}
 
 To construct an ensemble distribution from multiple mixture distributions, the 
-\texttt{UnivarMixingDistribution} is again a useful tool. The function takes 
+\texttt{UnivarMixingDistribution()} function may be used. The function takes 
 two or more
-\texttt{AbscontDistribution} or mixture distributions and a vector of weights 
-corresponding to each mixture. A new \texttt{AbscontDistribution} object is 
-returned as an ensemble of mixture distributions see (\ref{eq:bma}).
-
-At the onset of a collaborative forecast before the various models can be scored
-based on true observations, it may make sense to assign equal weight to each 
+\texttt{AbscontDistribution} distribution objects, including mixture 
+distribution objects, and a vector of weights 
+corresponding to each object. A new \texttt{AbscontDistribution} object is 
+returned as an ensemble of mixture distributions as in (\ref{eq:bma}). 
+Since they are \texttt{AbscontDistribution} objects, \texttt{mdist1} and 
+\texttt{mdist2} created in the code
+in Section \ref{section:tools} may be input as arguments into the function
+\texttt{UnivarMixingDistribution()}, but weights for each object need to also
+be determined.
+
+At the onset of a collaborative forecast before there are true event 
+observations which the forecasts may be scored on, 
+it may make sense to assign an equal weight to each 
 component distribution in an ensemble. As a project progresses however, 
@@
 If we have $T$ models ($M_t$) the posterior model probability of $M_t$ is 
-defined as
+defined as in \eqref{eq:pmp} where $p(\cdot |M_t) := p_m(\cdot)$ is the pdf 
+of the model distribution and 
+$p(M_j)$ is the prior probability assigned to the model. A common approach is to
+assume the prior
+probabilities for each model are equal or $p(M_t) = 1/T$ for all $t$ in which 
+case
+(\ref{eq:pmp}) is reduced to \eqref{eq:pmpeq}. In this case the posterior model 
+probability for the $t^th$ model is equal to the exponential of its negative 
+LogS or
+$p(M_t|x) = e^{-LogS(p(M_t|x))}$, so the performance of a forecast based on the
+LogS is directly related to its posterior model probability and may be used 
+as an 
+ensemble weight. For an observed event $x^*$, ensemble weights $(w_t)$ from 
+\eqref{eq:bma} may be defined as $w_t := p(M_t|x^*)$.
 
@@
 
-The posterior model probability $p(M_t|x^*)$ for an already observed event $x^*$
-are then used as weights for a yet unrealized event being forecasted i.e.
-$w_t := p(M_t|x^*)$ see (\ref{eq:bma}).
-
-From the same toy problem in the previous section, the following code shows how
-to use the posterior model probability to select weights and construct an 
-ensemble distribution and score the ensemble forecast. The ensemble distribution
+Using the illustrative example from Section \ref{section:tools}, 
+the following code shows how
+to use the posterior model probability to select weights, construct an 
+ensemble distribution, and score the ensemble forecast. Here again we take the 
+observed event value to be \texttt{3}.
+The ensemble distribution
 with components is show in figure \ref{fig:mixense}.
 
-<<eval=FALSE>>=
+<<>>=
 #posterior model probability for calculating weights
@@
 w2 <- 1-w1
-#w1 => 0.5286434
-#w2 => 0.4713566
+w1
+w2
 
@@
 #LogS for predictions at the realized observation
--log(densdist(ob)) # => 1.678156
+-log(densdist(ob))
 
 #CRPS for predictions at the realized observation
-CRPS(pensdist,y=ob) # => 0.5486368
+CRPS(pensdist,y=ob)
 @
@@
 \centerline{\includegraphics[scale=.15]{Images/mix_ense.png}}
-\caption[Toy ensemble forecast]{Toy ensemble forecast with component mixture
-distributions shown}
+\begin{center}
+ \begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
+\caption[Example ensemble forecast]{Ensemble forecast made from forecast 1 and 
+forecast 2 from Section \ref{section:tools}. The green line is the density 
+component of mixture forecast 1 with weight \Sexpr{round(w1,3)}. The 
+red line is the density component of mixture forecast 2 with weight 
+\Sexpr{round(w2,3)}. The blue line is the density of the ensemble forecast.}
 \label{fig:mixense}
+\end{minipage}
+\end{center}
 \end{figure}
@@
 representation formats for forecasting, it may be difficult for individual
-forecast teams to adjust to a discrete mixture distribution format. Exact 
-methods for modeling and forecasting may not cater well to submitting a forecast
-as a discrete parametric mixture distribution.
-
+forecast teams to adjust to a mixture distribution format. There may be several
+reasons for this, including that not all 
+forecast modeling methods will produce forecasts which may conveniently be
+represented by a mixture distribution.
 In this section we attempt to assess whether or not any forecasts from the CDC
-influenza forecast competition and the COVID-19 Forecast Hub were generated from
-common continuous parametric distributions. The forecasts we assess are in the 
-forms of discretized bin predictions or sets of predictive intervals. In these
-formats, not knowing anything about distributions or samples,  formal 
-statistical methods for fitting to parametric distributions 
-and assessing fit do not exist. Thus any results stated here may not be stated
-in terms of statistical certainty.
-
-\section{CDC Influenza like Illness}
-The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
-850,000 probabilistic influenza-like illness predictions for all combinations
-of eleven regions 
-in the United States and seven targets from twenty-seven different models. These
-include predictions during Influenza season between October 2010 and December
-2018. All predictions are in the form of discretized probability bins.
-
-We wanted to determine whether or not some or any of these binned forecasts were
-generated from known uniform, normal, 
-lognormal or gamma continuous distribution families. 
-The process we followed for making such a claim was
-to fit a distribution to the probabilities provided in the forecast by
-minimizing
-
-\begin{equation}
-  \sum_{i=1}^K (p_i - [F(b_i; \theta) - F(b_{i-1}; \theta)])^2
-  \label{eq:mds}
-\end{equation}
-
-Here $F(\cdot; \hat{\theta})$ is a CDF, $p_i$ is the reported probability for 
-the $i^{th}$ bin $B_i := [b_{i-1}, b_i)$ and $K$ is the number of bins.
+flu competition and the COVID-19 Forecast Hub were generated from one component
+mixture distribution models. We do this by fitting one component mixture 
+distributions to the forecasts and assessing how well the fit models represent
+the forecasts.
+
+Forecasters in both the CDC flu competition and the COVID-19 Forecast Hub do 
+not include with their forecast submissions information about modeling methods 
+or 
+distributional assumptions. Thus the only information we have for fitting
+distributions are bin
+forecasts and quantile forecasts. We are unaware of formal statistical 
+methods for fitting parametric distributions or mixture distributions to bin
+distributions. Methods of fitting a distribution to quantiles 
+include Bayesian Quantile Matching
+\cite[]{nirwan2020bayesian}, step interpolation with exponential tails 
+\cite[]{quinonero2005evaluating},
+and the Method of Simulated Quantiles 
+\cite[]{dominicy2013method}. These studies however lack claims that the methods
+for fitting are statistically formal.
+Nirwan and Bertshinger state that minimizing the mean square error between 
+quantile values and a CDF function has been the most common way to fit a 
+distribution
+to a set of quantiles. This is the method we will use in Section 
+\ref{section:covdretro}.
+Because of the lack of statistically formal methods for fitting a parametric
+distribution to a bin distribution or a set of quantiles, 
+it should be noted that any conclusions made in 
+this section may not be 
+stated in terms of statistical certainty.
+
+\section{CDC flu competition}
+The CDC Retrospective Forecasts project on zoltrdata.com \cite[]{zoltarflu} 
+contains over
+869,638 probabilistic influenza-like illness forecasts for all combinations
+of 11 regions 
+in the United States and seven targets from 27 different modeling teams. These
+include forecasts made during all flu seasons between October 2010 and December
+2018. All forecasts are represented by bin distributions. 
+We wanted to determine whether or not any of these forecasts were
+generated from one component mixture distributions of continuous uniform, 
+truncated normal (TN), truncated
+lognormal (TL), or truncated gamma (TG) distribution families.
+The process we followed for determining if a forecast was generated by one of
+these common families was to first fit a distribution of that family to the bin
+forecast and then measure the closeness of that fit. The decision to 
+fit truncated 
+distributions was due to all bin forecasts being assessed having a finite 
+support.
+
+In fitting a distribution to a forecast we want minimize \eqref{eq:msd}. We call
+\eqref{eq:msd} the mean square difference (MSD).
+Here $F(\cdot| \hat{\theta})$ is a CDF, $p_i$ is the reported probability for 
+the $i^{th}$ bin $B_i := [b_{i-1}, b_i)$, and $K$ is the number of bins.
 The fitted parameter vector $\hat{\theta}$ is the solution to 
-
-\begin{equation}
-\arg\min_{\theta}\sum_{i=1}^K (p_i - 
+\eqref{eq:discfit}.
+If a distribution was fit to the submitted bin forecast
+and the MSD was less than a 
+specified cutoff value, we
+concluded that the bin forecast may have been discretized from the 
+distribution.
+
+\begin{equation}
+  MSD = \sum_{i=1}^K (p_i - [F(b_i| \hat{\theta}) - F(b_{i-1}| \hat{\theta})])^2
+  \label{eq:msd}
+\end{equation}
+
+\begin{equation}
+\hat{\theta} = \arg\min_{\theta}\sum_{i=1}^K (p_i - 
 [F(b_i; \theta) - F(b_{i-1}; \theta)])^2
@@
 
-If a well known continuous distribution was fit to the submitted binned 
-prediction
-and the mean sum of squared differences (MSD) or \ref{eq:msd} fell below a 
-specified cutoff value, we
-considered that the binned predictions were plausibly discretized from the 
-continuous distribution.
-
 To determine what values to use as cutoffs we conducted a study where 
-binned distributions were discretized from known continuous distributions, 
-parameters were fit to the binned distrubtions and the MSD was calculated.
-
-For each of uniform, truncated normal (TN), truncated lognormal (TL) and 
-truncated gamma (TG) distributions the following was
-done 1,000 times. A set of 131 bins with interval lengths of 
-0.1 between 0 and 13.1 was constructed. 
-A value $\mu$ was selected from a $Uniform(a,b)$ distribution and $\sigma$ from 
-a $Uniform(.05,1.6)$ distribution. $\mu$ and $\sigma$ were taken as respectively 
+bin distributions were discretized from known distributions, 
+parameters were fit to the bin distributions, and the MSDs were calculated. This 
+was done 1,000 times for the four distribution families considered and the 
+cutoff 
+value for each family was set as the value under which 95\% of MSD values fell.
+The exact process is as follows.
+
+For each of uniform, TN, TL, and 
+TG distributions the following was
+done 1,000 times. A set of 131 bins with interval widths of 
+0.1 between 0 and 13 was constructed. 
+A value $u$ was selected from a $\mbox{Unif(0,13)}$ distribution and $v$ from 
+a $\mbox{Unif(.05,1.6)}$ distribution. The drawn values
+$u$ and $v$ were taken as respectively 
 the center and scale parameters of a TN distribution. 
-For uniform, TL and TG family
-distributions, model parameters were solved for so that $\mu$ and $\sigma$ 
-were roughly the mean and standard deviation. The minimization was done using 
+For uniform, TL, and TG family
+distributions, model parameters were computed such that $u$ and $v$ 
+were roughly the mean and standard deviation.
+% Had we accounted for the changes
+% in moment values from the truncation, the means and standard deviations could 
+% have been exactly $\mu$ and $\sigma$. But we considered the differences small 
+% enough that it didn't matter for our purpose.
+With a known distribution with $\theta = (u,v)$, 
+probabilities $p_i =F(b_i| \theta) - F(b_{i-1})$ were
+calculated for each bin. A distribution from the same
+family was fit to the bins by minimizing \eqref{eq:msd} with the resulting
+distribution function $F(\cdot| \hat{\theta})$. 
+The minimization was done using 
 the \texttt{optim} function in the \texttt{R} \texttt{stats} package.
-Had we accounted for the changes
-in moment values from the truncation, the means and standard deviations could 
-have been exactly $\mu$ and $\sigma$. But we considered the differences small 
-enough that it didn't matter for our purpose.
-
-With a known distribution, probabilities $p_i =F(b_i; \theta) - F(b_{i-1})$ were
-calculated for each bin. A uniform or truncated distribution from the same
-family was fit to the bins by minimizing \ref{eq:msd} with the resulting
-distribution function $F(\cdot; \hat{\theta})$. From the fitted distribution
+From the fit distribution
 $\hat{p_i} = F(b_i; \hat{\theta}) - F(b_{i-1}; \hat{\theta})$ was computed for 
-each of the 131 bins. Finally the mean sum of squared probability differences
-$\frac{1}{K}\sum_{i=1}^K (\hat{p_i} - p_i)^2$ was calculated. 
+each of the 131 bins. Finally the MSD was calculated. 
 Table \ref{table:bincutoffs}
@@
   \end{tabular}
-  \caption[Discretized bin distribution cutoff values]{If a binned 
-  distribution is fit to a parametric distribution and the MSD is smaller than
-  the corresponding cutoff value listed here, we consider that binned 
-  distribution to have been discretized from the fit parametric distribution.}
+  \begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
+  \caption[Bin distribution cutoff values]{If a binned 
+  one component mixture distribution is fit to a bin forecast
+  and the MSD is smaller than
+  the corresponding cutoff value listed here, we consider that bin 
+  distribution to have been discretized from the fit mixture distribution.}
   \label{table:bincutoffs}
+  \end{minipage}
+  \end{center}
 \end{table}
 
-Of the 869,638 predictions from the CDC Retrospective Forecast project, we fit
-each of Uniform, TN, TL and TG distributions to 11,715 of the individual 
-predictions. The MSD between the prediction probabilities and the fit
-discretized probabilities was calcuated. For each prediction, the fitted 
-distribution with the lowest MSD was considered the best fit and if the MSD fell
+Of the 869,638 forecasts from the CDC Retrospective Forecasts project, we fit
+each of uniform, TN, TL, and TG distributions to 11,715 of those
+forecasts. From each of the 27 teams represented, there is a list of forecast
+submissions from which we randomly selected 12. From each submission, we 
+we randomly selected six forecasts.
+In many cases the \texttt{optim} function used to fit the 
+distributions failed to converge, so of all forecasts we were only able to 
+successfully fit distributions to 11,715.
+We calculated the MSD for each of the four fits, and for each forecast the fit
+distribution with the lowest of the four MSDs was considered the best fit. If 
+the MSD from the best fit fell
 below the corresponding cutoff value listed in \ref{table:bincutoffs} we 
-considered that 
-the prediction was discretized from the fit distribution.
-
-Of the 11,715 binned distributions fit to continuous parametric distributions,
-2,502 of those fits producted MSD values below the values listed in table
+concluded that 
+the forecast was discretized from the fit distribution.
+
+Table \ref{table:bincutoffs} shows the results of this analysis. 
+Of the 11,715 binned distributions fit to the mixture distributions,
+2,502 of those fits had MSD values below the cutoff values listed in Table
 \ref{table:bincutoffs}. Thus we conclude that a proportion of 0.214 of those
-forecasts were generated from a common parametric distribution. The results for 
+forecasts were generated from a one component mixture distribution. 
+The results for 
 the
-11,715 fit distributions, which families the binned distributions were best
-fit to and whether or not the fits produce an MSD below the cutoff value, 
+11,715 fit distributions, which families the bin distributions were best
+fit to, and whether or not the fits produce an MSD below the cutoff value, 
 are seen in table \ref{table:cdcresults}. Figure \ref{fig:binparamfits} is an
-example of
-the best fit distributions to the same binned probability distribution.
+image showing a distribution from each of the four distribution families 
+considered
+fit to the same bin forecast.
 
@@
 \centerline{\includegraphics[scale=.15]{Images/flu_fit_17_10_3.png}}
+\begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
 \caption[Parametric distribution fits to binned distribution]{This figure shows
-the plots of fits from each a uniform, truncated normal, truncated lognormal
-and truncated gamma distributions to the same binned probability distribution.
+the plots of fits from each a uniform, TN, TL,
+and TG distributions to the same bin distribution. Each black vertical line is
+a bin probability $p_i \times 10$. The probabilities are multiplied by 10 to 
+better illustrate fitting a distribution to the probabilities.
+The title of this forecast
+given by the submission team is Bayesian Model Averaging. This forecast was
+submitted to the CDC on May 15, 2017 and is a three week ahead forecast of
+percent of hospital patients due to an influenza like illness for a specific
+region of the United States.
 In this case, the fit to the normal distribution produced an MSD below the 
-normal cutoff value, so we conclude that the binned distribution may have been
-discretized froma truncated normal.}
+TN cutoff value, so we conclude that the bin forecast may have been
+discretized from a TN. Proportions of distributions with MSDs 
+below the cutoff values are also included.}
 \label{fig:binparamfits}
+\end{minipage}
+\end{center}
 \end{figure}
@@
 \section{COVID-19 Forecast Hub}
-
-As of January 24, 2022 there were nearly 85,000,000 prediction distributions 
-from 114 different models submitted to the COVID-19 Forecast Hub (cite??). These 
-distributions covered all combinations of 3,202 municipalities (mostly counties) 
-in the United States with 441 targets. The first of these forecasts was 
-submitted in March of 2020 shortly after the initial outbreak of the virus in 
-the US and forecasts had been received weekly since. The forecast representation
-for these predictions is the quantile representation where a point estimated is
-submitted along with a number of confidence intervals -three or 11 for most
-targets. So the predictions typically include seven or 23 quantiles.
-
-To assess whether or not a quantile based forecast was calculated from a well
-known continuous distribution, we minimized the mean square error (MSE) between 
-the CDF and the given quantiles. The estimated parameters are the 
-solution to $argmin_{\theta} \sum_{i=1}^m (q_i - F(y; \theta))$ where $q_i$ is
-the $i^{th}$ given quantile value and $F(y; \theta)$ is the CDF with parameter
-$\theta$. This least squares estimating is a more common way to fit a model but
-other methods have been presented including Bayesian Quantile Matching
-\cite{nirwan2020bayesian}, step interpolation with exponential tails 
-\cite{quinonero2005evaluating}
-and the Method of Simulated Quantiles 
-\cite{dominicy2013method}.
-
-For each prediction used, we fit the quantiles to a uniform, normal, lognormal,
-gamma and location-scale t CDF. We included the t distribution in case of any
+\label{section:covdretro}
+
+As of April 4, 2022 there were over 90 million forecasts  
+from 117 different modeling teams submitted to the COVID-19 Forecast Hub 
+\cite[]{zoltarcovid}. 
+These 
+forecasts covered all combinations of 3,202 municipalities (mostly counties) 
+in the United States with 441 target/unit combinations. 
+The first of these forecasts was 
+submitted in March of 2020 shortly after the initial outbreak of the COVID-19 
+virus in 
+the US, and forecasts have been received weekly since. 
+The forecasts are all quantile forecasts made up of three or 11 predictive 
+intervals -depending on the specific unit for the forecast-
+and a median. Thus each forecasts includes seven or 23 quantiles.
+
+To assess whether or not a quantile forecast was calculated from a well
+known continuous distribution, we minimized the mean square error (MSE)  
+in \eqref{eq:mse} where $q_i$ is
+the $i^{th}$ quantile value from a forecast and $F(y| \hat{\theta})$ 
+is a fit CDF with 
+parameter $\hat{\theta}$. The parameter $\hat{\theta}$ is the solution to 
+\eqref{eq:minthet}.
+
+\begin{equation}
+  MSE = \sum_{i=1}^m (q_i - F(y| \hat{\theta}))
+  \label{eq:mse}
+\end{equation}
+
+\begin{equation}
+  \hat{\theta} = \arg\min_{\theta} \sum_{i=1}^m (q_i - F(y| \theta))
+  \label{eq:minthet}
+\end{equation}
+
+For each forecast assessed, we fit the quantiles to a uniform, normal, 
+lognormal,
+gamma, and location-scale t CDF. Unlike in the previous section, we felt no need
+to truncate the distributions because there is no range limit to these 
+forecasts. We also included the t distribution to account for any
 symmetric forecasts with heavier tails than in a normal distribution.
-
-If the MSE between a given forecast and a fit CDF fell below a certain cutoff,
-we considered the quantiles as approximately coming from the fit CDF. To
-determine the cutoff values, for each of the five distribution families the same
+If the MSE between a given forecast and a fit CDF fell below a certain cutoff
+value,
+we considered the quantiles as approximately matching those from the fit CDF. To
+determine the cutoff values, for each of the five distribution families,
+the same
 procedure was followed 1,000 times.
@@
 quantiles with probabilities 1/3 and 2/3 respectively. This was done because 
-in the COVID-19 Forecast Hub certain targets require seven quantiles and others 
-require 23. After that decision was made, a random value $\mu$ was drawn from
-a $Uniform(2,000,\; 25,000)$ distribution and another value $\sigma$ was drawn
-from a $Uniform(3, 200)$ distribution. These values were taken as the mean and
-standard deviation and for each of the distribution families considered, the
-proper transformations computed to find model parameters corresponding to the 
-distribution. Quantile values were calculated for each quantile. When using a 
-t distribution, a value for degrees of freedom was drawn from a 
-$Uniform(2,35)$ distribution. A CDF
-was fit by minimizing $\sum_{i=1}^m (q_i - F(y; \theta))$ over the parameter
-vector $\theta$ and the MSE value $\sum_{i=1}^m (q_i - F(y; \hat{\theta}))$ was 
+in the COVID-19 Forecast Hub certain target/unit combinations require 
+seven quantiles and others 
+require 23. The quantiles used matched those used by the COVID-19 Forecast Hub.
+After that decision was made, a random value $u$ was drawn from
+a $\mbox{Unif(2,000,\; 25,000)}$ distribution and another value $v$ was drawn
+from a $\mbox{Unif(3, 200)}$ distribution. These values were taken as the mean 
+and
+standard deviation for each of the five families and for each the
+proper transformations were computed to find model parameters corresponding to 
+the distribution family. 
+Quantile values were then calculated for each given quantile. When using 
+a t distribution, a value for degrees of freedom was drawn from a 
+$\mbox{Unif(2,35)}$ distribution. A CDF
+was fit by minimizing \eqref{eq:minthet} over the parameter
+vector $\theta$ and the MSE value from \eqref{eq:mse} was 
 calculated. The MSE value for which 95\% of the 1,000 simulated distributions
-fell below was considered the cutoff and is seen in table 
-\ref{table:quantcutoffs}.
+fell below was considered the cutoff for that family and is seen in table 
+\ref{table:quantcutoffs}. It is immediately noticeable that the cutoff value 
+for the location-scale t family is several orders of magnitude higher than for 
+the other distribution families. We believe this is related to the fact that 
+the t distribution is a three parameter family where as the other four families 
+are two 
+parameter families. Thus influencing the optimization methods used enough to 
+make such a difference in the cutoff value.
 
@@
   \end{tabular}
-  \caption[Quantile cutoff values]{If a set of quantiles
-  is fit to a parametric distribution CDF and the MSE is smaller than
-  the corresponding cutoff value listed here, we consider the quantiles to 
-  have been calculated parametric distribution.}
+  \begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
+  \caption[Quantile cutoff values]{If a one component mixture distribution of a
+  certain distribution family
+  is fit to a quantile forecast and the MSE is smaller than
+  the corresponding cutoff value listed here, we conclude the quantiles to 
+  have been calculated from the fit distribution.}
   \label{table:quantcutoffs}
+  \end{minipage}
+  \end{center}
 \end{table}
 
-With these cutoff values selected, models were then fit to quantile forecasts
-from the COVID-19 Forecasts on zoltardata.com. This was a computationally more
-difficult problem than fitting distributions to the binned forecasts of the 
-influenza project, so the number of predictions fit is much smaller. The 
-predictions fit were selected from each of the 115 models with model weeks, 
-targets and units selected randomly. In total 2,504 predictions were fit to each
-of the five distributions, the MSE was calculated for each and the fit with the
-lowest MSE was selected as the closest fit. If the MSE fell below the cutoff
-specified above, we considered that the quantile prediction was approximately
-from the same distribution as the fit distribution. Of the 2,504 fits, 99 of 
-them produced an MSE value below the corresponding cutoff. Results for fits by
-distribution are seen in table \ref{table:cresults}.
-Figures \ref{fig:qqfits} and \ref{fig:cdffits} show the QQ plots and CDF plots
-for different distribution fits to the same set of quantiles.
+With these cutoff values selected, distributions were then fit to quantile 
+forecasts
+from the COVID-19 Forecasts on zoltardata.com \cite[]{zoltarcovid}.
+From 115 modeling teams we randomly selected four forecast submissions. From 
+those submissions we randomly selected three units and attempted to assess
+forecasts for all targets under than unit.
+This was a computationally more
+difficult problem than fitting distributions to the bin forecasts from the CDC
+flu competition, so the number of forecasts where convergence for fitting was
+met was much smaller. In total distributions from all five families of interest
+were fit to 2,504 forecasts. 
+The MSE was calculated for each and the fit with the
+lowest MSE was selected as the best fit. If the MSE fell below the cutoff
+specified above, we concluded that the quantile forecast was approximately
+from the same distribution as the fit distribution.
+
+Table \ref{table:cresults} shows the results of the analysis by distribution
+family.
+Of the 2,504 fits, 99 of 
+them had an MSE value below the corresponding cutoff listed in Table
+\ref{table:quantcutoffs}. Thus we conclude that a proportion of 0.04 of the 
+forecasts assessed came from distributions fit to them.
+Results for fits by
+distribution are seen in Table \ref{table:cresults}.
+Figures \ref{fig:qqfits} and \ref{fig:cdffits} show the qq plots and thr CDF 
+plots
+for four of the different distribution families fit to the same set of quantiles.
 
@@
   \end{tabular}
+  \begin{center}
+\begin{minipage}{10cm}
+\captionsetup{font=scriptsize}
   \caption[COVID-19 Forecast Hub results]{Results for COVID-19 Forecast Hub
-  retro analysis}
+  retro analysis. Here is is seen that 239 of the forecasts were best fit by 
+  a uniform, 609 by a normal, 694 by a lognormal, 597 by a gamma, and 365 by
+  a location-scale t. Of those fits 0, 74, 0, 0, and 25 respectively had an 
+  MSE below the cutoff values give in Table \ref{table:quantcutoffs}.}
   \label{table:cresults}
+  \end{minipage}
+  \end{center}
 \end{table}
@@
 \label{fig:cdffits}
+\end{minipage}
+\end{center}
 \end{figure}
 
-The results in the previous two studies suggest that in some cases, forecasters
-are using methods which produce simple parametric distribution forecasts. Many
-likely are not. To improve upon these studies, one could fit the binned 
-influenza forecasts or the COVID-19 quantile forecasts to discrete mixture 
+The results from these two studies suggest that in some cases, forecasters
+are using methods which may produce one component mixture distribution
+forecasts. Many
+likely are not. To expand upon these studies, one could attempt to fit the 
+bin forecasts or the quantile forecasts to mixture 
 distributions with multiple components. Forecasts that are very close to 
 a mixture distribution may suggest that the forecasters already have models that
-make transition to a discrete mixture distribution forecast format easy or
+make transition to a mixture distribution forecast format easy or
 straightforward.
@@
 probabilistic 
-forecasting including proper scoring, data storage and ensemble model 
-construction for each type. We presented the discrete mixture distribution
-representation and we argue that its use in collaborative probabilistic 
+forecasting and discussed proper scoring, data storage, and ensemble model 
+construction for each type. We presented the mixture distribution
+representation and argue that its use in collaborative probabilistic 
 forecasting is preferable to the other representations.
-In terms of model flexibility, storage and 
-ensemble building it is
-comparable to discretized bins and interval forecasts but also provides a 
-forecast with a infinite nominal resolution. Thus we advocate its use in
-future forecasting projects like those done by the CDC and COVID-19 Forecast 
-Hub.
-
-For a number of reasons, the adoption of finite mixture distributions as the
-submission format may face hurdles. A collaborative forecast center, along with 
+In terms of model flexibility, storage, and 
+ensemble construction it is
+comparable to bin and quantile forecasts but also provides a 
+forecast with a infinite nominal resolution. Based on a retrospective analysis,
+we argue that among the teams participating in the CDC flu
+competition and the COVID-19 Forecast Hub, there are already some which produce
+forecasts already resembling single component mixture distributions making the 
+transition from past and current formats to a mixture distribution format 
+straightforward.
+We thus advocate for the use of mixture distributions in
+future forecasting projects like those done in the CDC flu competition or in the
+COVID-19 Forecast Hub.
+
+For a number of reasons, the adoption of mixture distributions as the
+submission format may be avoided. A collaborative forecast center, along with 
 forecasters, using a 
-different representation may simply not want to break from tradition. The 
+different representation format may simply not want to break from tradition. The 
 implementation of new scoring and ensemble construction methods may be a 
-barrier. One aspect of ensemble construction which received little attention in 
+barrier. Development of tools beyond what was used in Section 
+\ref{section:tools} would assist in making a transition to using mixture 
+distributions more straightforward.
+One aspect of ensemble construction which received little attention in 
 this paper is the selection of weights for components of an ensemble where each
-of the components is mixture distribution. Computing requirements could become a
+of the components is a mixture distribution. 
+Computing requirements could become a
 concern in such a problem and further research on this may provide
@@
 
-Another area of recommended research is the use of joint distributions for 
+Another area of recommended research is the use of joint mixture distributions 
+for 
 forecasting. We have only considered here probabilistic forecasting of one 
-event at a time. Number of new infections in one week at one specific location
+event at a time. Number of new infections in one week at one specific location,
 for example. This forecast is presented as a marginal distribution for that 
-specific target, time and location. A joint distribution for forecasting 
-multiple targets, times or locations may sometime be desirable and may require
+specific target, time, and location. A joint distribution for forecasting 
+multiple targets, times, or locations may sometimes be desirable and may require
 further consideration on how joint mixture distributions could be used as a 
@@
 \specialchapt{APPENDIX}
+\label{section:append}
 
 The following is the code to make the \texttt{MakeDist()} function introduced 
-in \ref{section:tools}.
+in \ref{section:tools}. Tables \ref{table:mixfams} and \ref{table:mixfamsparams}
+show how distribution family arguments are to be written and what parameters are
+to be used for the distributions in the \texttt{MakeDist()} function.
+
 <<eval=FALSE>>=
